### 2016-03-02 draft.tex
first commit
Signed-off-by: yangxuserene <yangxuserene@gmail.com>

%% bare_conf_compsoc.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE Computer
%% Society conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference,compsoc]{IEEEtran}
% Some/most Computer Society conferences require the compsoc mode option,
% but others may want the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
\usepackage{ifpdf}
\usepackage{framed}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
\usepackage{cuted}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

\usepackage{graphicx} % Required for including pictures
\graphicspath{{pics/}} % Specifies the directory where pictures are stored

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{Michael Shell}
% \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
% Georgia Institute of Technology\\
% Atlanta, Georgia 30332--0250\\
% Email: http://www.michaelshell.org/contact.html}
% \and
% \IEEEauthorblockN{Homer Simpson}
% \IEEEauthorblockA{Twentieth Century Fox\\
% Springfield, USA\\
% Email: homer@thesimpsons.com}
% \and
% \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
% \IEEEauthorblockA{Starfleet Academy\\
% San Francisco, California 96678-2391\\
% Telephone: (800) 555--1212\\
% Fax: (888) 555--1212}}

\author{

\IEEEauthorblockN{Xu Yang\IEEEauthorrefmark{1}, John Jenkins\IEEEauthorrefmark{2}, Misbah Mubarak\IEEEauthorrefmark{2}, Robert B. Ross\IEEEauthorrefmark{2}, Zhiling Lan\IEEEauthorrefmark{1}}

\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science,
Illinois Institute of Technology,
Chicago, Illinois, USA 60616\\
\{xyang56\}@hawk.iit.edu, lan@iit.edu}

\IEEEauthorblockA{\IEEEauthorrefmark{2}Mathematics and Computer Science Division, Argonne National Laboratory,
Argonne, IL, USA 60439\\
\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page (and note that there is less available width in this regard for
% compsoc conferences compared to traditional conferences), use this
% alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}

The high-radix, low-diameter dragonfly topology network will be the choice of many computing facilities for building their next generation supercomputers. Preliminary study shows that random job allocation with adaptive routing would be the rule of thumb to utilize such powerful network. However, in this work, we made the observation that although random job allocation with adaptive routing can alleviate the hotspot and make network traffic load-balanced for the workload, it can not guarantee the best performance for each single job. The performance improvement of communication intensive jobs comes with sacrifice of those less intensive jobs. We refer this phenomenon as ``bully" between concurrently running jobs. In this paper, we analyze the detailed reason for the happening of this ``bully" from the network level. Our study is based on a sophisticated, high-fidelity discrete even-driven simulation tool. We believe the observations and analysis in this work will make the chosen of job allocation and routing strategies more cautiously in future.

\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
\label{sec:intro}

The dragonfly topology can provide the ability for building high-radix, low-diameter network that are preferable for HPC systems. Compared with Torus topology, dragonfly can provide high-bandwidth, low-latency that are attractive for building multi-Petaflop/s supercomputers\cite{dally-dragonfly}. The procurement results from Trinity and CORAL project shows the great performance improvement from dragonfly network.

Even with such powerful network, the interference between concurrently running jobs is still a major factor impacting jobs' performance \cite{bhatele2015, dskinner}. Some research work propose that random job placement coupled with adaptive routing strategies can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}. They got this conclusion with different simulation tools and various synthetic workloads.

This is paper, we study the interference between concurrently running jobs on Dragonfly network with different job allocation policies and routing algorithms. Being unorthodox to most existing work, we use real application traces that collected from production system in our study. The advantage of using real application traces instead of synthetic workload is quite obvious. The traces collected from production system can capture application's communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity.

In this work, we focus on analyzing interference between concurrently running jobs on a 4K-node Dragonfly network. In the meanwhile, we also evaluate the network performance and jobs' performance when the Dragonfly network is configured with different job allocation strategies and routing algorithms. The job allocation strategies used in our study are Compact allocation and Random allocation, both of which can be seen in existing production HPC systems. The routing strategies been analyzed in this work are Minimal, Nonminimal and Adaptive.

We made observation from our comprehensive study that, when Dragonfly network enabled with random job allocation and adaptive routing in order to reach hotspot free and load balance, the performance of particular job would be impaired. The communication intensive jobs in the workload can benefit from random allocation and adaptive routing, with great performance improvement. Unfortunately, those less intensive jobs are the sacrifices for this improvement, their performance will be greatly reduced. The findings in this work also reconfirm that interference between concurrently running jobs would make the performance of some jobs every unpredictable. The detailed analysis about the traffic and congestion in network level unveil the undercurrent beneath that interference.

This work makes the following contributions:

\begin{itemize}

    \item Our real trace-based analysis about job interference on dragonfly network, shows that random allocation with adaptive routing can not guarantee the performance of every job in the workload. The hotspot-free and load-balanced reached by using random allocation with adaptive routing come with the cost of communication-less-intensive jobs performance degradation.

    \item We identify the ``bully" happening between jobs running concurrently on dragonfly network with random allocation and adaptive routing. Random allocation and adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resources(such as router ports and links), slow down the communication of those less intensive jobs.

    \item We found that compact allocation and minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may leads to local hotspot and severe network congestion. Actually, compact allocation and minimal routing are preferred by communication-less-intensive jobs, since it will prevent them from being bullied by other communication-intensive jobs.

\end{itemize}

To the best of our knowledge, using real application traces for the study of job interference on dragonfly network as not been reported so far. We believe the observations and analysis presented in this paper can be used by computing facilities to choose  job allocation and routing strategies wisely for their future dragonfly interconnected system. The conclusion from this paper would be useful for batch schedulers in dragonfly system to make better scheduling decisions for jobs with specific communication behavior.

\section{Application Study}
\label{sec:app study}

We choose three representative applications from DOE Design Forward Project\cite{designforwardwebpage}. . We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers. Sepcifically, we study the Algebraic MultiGrid Solver (AMG), Geometric MultiGrid (MultiGrid) and CrystalRouter MiniApps.

 AMG: The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages. It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.

\begin{figure*}[t!]
  \centering
  \includegraphics[height=2.2in]{data_amount}
  \caption{Applications data transfer amount}
  \label{fig:3app-data-amount}
\end{figure*}

MultiGrid: massively parallel block-structured adaptive mesh refinement (AMR) codes a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}. It is widely used for structured grid physics packages.

CrystalRouter: the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}. It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.

The amount of transferring data of each application are shown in Figure \ref{fig:3app-data-amount}.

\section{Dragonfly Network}
\label{sec:network}

\section{Job Placement and Routing}
\label{sec:placement-routing}

\section{Evaluation}
\label{sec:evaluation}

\section{Related Work}
\label{sec:related work}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
%   \section*{Acknowledgment}
\fi

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
\IEEEtriggeratref{4}

\bibliographystyle{IEEEtran}
\bibliography{./reference}

% \vspace{5\baselineskip}
% 
% \begin{framed}
% The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").  Argonne, a U.S. Department of Energy Office of Science laboratory, is operated under Contract No. DE-AC02-06CH11357.  The U.S. Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
% \end{framed}

% that's all folks
\end{document}

### 2016-03-03 draft.tex
edit section dragonfly network

@@
 This is paper, we study the interference between concurrently running jobs on Dragonfly network with different job allocation policies and routing algorithms.
-Being unorthodox to most existing work, we use real application traces that collected from production system in our study.
-The advantage of using real application traces instead of synthetic workload is quite obvious.
+Being unorthodox to most existing work, we use real application traces that collected from production system instead of synthetic workloads.
+The advantage of using real application traces is quite obvious.
 The traces collected from production system can capture application's communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity.
 
-In this work, we focus on analyzing interference between concurrently running jobs on a 4K-node Dragonfly network.
-In the meanwhile, we also evaluate the network performance and jobs' performance when the Dragonfly network is configured with different job allocation strategies and routing algorithms.
+We also evaluate the network performance and jobs' performance when the Dragonfly network is configured with different job allocation strategies and routing algorithms.
 The job allocation strategies used in our study are Compact allocation and Random allocation, both of which can be seen in existing production HPC systems.
@@
 
-We made observation from our comprehensive study that, when Dragonfly network enabled with random job allocation and adaptive routing in order to reach hotspot free and load balance, the performance of particular job would be impaired.
+We made observation from our comprehensive study that, when dragonfly network enabled with random job allocation and adaptive routing in order to reach hot-spot free and load balance, the performance of particular job would be impaired.
 The communication intensive jobs in the workload can benefit from random allocation and adaptive routing, with great performance improvement.
@@
 We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers.
-Sepcifically, we study the Algebraic MultiGrid Solver (AMG), Geometric MultiGrid (MultiGrid) and CrystalRouter MiniApps.
+Specifically, we study the Algebraic MultiGrid Solver (AMG), Geometric MultiGrid (MultiGrid) and CrystalRouter MiniApps.
 
@@
 \label{sec:network}
+It is difficult to do experiment with concurrently running jobs on HPC system.
+One reason is that job placement and routing strategy are part of system configuration, it is impossible for user to make changes at will.
+Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
+Therefore, we resort to simulation in our work.
+
+A simulation toolkit named CODES enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.
+CODES support dragonfly network with high fidelity flit-level simulation\cite{codes-dragonfly}.
+It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.
 
@@
 % the document is modified later
-\IEEEtriggeratref{4}
+%\IEEEtriggeratref{4}
 

### 2016-03-05 draft.tex
add workload overview section

@@
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
 \documentclass[conference,compsoc]{IEEEtran}
@@
 % \documentclass[conference,compsoc]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
 
@@
 \graphicspath{{pics/}} % Specifies the directory where pictures are stored
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-\begin{figure*}[t!]
-  \centering
-  \includegraphics[height=2.2in]{data_amount}
-  \caption{Applications data transfer amount}
-  \label{fig:3app-data-amount}
-\end{figure*}
+% \begin{figure*}[t!]
+%   \centering
+%   \includegraphics[height=2.2in]{data_amount}
+%   \caption{Applications data transfer amount}
+%   \label{fig:3app-data-amount}
+% \end{figure*}
 
@@
 \label{sec:evaluation}
+
+\subsection{Workload Overview}
+\label{sec: workload overview}
+
+We make a workload that consists of these three applications and simulate the running of this workload on dragonfly network.
+In our simulation, we adopt two job placement policies, Contiguous and Random, for mapping application MPI ranks to network terminal nodes.
+We also try two routing algorithms are commonly used in dragonfly network, Adaptive and Minimal.
+Therefore, there are 4 configurations “Contiguous placement with Adaptive routing” , “Contiguous placement with Minimal routing”, “Random placement with  Adaptive routing” and “Random placement with Minimal routing”.
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/tl-traffic}
+        \caption{Terminal Link Traffic}
+        \label{fig:terminal-link-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/lc-traffic}
+        \caption{Local Channel Traffic}
+        \label{fig:local-channel-traffic}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/gc-traffic}
+        \caption{Global Channel Traffic}
+        \label{fig:global-channel-traffic}
+    \end{subfigure}%
+   \caption{Network Traffic.}
+   \label{fig:wkld-network-traffic}
+\end{figure*}
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/tl-stime}
+        \caption{Terminal Link Busy Time}
+        \label{fig:terminal-link-stime}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/lc-stime}
+        \caption{Local Channel Busy Time}
+        \label{fig:local-channel-stime}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/gc-stime}
+        \caption{Global Channel Busy Time}
+        \label{fig:global-channel-stime}
+    \end{subfigure}%
+   \caption{Network Channel Busy Time.}
+   \label{fig:wkld-network-stime}
+\end{figure*}
+
+Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:global-channel-stime} shows that random job placement with adaptive routing can distribute workload traffic and balance the load over the network.
+Contiguous job placement
 

### 2016-03-06 draft.tex
add section app analysis

@@
 
+\subsection{Application Analysis}
+\label{sec:app analysis}
+
+The random job placement and adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
+In this section, we will show that not every application can benefit from random job placement and adaptive routing.
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{amg/commtime}
+        \caption{AMG Communication Time}
+        \label{fig:amg-commtime}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{mg/commtime}
+        \caption{MG Communication Time}
+        \label{fig:mg-commtime}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{cr/commtime}
+        \caption{CR Communication Time}
+        \label{fig:cr-commtime}
+    \end{subfigure}%
+   \caption{Application communication time.
+Three applications running concurrently on dragonfly network with different placement and routing configurations.
+Random job placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
+   \label{fig:apps-commtime}
+\end{figure*}
+
+Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently with 4 different placement and routing configurations.
+MG and CR can get improvement with random placement and adaptive routing, compared with contiguous placement and minimal routing.
+However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.
+
+The results of random placement shown in Figure \ref{fig:apps-commtime} are collected from extensive runs of different random placements, which can eliminate the possibility of variations.
+
+We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing.
+By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-router-traffic}.
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{amg/tl-traffic}
+        \caption{Terminal Link Traffic}
+        \label{fig:amg-tl-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{amg/lc-traffic}
+        \caption{Local Channel Traffic}
+        \label{fig:amg-lc-traffic}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{amg/gc-traffic}
+        \caption{Global Channel Traffic}
+        \label{fig:amg-gc-traffic}
+    \end{subfigure}%
+   \caption{AMG router traffic.}
+   \label{fig:amg-router-traffic}
+\end{figure*}
+
+Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.
+
 \section{Related Work}

### 2016-03-07 draft.tex
add section synthetic trace analysis

@@
 
-% \begin{figure*}[t!]
-%   \centering
-%   \includegraphics[height=2.2in]{data_amount}
-%   \caption{Applications data transfer amount}
-%   \label{fig:3app-data-amount}
-% \end{figure*}
-
 MultiGrid: massively parallel block-structured adaptive mesh refinement (AMR) codes a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
@@
 
-The amount of transferring data of each application are shown in Figure \ref{fig:3app-data-amount}.
+% The amount of transferring data of each application are shown in Figure \ref{fig:3app-data-amount}.
 
@@
 
-Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:global-channel-stime} shows that random job placement with adaptive routing can distribute workload traffic and balance the load over the network.
+Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:wkld-network-stime} shows that random job placement with adaptive routing can distribute workload traffic and balance the load over the network.
 Contiguous job placement
@@
         \centering
-        \includegraphics[height=1.8 in]{amg/commtime}
+        \includegraphics[height=1.5 in]{amg/commtime}
         \caption{AMG Communication Time}
@@
         \centering
-        \includegraphics[height=1.8 in]{mg/commtime}
+        \includegraphics[height=1.5 in]{mg/commtime}
         \caption{MG Communication Time}
@@
         \centering
-        \includegraphics[height=1.8 in]{cr/commtime}
+        \includegraphics[height=1.5 in]{cr/commtime}
         \caption{CR Communication Time}
@@
 We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing.
-By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-router-traffic}.
+By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}.
+Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.
+
+CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing.
 
@@
         \centering
-        \includegraphics[height=1.8 in]{amg/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:amg-tl-traffic}
+        \includegraphics[height=1.8 in]{amg/lc-traffic}
+        \caption{AMG Local Channel Traffic}
+        \label{fig:amg-lc-traffic}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[height=1.8 in]{amg/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:amg-lc-traffic}
+        \includegraphics[height=1.8 in]{mg/lc-traffic}
+        \caption{MG Local Channel Traffic}
+        \label{fig:mg-lc-traffic}
     \end{subfigure}%
@@
         \centering
+        \includegraphics[height=1.8 in]{cr/lc-traffic}
+        \caption{CR Local Channel Traffic}
+        \label{fig:cr-lc-traffic}
+    \end{subfigure}%
+   \caption{Each Application Router Local Channel Traffic.  }
+   \label{fig:3app-lc-traffic}
+\end{figure*}
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
         \includegraphics[height=1.8 in]{amg/gc-traffic}
-        \caption{Global Channel Traffic}
+        \caption{AMG Global Channel Traffic}
         \label{fig:amg-gc-traffic}
     \end{subfigure}%
-   \caption{AMG router traffic.}
-   \label{fig:amg-router-traffic}
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{mg/gc-traffic}
+        \caption{MG Global Channel Traffic}
+        \label{fig:mg-gc-traffic}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{cr/gc-traffic}
+        \caption{CR Global Channel Traffic}
+        \label{fig:cr-gc-traffic}
+    \end{subfigure}%
+   \caption{Each Application Router Global Channel Traffic.}
+   \label{fig:3app-gl-traffic}
 \end{figure*}
 
-Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.
+Why AMG is the only victim in the workload?
+The reason for CrystalRouter and MultiGrid get improvement in the sacrifice of AMG's performance is that AMG is the lest communication-intensive application in the workload.
+As shown in Figure \ref{fig:3app-data-amount}, AMG has the least amount of data transfer between its ranks.
+
+\begin{figure*}[t!]
+  \centering
+  \includegraphics[height=2.2in]{data_amount}
+  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with CR and MG.}
+  \label{fig:3app-data-amount}
+\end{figure*}
+
+Apparently, random placement and adaptive routing is quite efficient for orchestrate the traffic load in the network.
+Random placement and adaptive routing can uniformly distribute the workload traffic all over the network, make the load-balanced and avoid hot-spots.
+However, application like AMG will be impaired in this orchestration.
+The routers through which the less communication-intensive application traffic used to route, now have more traffic go through them.
+These extra traffic are from other communication-intensive applications.
+Beneath the facade of harmony, less communication-intensive application are bullied by their communication-intensive peers in the workload.
+
+\section{Analysis of Synthetic Workloads}
+
+To validate our assumption, we generate synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
+        \caption{sAMG Communication Time}
+        \label{fig:amg-commtime}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
+        \caption{MG Communication Time}
+        \label{fig:mg-commtime}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
+        \caption{CR Communication Time}
+        \label{fig:cr-commtime}
+    \end{subfigure}%
+   \caption{Application communication time.
+Three applications running concurrently on dragonfly network with different placement and routing configurations.
+Random placement and adaptive routing can improves AMG's communication time.
+MG and CR communication time are prolonged with random placement and adaptive routing.}
+   \label{fig:apps-commtime}
+\end{figure*}
 

### 2016-03-07 draft.tex
finish section synthetic workload analysis

@@
 These extra traffic are from other communication-intensive applications.
-Beneath the facade of harmony, less communication-intensive application are bullied by their communication-intensive peers in the workload.
+Beneath the facade of harmony, less communication-intensive application are ``bullied" by their communication-intensive peers in the workload.
 
-\section{Analysis of Synthetic Workloads}
+\subsection{Analysis of Synthetic Workloads}
 
 To validate our assumption, we generate synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+We run the new workload that consists of sAMG, MG and CR on the same dragonfly network with the same placement and routing configurations.
+As shown in Figure \ref{fig:syn-3app-data-amount}, sAMG become the most communication-intensive application in the new workload.
+
+\begin{figure*}[t!]
+  \centering
+  \includegraphics[height=2.2in]{syn-wkld/data_amount}
+  \caption{Applications Data Transfer Amount. sAMG has the most amount of data transfer, compared with CR and MG.}
+  \label{fig:syn-3app-data-amount}
+\end{figure*}
+
+The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}.
+The ``bully" become the ``bullyee".
+The less communication-intensive application, CrystalRouter and MultiGrid, suffer prolonged communication time when running concurrently with sAMG with random placement and adaptive routing configuration.
+The routers that belongs to MultiGrid  and now CrystalRouter has extra traffic go through them, shown in Figure  \ref{fig:syn-mg-lc-traffic} \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic} \ref{fig:syn-cr-gc-traffic}.
+The extra traffic come from sAMG, that been redirected by adaptive routing.
 
@@
         \caption{sAMG Communication Time}
-        \label{fig:amg-commtime}
+        \label{fig:samg-commtime}
     \end{subfigure}%
@@
         \caption{MG Communication Time}
-        \label{fig:mg-commtime}
+        \label{fig:syn-mg-commtime}
     \end{subfigure}%
@@
         \caption{CR Communication Time}
-        \label{fig:cr-commtime}
+        \label{fig:syn-cr-commtime}
     \end{subfigure}%
@@
 MG and CR communication time are prolonged with random placement and adaptive routing.}
-   \label{fig:apps-commtime}
+   \label{fig:syn-apps-commtime}
 \end{figure*}
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/amg10/lc-traffic}
+        \caption{AMG Local Channel Traffic}
+        \label{fig:samg-lc-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/mg/lc-traffic}
+        \caption{MG Local Channel Traffic}
+        \label{fig:syn-mg-lc-traffic}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/cr/lc-traffic}
+        \caption{CR Local Channel Traffic}
+        \label{fig:syn-cr-lc-traffic}
+    \end{subfigure}%
+   \caption{Each Application Router Local Channel Traffic.  }
+   \label{fig:syn-3app-lc-traffic}
+\end{figure*}
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/amg10/gc-traffic}
+        \caption{AMG Global Channel Traffic}
+        \label{fig:samg-gc-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/mg/gc-traffic}
+        \caption{MG Global Channel Traffic}
+        \label{fig:syn-mg-gc-traffic}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/cr/gc-traffic}
+        \caption{CR Global Channel Traffic}
+        \label{fig:syn-cr-gc-traffic}
+    \end{subfigure}%
+   \caption{Each Application Router Global Channel Traffic.}
+   \label{fig:syn-3app-gc-traffic}
+\end{figure*}
+
+Based on the results we got from both real application traces and synthetic workload, we can make the following observations:
+
+\begin{itemize}
+    \item Random placement and adaptive routing can uniformly distribute workload traffic over the network, make the whole network load-balanced and hot-spot free. 
+    \item Random placement and adaptive routing can not guarantee QoS for each application in the workload.
+In order to reach load-balanced and hot-spot free, the traffic from congested routers will be redirected to other less busy routers.
+This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.
+    \item Contiguous placement and minimal routing guarantee a consistent performance of each application.
+Although, contiguous placement and minimal routing usually results in local congestion and hot-spot, it can reduce the interference between concurrently running applications, thus prevent less communication-intensive application from being ``bully" by its intensive peers.
+\end{itemize}
+
+\section{Better Orchestration }
+According to our findings, we believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity.
+The less intensive applications should avoid sharing network resource with other applications, reduce the possible interference.
+Contiguous placement and adaptive routing can guarantee the QoS for the less intensive applications.
+
+The communication-intensive applications tend to cause local congestion. Random placement and adaptive routing can ...
 

### 2016-03-08 draft.tex
add section job placement and routing

@@
 
-\section{Job Placement and Routing}
+\subsection{Network Configuration}
+\label{sec: network config}
+
+ Here will talk about network configuration, such as network scale, link bandwidth etc. \\
+
+\subsection{Job Placement}
 \label{sec:placement-routing}
+
+Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by the job for execution.
+There are many works study various ways of doing job placement on HPC systems with different topologies \cite{yang-cluster14} \cite{zhou-ipdps15} \cite{hoefler-hpdc14}.
+In this work, we study the following two placement schemes:
+
+\textbf{Contiguous Placement:} In this scheme, the nodes will first be indexed consecutively in the increasing oder of their group id and router id.
+The job is allocated by cutting chunks of nodes from the sequentially ordered list.
+The nodes been allocated to each job will be adjacent to each other, usually they are attached to the same router, in the same group.
+Contiguous placement confines the traffic of application into the local area, which may leads to local network congestion and increase the possibility of hot-spots.
+
+\textbf{Random Placement:} In this scheme, job will get a set of nodes that randomly selected from all the available nodes in the system.
+The nodes allocated to each job would be attached to different routers in different groups.
+Some routers may be shared by different applications when using random placement.
+Random placement can spreading the traffic of application uniformly across the whole system, thus avoid the possible hot-spots and reach load balance.
+
+\subsection{Routing Schemes}
+\label{sec:routing}
+
+The implemented routing schemes in CODES dragonfly network model are based on the routing algorithm proposed by Kim et al.
+\cite{dally-dragonfly}.
+Two routing schemes studied in this work are \emph{Minimal} and \emph{Adaptive}.
+
+\textbf{Minimal:} The minimal routing sends a message from source router to destination router along the shortest path.
+When there are multiple shortest paths, the message is evenly divided among the paths.
+Minimal routing can guarantee the minimum hops the message takes from source to destination.
+However, it may leads to congestion along the shortest path.
+
+\textbf{Adaptive:} In this scheme, the path a message takes will be adaptively chosen between shortest and non-shortest path, depends on the congestion situation along that path.
+For the non-shortest path, an intermediate router will be randomly chosen.
+The message will first take the shortest path from source to that intermediate router, then it will take the shortest path between the intermediate router to the destination.
+Since adaptive scheme chooses routing path adaptively based on the congestion situation, it can void local congestion and reduce the possibility of hot-spots.
 
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/amg10/lc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
         \caption{AMG Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/mg/lc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
         \caption{MG Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/cr/lc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
         \caption{CR Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/amg10/gc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
         \caption{AMG Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/mg/gc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
         \caption{MG Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/cr/gc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
         \caption{CR Global Channel Traffic}
@@
 
-\section{Better Orchestration }
 According to our findings, we believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity.
 The less intensive applications should avoid sharing network resource with other applications, reduce the possible interference.
-Contiguous placement and adaptive routing can guarantee the QoS for the less intensive applications.
+Contiguous placement and adaptive routing can guarantee the QoS for the less intensive applications, thus prevent the ``bully" from happening.
 
-The communication-intensive applications tend to cause local congestion. Random placement and adaptive routing can ...
+The communication-intensive applications tend to cause local congestion.
+It is preferable to enable communication-intensive applications to have extra network resource by sharing with other applications.
+Random placement and adaptive routing can alleviate the local congestion by redirecting traffic to other less busy routers in the network.
+
+So the ideal placement and routing strategies for workload running on dragonfly network should be like this.
+The communication-intensive applications should be randomly allocated over the system and adaptive routing should be used by these applications to alleviate the local congestion.
+On the other hand, less intensive application should get contiguous allocation, minimal routing should be used by these applications to avoid network sharing and reduce interference.
 

### 2016-03-08 draft.tex
add some TODO and NOTE

@@
 % http://www.ctan.org/pkg/subfig
+
+\newcommand{\TODO}[1]{\hl{TODO: #1}}
+\newcommand{\NOTE}[1]{\hl{NOTE: #1}}
+\newcommand{\changed}[1]{\textcolor{red}{#1}}
 
@@
 
-\section{Application Study}
-\label{sec:app study}
-
-We choose three representative applications from DOE Design Forward Project\cite{designforwardwebpage}.
-.
-We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers.
-Specifically, we study the Algebraic MultiGrid Solver (AMG), Geometric MultiGrid (MultiGrid) and CrystalRouter MiniApps.
-
- AMG: The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
-It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.
-
-MultiGrid: massively parallel block-structured adaptive mesh refinement (AMR) codes a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
-It is widely used for structured grid physics packages.
-
-CrystalRouter: the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}.
-It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.
-
-% The amount of transferring data of each application are shown in Figure \ref{fig:3app-data-amount}.
-
 \section{Dragonfly Network}
@@
 
- Here will talk about network configuration, such as network scale, link bandwidth etc. \\
+ \TODO{Here will talk about network configuration, such as network scale, link bandwidth etc. }\\
 
@@
 
+\subsection{Application}
+\label{sec:app study}
+
+We choose three representative applications from DOE Design Forward Project\cite{designforwardwebpage}.
+.
+We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers.
+Specifically, we study the Algebraic MultiGrid Solver (AMG), Geometric MultiGrid (MultiGrid) and CrystalRouter MiniApps.
+
+AMG: The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
+It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.
+
+MultiGrid: massively parallel block-structured adaptive mesh refinement (AMR) codes a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
+It is widely used for structured grid physics packages.
+
+CrystalRouter: the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}.
+It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.
+
 \subsection{Workload Overview}
@@
     \end{subfigure}%
-   \caption{Network Traffic.}
+   \caption{Network Traffic. \TODO{More explanation to be added for this figure}}
    \label{fig:wkld-network-traffic}
@@
     \end{subfigure}%
-   \caption{Network Channel Busy Time.}
+   \caption{Network Channel Busy Time. \TODO{More explanation to be added for this figure}}
    \label{fig:wkld-network-stime}
@@
 
-Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:wkld-network-stime} shows that random job placement with adaptive routing can distribute workload traffic and balance the load over the network.
-Contiguous job placement
+Contiguous placement allocates each job a set of nodes that adjacent to each other, which confines the traffic of the application into the local area when coupled with minimal routing.
+This may leads to hot-spot in local area and unbalanced network utilization.
+As we can see from Figure \ref{fig:wkld-network-traffic} and \ref{fig:wkld-network-stime}, contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest network busytime.
+
+Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:wkld-network-stime} shows that random job placement with adaptive routing can uniformly distribute workload traffic and balance the load over the network.
 
@@
 However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.
+\TODO{More explanation about contiguous placement and minimal routing here}
 
@@
 Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.
+\TODO{More explanation about contiguous placement and minimal routing}
 
 CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing.
+\TODO{More explanation about contiguous placement and minimal routing}
 
@@
 
+We have tried three different congestion sensing schemes that used in adaptive routing\cite{dally-dragonfly}, although there are some variations of the experiments, none of the congestion sensing scheme can prevent the ``bully" from happening.
+
 \subsection{Analysis of Synthetic Workloads}
@@
 The extra traffic come from sAMG, that been redirected by adaptive routing.
+\TODO{More explanation about contiguous placement and minimal routing}.
 
@@
 \end{figure*}
+
+\NOTE{We can add another set of synthetic workload, in which three applications have similar data transfer amount, if necessary. }
 

### 2016-03-08 draft.tex
add more figures in repo

@@
 % http://www.ctan.org/pkg/subfig
-
+\usepackage{verbatim}
+\usepackage{soul}
+\usepackage{xcolor}
 \newcommand{\TODO}[1]{\hl{TODO: #1}}
-\newcommand{\NOTE}[1]{\hl{NOTE: #1}}
+\newcommand{\NOTE}[1]{\hl {NOTE: #1}}
 \newcommand{\changed}[1]{\textcolor{red}{#1}}
@@
 
- \TODO{Here will talk about network configuration, such as network scale, link bandwidth etc. }\\
+\TODO{xxx}
+\NOTE{yyy}
+Here will talk about network configuration, such as network scale, link bandwidth etc.\\
 
@@
     \end{subfigure}%
-   \caption{Network Traffic. \TODO{More explanation to be added for this figure}}
+   \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
    \label{fig:wkld-network-traffic}
@@
     \end{subfigure}%
-   \caption{Network Channel Busy Time. \TODO{More explanation to be added for this figure}}
+   \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
    \label{fig:wkld-network-stime}
@@
 However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.
-\TODO{More explanation about contiguous placement and minimal routing here}
+\textbf{More explanation about contiguous placement and minimal routing here}
 
@@
 Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.
-\TODO{More explanation about contiguous placement and minimal routing}
+\textbf{More explanation about contiguous placement and minimal routing}
 
 CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing.
-\TODO{More explanation about contiguous placement and minimal routing}
+\textbf{More explanation about contiguous placement and minimal routing}
 
@@
 The extra traffic come from sAMG, that been redirected by adaptive routing.
-\TODO{More explanation about contiguous placement and minimal routing}.
+\textbf{More explanation about contiguous placement and minimal routing}.
 
@@
 
-\NOTE{We can add another set of synthetic workload, in which three applications have similar data transfer amount, if necessary. }
+\textbf{We can add another set of synthetic workload, in which three applications have similar data transfer amount, if necessary. }
 

### 2016-03-09 draft.tex
add section related work

@@
 
-\TODO{xxx}
-\NOTE{yyy}
 Here will talk about network configuration, such as network scale, link bandwidth etc.\\
@@
 
+The impact of job placement to both system and application always catch researchers appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
+Skinner et al.\cite{dskinner} identified that network congestion could cause significant performance variability.
+Bhatele et al.
+\cite{abhinav-sc13} studied the performance variability of a specific application, p3FD, running on different production system.
+They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource.
+Jokanovic et al.\cite{jose-ipdps15} study the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing.
+
+Recently, several researchers have investigated the job placement and routing schemes on dragonfly network.
+Bogdan et al \cite{hoefler-hpdc14} proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network.
+Jain et al.
+\cite{jain-sc14} conducted a comprehensive analysis of various job placement and routing scheme with regard to network link throughput on dragonfly network.
+Their work is based on an analytical model and synthetic workload.
+Bhatele et al.\cite{bhatele-sc11} used simulation to study the performance of synthetic workload under the different task mapping and routing schemes on two-level direct networks.
+
+Our work different from the previous works in the following ways.
+First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven real application traces collected from production system.
+Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
+We found that although random placement and adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation.
+Third, with the sophisticated simulation tool CODES, we can get not only applications communication information, but also we have the insight about the network status when application is running.
+The traffic and busy time of router's each link are valuable information for detailed analysis.
+
 % An example of a floating figure using the graphicx package.

### 2016-03-09 draft.tex
update figures in section 4

@@
 
+\makeatletter % Put Roman Number in Text
+\newcommand{\rmnum}[1]{\romannumeral #1}
+\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
+\makeatother
+
 % *** Do not adjust lengths that control margins, column widths, etc. ***
@@
 
-\section{Dragonfly Network}
+\section{Background}
+\label{sec:background}
+The dragonfly network is promising alternative for connecting a large number of nodes for its high-radix and low-diameter topology\cite{dally-dragonfly} \cite{kim-micro} \cite{faanes}.
+However, even with such powerful network, the job placement and routing could still be important factor that impact application's performance.
+
+\subsection{Dragonfly Network Overview}
 \label{sec:network}
-It is difficult to do experiment with concurrently running jobs on HPC system.
-One reason is that job placement and routing strategy are part of system configuration, it is impossible for user to make changes at will.
-Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
-Therefore, we resort to simulation in our work.
+The dragonfly is a two-level hierarchical topology.
+It consists of several groups connected by All-to-All links.
+In each group, there could be ``a" number of routers connected via All-to-All local channels.
+For each router, there could be ``p" number of compute nodes attached to it via terminal link.
+The router has ``h" number of global channels that used as intergroup connections through which the router connected to other router in different groups.
+Thus, the radix of each router is $k = a+h+p-1$.
+The implementation of such dragonfly network could be different between different computing facilities.
+The choosing of proper $a$, $h$, $p$ could be involving many factors, such as system scale, building cost and workload requirements.
 
-A simulation toolkit named CODES enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.
-CODES support dragonfly network with high fidelity flit-level simulation\cite{codes-dragonfly}.
-It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.
-
-\subsection{Network Configuration}
-\label{sec: network config}
-
-Here will talk about network configuration, such as network scale, link bandwidth etc.\\
+For the purpose of loading balance, it is recommended that the proper dragonfly configuration is $a=2p=2h$\cite{kim-micro}.
+Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g = $.
 
@@
 Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by the job for execution.
-There are many works study various ways of doing job placement on HPC systems with different topologies \cite{yang-cluster14} \cite{zhou-ipdps15} \cite{hoefler-hpdc14}.
+As studied by several researchers, the job placement could be an important factor that impact application performance \cite{hoefler-hpdc14} \cite{bhatele-sc11} \cite{jain-sc14}.
 In this work, we study the following two placement schemes:
@@
 
-\section{Evaluation}
-\label{sec:evaluation}
+\section{Methodology}
+\label{sec: methodology}
 
-\subsection{Application}
-\label{sec:app study}
+It is difficult to do experiment with concurrently running jobs on HPC system.
+One reason is that job placement and routing strategy are part of system configuration, it is impossible for user to make changes at will.
+Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
+Therefore, we resort to simulation in our work.
+
+\subsection{Simulation Tool}
+A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.
+CODES support dragonfly network with high fidelity flit-level simulation\cite{codes-dragonfly}.
+It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.
+
+\subsection{Application Traces}
+\label{sec: application traces}
 
@@
 It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.
+The traces of AMG we chosen are comprised of 216 MPI ranks.
 
@@
 It is widely used for structured grid physics packages.
+The traces of AMG we chosen are comprised of 125 MPI ranks.
 
@@
 It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.
+The traces of AMG we chosen are comprised of 100 MPI ranks.
 
-\subsection{Workload Overview}
-\label{sec: workload overview}
+\subsection{Simulation Configuration}
+\label{sec: simulation configuration}
+
+The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it.
+Overall, there are 264 routers and 1056 compute nodes in the network.
+The bandwidth of both terminal links and local channel are set to 2GB/s, the global channel bandwidth is set to 4GB/s.
+
+There are four placement and routing scheme combinations, namely contiguous placement coupled with minimal routing, contiguous placement coupled with adaptive routing, random placement coupled with minimal routing, random placement coupled with adaptive routing.
+In this work, we enable the applications running on dragonfly network under different placement and routing scheme combination, and scrutinize the application's performance and network behavior in different running scenarios.
+
+\section{Parallel Workload \Rmnum{1 } Study}
+\label{sec: workload 1 overview}
 
@@
 
-\subsection{Analysis of Synthetic Workloads}
+\section{Parallel Workload \Rmnum{2 } Study}
 

### 2016-03-12 draft.tex
add overview figure, detail analysis in section 4

@@
 \fi
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-%
-% Note that some packages require special options to format as the Computer
-% Society requires. In particular, Computer Society  papers do not use
-% compressed citation ranges as is done in typical IEEE papers
-% (e.g., [1]-[4]). Instead, they list every citation separately in order
-% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
-% package with the nocompress option which is supported by cite.sty v4.0
-% and later.
 
@@
 \usepackage{subcaption}
+\usepackage{booktabs}
+\usepackage{multirow} % make table
 
@@
 
-The dragonfly topology can provide the ability for building high-radix, low-diameter network that are preferable for HPC systems.
-Compared with Torus topology, dragonfly can provide high-bandwidth, low-latency that are attractive for building multi-Petaflop/s supercomputers\cite{dally-dragonfly}.
-The procurement results from Trinity and CORAL project shows the great performance improvement from dragonfly network.
-
-Even with such powerful network, the interference between concurrently running jobs is still a major factor impacting jobs' performance \cite{bhatele2015, dskinner}.
-Some research work propose that random job placement coupled with adaptive routing strategies can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
-They got this conclusion with different simulation tools and various synthetic workloads.
-
-This is paper, we study the interference between concurrently running jobs on Dragonfly network with different job allocation policies and routing algorithms.
-Being unorthodox to most existing work, we use real application traces that collected from production system instead of synthetic workloads.
+The low latency and high bandwidth interconnect network plays a critical role in improving HPC system performance.
+As the computing ability of HPC system continue grows due to many-core nodes with accelerators, the network is now becoming a scare resources.
+HPC community start to explore the possible alternative to replace the commonly used Torus network.
+
+The building high-radix, low-diameter dragonfly topology can lower the cost of interconnect network, improve network bandwidth, reduce the packets traverse latency.
+This make the dragonfly network an very promising choice for building multi-Petaflop/s supercomputers\cite{dally-dragonfly}.
+The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
+
+Even with such powerful network, the interference between concurrently running jobs and thus presumably job placement remains an major factor cause performance variability on dragonfly network\cite{bhatele2015, dskinner}.
+Some research work suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
+
+This is paper, we study the interference between concurrently running jobs on dragonfly network with different job placement and routing schemes.
+Being unorthodox to most existing work that use synthetic workload, our work is based on application traces that collected from production system.
 The advantage of using real application traces is quite obvious.
@@
 
-We also evaluate the network performance and jobs' performance when the Dragonfly network is configured with different job allocation strategies and routing algorithms.
+%We also evaluate the network performance and jobs' performance when the Dragonfly network is configured with different job allocation strategies and routing algorithms.
 The job allocation strategies used in our study are Compact allocation and Random allocation, both of which can be seen in existing production HPC systems.
@@
 
-We made observation from our comprehensive study that, when dragonfly network enabled with random job allocation and adaptive routing in order to reach hot-spot free and load balance, the performance of particular job would be impaired.
-The communication intensive jobs in the workload can benefit from random allocation and adaptive routing, with great performance improvement.
+We made observation from our extensive study that, when dragonfly network enabled with random job placement and adaptive routing scheme in order to reach hot-spot free and load balance, the performance of particular job(s) in the workload would suffer degradation.
+The communication intensive jobs in the workload can benefit from random placement and adaptive routing, with great performance improvement.
 Unfortunately, those less intensive jobs are the sacrifices for this improvement, their performance will be greatly reduced.
-The findings in this work also reconfirm that interference between concurrently running jobs would make the performance of some jobs every unpredictable.
+
+The findings in this work also reconfirm that interference between concurrently running jobs would make the performance of some jobs very unpredictable.
 The detailed analysis about the traffic and congestion in network level unveil the undercurrent beneath that interference.
-
 This work makes the following contributions:
@@
 
-    \item Our real trace-based analysis about job interference on dragonfly network, shows that random allocation with adaptive routing can not guarantee the performance of every job in the workload.
-The hotspot-free and load-balanced reached by using random allocation with adaptive routing come with the cost of communication-less-intensive jobs performance degradation.
-
-    \item We identify the ``bully" happening between jobs running concurrently on dragonfly network with random allocation and adaptive routing.
-Random allocation and adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resources(such as router ports and links), slow down the communication of those less intensive jobs.
-
-    \item We found that compact allocation and minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may leads to local hotspot and severe network congestion.
-Actually, compact allocation and minimal routing are preferred by communication-less-intensive jobs, since it will prevent them from being bullied by other communication-intensive jobs.
+    \item Our real trace-based analysis about job interference on dragonfly network, shows that random placement with adaptive routing can not guarantee the performance of every job in the workload.
+The hotspot-free and load-balanced reached by using random placement with adaptive routing come with the cost of communication-less-intensive jobs performance degradation.
+
+    \item We identify the ``bully" behavior happening between jobs running concurrently on dragonfly network with random placement and adaptive routing.
+Random placement and adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resources, slow down the communication of those less intensive jobs.
+
+    \item We found that contiguous placement and minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may leads to local hotspot and severe network congestion.
+Actually, contiguous placement and minimal routing are preferred by communication-less-intensive jobs, since it will prevent them from being bullied by other communication-intensive jobs.
 
@@
 
-To the best of our knowledge, using real application traces for the study of job interference on dragonfly network as not been reported so far.
-We believe the observations and analysis presented in this paper can be used by computing facilities to choose  job allocation and routing strategies wisely for their future dragonfly interconnected system.
-The conclusion from this paper would be useful for batch schedulers in dragonfly system to make better scheduling decisions for jobs with specific communication behavior.
+To the best of our knowledge, using application traces from production system for the study of job interference on dragonfly network as not been reported so far.
+We believe the observations and analysis presented in this paper can be used by computing facilities to choose job placement and routing strategies wisely for their future dragonfly interconnected system.
+The conclusion from this paper would be useful for batch schedulers in dragonfly system to make better scheduling decisions for workload consists of jobs that have various communication behavior.
 
@@
 
+\begin{figure}[h!] 
+  \centering
+  \includegraphics[width=0.48\textwidth]{dragonfly-overview}
+  \caption{Dragonfly Network Overview.
+Illustration of part of dragonfly network.
+There are 19 groups, 6 routers in each group, 3 compute nodes connected to each router, 342 nodes in total.
+Job\_1 requires for 6 nodes, get the allocation by Random placement.
+Job\_2 requires for 8 nodes, get the allocation by Contiguous placement.
+}
+  \label{fig: dragonfly overview}
+\end{figure}
+
 \subsection{Job Placement}
@@
 \textbf{Contiguous Placement:} In this scheme, the nodes will first be indexed consecutively in the increasing oder of their group id and router id.
-The job is allocated by cutting chunks of nodes from the sequentially ordered list.
+The job is allocated by cutting chunks of nodes from the sequentially ordered list, as illustrated in Figure\ref{fig: dragonfly overview} as blue nodes.
 The nodes been allocated to each job will be adjacent to each other, usually they are attached to the same router, in the same group.
@@
 \textbf{Random Placement:} In this scheme, job will get a set of nodes that randomly selected from all the available nodes in the system.
-The nodes allocated to each job would be attached to different routers in different groups.
+The nodes allocated to each job would be attached to different routers in different groups, as illustrated in Figure\ref{fig: dragonfly overview} as red nodes.
 Some routers may be shared by different applications when using random placement.
@@
 
+\textbf{Progressive Adaptive:} \NOTE{say something about prog-adaptive routing.} \cite{won-prog-adaptive}.
+
 \section{Methodology}
@@
 We choose three representative applications from DOE Design Forward Project\cite{designforwardwebpage}.
-.
 We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers.
@@
 It is widely used for structured grid physics packages.
-The traces of AMG we chosen are comprised of 125 MPI ranks.
+The traces of MultiGrid we chosen are comprised of 125 MPI ranks.
 
@@
 It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.
-The traces of AMG we chosen are comprised of 100 MPI ranks.
+The traces of CrystalRouter we chosen are comprised of 100 MPI ranks.
 
@@
 
-There are four placement and routing scheme combinations, namely contiguous placement coupled with minimal routing, contiguous placement coupled with adaptive routing, random placement coupled with minimal routing, random placement coupled with adaptive routing.
-In this work, we enable the applications running on dragonfly network under different placement and routing scheme combination, and scrutinize the application's performance and network behavior in different running scenarios.
+There are 6 placement and routing scheme combinations, namely contiguous placement coupled with minimal routing, contiguous placement coupled with adaptive routing, contiguous placement coupled with progressive adaptive routing random placement coupled with minimal routing, random placement coupled with adaptive routing, random placement coupled with progressive adaptive routing.
+In this work, we enable the applications running on dragonfly network under different placement and routing configurations, and scrutinize the application's performance and network behavior in different running scenarios.
+
+\begin{table}[ht]
+\begin{center}
+\caption{Job placement and routing configurations} 
+\label{tab: placement routing configs}
+%\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c }
+\toprule % Top horizontal line
+\toprule
+&\multicolumn{3}{c}{Routing Schemes} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-4}
+Placement schemes & Minimal & Adaptive & Progressive adp\\ % Column names row
+\midrule % In-table horizontal line
+Contiguous  &     &      &     \\ % Content row 1
+\midrule
+Random  &     &      &     \\
+
+\midrule % In-table horizontal line
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\end{center}
+\end{table}
+
+The results of random placement shown in the following sections are collected from extensive runs of different random placements, which can eliminate the possibility of variations.
 
@@
 
-We make a workload that consists of these three applications and simulate the running of this workload on dragonfly network.
-In our simulation, we adopt two job placement policies, Contiguous and Random, for mapping application MPI ranks to network terminal nodes.
-We also try two routing algorithms are commonly used in dragonfly network, Adaptive and Minimal.
-Therefore, there are 4 configurations “Contiguous placement with Adaptive routing” , “Contiguous placement with Minimal routing”, “Random placement with  Adaptive routing” and “Random placement with Minimal routing”.
+The first parallel workload analyzed in our experiment consists of three applications, namely AMG , MultiGrid (MG) and CrystalRouter(CR).
+The details of this workload shown in Table \ref{tab: parallel workload-1}.
+
+\begin{table}[ht]
+\begin{center}
+\caption{Parallel Workload \Rmnum{1 }} 
+\label{tab: parallel workload-1}
+%\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c }
+\toprule % Top horizontal line
+\toprule
+&\multicolumn{3}{c}{Routing Schemes} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-4}
+Application & num. rank & Data per Rank & Total Data\\ % Column names row
+\midrule % In-table horizontal line
+AMG  &    216 &   0.6MB   &     \\ % Content row 1
+\midrule
+MultiGrid  &    125 &   5MB   &     \\ 
+\midrule
+CrystalRouter  &   100  &  35MB    &     \\
+
+\midrule % In-table horizontal line
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\end{center}
+\end{table}
+
+In our experiments, the workload running on the dragonfly network under 6 different job placement and routine scheme configurations as listed in Table \ref{tab: placement routing config}.
+We focus on the analysis of network status while the workload is running, as well as the performance of each individual application.
+We collected the following result data from the experiments:
+\begin{itemize}
+    \item router terminal link traffic and busy time.
+    \item router local channel traffic and busy time.
+    \item router global channel traffic and busy time.
+    \item The time application spend on communication. 
+\end{itemize}
+
+\TODO{need a figure show workload communication time!!!}
+
+Figure \ref{fig:wkld-network-traffic} shows the amount of traffic go through terminal links, local channels and global channels when the workload running on dragonfly network with 6 different placement and routing configurations, and Figure \ref{fig:wkld-network-stime} shows the corresponding busy time.
+
+%global link traffic and busy time explanation
+When the workload is running with contiguous placement and minimal routing, all the MPI ranks are physically adjacent to each other, and the packets are routed through the shortest path between its source rank to destination rank.
+In this case, all the traffic are on the first half of the network (node id from 0 to $216+125+100-1=440$, group id from 0 to 13 ), causing the network local congestion and traffic load on some routers are extremely high, as shown the blue dash line in Figure \ref{fig:global-channel-traffic}.
+Thus the busy time of global channel is also the highest when contiguous placement coupled with minimal routing, as shown in Figure \ref{fig:global-channel-stime} the blue dash line.
+
+When contiguous placement is coupled with adaptive routing or progressive adaptive routing, the local congestion on global channel will be greatly alleviated, as shown in Figure \ref{fig:global-channel-traffic} the red and green dash line.
+Since both adaptive and progressive adaptive routing are congestion aware, and be able to utilize the idle routers on the other part of the network.
+The busy time of global channel are also reduce by using contiguous placement coupled with either adaptive or progressive adaptive routing, as shown in Figure \ref{fig:global-channel-stime} the red and green dash line.
+
+Random placement can randomly allocate the MPI ranks to the physical nodes all over the network, thus prevent the traffic from congesting certain part of the network.
+Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic go through global channels are quite uniformly distributed across all the routers in the network, thus no particular global channel will suffer high traffic burden.
+When the random placement coupled with minimal routing, the packets can avoid unnecessary intermediate forwarding as introduced by adaptive and progressive routing, which results in generating less traffic.
+That's why the blue solid line is lower than the red and green solid line, shown in figure\ref{fig:global-channel-traffic}.
+Since the random placement can uniformly distribute the workload traffic, there are no sudden surge of busy time of global channel over the network, shown as solid lines in Fgiure \ref{fig:global-channel-stime}.
+
+%local channel traffic and busy time explanation
+
+We can get the same observation from the local channel traffic (Figure \ref{fig:local-channel-traffic}) and busy time (Figure \ref{fig:local-channel-stime}).
+Contiguous placement coupled with minimal routing results in local congestion, thus highest traffic amount on the local channel of certain routers.
+Even with adaptive or progressive adaptive routing, the local congestion caused by grouping MPI rank on adjacent nodes in contiguous placement can not be eliminated.
+The random placement can reduce the congestion on local channel for allocating MPI ranks to random selected nodes.
+
+%terminal link traffic and busy time explanation
+The distribution of traffic go through terminal links stay unchanged no matter which placement and routing configuration are used, as shown in Figure \ref{fig:terminal-link-traffic}.
+This is because only the location of each MPI rank in the network will be changed in different placement schemes, and the routing won't have effect the terminal link, so the traffic between compute node and the router won't change.
+Due to the traffic changes on global and local channels, the busy time of terminal links will also experience some variation when different placement and routing scheme configuration in use, as shown in Figure \ref{fig:terminal-link-stime}.
 
@@
     \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/gc-traffic}
+        \caption{Global Channel Traffic}
+        \label{fig:global-channel-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/lc-traffic}
+        \caption{Local Channel Traffic}
+        \label{fig:local-channel-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
     \begin{subfigure}[t]{0.32\textwidth}
@@
     \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:local-channel-traffic}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:global-channel-traffic}
-    \end{subfigure}%
   \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
@@
         \centering
+        \includegraphics[height=1.8 in]{wkld/gc-stime}
+        \caption{Global Channel Busy Time}
+        \label{fig:global-channel-stime}
+    \end{subfigure}%
+     \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/lc-stime}
+        \caption{Local Channel Busy Time}
+        \label{fig:local-channel-stime}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
         \includegraphics[height=1.8 in]{wkld/tl-stime}
@@
     \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-stime}
-        \caption{Local Channel Busy Time}
-        \label{fig:local-channel-stime}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-stime}
-        \caption{Global Channel Busy Time}
-        \label{fig:global-channel-stime}
-    \end{subfigure}%
    \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
@@
 
-Contiguous placement allocates each job a set of nodes that adjacent to each other, which confines the traffic of the application into the local area when coupled with minimal routing.
+\NOTE{The take-home message} from Figure \ref{fig:wkld-network-stime} and \ref{fig:wkld-network-traffic}.
+
+Contiguous placement allocates MPI ranks to physical nodes that are adjacent to each other, which confines the workload traffic to some local area when coupled with minimal routing.
 This may leads to hot-spot in local area and unbalanced network utilization.
-As we can see from Figure \ref{fig:wkld-network-traffic} and \ref{fig:wkld-network-stime}, contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest network busytime.
-
-Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:wkld-network-stime} shows that random job placement with adaptive routing can uniformly distribute workload traffic and balance the load over the network.
-
-\subsection{Application Analysis}
-\label{sec:app analysis}
-
-The random job placement and adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
-In this section, we will show that not every application can benefit from random job placement and adaptive routing.
+As we can see from Figure \ref{fig:wkld-network-traffic} and \ref{fig:wkld-network-stime}, contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest busy time.
+
+Random placement allocates MPI ranks to a set of randomly selected nodes all over the system, which will uniformly distribute workload traffic and avoid local congestion.
+When random placement is coupled with minimal routing, the packets will take the shortest path from source router to the destination router without routing to any intermediate routers, this will prevent the routing from generating extra traffic.
+When random placement is coupled with adaptive or progressive adaptive routing, the possibility of any congestion will be further reduced at the cost of extra intermediate traffic.
+
+% Start from here, we present the individual application analysis.
+The random job placement coupled with either minimal or adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
+The workload performance get greatly improved with these configurations.
+However, when we isolated individual application from the workload, we unveil the fact that not every application can benefit from random job placement.
 
@@
 Three applications running concurrently on dragonfly network with different placement and routing configurations.
-Random job placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
+Random placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
    \label{fig:apps-commtime}
@@
 
-Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently with 4 different placement and routing configurations.
-MG and CR can get improvement with random placement and adaptive routing, compared with contiguous placement and minimal routing.
-However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.
-\textbf{More explanation about contiguous placement and minimal routing here}
-
-The results of random placement shown in Figure \ref{fig:apps-commtime} are collected from extensive runs of different random placements, which can eliminate the possibility of variations.
-
+Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
+
+As shown in Figure \ref{fig:mg-commtime} \ref{fig:cr-commtime}, MG and CR suffer the longest communication time when running under the configuration of contiguous placement and minimal routing(CM).
+When contiguous placement coupled with adaptive or progressive adaptive routing, both MultiGrid and CrystalRouter will get great improvement in terms of communication efficiency.
+Random placement will further reduce the communication time of MultiGrid and CrystalRouter, and reach the best performance when coupled with (progressive) adaptive routing.
+Both MultiGrid and CrystalRouter shows the same trend as the workload when running under different placement and routing configurations.
+
+However, AMG's performance is quite an exception.
+As shown in Figure \ref{fig:amg-commtime}, the communication time of AMG is skyrocketing when it running under random placement coupled with (progressive) adaptive routing.
+The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
+The performance of AMG running under contiguous placement coupled with minimal routing is no better than random coupled with minimal routing, but still much better than random with (progressive) adaptive routing.
+
+% Show the evidence from network level, explain why AMG is different. 
 We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing.

### 2016-03-14 draft.tex
update figs in section 5, add conclusion section

@@
 A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.
-CODES support dragonfly network with high fidelity flit-level simulation\cite{codes-dragonfly}.
+CODES support dragonfly network with high fidelity packet-level simulation\cite{codes-dragonfly}.
 It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.
@@
 
-In our experiments, the workload running on the dragonfly network under 6 different job placement and routine scheme configurations as listed in Table \ref{tab: placement routing config}.
+Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application.
+Based on this figure, we could say that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width = 0.48\textwidth ]{data_amount}
+  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with CR and MG.}
+  \label{fig:3app-data-amount}
+\end{figure}
+
+In our experiments, the workload running on the dragonfly network under 6 different job placement and routine scheme configurations as listed in Table \ref{tab: placement routing configs}.
 We focus on the analysis of network status while the workload is running, as well as the performance of each individual application.
@@
 
-\TODO{need a figure show workload communication time!!!}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width = 0.48\textwidth ]{wkld/wkld-commtime}
+  \caption{Time spent on communication by Workload I when 6 different placement and routing scheme configurations are used.
+Random is better than contiguous in terms of improving communication efficiency.Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
+}
+  \label{fig:wkld-commtime}
+\end{figure}
 
@@
 
-Random placement can randomly allocate the MPI ranks to the physical nodes all over the network, thus prevent the traffic from congesting certain part of the network.
+Random placement can randomly allocate the MPI ranks to the physical nodes all over the network, thus prevent the traffic from being congested certain part of the network.
 Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic go through global channels are quite uniformly distributed across all the routers in the network, thus no particular global channel will suffer high traffic burden.
@@
 
-However, AMG's performance is quite an exception.
+However, AMG is quite an exception.
 As shown in Figure \ref{fig:amg-commtime}, the communication time of AMG is skyrocketing when it running under random placement coupled with (progressive) adaptive routing.
@@
 By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}.
-Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.
-\textbf{More explanation about contiguous placement and minimal routing}
-
-CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing.
-\textbf{More explanation about contiguous placement and minimal routing}
+Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
+
+No router will be shared between applications under contiguous placement.
+A set of successive groups will be allocated to each application under contiguous placement scheme.
+When contiguous placement coupled with minimal routing, application will be free of interference from its running neighbors.
+However, application communication traffic will be confined within their allocated routers, thus local congestion is very likely to happen depends on application communication intensity.
+As the lest communication intensive application, AMG can benefit from contiguous placement.
+Under contiguous placement, the traffic go through the local and global channels of the routers that belongs to AMG is significantly lower than random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
+MultiGrid and CrystalRouter are more communication intensive compared with AMG.
+They will suffer great amount local traffic in both local and global channels when contiguous placement is used, shown as the dash line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
+The random placement scheme can uniformly distribute their traffic all over the network by allocating randomly selected nodes to each MPI rank.
 
@@
 
-Why AMG is the only victim in the workload?
-The reason for CrystalRouter and MultiGrid get improvement in the sacrifice of AMG's performance is that AMG is the lest communication-intensive application in the workload.
-As shown in Figure \ref{fig:3app-data-amount}, AMG has the least amount of data transfer between its ranks.
-
-\begin{figure*}[t!]
-  \centering
-  \includegraphics[height=2.2in]{data_amount}
-  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with CR and MG.}
-  \label{fig:3app-data-amount}
-\end{figure*}
-
-Apparently, random placement and adaptive routing is quite efficient for orchestrate the traffic load in the network.
+The reason for AMG being the only victim from random placement and adaptive routing is due to  its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
+
+From the detailed analysis of three applications performance above, we know that random placement and adaptive routing is quite efficient for orchestrate the traffic load in the network.
 Random placement and adaptive routing can uniformly distribute the workload traffic all over the network, make the load-balanced and avoid hot-spots.
@@
 
-We have tried three different congestion sensing schemes that used in adaptive routing\cite{dally-dragonfly}, although there are some variations of the experiments, none of the congestion sensing scheme can prevent the ``bully" from happening.
+We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations of the experiments, none of the congestion sensing scheme can prevent the ``bully" from happening.
 
@@
 
-To validate our assumption, we generate synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
-We run the new workload that consists of sAMG, MG and CR on the same dragonfly network with the same placement and routing configurations.
+In order to prove that AMG being bullied only because it is less communication-intensive than its running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with 6 different placement and routing configurations.
 As shown in Figure \ref{fig:syn-3app-data-amount}, sAMG become the most communication-intensive application in the new workload.
 
-\begin{figure*}[t!]
-  \centering
-  \includegraphics[height=2.2in]{syn-wkld/data_amount}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width = 0.48\textwidth ]{syn-wkld/data_amount}
   \caption{Applications Data Transfer Amount. sAMG has the most amount of data transfer, compared with CR and MG.}
   \label{fig:syn-3app-data-amount}
-\end{figure*}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width = 0.48\textwidth ]{syn-wkld/wkld-commtime}
+  \caption{ Time spent on communication by Workload II when 6 different placement and routing scheme configurations are used.
+Random is better than contiguous in terms of improving communication efficiency.Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
+}
+  \label{fig:syn-wkld-commtime}
+\end{figure}
+
+\TODO{Explain} Figure \ref{fig:syn-wkld-commtime}.
 
@@
 The ``bully" become the ``bullyee".
-The less communication-intensive application, CrystalRouter and MultiGrid, suffer prolonged communication time when running concurrently with sAMG with random placement and adaptive routing configuration.
-The routers that belongs to MultiGrid  and now CrystalRouter has extra traffic go through them, shown in Figure  \ref{fig:syn-mg-lc-traffic} \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic} \ref{fig:syn-cr-gc-traffic}.
-The extra traffic come from sAMG, that been redirected by adaptive routing.
-\textbf{More explanation about contiguous placement and minimal routing}.
+The less communication-intensive applications in the workload this time are  MultiGrid and CrystalRouter.
+When random placement coupled with (progressive) adaptive routing is used, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
+sAMG on the other hand benefit from random placement, shown in Figure \ref{fig:syn-samg-commtime }.
+
+Contiguous placement coupled with minimal routing prevent applications from sharing network resource, and confine application communication traffic to their allocated routers.
+This can guarantee the performance of less communication intensive applications like MultiGrid and CrystalRouter, and make the communication intensive application like sAMG severely deteriorate.
 
@@
         \caption{sAMG Communication Time}
-        \label{fig:samg-commtime}
+        \label{fig:syn-samg-commtime}
     \end{subfigure}%
@@
 
+% explain the network status of sAMG, MG and CR
+We look into the network level to scrutinize the traffic went through the routers belongs to each application. 
+Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement and routing configuration is used.
+The traffic is skyrocketing in both local and global channels when contiguous placement coupled with minimal routing.
+The contiguous placement make all the MPI ranks of sAMG reside on a set of nodes in the groups that adjacent to each other and minimal routing confines the traffic in those groups, results in severe local congestion.
+When adaptive routing is used, the local congestion will be alleviated in both local and global channels, as some traffic will be redirected to other part of the network.
+Random placement scheme can further reduce the traffic burden on local and global channels by assigning each MPI rank of sAMG with randomly select nodes, thus uniformly distribute sAMG traffic over the network.
+
+MultiGrid become a victim of sAMG's bully when running under random placement.
+The traffic go through the local and global channels of the routers that belongs to MultiGrid are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic}.
+Although contiguous placement allocates all the MPI ranks in set of nodes in adjacent groups, causing possible local congestion, it will save MultiGrid's routers being shared by the traffic from its communication intensive peer, sAMG.
+As random placement is used, the traffic go through both local and global channels are greatly increased.
+
+CrystalRouter has more traffic than MultiGrid.
+The random placement won't redirect much traffic from other applications to the routers belongs to CrystalRouter, compared with contiguous placement, as shown in Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}.
+
 \begin{figure*}[t!]
@@
         \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
-        \caption{AMG Local Channel Traffic}
-        \label{fig:samg-lc-traffic}
+        \caption{sAMG Local Channel Traffic}
+        \label{fig:syn-samg-lc-traffic}
     \end{subfigure}%
@@
         \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
-        \caption{AMG Global Channel Traffic}
-        \label{fig:samg-gc-traffic}
+        \caption{sAMG Global Channel Traffic}
+        \label{fig:syn-samg-gc-traffic}
     \end{subfigure}%
@@
 \end{figure*}
-
-\textbf{We can add another set of synthetic workload, in which three applications have similar data transfer amount, if necessary. }
 
@@
 \section{Conclusion}
-The conclusion goes here.
+\label{sec:conclusion}
+
+In this paper, we have conducted extensive study about application's behavior when it running on dragonfly network with different job placement and routing configurations.
+We resorted to CODES, a HPC network simulation tool with high fidelity, and used three parallel applications traces collected from production system to analysis the applications' behavior on network level.
+We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network, alleviate local congestion, the performance of certain application would be impaired.
+We identify this phenomenon as ``bully" between concurrently running jobs, and the victim always being the less communication-intensive application.
+On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, the configuration can guarantee the performance of ``bullee" application by limiting the network sharing between concurrently running application.
+
+Due the presence of this ``bully", we suggest that when the batch scheduler make job placement for workload on system with dragonfly network, random placement shouldn't be the rule of thumb.
+Instead, the placement should made with consideration of jobs communication intensity.
+The less intensive application should get contiguous allocation coupled with adaptive routing, the intensive ones should get random allocation coupled with minimal routing.
+
+We believe the findings presented in this paper can illuminate a path to more efficient workload manager for future systems with dragonfly network.
 

### 2016-03-15 draft.tex
finish 1st version

@@
 The high-radix, low-diameter dragonfly topology network will be the choice of many computing facilities for building their next generation supercomputers.
-Preliminary study shows that random job allocation with adaptive routing would be the rule of thumb to utilize such powerful network.
-However, in this work, we made the observation that although random job allocation with adaptive routing can alleviate the hotspot and make network traffic load-balanced for the workload, it can not guarantee the best performance for each single job.
+Preliminary study shows that random placement with adaptive routing should be the rule of thumb to utilize such powerful network, since random placement can uniformly distribut traffic over the network, and adaptive routing can alleviate congestion.
+However, in this paper, we made the observation that although random placement coupled with adaptive routing can reach load-balanced over the network when multiple jobs running concurrently, it can not guarantee the best performance for each single job.
 The performance improvement of communication intensive jobs comes with sacrifice of those less intensive jobs.
 We refer this phenomenon as ``bully" between concurrently running jobs.
-In this paper, we analyze the detailed reason for the happening of this ``bully" from the network level.
+We analyze the detailed reason behind this ``bully" behavior between jobs from the underneath network level.
 Our study is based on a sophisticated, high-fidelity discrete even-driven simulation tool.
-We believe the observations and analysis in this work will make the chosen of job allocation and routing strategies more cautiously in future.
+We believe the observations and analysis in this work will make the chosen of job placement and routing strategies on dragonfly network more cautiously in future.
 
@@
 % no keywords
+
+% \keywords{Dragonfly, Job placement, Routing, Interference}
 
@@
 The low latency and high bandwidth interconnect network plays a critical role in improving HPC system performance.
-As the computing ability of HPC system continue grows due to many-core nodes with accelerators, the network is now becoming a scare resources.
+As the computing ability continue grows due to many-core nodes with accelerators, the network is now becoming a scare resources.
 HPC community start to explore the possible alternative to replace the commonly used Torus network.
 
-The building high-radix, low-diameter dragonfly topology can lower the cost of interconnect network, improve network bandwidth, reduce the packets traverse latency.
+The high-radix, low-diameter dragonfly topology can lower the cost of interconnect network, improve network bandwidth, reduce the packets traverse latency.
 This make the dragonfly network an very promising choice for building multi-Petaflop/s supercomputers\cite{dally-dragonfly}.
@@
 This is paper, we study the interference between concurrently running jobs on dragonfly network with different job placement and routing schemes.
-Being unorthodox to most existing work that use synthetic workload, our work is based on application traces that collected from production system.
-The advantage of using real application traces is quite obvious.
-The traces collected from production system can capture application's communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity.
+Being unorthodox to most existing work that use synthetic workload, parallel scientific application traces that collected from production system are used in our study.
+The advantage of using real application traces is quite obvious, these traces can capture application's communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity.
+Applicatoins usually are distinctive from each other in terms of  data transfer amount, communication pattern, operation dependency etc.
+which are impossible to reproduce in synthetic workload.
 
@@
 
-We made observation from our extensive study that, when dragonfly network enabled with random job placement and adaptive routing scheme in order to reach hot-spot free and load balance, the performance of particular job(s) in the workload would suffer degradation.
+We made observation from our extensive study that, when dragonfly network is configured with random placement and adaptive routing scheme in order to reach hot-spots free and load balance, the performance of particular job(s) in the workload would suffer degradation.
 The communication intensive jobs in the workload can benefit from random placement and adaptive routing, with great performance improvement.
 Unfortunately, those less intensive jobs are the sacrifices for this improvement, their performance will be greatly reduced.
+We identify this phenomenon as ``bully" between concurrently running jobs.
 
@@
     \item Our real trace-based analysis about job interference on dragonfly network, shows that random placement with adaptive routing can not guarantee the performance of every job in the workload.
-The hotspot-free and load-balanced reached by using random placement with adaptive routing come with the cost of communication-less-intensive jobs performance degradation.
-
-    \item We identify the ``bully" behavior happening between jobs running concurrently on dragonfly network with random placement and adaptive routing.
-Random placement and adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resources, slow down the communication of those less intensive jobs.
-
-    \item We found that contiguous placement and minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may leads to local hotspot and severe network congestion.
-Actually, contiguous placement and minimal routing are preferred by communication-less-intensive jobs, since it will prevent them from being bullied by other communication-intensive jobs.
+The hot-spots free and load-balanced reached by using random placement with adaptive routing come with the cost of less communication-intensive jobs performance degradation.
+
+    \item We identify the ``bully" behavior happening between concurrently running jobs on dragonfly network when random placement and adaptive routing in use.
+Random placement and adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resource such as local and global channel bandwidth, slow down the communication of those less intensive jobs.
+
+    \item We found that contiguous placement and minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may result in hot-spots and local network congestion.
+Actually, contiguous placement and minimal routing are preferred by communication-less-intensive jobs, since it will prevent them from being ``bullied" by other communication-intensive jobs.
 
@@
 
-To the best of our knowledge, using application traces from production system for the study of job interference on dragonfly network as not been reported so far.
+To the best of our knowledge, using parallel application traces from production system for the study of job interference on dragonfly network has not been reported so far.
 We believe the observations and analysis presented in this paper can be used by computing facilities to choose job placement and routing strategies wisely for their future dragonfly interconnected system.
-The conclusion from this paper would be useful for batch schedulers in dragonfly system to make better scheduling decisions for workload consists of jobs that have various communication behavior.
+The conclusion from this paper would be useful for workload manager in dragonfly system to make better scheduling decisions for jobs with distinctive communication behavior.
 
@@
 In each group, there could be ``a" number of routers connected via All-to-All local channels.
-For each router, there could be ``p" number of compute nodes attached to it via terminal link.
-The router has ``h" number of global channels that used as intergroup connections through which the router connected to other router in different groups.
+For each router, there could be ``p" number of compute nodes attached to it via terminal links.
+The router has ``h" number of global channels that used as intergroup connections through which the router connected to other routers in different groups.
 Thus, the radix of each router is $k = a+h+p-1$.
@@
 
-For the purpose of loading balance, it is recommended that the proper dragonfly configuration is $a=2p=2h$\cite{kim-micro}.
-Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g = $.
+For the purpose of loading balance, it is recommended that the proper dragonfly configuration should be like $a=2p=2h$\cite{kim-micro}.
+Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g $.
+Figure \ref{fig:dragonfly overview} illustrated an implementation of dragonfly network follows such configuration.
+There are 6 routers in each group, each router has 3 compute nodes attached to it.
+This dragonfly implementation consists of 19 groups and 342 nodes in total.
 
@@
 }
-  \label{fig: dragonfly overview}
+  \label{fig:dragonfly overview}
 \end{figure}
@@
 
-Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by the job for execution.
+Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by each job for execution.
 As studied by several researchers, the job placement could be an important factor that impact application performance \cite{hoefler-hpdc14} \cite{bhatele-sc11} \cite{jain-sc14}.
-In this work, we study the following two placement schemes:
-
-\textbf{Contiguous Placement:} In this scheme, the nodes will first be indexed consecutively in the increasing oder of their group id and router id.
-The job is allocated by cutting chunks of nodes from the sequentially ordered list, as illustrated in Figure\ref{fig: dragonfly overview} as blue nodes.
-The nodes been allocated to each job will be adjacent to each other, usually they are attached to the same router, in the same group.
-Contiguous placement confines the traffic of application into the local area, which may leads to local network congestion and increase the possibility of hot-spots.
+In this work, we study the following two placement schemes that are most likely to be deployed in the future dragonfly system.
+
+\textbf{Contiguous Placement:} In this scheme, the nodes will first be indexed consecutively in an increasing order of their group id and router id.
+The schedul assign each job required number of nodes by cutting chunks of nodes from the sequentially ordered list, as illustrated in Figure \ref{fig: dragonfly overview} as blue nodes assigned to job\_2.
+The nodes been allocated to the same job will be adjacent to each other, usually they are attached to the same router or in the same group, depends on the size of the job.
+Contiguous placement confines the traffic of application into the local area, which may result in local network congestion and increase the possibility of hot-spots.
 
 \textbf{Random Placement:} In this scheme, job will get a set of nodes that randomly selected from all the available nodes in the system.
-The nodes allocated to each job would be attached to different routers in different groups, as illustrated in Figure\ref{fig: dragonfly overview} as red nodes.
+The nodes allocated to each job would be attached to different routers in different groups, as illustrated in Figure \ref{fig: dragonfly overview} the red nodes assigned to job\_1.
 Some routers may be shared by different applications when using random placement.
-Random placement can spreading the traffic of application uniformly across the whole system, thus avoid the possible hot-spots and reach load balance.
+Random placement can spreading the traffic of application uniformly across the whole system, thus avoid the possible local congestion and reach load balance.
 
@@
 The implemented routing schemes in CODES dragonfly network model are based on the routing algorithm proposed by Kim et al.
-\cite{dally-dragonfly}.
-Two routing schemes studied in this work are \emph{Minimal} and \emph{Adaptive}.
-
-\textbf{Minimal:} The minimal routing sends a message from source router to destination router along the shortest path.
-When there are multiple shortest paths, the message is evenly divided among the paths.
+\cite{dally-dragonfly} and Jiang et al.
+\cite{jiang}.
+Three routing schemes are studied in this work are \emph{Minimal}, \emph{Adaptive} and \emph{Progressive Adaptive}.
+
+\textbf{Minimal:} When the network deploy minimal routing, a message from source router will take the the shortest path to the destination router.
+When there are multiple shortest paths between the rource and destination router, the message will be evenly divided among the paths.
 Minimal routing can guarantee the minimum hops the message takes from source to destination.
-However, it may leads to congestion along the shortest path.
+However, it may result in congestion along the shortest path.
 
@@
 For the non-shortest path, an intermediate router will be randomly chosen.
-The message will first take the shortest path from source to that intermediate router, then it will take the shortest path between the intermediate router to the destination.
+The message will first take the shortest path from source to that intermediate router, then it will take the shortest path from that intermediate router to the destination.
 Since adaptive scheme chooses routing path adaptively based on the congestion situation, it can void local congestion and reduce the possibility of hot-spots.
 
-\textbf{Progressive Adaptive:} \NOTE{say something about prog-adaptive routing.} \cite{won-prog-adaptive}.
+\textbf{Progressive Adaptive:} In this scheme, the decision to route minimally at each hop in the source group will be re-evaluated and any decision to route non-minimally at source router or at a subsequent hop is permant and is not re-evaluated \cite{jiang}.
+The progressive adaptive is capable of handling the case where a global link is congested but this information has not yet propagated back to the source router \cite{jiang}.
+The packet will take the non-minimal route only when the congestion is encountered.
 
@@
 A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.
-CODES support dragonfly network with high fidelity packet-level simulation\cite{codes-dragonfly}.
+CODES supports dragonfly network with packet-level high-fidelity simulation\cite{codes-dragonfly}.
 It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.
@@
 
-We choose three representative applications from DOE Design Forward Project\cite{designforwardwebpage}.
+We choose three representative parallel applications from DOE Design Forward Project\cite{designforwardwebpage}.
 We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers.
@@
 It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.
-The traces of AMG we chosen are comprised of 216 MPI ranks.
-
-MultiGrid: massively parallel block-structured adaptive mesh refinement (AMR) codes a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
+% The traces of AMG we chosen are comprised of 216 MPI ranks.
+
+MultiGrid:  geometric multi-grid v-cycle from the production elliptic solver BoxLib, a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
 It is widely used for structured grid physics packages.
-The traces of MultiGrid we chosen are comprised of 125 MPI ranks.
+% The traces of MultiGrid we chosen are comprised of 125 MPI ranks.
 
@@
 It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.
-The traces of CrystalRouter we chosen are comprised of 100 MPI ranks.
+% The traces of CrystalRouter we chosen are comprised of 100 MPI ranks.
 
@@
 
-The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it.
-Overall, there are 264 routers and 1056 compute nodes in the network.
-The bandwidth of both terminal links and local channel are set to 2GB/s, the global channel bandwidth is set to 4GB/s.
-
-There are 6 placement and routing scheme combinations, namely contiguous placement coupled with minimal routing, contiguous placement coupled with adaptive routing, contiguous placement coupled with progressive adaptive routing random placement coupled with minimal routing, random placement coupled with adaptive routing, random placement coupled with progressive adaptive routing.
-In this work, we enable the applications running on dragonfly network under different placement and routing configurations, and scrutinize the application's performance and network behavior in different running scenarios.
-
 \begin{table}[ht]
 \begin{center}
-\caption{Job placement and routing configurations} 
+\caption{The notation for different placement \& routing configurations} 
 \label{tab: placement routing configs}
@@
 \toprule
-&\multicolumn{3}{c}{Routing Schemes} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{3}{c}{Routing} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
 \cmidrule(l){2-4}
-Placement schemes & Minimal & Adaptive & Progressive adp\\ % Column names row
+Placement  & Minimal & Adaptive & Progressive adaptive\\ % Column names row
 \midrule % In-table horizontal line
-Contiguous  &     &      &     \\ % Content row 1
+Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
 \midrule
-Random  &     &      &     \\
+Random  &   RM  &   RA   &  RPA   \\
 
@@
 
-The results of random placement shown in the following sections are collected from extensive runs of different random placements, which can eliminate the possibility of variations.
-
-\section{Parallel Workload \Rmnum{1 } Study}
+The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it.
+Overall, there are 264 routers and 1056 compute nodes in the network.
+The bandwidth of both terminal links and local channel are set to 2GB/s, the global channel bandwidth is set to 4GB/s.
+
+We focus on the study of two placement schemes and three routing schemes, so there will be 6 different placement\&routing configurations, as listed in Table \ref{tab: placement routing configs}.
+In this work, we enable the applications running on dragonfly network under different placement and routing configurations, and scrutinize the application's performance and network behavior in different running scenarios.
+
+In our experiments, the workload running on the dragonfly network under 6 different placement and routing configurations as listed in Table \ref{tab: placement routing configs}.
+We focus on the analysis of network status while the workload is running, as well as the performance of each individual application.
+We collected the following result data from the experiments:
+
+\begin{itemize}
+    \item router terminal link traffic and busy time.
+    \item router local channel traffic and busy time.
+    \item router global channel traffic and busy time.
+    \item The time spend on communication for each MPI rank. 
+\end{itemize}
+
+The results of random placement shown in the following experiments are collected from extensive runs of different random placements, which can eliminate the possibility of variations.
+
+\section{Parallel Workload \Rmnum{1 }}
 \label{sec: workload 1 overview}
 
-The first parallel workload analyzed in our experiment consists of three applications, namely AMG , MultiGrid (MG) and CrystalRouter(CR).
+The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces} .
 The details of this workload shown in Table \ref{tab: parallel workload-1}.
@@
 \begin{center}
-\caption{Parallel Workload \Rmnum{1 }} 
+\caption{Details of Parallel Workload \Rmnum{1 }.} 
 \label{tab: parallel workload-1}
@@
 \toprule
-&\multicolumn{3}{c}{Routing Schemes} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{3}{c}{Application Details} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
 \cmidrule(l){2-4}
-Application & num. rank & Data per Rank & Total Data\\ % Column names row
+App Name & num. rank & Data per Rank & Total Data\\ % Column names row
 \midrule % In-table horizontal line
-AMG  &    216 &   0.6MB   &     \\ % Content row 1
+AMG  &    216 &   0.6MB   &     130MB\\ % Content row 1
 \midrule
-MultiGrid  &    125 &   5MB   &     \\ 
+MultiGrid  &    125 &   5MB   &     625MB\\ 
 \midrule
-CrystalRouter  &   100  &  35MB    &     \\
+CrystalRouter  &   100  &  35MB    &     3500MB\\
 
@@
 
-Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application.
-Based on this figure, we could say that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive.
-
 \begin{figure}[h!]
@@
 
-In our experiments, the workload running on the dragonfly network under 6 different job placement and routine scheme configurations as listed in Table \ref{tab: placement routing configs}.
-We focus on the analysis of network status while the workload is running, as well as the performance of each individual application.
-We collected the following result data from the experiments:
-\begin{itemize}
-    \item router terminal link traffic and busy time.
-    \item router local channel traffic and busy time.
-    \item router global channel traffic and busy time.
-    \item The time application spend on communication. 
-\end{itemize}
-
+Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application.
+Based on this figure, we can tell that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive.
+
+\subsection{Workload Analysis}
 \begin{figure}[h!]
@@
   \includegraphics[width = 0.48\textwidth ]{wkld/wkld-commtime}
-  \caption{Time spent on communication by Workload I when 6 different placement and routing scheme configurations are used.
+  \caption{Time spent on communication by Workload I when 6 different placement and routing configurations are used.
 Random is better than contiguous in terms of improving communication efficiency.Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
@@
 \end{figure}
+
+The communication time spent by parallel workload \Rmnum{1} under different placement and routing configuration shown in Figure \ref{fig:wkld-commtime}.
+The contiguous placement coupled with minimal routing results in highest communication time.
+The random placement coupled with minimal routing is the most efficient.
+Progressive adaptive routing is basically the same as adaptive when coupled with both placement schemes.
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/gc-traffic}
+        \caption{Global Channel Traffic}
+        \label{fig:global-channel-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/lc-traffic}
+        \caption{Local Channel Traffic}
+        \label{fig:local-channel-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/tl-traffic}
+        \caption{Terminal Link Traffic}
+        \label{fig:terminal-link-traffic}
+    \end{subfigure}%
+  \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
+   \label{fig:wkld-network-traffic}
+\end{figure*}
+
+\begin{figure*}[t!]
+    \centering   
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/gc-stime}
+        \caption{Global Channel Busy Time}
+        \label{fig:global-channel-stime}
+    \end{subfigure}%
+     \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/lc-stime}
+        \caption{Local Channel Busy Time}
+        \label{fig:local-channel-stime}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/tl-stime}
+        \caption{Terminal Link Busy Time}
+        \label{fig:terminal-link-stime}
+    \end{subfigure}%
+   \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
+   \label{fig:wkld-network-stime}
+\end{figure*}
 
@@
 
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:global-channel-traffic}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:local-channel-traffic}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:terminal-link-traffic}
-    \end{subfigure}%
-  \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
-   \label{fig:wkld-network-traffic}
-\end{figure*}
-
-\begin{figure*}[t!]
-    \centering   
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-stime}
-        \caption{Global Channel Busy Time}
-        \label{fig:global-channel-stime}
-    \end{subfigure}%
-     \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-stime}
-        \caption{Local Channel Busy Time}
-        \label{fig:local-channel-stime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-stime}
-        \caption{Terminal Link Busy Time}
-        \label{fig:terminal-link-stime}
-    \end{subfigure}%
-   \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
-   \label{fig:wkld-network-stime}
-\end{figure*}
-
-\NOTE{The take-home message} from Figure \ref{fig:wkld-network-stime} and \ref{fig:wkld-network-traffic}.
+% \NOTE{The take-home message} from Figure \ref{fig:wkld-network-stime} and \ref{fig:wkld-network-traffic}.
 
@@
 However, when we isolated individual application from the workload, we unveil the fact that not every application can benefit from random job placement.
+
+\subsection{Individual Application Analysis}
 
@@
 The performance of AMG running under contiguous placement coupled with minimal routing is no better than random coupled with minimal routing, but still much better than random with (progressive) adaptive routing.
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{amg/lc-traffic}
+        \caption{AMG Local Channel Traffic}
+        \label{fig:amg-lc-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{mg/lc-traffic}
+        \caption{MG Local Channel Traffic}
+        \label{fig:mg-lc-traffic}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{cr/lc-traffic}
+        \caption{CR Local Channel Traffic}
+        \label{fig:cr-lc-traffic}
+    \end{subfigure}%
+   \caption{Each Application Router Local Channel Traffic.  }
+   \label{fig:3app-lc-traffic}
+\end{figure*}
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{amg/gc-traffic}
+        \caption{AMG Global Channel Traffic}
+        \label{fig:amg-gc-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{mg/gc-traffic}
+        \caption{MG Global Channel Traffic}
+        \label{fig:mg-gc-traffic}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{cr/gc-traffic}
+        \caption{CR Global Channel Traffic}
+        \label{fig:cr-gc-traffic}
+    \end{subfigure}%
+   \caption{Each Application Router Global Channel Traffic.}
+   \label{fig:3app-gl-traffic}
+\end{figure*}
 
@@
 
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{amg/lc-traffic}
-        \caption{AMG Local Channel Traffic}
-        \label{fig:amg-lc-traffic}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
-        \label{fig:mg-lc-traffic}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
-        \label{fig:cr-lc-traffic}
-    \end{subfigure}%
-   \caption{Each Application Router Local Channel Traffic.  }
-   \label{fig:3app-lc-traffic}
-\end{figure*}
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{amg/gc-traffic}
-        \caption{AMG Global Channel Traffic}
-        \label{fig:amg-gc-traffic}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:mg-gc-traffic}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:cr-gc-traffic}
-    \end{subfigure}%
-   \caption{Each Application Router Global Channel Traffic.}
-   \label{fig:3app-gl-traffic}
-\end{figure*}
-
 The reason for AMG being the only victim from random placement and adaptive routing is due to  its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
@@
 
-\section{Parallel Workload \Rmnum{2 } Study}
-
-In order to prove that AMG being bullied only because it is less communication-intensive than its running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
-We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with 6 different placement and routing configurations.
-As shown in Figure \ref{fig:syn-3app-data-amount}, sAMG become the most communication-intensive application in the new workload.
+\section{Parallel Workload \Rmnum{2 }}
+
+\begin{table}[ht]
+\begin{center}
+\caption{Details of Parallel Workload \Rmnum{2 }.} 
+\label{tab: parallel workload-2}
+%\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c }
+\toprule % Top horizontal line
+\toprule
+&\multicolumn{3}{c}{Application Details} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-4}
+App Name & num. rank & Data per Rank & Total Data\\ % Column names row
+\midrule % In-table horizontal line
+sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
+\midrule
+MultiGrid  &    125 &   5MB   &     625MB\\ 
+\midrule
+CrystalRouter  &   100  &  35MB    &     3500MB\\
+
+\midrule % In-table horizontal line
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 \end{figure}
+
+In order to prove that AMG being bullied only because it is less communication-intensive than its running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with 6 different placement and routing configurations.
+As shown in Figure \ref{fig:syn-3app-data-amount}, sAMG become the most communication-intensive application in the new workload.
+
+\subsection{Workload Analysis}
 
@@
 
-\TODO{Explain} Figure \ref{fig:syn-wkld-commtime}.
+The communication time spent by parallel workload \Rmnum{2} under different placement and routing configuration shown in Figure \ref{fig:syn-wkld-commtime}.
+As the data transfer amount increased in the workload(due to sAMG), the time spent on communication under each configuration also increases.
+But the performance of each configuration still keep the same trend as parallwl workload \Rmnum{1}.
+The contiguous placement coupled with minimal routing results in highest communication time.
+The random placement coupled with minimal routing is the most efficient.
+Progressive adaptive routing is better than adaptive when random placement is used.
+And they have comparable results when contiguous placement is used.
+
+\\ \TODO{Explain Figure }  \ref{fig:synwkld-network-traffic} \ref{fig:synwkld-network-stime}
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
+        \caption{Global Channel Traffic}
+        \label{fig:synwkld-global-channel-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
+        \caption{Local Channel Traffic}
+        \label{fig:synwkld-local-channel-traffic}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
+        \caption{Terminal Link Traffic}
+        \label{fig:synwkld-terminal-link-traffic}
+    \end{subfigure}%
+  \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
+   \label{fig:synwkld-network-traffic}
+\end{figure*}
+
+\begin{figure*}[t!]
+    \centering   
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
+        \caption{Global Channel Busy Time}
+        \label{fig:synwkld-global-channel-stime}
+    \end{subfigure}%
+     \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
+        \caption{Local Channel Busy Time}
+        \label{fig:synwkld-local-channel-stime}
+    \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
+        \caption{Terminal Link Busy Time}
+        \label{fig:synwkld-terminal-link-stime}
+    \end{subfigure}%
+   \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
+   \label{fig:synwkld-network-stime}
+\end{figure*}
+
+\subsection{Individual Application Analysis}
 
@@
 When random placement coupled with (progressive) adaptive routing is used, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
-sAMG on the other hand benefit from random placement, shown in Figure \ref{fig:syn-samg-commtime }.
+sAMG on the other hand benefit from random placement, shown in Figure \ref{fig:syn-samg-commtime}.
 
@@
 \end{figure*}
+
+\section{Summary}
 
@@
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-
 \section{Conclusion}
@@
 
-The authors would like to thank...
+The work at Illinois Institute of Technology is supported in part by U.S.
+National Science Foundation grants CNS-1320125 and CCF-1422009.
+This work is also supported by the U.S.
+Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract DE-AC02-06CH11357.
 

### 2016-03-15 draft.tex
finish 1st round selfcheck

@@
 
-The results of random placement shown in the following experiments are collected from extensive runs of different random placements, which can eliminate the possibility of variations.
+The results of random placement shown in the following experiments are collected from extensive runs of different random placements, which can eliminate the possibility of variation.
 
@@
 
-The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces} .
+The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces}.
 The details of this workload shown in Table \ref{tab: parallel workload-1}.
@@
   \includegraphics[width = 0.48\textwidth ]{data_amount}
-  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with CR and MG.}
+  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with MultiGrid and CrystalRouter.\NOTE{y axis in log?} }
   \label{fig:3app-data-amount}
@@
   \caption{Time spent on communication by Workload I when 6 different placement and routing configurations are used.
-Random is better than contiguous in terms of improving communication efficiency.Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
+Random is better than contiguous in terms of improving communication efficiency.
+Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
 }
@@
 The contiguous placement coupled with minimal routing results in highest communication time.
-The random placement coupled with minimal routing is the most efficient.
-Progressive adaptive routing is basically the same as adaptive when coupled with both placement schemes.
+Progressive adaptive and adaptive routing have comparable results when coupled with contiguous placement.
+The random placement results the comparable performance with any routing schemes and they all outperform the contiguous placement configurations.
 
@@
     \end{subfigure}%
-  \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
+  \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration. }
    \label{fig:wkld-network-traffic}
@@
     \end{subfigure}%
-   \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
+   \caption{The busy time of links in different level in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration.}
    \label{fig:wkld-network-stime}
@@
 When the workload is running with contiguous placement and minimal routing, all the MPI ranks are physically adjacent to each other, and the packets are routed through the shortest path between its source rank to destination rank.
-In this case, all the traffic are on the first half of the network (node id from 0 to $216+125+100-1=440$, group id from 0 to 13 ), causing the network local congestion and traffic load on some routers are extremely high, as shown the blue dash line in Figure \ref{fig:global-channel-traffic}.
+In this case, all the traffic are on the first half of the network (node id from 0 to $216+125+100-1=440$, group id from 0 to 13 ), causing local congestion and traffic load on some routers are extremely high, as shown the blue dash line in Figure \ref{fig:global-channel-traffic}.
 Thus the busy time of global channel is also the highest when contiguous placement coupled with minimal routing, as shown in Figure \ref{fig:global-channel-stime} the blue dash line.
 
-When contiguous placement is coupled with adaptive routing or progressive adaptive routing, the local congestion on global channel will be greatly alleviated, as shown in Figure \ref{fig:global-channel-traffic} the red and green dash line.
-Since both adaptive and progressive adaptive routing are congestion aware, and be able to utilize the idle routers on the other part of the network.
+When contiguous placement is coupled with (progressive) adaptive routing, the local congestion on global channel will be greatly alleviated, as shown in Figure \ref{fig:global-channel-traffic} the red and green dash line.
+Since (progressive) adaptive routing are congestion aware, and be able to utilize the idle routers on the other part of the network.
 The busy time of global channel are also reduce by using contiguous placement coupled with either adaptive or progressive adaptive routing, as shown in Figure \ref{fig:global-channel-stime} the red and green dash line.
 
-Random placement can randomly allocate the MPI ranks to the physical nodes all over the network, thus prevent the traffic from being congested certain part of the network.
-Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic go through global channels are quite uniformly distributed across all the routers in the network, thus no particular global channel will suffer high traffic burden.
+Random placement can randomly allocate the MPI ranks to the physical nodes all over the network, thus prevent certain part of the network from being congested by traffic.
+Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic go through global channels are uniformly distributed across all the routers in the network, thus no particular global channel will suffer high traffic burden.
 When the random placement coupled with minimal routing, the packets can avoid unnecessary intermediate forwarding as introduced by adaptive and progressive routing, which results in generating less traffic.
-That's why the blue solid line is lower than the red and green solid line, shown in figure\ref{fig:global-channel-traffic}.
-Since the random placement can uniformly distribute the workload traffic, there are no sudden surge of busy time of global channel over the network, shown as solid lines in Fgiure \ref{fig:global-channel-stime}.
+That's why the blue solid line is lower than the red and green solid line.
+Since the random placement can uniformly distribute the workload traffic, there are no sudden surge of busy time of global channel over the network, shown as solid lines in Figure \ref{fig:global-channel-stime}.
 
@@
 %terminal link traffic and busy time explanation
-The distribution of traffic go through terminal links stay unchanged no matter which placement and routing configuration are used, as shown in Figure \ref{fig:terminal-link-traffic}.
+The distribution of traffic go through terminal links stay unchanged no matter which placement \& routing configuration in use, as shown in Figure \ref{fig:terminal-link-traffic}.
 This is because only the location of each MPI rank in the network will be changed in different placement schemes, and the routing won't have effect the terminal link, so the traffic between compute node and the router won't change.
-Due to the traffic changes on global and local channels, the busy time of terminal links will also experience some variation when different placement and routing scheme configuration in use, as shown in Figure \ref{fig:terminal-link-stime}.
+Due to the traffic changes on global and local channels, the busy time of terminal links will experience variability when different routing schemes in use, as shown in Figure \ref{fig:terminal-link-stime}.
 
@@
 Contiguous placement allocates MPI ranks to physical nodes that are adjacent to each other, which confines the workload traffic to some local area when coupled with minimal routing.
-This may leads to hot-spot in local area and unbalanced network utilization.
+This may result in local congestion and unbalanced network utilization.
 As we can see from Figure \ref{fig:wkld-network-traffic} and \ref{fig:wkld-network-stime}, contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest busy time.
 
-Random placement allocates MPI ranks to a set of randomly selected nodes all over the system, which will uniformly distribute workload traffic and avoid local congestion.
+Random placement allocates MPI ranks to a set of randomly selected nodes all over the system, uniformly distributes workload traffic and avoids local congestion.
 When random placement is coupled with minimal routing, the packets will take the shortest path from source router to the destination router without routing to any intermediate routers, this will prevent the routing from generating extra traffic.
@@
 
+The random job placement coupled with either minimal or adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
+The workload performance get greatly improved with this configuration.
+However, when we isolated individual application from the workload, we unveil the fact that not every application can benefit from random job placement.
+
 % Start from here, we present the individual application analysis.
-The random job placement coupled with either minimal or adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
-The workload performance get greatly improved with these configurations.
-However, when we isolated individual application from the workload, we unveil the fact that not every application can benefit from random job placement.
-
 \subsection{Individual Application Analysis}
@@
 
-As shown in Figure \ref{fig:mg-commtime} \ref{fig:cr-commtime}, MG and CR suffer the longest communication time when running under the configuration of contiguous placement and minimal routing(CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing, both MultiGrid and CrystalRouter will get great improvement in terms of communication efficiency.
-Random placement will further reduce the communication time of MultiGrid and CrystalRouter, and reach the best performance when coupled with (progressive) adaptive routing.
-Both MultiGrid and CrystalRouter shows the same trend as the workload when running under different placement and routing configurations.
-
-However, AMG is quite an exception.
-As shown in Figure \ref{fig:amg-commtime}, the communication time of AMG is skyrocketing when it running under random placement coupled with (progressive) adaptive routing.
+As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MG and CR suffer the longest communication time when running with contiguous placement \& minimal routing (CM).
+When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), both MultiGrid and CrystalRouter will get great improvement, their communication time reduce a lot.
+Random placement will further reduce the communication time of MultiGrid and CrystalRouter, and reach the best performance when coupled with (progressive) adaptive routing (RPA, RA).
+Both MultiGrid and CrystalRouter shows the same trend as the workload when running under different placement \& routing configurations.
+
+AMG is quite an exception.
+As shown in Figure \ref{fig:amg-commtime}, the communication time of AMG is skyrocketing when it running under random placement coupled with (progressive) adaptive routing (RPA, RA).
 The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
-The performance of AMG running under contiguous placement coupled with minimal routing is no better than random coupled with minimal routing, but still much better than random with (progressive) adaptive routing.
+The performance of AMG running under contiguous placement coupled with minimal routing (CM) is no better than random coupled with minimal routing (RM), but still much better than random with (progressive) adaptive routing (RPA, RA).
 
@@
     \end{subfigure}%
-   \caption{Each Application Router Local Channel Traffic.  }
+   \caption{The traffic go through the local channels of routers that belongs to specific application.  }
    \label{fig:3app-lc-traffic}
 \end{figure*}
+
+% Show the evidence from network level, explain why AMG is different. 
+We look into network level to identify the culprit behind AMG's abnormal behavior with random placement \& adaptive routing.
+By identifying the terminal nodes each MPI rank resides on and routers that each application's traffic go through, we can see that the traffic go through the routers that belongs to AMG is skyrocketing when random placement \& adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}.
+Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
+
+No router will be shared between applications under contiguous placement.
+A set of successive groups will be allocated to each application under contiguous placement scheme.
+When contiguous placement coupled with minimal routing, application will be free of interference from its concurrently running peers.
+However, application communication traffic will be confined within their allocated routers, thus local congestion is very likely to happen depends on application communication intensity.
+As the lest communication intensive application in the workload, AMG can benefit from contiguous placement.
+Under contiguous placement, the traffic go through the local and global channels of the routers that belongs to AMG is significantly lower than random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
+
+MultiGrid and CrystalRouter are more communication intensive compared with AMG.
+They will suffer great amount local traffic in both local and global channels when contiguous placement is used, shown as the dash line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
+On the other hand, the random placement scheme can uniformly distribute their traffic all over the network by allocating randomly selected nodes to each MPI rank, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
 
@@
     \end{subfigure}%
-   \caption{Each Application Router Global Channel Traffic.}
+   \caption{The traffic go through the global channels of routers that belongs to specific application.}
    \label{fig:3app-gl-traffic}
@@
 
-% Show the evidence from network level, explain why AMG is different. 
-We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing.
-By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}.
-Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
-
-No router will be shared between applications under contiguous placement.
-A set of successive groups will be allocated to each application under contiguous placement scheme.
-When contiguous placement coupled with minimal routing, application will be free of interference from its running neighbors.
-However, application communication traffic will be confined within their allocated routers, thus local congestion is very likely to happen depends on application communication intensity.
-As the lest communication intensive application, AMG can benefit from contiguous placement.
-Under contiguous placement, the traffic go through the local and global channels of the routers that belongs to AMG is significantly lower than random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
-MultiGrid and CrystalRouter are more communication intensive compared with AMG.
-They will suffer great amount local traffic in both local and global channels when contiguous placement is used, shown as the dash line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-The random placement scheme can uniformly distribute their traffic all over the network by allocating randomly selected nodes to each MPI rank.
-
-The reason for AMG being the only victim from random placement and adaptive routing is due to  its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
-
-From the detailed analysis of three applications performance above, we know that random placement and adaptive routing is quite efficient for orchestrate the traffic load in the network.
-Random placement and adaptive routing can uniformly distribute the workload traffic all over the network, make the load-balanced and avoid hot-spots.
+So far we know that the reason for AMG being the only victim from random placement \& adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
+
+From the detailed analysis of three applications performance above, we know that random placement \& adaptive routing is quite efficient for orchestrate the traffic load in the network.
+Random placement \& adaptive routing can uniformly distribute the workload traffic all over the network, make the load-balanced and avoid hot-spots.
 However, application like AMG will be impaired in this orchestration.
@@
 These extra traffic are from other communication-intensive applications.
-Beneath the facade of harmony, less communication-intensive application are ``bullied" by their communication-intensive peers in the workload.
-
-We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations of the experiments, none of the congestion sensing scheme can prevent the ``bully" from happening.
+Beneath the facade of harmony, less communication-intensive application are ``bullied" by their concurrently running communication-intensive peers in the workload.
+
+We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.
 
@@
 
-In order to prove that AMG being bullied only because it is less communication-intensive than its running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
-We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with 6 different placement and routing configurations.
+In order to prove that AMG being bullied only because it is less communication-intensive than its concurrently running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with the same placement \& routing configurations.
 As shown in Figure \ref{fig:syn-3app-data-amount}, sAMG become the most communication-intensive application in the new workload.
@@
   \includegraphics[width = 0.48\textwidth ]{syn-wkld/wkld-commtime}
-  \caption{ Time spent on communication by Workload II when 6 different placement and routing scheme configurations are used.
-Random is better than contiguous in terms of improving communication efficiency.Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
+  \caption{ Time spent on communication by Workload II when using 6 different placement and routing scheme configurations.
+Random is better than contiguous in terms of improving communication efficiency.
+Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
 }
@@
 
-The communication time spent by parallel workload \Rmnum{2} under different placement and routing configuration shown in Figure \ref{fig:syn-wkld-commtime}.
-As the data transfer amount increased in the workload(due to sAMG), the time spent on communication under each configuration also increases.
-But the performance of each configuration still keep the same trend as parallwl workload \Rmnum{1}.
+The communication time spent by parallel workload \Rmnum{2} under different placement \& routing configurations shown in Figure \ref{fig:syn-wkld-commtime}.
+As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases.
+But the performance of each configuration still keep the same trend as parallel workload \Rmnum{1}.
 The contiguous placement coupled with minimal routing results in highest communication time.
 The random placement coupled with minimal routing is the most efficient.
-Progressive adaptive routing is better than adaptive when random placement is used.
-And they have comparable results when contiguous placement is used.
-
-\\ \TODO{Explain Figure }  \ref{fig:synwkld-network-traffic} \ref{fig:synwkld-network-stime}
+Progressive adaptive routing is better than adaptive routing when random placement is in use.
+And they have comparable results when coupled contiguous placement.
+
+Figure \ref{fig:synwkld-network-traffic}, \ref{fig:synwkld-network-stime} show the network status when Workload \Rmnum{2} running under different placement \& routing configurations.
+Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel.
+When coupled with (progressive) adaptive routing, the local congestion can get alleviated in contiguous placement.
+The random placement reach the comparable performance with any routing schemes in terms of both traffic and busy time.
+They are better than contiguous \& minimal configuration, but not too much improvement against contiguous\&(progressive) adaptive configuration.
 
@@
     \end{subfigure}%
-  \caption{Network Traffic. \textbf{More explanation to be added for this figure}}
+  \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
    \label{fig:synwkld-network-traffic}
@@
     \end{subfigure}%
-   \caption{Network Channel Busy Time. \textbf{More explanation to be added for this figure}}
+   \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
    \label{fig:synwkld-network-stime}
@@
 The ``bully" become the ``bullyee".
-The less communication-intensive applications in the workload this time are  MultiGrid and CrystalRouter.
+The less communication-intensive applications in Workload \Rmnum{2} are  MultiGrid and CrystalRouter.
 When random placement coupled with (progressive) adaptive routing is used, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
@@
 
-Contiguous placement coupled with minimal routing prevent applications from sharing network resource, and confine application communication traffic to their allocated routers.
+Contiguous placement coupled with minimal routing prevent applications from sharing network resource, and confine application communication traffic to the routers assigned to each application.
 This can guarantee the performance of less communication intensive applications like MultiGrid and CrystalRouter, and make the communication intensive application like sAMG severely deteriorate.
@@
 % explain the network status of sAMG, MG and CR
-We look into the network level to scrutinize the traffic went through the routers belongs to each application. 
-Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement and routing configuration is used.
+We look into the network level to scrutinize the traffic go through the routers belongs to each application. 
+Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement \& routing configuration in use.
 The traffic is skyrocketing in both local and global channels when contiguous placement coupled with minimal routing.
@@
 The traffic go through the local and global channels of the routers that belongs to MultiGrid are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic}.
-Although contiguous placement allocates all the MPI ranks in set of nodes in adjacent groups, causing possible local congestion, it will save MultiGrid's routers being shared by the traffic from its communication intensive peer, sAMG.
+Although contiguous placement allocates all the MPI ranks in set of nodes in adjacent groups, causing possible local congestion, it will stop MultiGrid's routers being shared by the traffic from its communication-intensive peer, sAMG.
 As random placement is used, the traffic go through both local and global channels are greatly increased.
@@
 \begin{itemize}
-    \item Random placement and adaptive routing can uniformly distribute workload traffic over the network, make the whole network load-balanced and hot-spot free. 
+    \item Random placement and adaptive routing can uniformly distribute workload traffic over the network, make the whole network load-balanced and hot-spots free. 
     \item Random placement and adaptive routing can not guarantee QoS for each application in the workload.
-In order to reach load-balanced and hot-spot free, the traffic from congested routers will be redirected to other less busy routers.
+In order to reach load-balanced and hot-spots free, the traffic from congested routers will be redirected to other less busy routers.
 This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.
     \item Contiguous placement and minimal routing guarantee a consistent performance of each application.
-Although, contiguous placement and minimal routing usually results in local congestion and hot-spot, it can reduce the interference between concurrently running applications, thus prevent less communication-intensive application from being ``bully" by its intensive peers.
+Although, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization, it can reduce the interference between concurrently running applications, thus prevent less communication-intensive application from being ``bullied" by its communication-intensive peers.
 \end{itemize}
 
-According to our findings, we believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity.
+We believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity.
 The less intensive applications should avoid sharing network resource with other applications, reduce the possible interference.
@@
 The impact of job placement to both system and application always catch researchers appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
-Skinner et al.\cite{dskinner} identified that network congestion could cause significant performance variability.
+Skinner et al.
+identified that network congestion could cause significant performance variability \cite{dskinner}.
 Bhatele et al.
-\cite{abhinav-sc13} studied the performance variability of a specific application, p3FD, running on different production system.
+studied the performance variability of a specific application, p3FD, running on different production system \cite{abhinav-sc13}.
 They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource.
-Jokanovic et al.\cite{jose-ipdps15} study the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing.
+Jokanovic et al.
+studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing \cite{jose-ipdps15}.
 
 Recently, several researchers have investigated the job placement and routing schemes on dragonfly network.
-Bogdan et al \cite{hoefler-hpdc14} proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network.
+Bogdan et al.
+proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network \cite{hoefler-hpdc14}.
 Jain et al.
-\cite{jain-sc14} conducted a comprehensive analysis of various job placement and routing scheme with regard to network link throughput on dragonfly network.
+conducted a comprehensive analysis of various job placement and routing scheme with regard to network link throughput on dragonfly network \cite{jain-sc14}.
 Their work is based on an analytical model and synthetic workload.
-Bhatele et al.\cite{bhatele-sc11} used simulation to study the performance of synthetic workload under the different task mapping and routing schemes on two-level direct networks.
+Bhatele et al.
+used simulation to study the performance of synthetic workload under the different task mapping and routing schemes on two-level direct networks \cite{bhatele-sc11}.
 
 Our work different from the previous works in the following ways.
-First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven real application traces collected from production system.
+First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system.
 Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
-We found that although random placement and adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation.
-Third, with the sophisticated simulation tool CODES, we can get not only applications communication information, but also we have the insight about the network status when application is running.
+We found that although random placement \& adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation.
+Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network status when application is running.
 The traffic and busy time of router's each link are valuable information for detailed analysis.
@@
 
-In this paper, we have conducted extensive study about application's behavior when it running on dragonfly network with different job placement and routing configurations.
-We resorted to CODES, a HPC network simulation tool with high fidelity, and used three parallel applications traces collected from production system to analysis the applications' behavior on network level.
-We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network, alleviate local congestion, the performance of certain application would be impaired.
-We identify this phenomenon as ``bully" between concurrently running jobs, and the victim always being the less communication-intensive application.
-On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, the configuration can guarantee the performance of ``bullee" application by limiting the network sharing between concurrently running application.
-
-Due the presence of this ``bully", we suggest that when the batch scheduler make job placement for workload on system with dragonfly network, random placement shouldn't be the rule of thumb.
+In this paper, we have conducted extensive study about application's behavior when running on dragonfly network with different job placement and routing configurations.
+We resorted to CODES, a high-fidelity HPC network simulation tool, and used three parallel scientific applications traces collected from production system to analysis the applications' behavior on network level.
+We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network to reach load balance and hot-spots free for the network, the performance of certain application would be impaired.
+We identify this phenomenon as ``bully" between concurrently running applications, and the victim always being the less communication-intensive one.
+On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, the configuration can guarantee the performance of ``bullee" application by limiting the network sharing between concurrently running peers.
+
+Due the presence of this ``bully", we suggest that when the batch scheduler make job placement for workload on dragonfly system, random placement shouldn't be the rule of thumb.
 Instead, the placement should made with consideration of jobs communication intensity.
 The less intensive application should get contiguous allocation coupled with adaptive routing, the intensive ones should get random allocation coupled with minimal routing.
-
 We believe the findings presented in this paper can illuminate a path to more efficient workload manager for future systems with dragonfly network.

### 2016-03-16 draft.tex
changes based on lan's comments

@@
 The low latency and high bandwidth interconnect network plays a critical role in improving HPC system performance.
-As the computing ability continue grows due to many-core nodes with accelerators, the network is now becoming a scare resources.
-HPC community start to explore the possible alternative to replace the commonly used Torus network.
-
-The high-radix, low-diameter dragonfly topology can lower the cost of interconnect network, improve network bandwidth, reduce the packets traverse latency.
-This make the dragonfly network an very promising choice for building multi-Petaflop/s supercomputers\cite{dally-dragonfly}.
-The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
-
-Even with such powerful network, the interference between concurrently running jobs and thus presumably job placement remains an major factor cause performance variability on dragonfly network\cite{bhatele2015, dskinner}.
+As the computing ability continue to grow due to many-core nodes with accelerators, the network is now becoming a scare resources.
+HPC community start to explore the new network topology to replace the commonly used torus-connected network.
+The high-radix, low-diameter dragonfly topology can lower the cost of interconnect network, improve network bandwidth, reduce the packets traverse latency \cite{dally-dragonfly}.
+This make the dragonfly network an very promising choice for building Petaflop and beyond supercomputers.
+%The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
+
+While dragonfly topology provides low-latency and high-bandwidth interconnected network, how to efficiently utilize it is greatly relying on the upper level system software.
+In particular, intelligent job placement to avoid interference is of paramount importance for guarantee the performance of concurrently running jobs that sharing network resources \cite{bhatele2015, dskinner}.
 Some research work suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
 
-This is paper, we study the interference between concurrently running jobs on dragonfly network with different job placement and routing schemes.
-Being unorthodox to most existing work that use synthetic workload, parallel scientific application traces that collected from production system are used in our study.
+In this work, we study the interference between concurrently running jobs on dragonfly network with different job placement and routing schemes.
+We use CODES, a HPC network simulation toolkit with high fidelity, excellent scalability for packet level simulation \cite{codes}.
+And being unorthodox to most existing work that use synthetic workload, we use traces of three representative applications from DOE Design Forward Project \cite{designforwardwebpage}.
 The advantage of using real application traces is quite obvious, these traces can capture application's communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity.
-Applicatoins usually are distinctive from each other in terms of  data transfer amount, communication pattern, operation dependency etc.
+Applications usually are distinctive from each other in terms of data transfer amount, communication pattern, operation dependency etc.
 which are impossible to reproduce in synthetic workload.
 
-%We also evaluate the network performance and jobs' performance when the Dragonfly network is configured with different job allocation strategies and routing algorithms.
-The job allocation strategies used in our study are Compact allocation and Random allocation, both of which can be seen in existing production HPC systems.
-The routing strategies been analyzed in this work are Minimal, Nonminimal and Adaptive.
-
-We made observation from our extensive study that, when dragonfly network is configured with random placement and adaptive routing scheme in order to reach hot-spots free and load balance, the performance of particular job(s) in the workload would suffer degradation.
+We conduct extensive experiments with three applications running on dragonfly network with two job placement schemes and three routing schemes.
+We analyze the applications' performance in terms of communication time when they running with different placement\& routing configuration.
+Our evaluation is based on more than 1000 runs of simulation.
+Through extensive simulation with application traces, we make several interesting observations.
+
+%We made observation from our extensive study that, when dragonfly network is configured with random placement and adaptive routing scheme in order to reach hot-spots free and load balance, the performance of particular job(s) in the workload would suffer degradation.
 The communication intensive jobs in the workload can benefit from random placement and adaptive routing, with great performance improvement.
@@
 
-The findings in this work also reconfirm that interference between concurrently running jobs would make the performance of some jobs very unpredictable.
+\begin{itemize}
+
+    \item Random placement coupled with adaptive routing can not guarantee the performance of every job in the workload.
+The hot-spots free and load-balanced network status reached by using random placement with adaptive routing come with the cost of less communication-intensive jobs performance degradation.
+
+    \item We identify the ``bully" behavior happening between concurrently running jobs on dragonfly network when random placement \& adaptive routing in use.
+Random placement \& adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resource such as local and global channel bandwidth, slow down the communication of those less intensive jobs.
+
+    \item We found that contiguous placement \& minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may result in local network congestion and unbalanced network utilization.
+Contiguous placement \& minimal routing are preferred by less communication-intensive jobs, since it will prevent them from being ``bullied" by other communication-intensive jobs.
+
+\end{itemize}
+
+These observations also reconfirm that interference between concurrently running jobs would make the performance of some jobs very unpredictable.
 The detailed analysis about the traffic and congestion in network level unveil the undercurrent beneath that interference.
-This work makes the following contributions:
-
-\begin{itemize}
-
-    \item Our real trace-based analysis about job interference on dragonfly network, shows that random placement with adaptive routing can not guarantee the performance of every job in the workload.
-The hot-spots free and load-balanced reached by using random placement with adaptive routing come with the cost of less communication-intensive jobs performance degradation.
-
-    \item We identify the ``bully" behavior happening between concurrently running jobs on dragonfly network when random placement and adaptive routing in use.
-Random placement and adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resource such as local and global channel bandwidth, slow down the communication of those less intensive jobs.
-
-    \item We found that contiguous placement and minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may result in hot-spots and local network congestion.
-Actually, contiguous placement and minimal routing are preferred by communication-less-intensive jobs, since it will prevent them from being ``bullied" by other communication-intensive jobs.
-
-\end{itemize}
-
-To the best of our knowledge, using parallel application traces from production system for the study of job interference on dragonfly network has not been reported so far.
-We believe the observations and analysis presented in this paper can be used by computing facilities to choose job placement and routing strategies wisely for their future dragonfly interconnected system.
-The conclusion from this paper would be useful for workload manager in dragonfly system to make better scheduling decisions for jobs with distinctive communication behavior.
+
+To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly network has not been reported so far.
+We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing facility, system software development, and system administration.
+The computing facility should choose the configuration for dragonfly network implementation with consideration about resource sharing between concurrently running jobs.
+The workload manager would come up with better scheduling algorithm for jobs with distinctive communication behavior.
+And the system administration would be more efficient with the knowledge about jobs running status under different placement and routing configuration.
+
+The rest of this paper is organized as follows.
+Section \ref{sec:background} describes the dragonfly network and the placement \& routing schemes.
+Section \ref{sec: methodology} talks about the use of CODES as research vehicle and three representative applications from DOE Design Forward Project.
+Section \ref{sec:workload-1} presents the analysis of three applications running on dragonfly network with different placement \& routing configuration.
+Section \ref{sec:workload-2} validates the observations we get in section \ref{sec:workload-1}.
+Section \ref{sec:related work} discusses related work.
+Finally, the conclusion is presented in Section \ref{sec:conclusion}.
 
@@
 \label{sec:background}
-The dragonfly network is promising alternative for connecting a large number of nodes for its high-radix and low-diameter topology\cite{dally-dragonfly} \cite{kim-micro} \cite{faanes}.
-However, even with such powerful network, the job placement and routing could still be important factor that impact application's performance.
-
-\subsection{Dragonfly Network Overview}
+
+In this section, we talk about the Dragonfly topology and one of its implementation. We also present the placement and routing schemes  used on dragonfly network.
+
+\subsection{Dragonfly Network}
 \label{sec:network}
@@
 Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g $.
-Figure \ref{fig:dragonfly overview} illustrated an implementation of dragonfly network follows such configuration.
+Figure \ref{fig:dragonfly-overview} illustrated an implementation of dragonfly network follows such configuration.
 There are 6 routers in each group, each router has 3 compute nodes attached to it.
@@
 }
-  \label{fig:dragonfly overview}
+  \label{fig:dragonfly-overview}
 \end{figure}
 
-\subsection{Job Placement}
-\label{sec:placement-routing}
-
-Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by each job for execution.
+\subsection{Job Placement on Dragonfly}
+\label{sec:placement-schemes}
+
+For a parallel application requiring multiple compute nodes, job placement refers to the process of assigning the tasks of the application onto the system by a system software such as batch scheduler \cite{xu-cluster14}.
+In this work, we study two well cited placement policies for dragonfly systems:
+
+%Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by each job for execution.
 As studied by several researchers, the job placement could be an important factor that impact application performance \cite{hoefler-hpdc14} \cite{bhatele-sc11} \cite{jain-sc14}.
@@
 \textbf{Contiguous Placement:} In this scheme, the nodes will first be indexed consecutively in an increasing order of their group id and router id.
-The schedul assign each job required number of nodes by cutting chunks of nodes from the sequentially ordered list, as illustrated in Figure \ref{fig: dragonfly overview} as blue nodes assigned to job\_2.
+The schedul assign each job required number of nodes by cutting chunks of nodes from the sequentially ordered list, as illustrated in Figure \ref{fig:dragonfly-overview} as blue nodes assigned to job\_2.
 The nodes been allocated to the same job will be adjacent to each other, usually they are attached to the same router or in the same group, depends on the size of the job.
@@
 \textbf{Random Placement:} In this scheme, job will get a set of nodes that randomly selected from all the available nodes in the system.
-The nodes allocated to each job would be attached to different routers in different groups, as illustrated in Figure \ref{fig: dragonfly overview} the red nodes assigned to job\_1.
+The nodes allocated to each job would be attached to different routers in different groups, as illustrated in Figure \ref{fig:dragonfly-overview} the red nodes assigned to job\_1.
 Some routers may be shared by different applications when using random placement.
@@
 
-\subsection{Routing Schemes}
-\label{sec:routing}
-
-The implemented routing schemes in CODES dragonfly network model are based on the routing algorithm proposed by Kim et al.
-\cite{dally-dragonfly} and Jiang et al.
-\cite{jiang}.
-Three routing schemes are studied in this work are \emph{Minimal}, \emph{Adaptive} and \emph{Progressive Adaptive}.
+\subsection{Routing on Dragonfly}
+\label{sec:routing-schemes}
+The routing scheme refers to the strategy adopted to route messages from the source router to the destination router.
+The well studied routing schemes for dragonfly network include minimal routing, adaptive routing \cite{dally-dragonfly}, and progressive adaptive routing\cite{jiang}, and some of their variations \cite{won-prog-adaptive}.
+In this work we study three widely adopted routing mechanisms in dragonfly systems
 
 \textbf{Minimal:} When the network deploy minimal routing, a message from source router will take the the shortest path to the destination router.
-When there are multiple shortest paths between the rource and destination router, the message will be evenly divided among the paths.
+When there are multiple shortest paths between the source and destination router, the message will be evenly divided among the paths.
 Minimal routing can guarantee the minimum hops the message takes from source to destination.
@@
 \subsection{Simulation Tool}
-A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.
-CODES supports dragonfly network with packet-level high-fidelity simulation\cite{codes-dragonfly}.
-It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.
-
-\subsection{Application Traces}
+\label{sec:simulation-tool}
+A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability \cite{codes}.
+CODES supports dragonfly network with packet-level high-fidelity simulation\cite{codes-dragonfly} \cite{misbah-tpds}.
+It can take real MPI application traces generated by SST DUMPI\cite{sst} to drive CODES network model.
+In this work, we focus on an in-depth analysis of interference  with different job placement \& routing schemes on dragonfly network.
+
+\subsection{Parallel Applications}
 \label{sec: application traces}
@@
 
-AMG: The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
+\textbf{AMG:} The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
 It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.
@@
 
-MultiGrid:  geometric multi-grid v-cycle from the production elliptic solver BoxLib, a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
+\textbf{MultiGrid:}  geometric multi-grid v-cycle from the production elliptic solver BoxLib, a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
 It is widely used for structured grid physics packages.
@@
 
-CrystalRouter: the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}.
+\textbf{CrystalRouter:} the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}.
 It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.
@@
 
-\subsection{Simulation Configuration}
+\subsection{System Configuration}
 \label{sec: simulation configuration}
@@
 
-We focus on the study of two placement schemes and three routing schemes, so there will be 6 different placement\&routing configurations, as listed in Table \ref{tab: placement routing configs}.
-In this work, we enable the applications running on dragonfly network under different placement and routing configurations, and scrutinize the application's performance and network behavior in different running scenarios.
-
-In our experiments, the workload running on the dragonfly network under 6 different placement and routing configurations as listed in Table \ref{tab: placement routing configs}.
-We focus on the analysis of network status while the workload is running, as well as the performance of each individual application.
-We collected the following result data from the experiments:
+In this work we simulate and analyze six combinations of placement policies and routing schemes, which are summarized in Table ref{tab: placement routing configs}.
+Our analysis focuses on both overall network workload and individual application performance.
+For overall workload analysis, we focus on the time spent on communication by the workload, the network traffic throughput and busy time of links and channels.
+For individual application analysis, we study the time spent on communication by each MPI rank, traffic and busy time of each router that belongs to specific application.
+In our experiments, we collect and analyze the following data:
 
@@
     \item router global channel traffic and busy time.
-    \item The time spend on communication for each MPI rank. 
+    \item communication time spent by each MPI rank. 
 \end{itemize}
 
-The results of random placement shown in the following experiments are collected from extensive runs of different random placements, which can eliminate the possibility of variation.
-
-\section{Parallel Workload \Rmnum{1 }}
-\label{sec: workload 1 overview}
+With respect to random placement, we conduct a number of random runs, which are used to eliminate the possibility of variation.
+
+%\subsection{Workload Combinations}
+%\label{sec:workload-combination}
+%
+%We come up with two parallel workloads.
+The first workload consists of the original application traces described in Section \ref{sec: application traces}, while the second workload is a modified version of the first workload for the purpose of validation.
+
+\section{Study of Parallel Workload \Rmnum{1 }}
+\label{sec:workload-1}
 
@@
 
-From the detailed analysis of three applications performance above, we know that random placement \& adaptive routing is quite efficient for orchestrate the traffic load in the network.
-Random placement \& adaptive routing can uniformly distribute the workload traffic all over the network, make the load-balanced and avoid hot-spots.
+\subsection{Key Findings}
+We can get the following key findings from the detailed analysis of three applications.
+
+\emph{Random placement \& adaptive routing is quite efficient for orchestrate the traffic load in the network by uniformly distributing the workload traffic all over the network.
 However, application like AMG will be impaired in this orchestration.
@@
 Beneath the facade of harmony, less communication-intensive application are ``bullied" by their concurrently running communication-intensive peers in the workload.
+}
+
+\emph{Random placement \& adaptive routing can not guarantee QoS for each application in the workload.
+In order to reach load-balanced and hot-spots free, the traffic from congested routers will be redirected to other less busy routers.
+This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.}
+
+\emph{Contiguous placement \& minimal routing guarantee a consistent performance of each application.
+Although, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization, it can reduce the interference between concurrently running applications, thus prevent less communication-intensive application from being ``bullied" by its communication-intensive peers.}
 
@@
 \section{Parallel Workload \Rmnum{2 }}
+\label{sec:workload-2}
 
@@
 
-\section{Summary}
-
-Based on the results we got from both real application traces and synthetic workload, we can make the following observations:
-
-\begin{itemize}
-    \item Random placement and adaptive routing can uniformly distribute workload traffic over the network, make the whole network load-balanced and hot-spots free. 
-    \item Random placement and adaptive routing can not guarantee QoS for each application in the workload.
+\subsection{Key Finding}
+Our study with synthetic workload confirms that the ``bully" behavior among concurrently running applications would happen when two conditions are satisfied.
+
+\emph{First, the placement \& routing configuration allows network resource sharing between concurrently running applications.
+Random placement enables the router sharing and adaptive routing enables local and global channel sharing.}
+
+\emph{Second, there are variance in terms of communication intensity between concurrently running applications.
+In workload \Rmnum{1}, AMG has the least amount of communication traffic compared with MultiGrid and CrystalRouter and it become the ``bullee".
+In workload \Rmnum{2}, sAMG has the most amount of communication traffic, which makes it the ``bully".
+}
+
+We can stop this ``bully" by making either one of these conditions invalid.
+
+%\section{Summary}
+%Based on the results we got from both real application traces and synthetic workload, we can make the following observations:
+%
+%\begin{itemize}
+%    \item Random placement and adaptive routing can uniformly distribute workload traffic over the network, make the whole network load-balanced and hot-spots free. 
+%    \item Random placement and adaptive routing can not guarantee QoS for each application in the workload.
 In order to reach load-balanced and hot-spots free, the traffic from congested routers will be redirected to other less busy routers.
 This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.
-    \item Contiguous placement and minimal routing guarantee a consistent performance of each application.
+%    \item Contiguous placement and minimal routing guarantee a consistent performance of each application.
 Although, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization, it can reduce the interference between concurrently running applications, thus prevent less communication-intensive application from being ``bullied" by its communication-intensive peers.
-\end{itemize}
-
-We believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity.
+%\end{itemize}
+
+%We believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity.
 The less intensive applications should avoid sharing network resource with other applications, reduce the possible interference.
@@
 
-The communication-intensive applications tend to cause local congestion.
+%The communication-intensive applications tend to cause local congestion.
 It is preferable to enable communication-intensive applications to have extra network resource by sharing with other applications.
@@
 
-So the ideal placement and routing strategies for workload running on dragonfly network should be like this.
+%So the ideal placement and routing strategies for workload running on dragonfly network should be like this.
 The communication-intensive applications should be randomly allocated over the system and adaptive routing should be used by these applications to alleviate the local congestion.
@@
 
-% \vspace{5\baselineskip}
-% 
-% \begin{framed}
-% The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
+ \vspace{5\baselineskip}
+
+ \begin{framed}
+ The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
 Argonne, a U.S.
@@
 Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
-% \end{framed}
+ \end{framed}
 

### 2016-03-19 draft.tex
update all the figures

@@
 Overall, there are 264 routers and 1056 compute nodes in the network.
-The bandwidth of both terminal links and local channel are set to 2GB/s, the global channel bandwidth is set to 4GB/s.
+The ratio between aggregrated local and global channel bandwidth are set propotional to the Cray Cascade system\cite{faanes} based on the dragonfly topology\cite{dally-dragonfly}.
 
@@
 The first workload consists of the original application traces described in Section \ref{sec: application traces}, while the second workload is a modified version of the first workload for the purpose of validation.
-
-\section{Study of Parallel Workload \Rmnum{1 }}
-\label{sec:workload-1}
-
-The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces}.
-The details of this workload shown in Table \ref{tab: parallel workload-1}.
+\subsection{Workload Summary}
+\label{sec:workload summary}
+
+Workload \Rmnum{1} comprises the original AMG, MultiGrid and CrystalRouter.
+As we see in Table \ref{tab:apps-detail}, AMG has the least amount of data transfer, thus contributes the least amount of traffic in Wrokload \Rmnum{1}.
+
+Workload \Rmnum{2} comprises sAMG, MultiGrid and CrystalRouter.
+sAMG consists of synthetic traces that are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+The traffic from sAMG is the dominant in Workload \Rmnum{2}.
 
@@
 \begin{center}
-\caption{Details of Parallel Workload \Rmnum{1 }.} 
-\label{tab: parallel workload-1}
+\caption{Details of Application Traces.} 
+\label{tab:apps-detail}
 %\centering % Centers the table on the page, comment out to left-justify
@@
 CrystalRouter  &   100  &  35MB    &     3500MB\\ 
-
+\midrule
+sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
 \midrule % In-table horizontal line
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width = 0.48\textwidth ]{data_amount}
-  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with MultiGrid and CrystalRouter.\NOTE{y axis in log?} }
-  \label{fig:3app-data-amount}
-\end{figure}
-
-Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application.
+\section{Study of Parallel Workload \Rmnum{1 }}
+\label{sec:workload-1}
+
+% The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces}.
+The details of this workload shown in Table \ref{tab: parallel workload-1}.
+
+% 
+% \begin{figure}[h!]
+%   \centering
+%   \includegraphics[width = 0.48\textwidth ]{data_amount}
+%   \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with MultiGrid and CrystalRouter.\NOTE{y axis in log?} }
+%   \label{fig:3app-data-amount}
+% \end{figure}
+% 
+% Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application.
 Based on this figure, we can tell that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive.
-
-\subsection{Workload Analysis}
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width = 0.48\textwidth ]{wkld/wkld-commtime}
-  \caption{Time spent on communication by Workload I when 6 different placement and routing configurations are used.
+% 
+% 
+% \subsection{Workload Analysis}
+%  
+% \begin{figure}[h!]
+%   \centering
+%   \includegraphics[width = 0.48\textwidth ]{wkld/wkld-commtime}
+%   \caption{Time spent on communication by Workload I when 6 different placement and routing configurations are used.
 Random is better than contiguous in terms of improving communication efficiency.
@@
 }
-  \label{fig:wkld-commtime}
-\end{figure}
-
-The communication time spent by parallel workload \Rmnum{1} under different placement and routing configuration shown in Figure \ref{fig:wkld-commtime}.
+%   \label{fig:wkld-commtime}
+% \end{figure}
+
+\begin{table}[ht]
+\begin{center}
+\caption{Time spent on communication (MilliSecond) by Workload II when 6 different placement\&routing configuration in use.} 
+\label{tab:wkld-commtime}
+%\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c c c c }
+\toprule % Top horizontal line
+\toprule
+&\multicolumn{6}{c}{Placement\&Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-7}
+	 & CM & CA & CPA & RM & RA & RPA \\ % Column names row
+\midrule % In-table horizontal line
+Runtime  &  1870 & 1250 & 1248 & 860 & 835 &830\\ % Content row 1
+
+\midrule % In-table horizontal line
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\end{center}
+\end{table}
+
+The communication time spent by parallel workload \Rmnum{1} under different placement and routing configuration shown in Table \ref{tab:wkld-commtime}.
 The contiguous placement coupled with minimal routing results in highest communication time.
@@
         \label{fig:global-channel-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
         \label{fig:local-channel-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
         \label{fig:terminal-link-traffic}
-    \end{subfigure}%
-  \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration. }
-   \label{fig:wkld-network-traffic}
-\end{figure*}
-
-\begin{figure*}[t!]
+    \end{subfigure}\\
+
     \centering   
@@
         \label{fig:global-channel-stime}
-    \end{subfigure}%
+    \end{subfigure}\hfill
      \hspace{1em}%
@@
         \label{fig:local-channel-stime}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
     \end{subfigure}%
-   \caption{The busy time of links in different level in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration.}
-   \label{fig:wkld-network-stime}
+   \caption{Traffic and saturated time of links in different level in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration.}
+   \label{fig:wkld-network-traffic-stime}
 \end{figure*}
 
-Figure \ref{fig:wkld-network-traffic} shows the amount of traffic go through terminal links, local channels and global channels when the workload running on dragonfly network with 6 different placement and routing configurations, and Figure \ref{fig:wkld-network-stime} shows the corresponding busy time.
+Figure \ref{fig:wkld-network-traffic-stime} shows the amount of traffic go through terminal links, local channels and global channels, and the corresponding saturated time when the workload running on dragonfly network with 6 different placement and routing configurations
 
@@
 This may result in local congestion and unbalanced network utilization.
-As we can see from Figure \ref{fig:wkld-network-traffic} and \ref{fig:wkld-network-stime}, contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest busy time.
+Contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest busy time.
 
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[t]
     \centering
@@
         \label{fig:amg-lc-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
         \label{fig:mg-lc-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \begin{subfigure}[t]{0.32\textwidth}
@@
         \label{fig:cr-lc-traffic}
+    \end{subfigure}\\
+
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{amg/gc-traffic}
+        \caption{AMG Global Channel Traffic}
+        \label{fig:amg-gc-traffic}
+    \end{subfigure}\hfill
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{mg/gc-traffic}
+        \caption{MG Global Channel Traffic}
+        \label{fig:mg-gc-traffic}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{cr/gc-traffic}
+        \caption{CR Global Channel Traffic}
+        \label{fig:cr-gc-traffic}
     \end{subfigure}%
-   \caption{The traffic go through the local channels of routers that belongs to specific application.  }
-   \label{fig:3app-lc-traffic}
+   \caption{The traffic go through the local and global channels of routers that belongs to specific application.}
+   \label{fig:3app-lc-gc-traffic}
 \end{figure*}
@@
 
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{amg/gc-traffic}
-        \caption{AMG Global Channel Traffic}
-        \label{fig:amg-gc-traffic}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:mg-gc-traffic}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:cr-gc-traffic}
-    \end{subfigure}%
-   \caption{The traffic go through the global channels of routers that belongs to specific application.}
-   \label{fig:3app-gl-traffic}
-\end{figure*}
-
 So far we know that the reason for AMG being the only victim from random placement \& adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
@@
 
+In order to prove that AMG being bullied only because it is less communication-intensive than its concurrently running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with the same placement \& routing configurations.
+As shown in Table \ref{tab:apps-detail}, sAMG become the most communication-intensive application in the new workload.
+
+\subsection{Workload Analysis}
+
 \begin{table}[ht]
 \begin{center}
-\caption{Details of Parallel Workload \Rmnum{2 }.} 
-\label{tab: parallel workload-2}
+\caption{Time spent on communication (MilliSecond) by Workload II when 6 different placement\&routing configuration in use.} 
+\label{tab:syn-wkld-commtime}
 %\centering % Centers the table on the page, comment out to left-justify
-\begin{tabular}{l c c c }
+\begin{tabular}{l c c c c c c }
 \toprule % Top horizontal line
 \toprule
-&\multicolumn{3}{c}{Application Details} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
-\cmidrule(l){2-4}
-App Name & num. rank & Data per Rank & Total Data\\ % Column names row
+&\multicolumn{6}{c}{Placement\&Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-7}
+	 & CM & CA & CPA & RM & RA & RPA \\ % Column names row
 \midrule % In-table horizontal line
-sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
-\midrule
-MultiGrid  &    125 &   5MB   &     625MB\\ 
-\midrule
-CrystalRouter  &   100  &  35MB    &     3500MB\\
+Runtime  &  6123 & 3231 & 3725 & 2544 & 3701 & 3228 \\ % Content row 1
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width = 0.48\textwidth ]{syn-wkld/data_amount}
-  \caption{Applications Data Transfer Amount. sAMG has the most amount of data transfer, compared with CR and MG.}
-  \label{fig:syn-3app-data-amount}
-\end{figure}
-
-In order to prove that AMG being bullied only because it is less communication-intensive than its concurrently running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
-We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with the same placement \& routing configurations.
-As shown in Figure \ref{fig:syn-3app-data-amount}, sAMG become the most communication-intensive application in the new workload.
-
-\subsection{Workload Analysis}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width = 0.48\textwidth ]{syn-wkld/wkld-commtime}
-  \caption{ Time spent on communication by Workload II when using 6 different placement and routing scheme configurations.
-Random is better than contiguous in terms of improving communication efficiency.
-Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
-}
-  \label{fig:syn-wkld-commtime}
-\end{figure}
-
-The communication time spent by parallel workload \Rmnum{2} under different placement \& routing configurations shown in Figure \ref{fig:syn-wkld-commtime}.
+The communication time spent by parallel workload \Rmnum{2} under different placement \& routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
 As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases.
@@
 
-Figure \ref{fig:synwkld-network-traffic}, \ref{fig:synwkld-network-stime} show the network status when Workload \Rmnum{2} running under different placement \& routing configurations.
+Figure \ref{fig:synwkld-network-traffic-stime} show the network status when Workload \Rmnum{2} running under different placement \& routing configurations.
 Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel.
@@
         \label{fig:synwkld-global-channel-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
         \label{fig:synwkld-local-channel-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
         \label{fig:synwkld-terminal-link-traffic}
-    \end{subfigure}%
-  \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
-   \label{fig:synwkld-network-traffic}
-\end{figure*}
-
-\begin{figure*}[t!]
-    \centering   
+    \end{subfigure}\\
+
     \begin{subfigure}[t]{0.32\textwidth}
@@
         \label{fig:synwkld-global-channel-stime}
-    \end{subfigure}%
+    \end{subfigure}\hfill
      \hspace{1em}%
@@
         \label{fig:synwkld-local-channel-stime}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
     \end{subfigure}%
-   \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
-   \label{fig:synwkld-network-stime}
+   \caption{Traffic and Saturated Time of different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
+   \label{fig:synwkld-network-traffic-stime}
 \end{figure*}
@@
         \label{fig:syn-samg-lc-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
         \label{fig:syn-mg-lc-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \begin{subfigure}[t]{0.32\textwidth}
@@
         \label{fig:syn-cr-lc-traffic}
-    \end{subfigure}%
-   \caption{Each Application Router Local Channel Traffic.  }
-   \label{fig:syn-3app-lc-traffic}
-\end{figure*}
-
-\begin{figure*}[t!]
+    \end{subfigure}\\
     \centering
@@
         \label{fig:syn-samg-gc-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \hspace{1em}%
@@
         \label{fig:syn-mg-gc-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
     \begin{subfigure}[t]{0.32\textwidth}
@@
     \end{subfigure}%
-   \caption{Each Application Router Global Channel Traffic.}
+   \caption{Each Application Router Local and Global Channel Traffic.}
    \label{fig:syn-3app-gc-traffic}

### 2016-03-20 draft.tex
add a few missing word
add figs with hybrid placement

@@
 % Do not put math or special symbols in the title.
-\title{Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network}
+\title{Watch Out for the Bully! Job Interference Study on Dragonfly Network}
 
@@
 
-In this work we simulate and analyze six combinations of placement policies and routing schemes, which are summarized in Table ref{tab: placement routing configs}.
+In this work we simulate and analyze six combinations of placement policies and routing schemes, which are summarized in Table \ref{tab: placement routing configs}.
 Our analysis focuses on both overall network workload and individual application performance.
@@
 
-With respect to random placement, we conduct a number of random runs, which are used to eliminate the possibility of variation.
+With respect to random placement, we conduct our experiment with a set of distinctive random allocation, which are intended to eliminate the possibility of variation.
 
@@
 
-\section{Study of Parallel Workload \Rmnum{1 }}
+% \section{Study of Parallel Workload \Rmnum{1 }}
+\section{Identify the ``Bully"}
 \label{sec:workload-1}
@@
         \centering
-        \includegraphics[height=1.5 in]{amg/commtime}
+        \includegraphics[height=1.5 in]{wkld/amg/commtime}
         \caption{AMG Communication Time}
@@
         \centering
-        \includegraphics[height=1.5 in]{mg/commtime}
+        \includegraphics[height=1.5 in]{wkld/mg/commtime}
         \caption{MG Communication Time}
@@
         \centering
-        \includegraphics[height=1.5 in]{cr/commtime}
+        \includegraphics[height=1.5 in]{wkld/cr/commtime}
         \caption{CR Communication Time}
@@
         \centering
-        \includegraphics[height=1.8 in]{amg/lc-traffic}
+        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
         \caption{AMG Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{mg/lc-traffic}
+        \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
         \caption{MG Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{cr/lc-traffic}
+        \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
         \caption{CR Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{amg/gc-traffic}
+        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
         \caption{AMG Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{mg/gc-traffic}
+        \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
         \caption{MG Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{cr/gc-traffic}
+        \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
         \caption{CR Global Channel Traffic}
@@
     \end{subfigure}%
-   \caption{The traffic go through the local and global channels of routers that belongs to specific application.}
+   \caption{The traffic go through the local and global channels of routers that belong to specific application.}
    \label{fig:3app-lc-gc-traffic}
@@
 
-\emph{Random placement \& adaptive routing is quite efficient for orchestrate the traffic load in the network by uniformly distributing the workload traffic all over the network.
+\emph{Random placement \& adaptive routing is quite efficient for orchestrating the traffic load in the network by uniformly distributing the workload traffic all over the network.
 However, application like AMG will be impaired in this orchestration.
-The routers through which the less communication-intensive application traffic used to route, now have more traffic go through them.
-These extra traffic are from other communication-intensive applications.
 Beneath the facade of harmony, less communication-intensive application are ``bullied" by their concurrently running communication-intensive peers in the workload.
@@
 
-\emph{Random placement \& adaptive routing can not guarantee QoS for each application in the workload.
-In order to reach load-balanced and hot-spots free, the traffic from congested routers will be redirected to other less busy routers.
+% The routers through which the less communication-intensive application traffic used to route, now have more traffic go through them.
+These extra traffic are from other communication-intensive applications.
+
+\emph{Random placement \& adaptive routing can not guarantee the qualify of service for each application in the workload.
+In order to reach load-balanced and hot-spots free over the whole network, the traffic from congested routers will be redirected to other less busy routers.
 This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.}
@@
 
-\section{Parallel Workload \Rmnum{2 }}
+% \section{Parallel Workload \Rmnum{2 }}
+\section{``Bully" become ``Bullee"}
 \label{sec:workload-2}
@@
     \end{subfigure}%
-   \caption{Each Application Router Local and Global Channel Traffic.}
+   \caption{The traffic go through the local and global channels of routers that belong to specific application.}
    \label{fig:syn-3app-gc-traffic}
@@
 
-\emph{Second, there are variance in terms of communication intensity between concurrently running applications.
+\emph{Second, there are difference in terms of communication intensity between concurrently running applications.
 In workload \Rmnum{1}, AMG has the least amount of communication traffic compared with MultiGrid and CrystalRouter and it become the ``bullee".
@@
 
-We can stop this ``bully" by making either one of these conditions invalid.
+We can stop this ``bully" by making both conditions invalid.
+
+\section{Stop the ``Bully"}
+
+The solution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs.
+Using contiguous placement\& minimal routing could be a way avoid network sharing, but both the workload and network performance could suffer degradation due to local congestion.
+It is also unrealistic to use different routing scheme for each application with regard to its communication intensity, since routing scheme is pre-configured in the system and can not be changed on the fly.
+However, the job placement can be versatile to assign different allocation (contiguous or random) to specific application.
+
+Thus, we propose the hybrid placement as a reconcile solution.
+In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation.
+We evaluate the performance of hybrid placement\&routing configurations with parallel Workload \Rmnum{1}.
+AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation.
+
+Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing, together with other configurations.
+As we see from Figure \ref{fig:hyb-plcmt-amg-commtime},
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
+        \caption{AMG Communication Time}
+        \label{fig:hyb-plcmt-amg-commtime}
+    \end{subfigure}\hfill
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
+        \caption{MG Communication Time}
+        \label{fig:hyb-plcmt-mg-commtime}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
+        \caption{CR Communication Time}
+        \label{fig:hyb-plcmt-cr-commtime}
+    \end{subfigure}%
+   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement\& routing configurations. }
+   \label{fig:hyb-plcmt-apps-commtime}
+\end{figure*}
 

### 2016-03-20 draft.tex
add new section--Stop the Bully

@@
 
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
+        \caption{AMG Communication Time}
+        \label{fig:hyb-plcmt-amg-commtime}
+    \end{subfigure}\hfill
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
+        \caption{MG Communication Time}
+        \label{fig:hyb-plcmt-mg-commtime}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
+        \caption{CR Communication Time}
+        \label{fig:hyb-plcmt-cr-commtime}
+    \end{subfigure}%
+   \caption{Application communication time.
+Three applications running concurrently on dragonfly network with different placement\& routing configurations.
+\textbf{HM, HA, HPA} denote hybrid placement coupled with minimal, adaptive and progressive adaptive routing respectively.
+}
+   \label{fig:hyb-plcmt-apps-commtime}
+\end{figure*}
+
 Thus, we propose the hybrid placement as a reconcile solution.
@@
 AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation.
-
-Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing, together with other configurations.
-As we see from Figure \ref{fig:hyb-plcmt-amg-commtime},
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
-        \caption{AMG Communication Time}
-        \label{fig:hyb-plcmt-amg-commtime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
-        \caption{MG Communication Time}
-        \label{fig:hyb-plcmt-mg-commtime}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
-        \caption{CR Communication Time}
-        \label{fig:hyb-plcmt-cr-commtime}
-    \end{subfigure}%
-   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement\& routing configurations. }
-   \label{fig:hyb-plcmt-apps-commtime}
-\end{figure*}
+Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing schemes, together with other configurations.
+
+MultiGrid and CrystalRouter have basically the same performance with hybrid placement compared against random placement.
+Since they get random allocation in the hybrid placement scheme.
+AMG being improved a lot when hybrid placement in use.
+Compared with ``RA" and ``RPA", ``HA" and ``HPA" can significantly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}.
+This is due the contiguous allocation AMG gets in the hybrid placement scheme.
+AMG doesn't share router with other applications.
+However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter is still being redirected to the groups where AMG resides.
+Since AMG is less communication-intensive and can not fully utilize network bandwidth, it is likely that the intermediate routers pick for the traffic from MultiGrid and CrystalRouter are from AMG's group.
 
@@
 
- \vspace{5\baselineskip}
+ \vspace{1\baselineskip}
 

### 2016-03-26 draft.tex
add a missing sentence
made changes based on John's comments

@@
 
-The high-radix, low-diameter dragonfly topology network will be the choice of many computing facilities for building their next generation supercomputers.
-Preliminary study shows that random placement with adaptive routing should be the rule of thumb to utilize such powerful network, since random placement can uniformly distribut traffic over the network, and adaptive routing can alleviate congestion.
-However, in this paper, we made the observation that although random placement coupled with adaptive routing can reach load-balanced over the network when multiple jobs running concurrently, it can not guarantee the best performance for each single job.
-The performance improvement of communication intensive jobs comes with sacrifice of those less intensive jobs.
+The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers.
+Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks, since random placement with adaptive routing can uniformly distribute traffic over the network and alleviate congestion.
+However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network when multiple jobs are running concurrently, they can not guarantee the best performance for each single job.
+The performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs.
 We refer this phenomenon as ``bully" between concurrently running jobs.
-We analyze the detailed reason behind this ``bully" behavior between jobs from the underneath network level.
-Our study is based on a sophisticated, high-fidelity discrete even-driven simulation tool.
-We believe the observations and analysis in this work will make the chosen of job placement and routing strategies on dragonfly network more cautiously in future.
+We presented a detailed analysis about this ``bully" behavior between jobs at the network level based on a sophisticated, high-fidelity discrete even-driven simulation tool.
+The observations and analysis presented in this work illuminate a path to the adoption of more efficient job placement policy and routing algorithm for HPC systems with dragonfly network.
 
@@
 
-The low latency and high bandwidth interconnect network plays a critical role in improving HPC system performance.
-As the computing ability continue to grow due to many-core nodes with accelerators, the network is now becoming a scare resources.
-HPC community start to explore the new network topology to replace the commonly used torus-connected network.
-The high-radix, low-diameter dragonfly topology can lower the cost of interconnect network, improve network bandwidth, reduce the packets traverse latency \cite{dally-dragonfly}.
-This make the dragonfly network an very promising choice for building Petaflop and beyond supercomputers.
+The low latency and high bandwidth interconnect network plays a critical role in HPC system performance.
+As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scare resources.
+The high-radix, low-diameter dragonfly topology can lower the \NOTE{?} cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
+This make the dragonfly network an very promising choice for building petaflop and beyond supercomputers.
 %The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
 
-While dragonfly topology provides low-latency and high-bandwidth interconnected network, how to efficiently utilize it is greatly relying on the upper level system software.
-In particular, intelligent job placement to avoid interference is of paramount importance for guarantee the performance of concurrently running jobs that sharing network resources \cite{bhatele2015, dskinner}.
-Some research work suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
-
-In this work, we study the interference between concurrently running jobs on dragonfly network with different job placement and routing schemes.
-We use CODES, a HPC network simulation toolkit with high fidelity, excellent scalability for packet level simulation \cite{codes}.
-And being unorthodox to most existing work that use synthetic workload, we use traces of three representative applications from DOE Design Forward Project \cite{designforwardwebpage}.
-The advantage of using real application traces is quite obvious, these traces can capture application's communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity.
+While dragonfly topologies provide low-latency and high-bandwidth networking, efficiently utilizing it is a significant concern.
+In particular, intelligent job placement to avoid interference is of paramount importance to guarantee the performance of each job when it shares network resources with other concurrently running peers \cite{bhatele2015, dskinner}.
+Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
+
+In this work, we study the interference between concurrently running jobs on dragonfly networks with different job placement and routing policies.
+We use CODES, an HPC network simulation toolkit with high fidelity and excellent scalability for packet level simulation \cite{codes}.
+Unlike much existing work that rely on synthetic workloads, we use traces of three representative applications from the DOE Design Forward Project \cite{designforwardwebpage}.
+The advantage of using real application traces is straight forward: \TODO{ these traces can capture application communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity}.
 Applications usually are distinctive from each other in terms of data transfer amount, communication pattern, operation dependency etc.
-which are impossible to reproduce in synthetic workload.
-
-We conduct extensive experiments with three applications running on dragonfly network with two job placement schemes and three routing schemes.
-We analyze the applications' performance in terms of communication time when they running with different placement\& routing configuration.
+which can be impractical to reproduce in a synthetic workload.
+
+We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies.
+We analyze the applications' performance in terms of communication time when running with different placement and routing configurations.
 Our evaluation is based on more than 1000 runs of simulation.
@@
 
-    \item Random placement coupled with adaptive routing can not guarantee the performance of every job in the workload.
-The hot-spots free and load-balanced network status reached by using random placement with adaptive routing come with the cost of less communication-intensive jobs performance degradation.
-
-    \item We identify the ``bully" behavior happening between concurrently running jobs on dragonfly network when random placement \& adaptive routing in use.
-Random placement \& adaptive routing redirect the traffic of communication intensive jobs to the routers through which less intensive jobs' traffic used to go, embezzle the network resource such as local and global channel bandwidth, slow down the communication of those less intensive jobs.
-
-    \item We found that contiguous placement \& minimal routing can guarantee the consistent performance of each job running on dragonfly network, while may result in local network congestion and unbalanced network utilization.
-Contiguous placement \& minimal routing are preferred by less communication-intensive jobs, since it will prevent them from being ``bullied" by other communication-intensive jobs.
+    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion.
+The network could reach the optimal performance by using random placement and adaptive routing.
+
+    \item ``Bully" behavior is happening between concurrently running jobs on dragonfly network when random placement and adaptive routing in use.
+The performance improvement obtained by communication-intensive jobs come with the cost of less intensive jobs suffering performance degradation.
+
+    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of each job by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
+Contiguous placement and minimal routing are preferred by less communication-intensive jobs, since it will prevent them from being ``bullied" by other communication-intensive jobs.
 
@@
 
-These observations also reconfirm that interference between concurrently running jobs would make the performance of some jobs very unpredictable.
+%These observations also reconfirm that interference between concurrently running jobs would make the performance of some jobs very unpredictable.
 The detailed analysis about the traffic and congestion in network level unveil the undercurrent beneath that interference.
 
-To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly network has not been reported so far.
-We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing facility, system software development, and system administration.
-The computing facility should choose the configuration for dragonfly network implementation with consideration about resource sharing between concurrently running jobs.
-The workload manager would come up with better scheduling algorithm for jobs with distinctive communication behavior.
-And the system administration would be more efficient with the knowledge about jobs running status under different placement and routing configuration.
+Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to job communication intensity.
+\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, while the less intensive jobs should run with contiguous placement and minimal routing.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly network has not been reported so far.
+We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
+The computing centers could choose the configuration for implementing a dragonfly network with consideration about resource sharing between concurrently running jobs.
+System software such as workload manager could come up with better scheduling algorithm for jobs with distinctive communication behavior.
+And system administrators could be able to make accurate predication about system availability with the knowledge of jobs running status under different placement and routing configurations.
 
 The rest of this paper is organized as follows.
-Section \ref{sec:background} describes the dragonfly network and the placement \& routing schemes.
-Section \ref{sec: methodology} talks about the use of CODES as research vehicle and three representative applications from DOE Design Forward Project.
-Section \ref{sec:workload-1} presents the analysis of three applications running on dragonfly network with different placement \& routing configuration.
+Section \ref{sec:background} describes the dragonfly network and the placement and routing policies.
+Section \ref{sec: methodology} talks about the use of CODES as research vehicle and three representative applications from the DOE Design Forward Project.
+Section \ref{sec:workload-1} presents the analysis of three applications running on a dragonfly network with different placement and routing configurations.
 Section \ref{sec:workload-2} validates the observations we get in section \ref{sec:workload-1}.
-Section \ref{sec:related work} discusses related work.
+Section \ref{sec:related work} discusses the related work.
 Finally, the conclusion is presented in Section \ref{sec:conclusion}.
@@
 
-In this section, we talk about the Dragonfly topology and one of its implementation. We also present the placement and routing schemes  used on dragonfly network.
+In this section, we review the dragonfly topology, including the placement and routing policies examined in previous work.
 
@@
 The dragonfly is a two-level hierarchical topology.
-It consists of several groups connected by All-to-All links.
-In each group, there could be ``a" number of routers connected via All-to-All local channels.
+It consists of several groups connected by all-to-all links.
+In each group, there could be ``a" number of routers connected via all-to-all local channels.
 For each router, there could be ``p" number of compute nodes attached to it via terminal links.
@@
 Thus, the radix of each router is $k = a+h+p-1$.
-The implementation of such dragonfly network could be different between different computing facilities.
-The choosing of proper $a$, $h$, $p$ could be involving many factors, such as system scale, building cost and workload requirements.
-
-For the purpose of loading balance, it is recommended that the proper dragonfly configuration should be like $a=2p=2h$\cite{kim-micro}.
+The implementation of such dragonfly network could choose different value for ``a", ``p" and ``h" in different computing centers.
+The adoption of proper $a$, $h$, $p$ could be involving many factors, such as system scale, building cost and workload requirements.
+
+For the purpose of load balance, it is recommended that the proper dragonfly configuration should follow $a=2p=2h$\cite{kim-micro}.
 Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g $.
-Figure \ref{fig:dragonfly-overview} illustrated an implementation of dragonfly network follows such configuration.
+An implementation of dragonfly network follows such configuration is illustrated in Figure \ref{fig:dragonfly-overview}.
 There are 6 routers in each group, each router has 3 compute nodes attached to it.
@@
 There are 19 groups, 6 routers in each group, 3 compute nodes connected to each router, 342 nodes in total.
-Job\_1 requires for 6 nodes, get the allocation by Random placement.
-Job\_2 requires for 8 nodes, get the allocation by Contiguous placement.
+Job $J1$ requires for 7 nodes, gets its allocation by random placement.
+Job $J2$ requires for 8 nodes, gets its allocation by contiguous placement.
 }
@@
 
-For a parallel application requiring multiple compute nodes, job placement refers to the process of assigning the tasks of the application onto the system by a system software such as batch scheduler \cite{xu-cluster14}.
-In this work, we study two well cited placement policies for dragonfly systems:
+For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning the tasks of the application onto the system by a system software such as batch scheduler \cite{xu-cluster14}.
+In this work, we study two alternative placement policies considered by the community for dragonfly systems:
 
@@
 
-\textbf{Contiguous Placement:} In this scheme, the nodes will first be indexed consecutively in an increasing order of their group id and router id.
-The schedul assign each job required number of nodes by cutting chunks of nodes from the sequentially ordered list, as illustrated in Figure \ref{fig:dragonfly-overview} as blue nodes assigned to job\_2.
-The nodes been allocated to the same job will be adjacent to each other, usually they are attached to the same router or in the same group, depends on the size of the job.
-Contiguous placement confines the traffic of application into the local area, which may result in local network congestion and increase the possibility of hot-spots.
-
-\textbf{Random Placement:} In this scheme, job will get a set of nodes that randomly selected from all the available nodes in the system.
-The nodes allocated to each job would be attached to different routers in different groups, as illustrated in Figure \ref{fig:dragonfly-overview} the red nodes assigned to job\_1.
-Some routers may be shared by different applications when using random placement.
-Random placement can spreading the traffic of application uniformly across the whole system, thus avoid the possible local congestion and reach load balance.
+\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to job in a consecutive manner.
+The assignment fills up a group first, only crosses group boundaries and start to fill the next group as necessary.
+Job $J2$, illustrated as blue in Figure \ref{fig:dragonfly-overview}, gets the required amount of nodes by contiguous placement.
+Contiguous placement confines the tasks of a job into the same group, which may result in local network congestion and increase the possibility of hot-spots.
+
+\textbf{Random Placement:} In this policy, job will get a set of nodes that randomly selected from all the available nodes in the system.
+The nodes assigned to each job would be attached to different routers in different groups, as illustrated in Figure \ref{fig:dragonfly-overview} the red nodes assigned to job $J1$.
+Some routers may be shared by different jobs when random placement in use.
+Random placement can distribute the tasks of  a job uniformly across the whole system, thus avoid the possible local congestion and reach load balance.
+However, random placement may cause possible congestion on global links.
 
@@
 \label{sec:routing-schemes}
-The routing scheme refers to the strategy adopted to route messages from the source router to the destination router.
-The well studied routing schemes for dragonfly network include minimal routing, adaptive routing \cite{dally-dragonfly}, and progressive adaptive routing\cite{jiang}, and some of their variations \cite{won-prog-adaptive}.
-In this work we study three widely adopted routing mechanisms in dragonfly systems
-
-\textbf{Minimal:} When the network deploy minimal routing, a message from source router will take the the shortest path to the destination router.
+The routing policy refers to the strategy adopted to route messages \NOTE{(message refers to a stream of packets)} from the source router to the destination router.
+Previously studied routing policies for dragonfly network include minimal routing, adaptive routing \cite{dally-dragonfly}, and progressive adaptive routing\cite{jiang}, and some of their variations \cite{won-prog-adaptive}.
+In this work we study three widely adopted routing policies on dragonfly networks.
+
+\textbf{Minimal:} In this policy, a message from source router will take the the shortest path to the destination router.
 When there are multiple shortest paths between the source and destination router, the message will be evenly divided among the paths.
@@
 
-\textbf{Adaptive:} In this scheme, the path a message takes will be adaptively chosen between shortest and non-shortest path, depends on the congestion situation along that path.
+\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest path, depends on the congestion situation along that path.
 For the non-shortest path, an intermediate router will be randomly chosen.
 The message will first take the shortest path from source to that intermediate router, then it will take the shortest path from that intermediate router to the destination.
-Since adaptive scheme chooses routing path adaptively based on the congestion situation, it can void local congestion and reduce the possibility of hot-spots.
-
-\textbf{Progressive Adaptive:} In this scheme, the decision to route minimally at each hop in the source group will be re-evaluated and any decision to route non-minimally at source router or at a subsequent hop is permant and is not re-evaluated \cite{jiang}.
+Since routing path are chosen adaptively based on the congestion situation, it can avoid local congestion and possible hot-spots.
+Adaptive routing collapses to minimal routing in the absence of traffic congestion.
+
+\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated.
+And any decision to route non-minimally at source router or at a subsequent hop is permanent and won't be re-evaluated \cite{jiang}.
 The progressive adaptive is capable of handling the case where a global link is congested but this information has not yet propagated back to the source router \cite{jiang}.
@@
 
-It is difficult to do experiment with concurrently running jobs on HPC system.
-One reason is that job placement and routing strategy are part of system configuration, it is impossible for user to make changes at will.
+It is difficult to do experiment with concurrently running jobs on HPC system\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
+One reason is that job placement and routing policies are part of system configuration, it is impossible for user to make changes at will.
 Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
+Last but not least, configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
 Therefore, we resort to simulation in our work.
@@
 A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability \cite{codes}.
-CODES supports dragonfly network with packet-level high-fidelity simulation\cite{codes-dragonfly} \cite{misbah-tpds}.
-It can take real MPI application traces generated by SST DUMPI\cite{sst} to drive CODES network model.
-In this work, we focus on an in-depth analysis of interference  with different job placement \& routing schemes on dragonfly network.
+CODES supports dragonfly network\cite{codes-dragonfly} \cite{misbah-tpds}, as well as other topologies such as torus\cite{misbah-pads-2014}\cite{ning-pads-2011} and fat-tree\cite{ning-pads-2015}, with packet-level high-fidelity simulation.
+It can drive these models through an MPI simulation later that utilizing DUMPI traces\cite{sst}.
+In this work, we perform an in-depth analysis of job interference with different job placement and routing policies on dragonfly network.
 
@@
 
-We choose three representative parallel applications from DOE Design Forward Project\cite{designforwardwebpage}.
+We choose three representative parallel applications from the DOE Design Forward Project\cite{designforwardwebpage}.
 We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers.
-Specifically, we study the Algebraic MultiGrid Solver (AMG), Geometric MultiGrid (MultiGrid) and CrystalRouter MiniApps.
-
-\textbf{AMG:} The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
-It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.
-% The traces of AMG we chosen are comprised of 216 MPI ranks.
-
-\textbf{MultiGrid:}  geometric multi-grid v-cycle from the production elliptic solver BoxLib, a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}.
+Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from production elliptic solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
+
+\textbf{AMG:} The Algebraic MultiGrid Solver is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
+It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL \cite{amg}.
+
+\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes \cite{boxlib}.
 It is widely used for structured grid physics packages.
-% The traces of MultiGrid we chosen are comprised of 125 MPI ranks.
-
-\textbf{CrystalRouter:} the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}.
-It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.
-% The traces of CrystalRouter we chosen are comprised of 100 MPI ranks.
+
+\textbf{CrystalRouter:} The CrystalRouter MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory.
+It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.
 
@@
 
+\NOTE{justify network size}The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it.
+Overall, there are 264 routers and 1056 compute nodes in the network.
+The ratio between aggregated local and global channel bandwidth are set propotional to the Cray Cascade system\cite{faanes} based on the dragonfly topology\cite{dally-dragonfly}.
+
+In this work, we study both the network behavior and the job interference when dragonfly network is configured with 6 different job placement and routing policy combinations, which are summarized in Table \ref{tab: placement routing configs}.
+
 \begin{table}[ht]
 \begin{center}
-\caption{The notation for different placement \& routing configurations} 
+\caption{The notation for different placement and routing configurations} 
 \label{tab: placement routing configs}
@@
 \toprule
-&\multicolumn{3}{c}{Routing} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{3}{c}{Routing Policies} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
 \cmidrule(l){2-4}
-Placement  & Minimal & Adaptive & Progressive adaptive\\ % Column names row
+Placement Policies & Minimal & Adaptive & Progressive Adaptive\\ % Column names row
 \midrule % In-table horizontal line
@@
 Random  &   RM  &   RA   &  RPA   \\ 
-
 \midrule % In-table horizontal line
@@
 
-The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it.
-Overall, there are 264 routers and 1056 compute nodes in the network.
-The ratio between aggregrated local and global channel bandwidth are set propotional to the Cray Cascade system\cite{faanes} based on the dragonfly topology\cite{dally-dragonfly}.
-
-In this work we simulate and analyze six combinations of placement policies and routing schemes, which are summarized in Table \ref{tab: placement routing configs}.
-Our analysis focuses on both overall network workload and individual application performance.
+%Our analysis focuses on both overall network workload and individual application performance.
 For overall workload analysis, we focus on the time spent on communication by the workload, the network traffic throughput and busy time of links and channels.
@@
 In our experiments, we collect and analyze the following data:
-
+Our analysis focus on the following metrics:
 \begin{itemize}
-    \item router terminal link traffic and busy time.
-    \item router local channel traffic and busy time.
-    \item router global channel traffic and busy time.
-    \item communication time spent by each MPI rank. 
+
+    \item \textbf{Network Traffic:} The traffic refers to the amount of data go through each router in the network.
+For each router, the traffic go through its terminal link, local channel and global channel are analyzed respectively.
+
+    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when  the buffer of certain port in the router is full.
+Saturated time can denote the congestion on certain port.
+
+    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time spent by the rank to complete its message exchange with all other ranks.
+For each job, this metric refers to the time spent to complete the message exchange by all its ranks.
+
 \end{itemize}
 
-With respect to random placement, we conduct our experiment with a set of distinctive random allocation, which are intended to eliminate the possibility of variation.
+\NOTE{limitations:}Since our study is about network behavior and job interference during communication, the time spent by each MPI rank on computation will not be counted in our experiments.
+
+With respect to random placement, we conduct our experiments with 50 sets of distinctive allocation generated by random placement.
+The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.
 
@@
 
-Workload \Rmnum{1} comprises the original AMG, MultiGrid and CrystalRouter.
-As we see in Table \ref{tab:apps-detail}, AMG has the least amount of data transfer, thus contributes the least amount of traffic in Wrokload \Rmnum{1}.
-
-Workload \Rmnum{2} comprises sAMG, MultiGrid and CrystalRouter.
-sAMG consists of synthetic traces that are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
-The traffic from sAMG is the dominant in Workload \Rmnum{2}.
+%In this work, we use two sets of parallel workloads to quantified study the network behavior as well as job interference when the dragonfly network equipped with different placement and routing configurations.
+
+In this study, we use two sets of parallel workloads.
+Workload \Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
+As we see in Table \ref{tab:apps-detail}, AMG has the least amount of data transfer, thus contributes the least amount of traffic in Workload \Rmnum{1}.
+Workload \Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
+sAMG is a synthetic version of AMG, which is the same as AMG in every aspect expect that the data transfer amount 100x greater than AMG.
+sAMG contributes the dominant amount of traffic in Workload \Rmnum{2}.
+
+Workload \Rmnum{1} is used to identify the ``bully" behavior between concurrently running jobs on dragonfly network.
+Workload \Rmnum{2} is used to verify the results and conclusion obtained from the study about Workload \Rmnum{1}.
+
+Table \ref{tab:apps-detail} summarizes the details of each application.
+It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.
 
@@
 \begin{center}
-\caption{Details of Application Traces.} 
+\caption{The details of each application.} 
 \label{tab:apps-detail}
@@
 \cmidrule(l){2-4}
-App Name & num. rank & Data per Rank & Total Data\\ % Column names row
+App Name & Num. Rank & Avg. Data/Rank & Total Data\\ % Column names row
 \midrule % In-table horizontal line
@@
 
-% \section{Study of Parallel Workload \Rmnum{1 }}
-\section{Identify the ``Bully"}
+\section{Study of Parallel Workload \Rmnum{1 }}
+%\section{Identify the ``Bully"}
 \label{sec:workload-1}
 
-% The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces}.
-The details of this workload shown in Table \ref{tab: parallel workload-1}.
-
-% 
+We study the network behavior as well as application interference under different placement and routing configurations from two perspectives.
+First, we analyze the network performance in terms of workload communication time.
+Then, we isolate each application from the workload, and analyze the interference by scrutinizing the traffic go through the routers that serving each application.
+
 % \begin{figure}[h!]
@@
 Based on this figure, we can tell that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive.
-% 
-% 
-% \subsection{Workload Analysis}
+
+\subsection{Network Performance Analysis}
 %  
@@
 \begin{center}
-\caption{Time spent on communication (MilliSecond) by Workload II when 6 different placement\&routing configuration in use.} 
+\caption{Time spent on communication by Workload I when dragonfly network equipped with 6 different placement and routing configurations.} 
 \label{tab:wkld-commtime}
@@
 \toprule
-&\multicolumn{6}{c}{Placement\&Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{6}{c}{Placement and Routing Configurations} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
 \cmidrule(l){2-7}
@@
 \midrule % In-table horizontal line
-Runtime  &  1870 & 1250 & 1248 & 860 & 835 &830\\ % Content row 1
+Time(ms)  &  1870 & 1250 & 1248 & 860 & 835 &830\\ % Content row 1
 
@@
 
-The communication time spent by parallel workload \Rmnum{1} under different placement and routing configuration shown in Table \ref{tab:wkld-commtime}.
-The contiguous placement coupled with minimal routing results in highest communication time.
-Progressive adaptive and adaptive routing have comparable results when coupled with contiguous placement.
-The random placement results the comparable performance with any routing schemes and they all outperform the contiguous placement configurations.
+The communication time spent by Workload \Rmnum{1} under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}.
+The contiguous placement coupled with minimal routing (CM) results in highest communication time.
+When contiguous placement coupled with progressive adaptive and adaptive routing (CA, CPA), Workload \Rmnum{1} spends  comparable amount of time to complete communication.
+The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.
 
@@
     \end{subfigure}%
-   \caption{Traffic and saturated time of links in different level in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration.}
+   \caption{The aggregate traffic and saturated time of links in different level in the dragonfly network when Workload \Rmnum{1} running under 6 different placement and routing configurations.
+``CA" and ``CPA" have comparably same performance and the corresponding lines are overlapped.
+}
    \label{fig:wkld-network-traffic-stime}
@@
 
-Figure \ref{fig:wkld-network-traffic-stime} shows the amount of traffic go through terminal links, local channels and global channels, and the corresponding saturated time when the workload running on dragonfly network with 6 different placement and routing configurations
+Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{1} running on dragonfly network with 6 different placement and routing configurations.
 
 %global link traffic and busy time explanation
-When the workload is running with contiguous placement and minimal routing, all the MPI ranks are physically adjacent to each other, and the packets are routed through the shortest path between its source rank to destination rank.
-In this case, all the traffic are on the first half of the network (node id from 0 to $216+125+100-1=440$, group id from 0 to 13 ), causing local congestion and traffic load on some routers are extremely high, as shown the blue dash line in Figure \ref{fig:global-channel-traffic}.
-Thus the busy time of global channel is also the highest when contiguous placement coupled with minimal routing, as shown in Figure \ref{fig:global-channel-stime} the blue dash line.
-
-When contiguous placement is coupled with (progressive) adaptive routing, the local congestion on global channel will be greatly alleviated, as shown in Figure \ref{fig:global-channel-traffic} the red and green dash line.
-Since (progressive) adaptive routing are congestion aware, and be able to utilize the idle routers on the other part of the network.
-The busy time of global channel are also reduce by using contiguous placement coupled with either adaptive or progressive adaptive routing, as shown in Figure \ref{fig:global-channel-stime} the red and green dash line.
-
-Random placement can randomly allocate the MPI ranks to the physical nodes all over the network, thus prevent certain part of the network from being congested by traffic.
-Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic go through global channels are uniformly distributed across all the routers in the network, thus no particular global channel will suffer high traffic burden.
-When the random placement coupled with minimal routing, the packets can avoid unnecessary intermediate forwarding as introduced by adaptive and progressive routing, which results in generating less traffic.
+When Workload \Rmnum{1} running with contiguous placement and minimal routing(CM), all its traffic is happening in the contiguously allocated groups, causing congestion along certain shortest paths from source routers to destination routers.
+Both the traffic through the global channels in those congested paths and the corresponding saturated time are the highest compared with other configurations, shown as the blue dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
+When contiguous placement is coupled with (progressive) adaptive routing (CA and CPA), the traffic through congested global channels will be greatly reduced, so does corresponding saturated time, shown as the red and green dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
+Since (progressive) adaptive routing are congestion aware, the traffic would be redirected to the intermediate routers in other idle groups when congestion occurs, thus the traffic burden on the contiguously allocated groups will be alleviated.
+
+Random placement policy performs comparably with three different routing policies.
+Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic go through global channels are quite balanced across all the routers in the network, thus no particular global channel will suffer high traffic burden.
+When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by adaptive and progressive routing, which results in generating less traffic.
 That's why the blue solid line is lower than the red and green solid line.
-Since the random placement can uniformly distribute the workload traffic, there are no sudden surge of busy time of global channel over the network, shown as solid lines in Figure \ref{fig:global-channel-stime}.
+Since the random placement can uniformly distribute traffic, there are no sudden surge of saturated time of global channel over the network, shown as solid lines in Figure \ref{fig:global-channel-stime}.
 
@@
 
-We can get the same observation from the local channel traffic (Figure \ref{fig:local-channel-traffic}) and busy time (Figure \ref{fig:local-channel-stime}).
-Contiguous placement coupled with minimal routing results in local congestion, thus highest traffic amount on the local channel of certain routers.
-Even with adaptive or progressive adaptive routing, the local congestion caused by grouping MPI rank on adjacent nodes in contiguous placement can not be eliminated.
-The random placement can reduce the congestion on local channel for allocating MPI ranks to random selected nodes.
+We observe similar phenomena from the local channel traffic (Figure \ref{fig:local-channel-traffic}) and saturated time (Figure \ref{fig:local-channel-stime}).
+Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus high aggregate traffic on the local channels of certain routers.
+Even with adaptive or progressive adaptive routing, the local congestion caused by grouping all MPI ranks in the same group(s) in contiguous placement can not be eliminated.
+Random placement is effective at addressing this type of congestion.
 
 %terminal link traffic and busy time explanation
-The distribution of traffic go through terminal links stay unchanged no matter which placement \& routing configuration in use, as shown in Figure \ref{fig:terminal-link-traffic}.
-This is because only the location of each MPI rank in the network will be changed in different placement schemes, and the routing won't have effect the terminal link, so the traffic between compute node and the router won't change.
-Due to the traffic changes on global and local channels, the busy time of terminal links will experience variability when different routing schemes in use, as shown in Figure \ref{fig:terminal-link-stime}.
+Figure \ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which won't change when different placement and routing configurations in use.
+All 6 lines are overlapped in Figure \ref{fig:terminal-link-traffic}.
+However, due to the traffic changes on global and local channels, the saturated time of terminal links will experience variability when different routing schemes in use, as shown in Figure \ref{fig:terminal-link-stime}.
+When contiguous placement coupled with minimal routing(CM), the accumulated congestion on local and global channels cause extremely long saturated time on the terminal link, shown as the blue dashed line in Figure \ref{fig:terminal-link-stime}.
+This again manifests the severe congestion caused by using contiguous placement and minimal routing.
 
@@
 
-Contiguous placement allocates MPI ranks to physical nodes that are adjacent to each other, which confines the workload traffic to some local area when coupled with minimal routing.
+%MPI ranks are assigned to physical nodes that are adjacent to each other in contiguous placement, which confines the workload traffic to certain local area when coupled with minimal routing.
 This may result in local congestion and unbalanced network utilization.
-Contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest busy time.
-
-Random placement allocates MPI ranks to a set of randomly selected nodes all over the system, uniformly distributes workload traffic and avoids local congestion.
+Contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest saturated time.
+
+%Random placement allocates MPI ranks to a set of randomly selected nodes all over the system, uniformly distributes workload traffic and avoids local congestion.
 When random placement is coupled with minimal routing, the packets will take the shortest path from source router to the destination router without routing to any intermediate routers, this will prevent the routing from generating extra traffic.
@@
 
-The random job placement coupled with either minimal or adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
+%The random job placement coupled with either minimal or adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
 The workload performance get greatly improved with this configuration.
@@
 
-% Start from here, we present the individual application analysis.
 \subsection{Individual Application Analysis}
@@
 
-Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
-
-As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MG and CR suffer the longest communication time when running with contiguous placement \& minimal routing (CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), both MultiGrid and CrystalRouter will get great improvement, their communication time reduce a lot.
-Random placement will further reduce the communication time of MultiGrid and CrystalRouter, and reach the best performance when coupled with (progressive) adaptive routing (RPA, RA).
-Both MultiGrid and CrystalRouter shows the same trend as the workload when running under different placement \& routing configurations.
+Figure \ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
+
+As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MultiGrid and CrystalRouter suffer the longest communication time when running with contiguous placement and minimal routing (CM).
+When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter is significantly reduced.
+Random placement further reduces their communication time, and reaches the best performance when coupled with (progressive) adaptive routing (RPA, RA).
+Both MultiGrid and CrystalRouter show the same trend as the workload when running under different placement and routing configurations.
 
 AMG is quite an exception.
-As shown in Figure \ref{fig:amg-commtime}, the communication time of AMG is skyrocketing when it running under random placement coupled with (progressive) adaptive routing (RPA, RA).
+As shown in Figure \ref{fig:amg-commtime}, the communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA).
 The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
@@
     \end{subfigure}%
-   \caption{The traffic go through the local and global channels of routers that belong to specific application.}
+   \caption{The aggregate traffic go through the local and global channels of routers belonging to specific application.
+``CA" and ``CPA" have comparably same performance and the corresponding lines are overlapped.}
    \label{fig:3app-lc-gc-traffic}
@@
 % Show the evidence from network level, explain why AMG is different. 
-We look into network level to identify the culprit behind AMG's abnormal behavior with random placement \& adaptive routing.
-By identifying the terminal nodes each MPI rank resides on and routers that each application's traffic go through, we can see that the traffic go through the routers that belongs to AMG is skyrocketing when random placement \& adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}.
-Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
+We look into network level to identify the culprit behind AMG's abnormal behavior with random placement and adaptive routing.
+By identifying the compute nodes each MPI rank resides on and routers that serving each application, we can see that the traffic go through the routers serving AMG skyrockets when random placement and adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and \ref{fig:amg-gc-traffic}.
+Adaptive routing will redirect the traffic of other applications to go through the routers belonging to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
 
 No router will be shared between applications under contiguous placement.
-A set of successive groups will be allocated to each application under contiguous placement scheme.
+A number of successive groups will be allocated to the same application under contiguous placement policy.
 When contiguous placement coupled with minimal routing, application will be free of interference from its concurrently running peers.
-However, application communication traffic will be confined within their allocated routers, thus local congestion is very likely to happen depends on application communication intensity.
-As the lest communication intensive application in the workload, AMG can benefit from contiguous placement.
-Under contiguous placement, the traffic go through the local and global channels of the routers that belongs to AMG is significantly lower than random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
-
-MultiGrid and CrystalRouter are more communication intensive compared with AMG.
-They will suffer great amount local traffic in both local and global channels when contiguous placement is used, shown as the dash line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-On the other hand, the random placement scheme can uniformly distribute their traffic all over the network by allocating randomly selected nodes to each MPI rank, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
+However, application communication traffic will be confined within their allocated groups, thus congestion is very likely to happen depending on application communication intensity.
+As the lest communication-intensive application in Workload \Rmnum{1}, AMG can benefit from contiguous placement.
+Under contiguous placement, the traffic go through the local and global channels of the routers belonging to AMG is significantly lower than with random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
+
+MultiGrid and CrystalRouter are more communication-intensive compared with AMG.
+They will suffer congestion on both local and global channels when contiguous placement is in use, shown as the dashed line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
+On the other hand, the random placement can uniformly distribute their traffic all over the network, alleviate the possible congestion, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
 
@@
 
-\subsection{Workload Analysis}
+\subsection{Network Performance Analysis}
 

### 2016-03-27 draft.tex
made changes based on Zhiling's comments

@@
 
-We study the network behavior as well as application interference under different placement and routing configurations from two perspectives.
-First, we analyze the network performance in terms of workload communication time.
+We study the network behavior as well as application interference from two perspectives.
+First, we analyze the network performance when Workload \Rmnum{1 } is running under different placement and routing configurations.
 Then, we isolate each application from the workload, and analyze the interference by scrutinizing the traffic go through the routers that serving each application.
+These analysis allow us to identify the ``bully" in the workload.
 
@@
 \subsection{Network Performance Analysis}
+\label{sec: workload-1 network analysis}
 %  
@@
 \subsection{Individual Application Analysis}
+\label{sec: workload-1 app analysis}
 
@@
 
-\subsection{Key Findings}
-We can get the following key findings from the detailed analysis of three applications.
-
-\emph{Random placement \& adaptive routing is quite efficient for orchestrating the traffic load in the network by uniformly distributing the workload traffic all over the network.
-However, application like AMG will be impaired in this orchestration.
-Beneath the facade of harmony, less communication-intensive application are ``bullied" by their concurrently running communication-intensive peers in the workload.
-}
-
-% The routers through which the less communication-intensive application traffic used to route, now have more traffic go through them.
-These extra traffic are from other communication-intensive applications.
-
-\emph{Random placement \& adaptive routing can not guarantee the qualify of service for each application in the workload.
-In order to reach load-balanced and hot-spots free over the whole network, the traffic from congested routers will be redirected to other less busy routers.
-This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.}
-
-\emph{Contiguous placement \& minimal routing guarantee a consistent performance of each application.
-Although, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization, it can reduce the interference between concurrently running applications, thus prevent less communication-intensive application from being ``bullied" by its communication-intensive peers.}
-
-We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.
-
-% \section{Parallel Workload \Rmnum{2 }}
-\section{``Bully" become ``Bullee"}
+\subsection{Key Observations}
+In summary, based on the results presented in section \ref{sec: workload-1 network analysis}  and \ref{sec: workload-1 app analysis}, we have made the following observations.
+
+\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers.
+Therefore, the network could reach load-balance and hot-spots.
+
+\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network is configured with random placement and adaptive routing.}\NOTE{footnote} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
+AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use.
+The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slow down AMG's communication.
+
+\emph{Consistent performance of each application can be guaranteed when network is configured with contiguous placement and minimal routing.} The router and group sharing between jobs are prohibited in contiguous placement policy.
+The traffic won't be redirected from over-loaded routers to less busy ones when minimal routing is in use.
+Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
+However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.
+
+\TODO{make this paragraph into footnote} We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.
+
+\section{Study of Parallel Workload \Rmnum{2 }}
+%\section{``Bully" become ``Bullee"}
 \label{sec:workload-2}
 
-In order to prove that AMG being bullied only because it is less communication-intensive than its concurrently running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
-We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with the same placement \& routing configurations.
-As shown in Table \ref{tab:apps-detail}, sAMG become the most communication-intensive application in the new workload.
+In this section, we will verify the observations made in the previous section by experimenting with Workload \Rmnum{1 } running on our dragonfly network under different placement and routing configurations.
+By generating a synthetic application, we turn a ``bully" into a ``bullee".
+
+The synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+We run the Workload \Rmnum{2 } that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with different placement and routing configurations.
+As shown in Table \ref{tab:apps-detail}, sAMG become the most communication-intensive application in Workload \Rmnum{2 }.
 
@@
 
-\subsection{Key Finding}
+\subsection{Key Observations}
 Our study with synthetic workload confirms that the ``bully" behavior among concurrently running applications would happen when two conditions are satisfied.

### 2016-03-27 draft.tex
change key observations in section 5

@@
 
-In this section, we will verify the observations made in the previous section by experimenting with Workload \Rmnum{1 } running on our dragonfly network under different placement and routing configurations.
-By generating a synthetic application, we turn a ``bully" into a ``bullee".
+In this section, we will verify the observations made in the previous section by experimenting with Workload \Rmnum{1 } running on dragonfly network under different placement and routing configurations.
+By generating a synthetic application, we turn the ``bully" into ``bullee".
 
@@
 \subsection{Network Performance Analysis}
+\label{sec: workload-2 network analysis}
 
@@
 \subsection{Individual Application Analysis}
+\label{sec: workload-2 app analysis}
 
@@
 \subsection{Key Observations}
-Our study with synthetic workload confirms that the ``bully" behavior among concurrently running applications would happen when two conditions are satisfied.
-
-\emph{First, the placement \& routing configuration allows network resource sharing between concurrently running applications.
+
+In summary, based on the results presented in section \ref{sec: workload-2 network analysis} and \ref{sec: workload-2 app analysis}, we have made the following observations.
+
+%Our study with synthetic workload confirms that the ``bully" behavior among concurrently running applications would happen when two conditions are satisfied.
+
+%\emph{First, the placement \& routing configuration allows network resource sharing between concurrently running applications.
 Random placement enables the router sharing and adaptive routing enables local and global channel sharing.}
 
-\emph{Second, there are difference in terms of communication intensity between concurrently running applications.
-In workload \Rmnum{1}, AMG has the least amount of communication traffic compared with MultiGrid and CrystalRouter and it become the ``bullee".
-In workload \Rmnum{2}, sAMG has the most amount of communication traffic, which makes it the ``bully".
-}
-
-We can stop this ``bully" by making both conditions invalid.
-
-\section{Stop the ``Bully"}
+\emph{The application becomes ``bully" only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled in random placement and adaptive routing policy.
+
+\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullee" when running concurrently with sAMG in Workload \Rmnum{2}.
+
+\section{Hybrid Job Placement}
 
 The solution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs.
-Using contiguous placement\& minimal routing could be a way avoid network sharing, but both the workload and network performance could suffer degradation due to local congestion.
+Using contiguous placement and minimal routing could be a way to avoid network sharing, but both the workload and network performance could suffer degradation due to local congestion.
 It is also unrealistic to use different routing scheme for each application with regard to its communication intensity, since routing scheme is pre-configured in the system and can not be changed on the fly.
@@
    \caption{Application communication time.
-Three applications running concurrently on dragonfly network with different placement\& routing configurations.
+Three applications running concurrently on dragonfly network with different placement and routing configurations.
 \textbf{HM, HA, HPA} denote hybrid placement coupled with minimal, adaptive and progressive adaptive routing respectively.
@@
 In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation.
-We evaluate the performance of hybrid placement\&routing configurations with parallel Workload \Rmnum{1}.
+We evaluate the performance of hybrid placement and routing configurations with parallel Workload \Rmnum{1}.
 AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation.
@@
 Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
-We found that although random placement \& adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation.
+We found that although random placement coupled with adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation.
 Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network status when application is running.

### 2016-03-28 draft.tex
replace table3,4,5 with mpi rank avg. communication time

@@
 \begin{center}
-\caption{Time spent on communication by Workload I when dragonfly network equipped with 6 different placement and routing configurations.} 
+\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under 6 different placement and routing configurations.} 
 \label{tab:wkld-commtime}
@@
 \midrule % In-table horizontal line
-Time(ms)  &  1870 & 1250 & 1248 & 860 & 835 &830\\ % Content row 1
+Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
 
@@
 
-The communication time spent by Workload \Rmnum{1} under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}.
+The average communication time spent by all MPI ranks when Workload \Rmnum{1} is running under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}.
 The contiguous placement coupled with minimal routing (CM) results in highest communication time.
@@
 
-So far we know that the reason for AMG being the only victim from random placement \& adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
+So far we know that the reason for AMG being the only victim from random placement and adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
 
@@
 \emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers.
-Therefore, the network could reach load-balance and hot-spots.
-
-\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network is configured with random placement and adaptive routing.}\NOTE{footnote} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
+Therefore, the network could reach the status of load-balanced and hot-spots free.
+
+\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network is configured with random placement and adaptive routing.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
 AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use.
 The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slow down AMG's communication.
+\footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
 
@@
 
-\TODO{make this paragraph into footnote} We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.
-
 \section{Study of Parallel Workload \Rmnum{2 }}
@@
 \begin{center}
-\caption{Time spent on communication (MilliSecond) by Workload II when 6 different placement\&routing configuration in use.} 
+\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under 6 different placement and routing configurations.} 
 \label{tab:syn-wkld-commtime}
@@
 \toprule
-&\multicolumn{6}{c}{Placement\&Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
 \cmidrule(l){2-7}
@@
 \midrule % In-table horizontal line
-Runtime  &  6123 & 3231 & 3725 & 2544 & 3701 & 3228 \\ % Content row 1
+Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
 
@@
 
-The communication time spent by parallel workload \Rmnum{2} under different placement \& routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
+The average communication time spent by all MPI ranks when Workload \Rmnum{2} running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
 As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases.
-But the performance of each configuration still keep the same trend as parallel workload \Rmnum{1}.
+But the performance of each configuration still keep the similar trend as parallel Workload \Rmnum{1}.
 The contiguous placement coupled with minimal routing results in highest communication time.
@@
 
-Figure \ref{fig:synwkld-network-traffic-stime} show the network status when Workload \Rmnum{2} running under different placement \& routing configurations.
+Figure \ref{fig:synwkld-network-traffic-stime} show the network status when Workload \Rmnum{2} running under different placement and routing configurations.
 Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel.
@@
 The random placement reach the comparable performance with any routing schemes in terms of both traffic and busy time.
-They are better than contiguous \& minimal configuration, but not too much improvement against contiguous\&(progressive) adaptive configuration.
+They are better than contiguous and minimal configuration, but not too much improvement against contiguous and (progressive) adaptive configuration.
 
@@
 We look into the network level to scrutinize the traffic go through the routers belongs to each application. 
-Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement \& routing configuration in use.
+Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement and routing configuration in use.
 The traffic is skyrocketing in both local and global channels when contiguous placement coupled with minimal routing.
@@
 \section{Hybrid Job Placement}
+
+\begin{table}[ht]
+\begin{center}
+\caption{Average time spent on communication by all MPI ranks when Workload I, II are running on dragonfly network under hybrid placement and random placement policies.} 
+\label{tab: hyb-placement-wkld-commtime}
+%\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c c c c }
+\toprule % Top horizontal line
+\toprule
+&\multicolumn{6}{c}{Placement and Routing Configurations} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-7}
+	      & HM & HA & HPA & RM & RA & RPA \\ % Column names row
+\midrule % In-table horizontal line
+Workload I  &273 &255 &255 &255 &265 &264  \\ % Content row 1
+\midrule
+Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
+\midrule % In-table horizontal line
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\end{center}
+\end{table}
 

### 2016-03-28 draft.tex
made changes in section 5, re-write section 6

@@
 Workload \Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
-sAMG is a synthetic version of AMG, which is the same as AMG in every aspect expect that the data transfer amount 100x greater than AMG.
+sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x.
 sAMG contributes the dominant amount of traffic in Workload \Rmnum{2}.
@@
         \includegraphics[height=1.8 in]{wkld/gc-stime}
-        \caption{Global Channel Busy Time}
+        \caption{Global Channel Saturated Time}
         \label{fig:global-channel-stime}
@@
         \includegraphics[height=1.8 in]{wkld/lc-stime}
-        \caption{Local Channel Busy Time}
+        \caption{Local Channel Saturated Time}
         \label{fig:local-channel-stime}
@@
         \includegraphics[height=1.8 in]{wkld/tl-stime}
-        \caption{Terminal Link Busy Time}
+        \caption{Terminal Link Saturated Time}
         \label{fig:terminal-link-stime}
@@
 
-Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{1} running on dragonfly network with 6 different placement and routing configurations.
+Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{1} is running on dragonfly network with 6 different placement and routing configurations.
 
@@
         \includegraphics[height=1.5 in]{wkld/amg/commtime}
-        \caption{AMG Communication Time}
+        \caption{AMG}
         \label{fig:amg-commtime}
@@
         \includegraphics[height=1.5 in]{wkld/mg/commtime}
-        \caption{MG Communication Time}
+        \caption{MultiGrid}
         \label{fig:mg-commtime}
@@
         \includegraphics[height=1.5 in]{wkld/cr/commtime}
-        \caption{CR Communication Time}
+        \caption{CrystalRouter}
         \label{fig:cr-commtime}
     \end{subfigure}%
-   \caption{Application communication time.
+   \caption{The communication time of all ranks in each application.
 Three applications running concurrently on dragonfly network with different placement and routing configurations.
@@
     \end{subfigure}\\
-
     \centering
@@
     \end{subfigure}%
-   \caption{The aggregate traffic go through the local and global channels of routers belonging to specific application.
-``CA" and ``CPA" have comparably same performance and the corresponding lines are overlapped.}
+   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
+``CA" and ``CPA" have comparably same performance and the corresponding lines are overlapped.
+More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
    \label{fig:3app-lc-gc-traffic}
@@
 
-So far we know that the reason for AMG being the only victim from random placement and adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
+%So far we know that the reason for AMG being the only victim from random placement and adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
 
@@
 
-\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network is configured with random placement and adaptive routing.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
+\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network random placement and adaptive routing are in use.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
 AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use.
@@
 
-\emph{Consistent performance of each application can be guaranteed when network is configured with contiguous placement and minimal routing.} The router and group sharing between jobs are prohibited in contiguous placement policy.
-The traffic won't be redirected from over-loaded routers to less busy ones when minimal routing is in use.
+\emph{Consistent performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} The router and group sharing between jobs are prohibited in contiguous placement policy.
+The traffic won't be redirected from congested routers to less busy ones when minimal routing is in use.
 Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
@@
 
-In this section, we will verify the observations made in the previous section by experimenting with Workload \Rmnum{1 } running on dragonfly network under different placement and routing configurations.
+In this section, we will verify the observations made in the previous section when Workload \Rmnum{1 } is running on dragonfly network under different placement and routing configurations.
 By generating a synthetic application, we turn the ``bully" into ``bullee".
 
-The synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.
+The synthetic application, sAMG, is generated by increasing AMG data transfer amount by 100x.
 We run the Workload \Rmnum{2 } that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with different placement and routing configurations.
@@
 
-The average communication time spent by all MPI ranks when Workload \Rmnum{2} running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
-As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases.
-But the performance of each configuration still keep the similar trend as parallel Workload \Rmnum{1}.
+The average communication time spent by all MPI ranks when Workload \Rmnum{2} is running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
+Since the total data transfer amount of Workload \Rmnum{2} increases a lot due to the presence of sAMG, the time spent on communication under all configurations increase as well.
 The contiguous placement coupled with minimal routing results in highest communication time.
@@
 And they have comparable results when coupled contiguous placement.
-
-Figure \ref{fig:synwkld-network-traffic-stime} show the network status when Workload \Rmnum{2} running under different placement and routing configurations.
-Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel.
-When coupled with (progressive) adaptive routing, the local congestion can get alleviated in contiguous placement.
-The random placement reach the comparable performance with any routing schemes in terms of both traffic and busy time.
-They are better than contiguous and minimal configuration, but not too much improvement against contiguous and (progressive) adaptive configuration.
+The performance of Workload \Rmnum{2} under different configurations keep the same trend as it of Workload \Rmnum{1}.
+
+Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running on dragonfly network with 6 different placement and routing configurations.
+Contiguous placement coupled with minimal routing(CM) results in most traffic go through certain local and global channel, thus the longest saturated time for terminal link, local and global channel.
+When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion can get alleviated.
+The random placement coupled with any routing policy(RM, RA, RPA) performs comparably in terms of both traffic and saturated time.
+They are better than contiguous placement and minimal routing(CM), but not too much improvement against contiguous and (progressive) adaptive (CA, CPA).
 
@@
         \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
-        \caption{Global Channel Busy Time}
+        \caption{Global Channel Saturated Time}
         \label{fig:synwkld-global-channel-stime}
@@
         \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
-        \caption{Local Channel Busy Time}
+        \caption{Local Channel Saturated Time}
         \label{fig:synwkld-local-channel-stime}
@@
         \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
-        \caption{Terminal Link Busy Time}
+        \caption{Terminal Link Saturated Time}
         \label{fig:synwkld-terminal-link-stime}
     \end{subfigure}%
-   \caption{Traffic and Saturated Time of different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
+   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under 6 different placement and routing configurations.}
    \label{fig:synwkld-network-traffic-stime}
@@
 The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}.
-The ``bully" become the ``bullyee".
-The less communication-intensive applications in Workload \Rmnum{2} are  MultiGrid and CrystalRouter.
-When random placement coupled with (progressive) adaptive routing is used, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
-sAMG on the other hand benefit from random placement, shown in Figure \ref{fig:syn-samg-commtime}.
-
-Contiguous placement coupled with minimal routing prevent applications from sharing network resource, and confine application communication traffic to the routers assigned to each application.
-This can guarantee the performance of less communication intensive applications like MultiGrid and CrystalRouter, and make the communication intensive application like sAMG severely deteriorate.
+The ``bully" in Workload \Rmnum{1} becomes the ``bullyee" in Workload \Rmnum{2}.
+MultiGrid and CrystalRouter are the less communication-intensive applications in Workload \Rmnum{2}.
+When random placement coupled with (progressive) adaptive routing is in use, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
+sAMG on the other hand benefits from random placement, shown in Figure \ref{fig:syn-samg-commtime}.
+Contiguous placement coupled with minimal routing prevents applications from sharing network resource, thus guarantee the performance of less communication intensive applications like MultiGrid and CrystalRouter while causing severe performance degradation to sAMG.
 
@@
         \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
-        \caption{sAMG Communication Time}
+        \caption{sAMG}
         \label{fig:syn-samg-commtime}
@@
         \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
-        \caption{MG Communication Time}
+        \caption{MultiGrid}
         \label{fig:syn-mg-commtime}
@@
         \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
-        \caption{CR Communication Time}
+        \caption{CrystalRouter}
         \label{fig:syn-cr-commtime}
     \end{subfigure}%
-   \caption{Application communication time.
+   \caption{The communication time of all ranks in each application.
 Three applications running concurrently on dragonfly network with different placement and routing configurations.
-Random placement and adaptive routing can improves AMG's communication time.
-MG and CR communication time are prolonged with random placement and adaptive routing.}
+The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullee", MultiGrid and CrystalRouter, suffer performance degradation.}
    \label{fig:syn-apps-commtime}
@@
 % explain the network status of sAMG, MG and CR
-We look into the network level to scrutinize the traffic go through the routers belongs to each application. 
-Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement and routing configuration in use.
-The traffic is skyrocketing in both local and global channels when contiguous placement coupled with minimal routing.
-The contiguous placement make all the MPI ranks of sAMG reside on a set of nodes in the groups that adjacent to each other and minimal routing confines the traffic in those groups, results in severe local congestion.
-When adaptive routing is used, the local congestion will be alleviated in both local and global channels, as some traffic will be redirected to other part of the network.
-Random placement scheme can further reduce the traffic burden on local and global channels by assigning each MPI rank of sAMG with randomly select nodes, thus uniformly distribute sAMG traffic over the network.
-
-MultiGrid become a victim of sAMG's bully when running under random placement.
-The traffic go through the local and global channels of the routers that belongs to MultiGrid are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic}.
-Although contiguous placement allocates all the MPI ranks in set of nodes in adjacent groups, causing possible local congestion, it will stop MultiGrid's routers being shared by the traffic from its communication-intensive peer, sAMG.
-As random placement is used, the traffic go through both local and global channels are greatly increased.
-
-CrystalRouter has more traffic than MultiGrid.
-The random placement won't redirect much traffic from other applications to the routers belongs to CrystalRouter, compared with contiguous placement, as shown in Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}.
+We look into the network level to scrutinize the traffic go through the routers serving each application.
+Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers serving sAMG.
+The traffic skyrockets in both local and global channels when contiguous placement coupled with minimal routing (CM) is in use.
+The congestion will be alleviated in both local and global channels, when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use.
+Random placement can further reduce the traffic burden on local and global channels by uniformly distributing sAMG traffic over the network.
+
+The traffic go through the local and global channels of the routers serving MultiGrid and CrystalRouter are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}.
+There are more traffic going through when random placement is in use, compared with contiguous placement.
+The extra traffic coming from the ``bully" sAMG cause performance degradation to MultiGrid and CrystalRouter.
 
@@
     \end{subfigure}%
-   \caption{The traffic go through the local and global channels of routers that belong to specific application.}
+   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
+``CA" and ``CPA" have comparably the same performance and the corresponding lines are overlapped.
+More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
    \label{fig:syn-3app-gc-traffic}
@@
 
-In summary, based on the results presented in section \ref{sec: workload-2 network analysis} and \ref{sec: workload-2 app analysis}, we have made the following observations.
+In summary, based on the Workload \Rmnum{2}, we have made the following observations.
 
@@
 
-\emph{The application becomes ``bully" only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled in random placement and adaptive routing policy.
+\emph{The application becomes ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
 
@@
 \section{Hybrid Job Placement}
+
+The precaution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs.
+Using contiguous placement and minimal routing could be a way to avoid network sharing, but network performance could suffer degradation due to local congestion.
+Running each job with dedicated routing policy with regard to communication intensity is unrealistic, since routing policy is pre-configured in the system and can not be changed on the fly upon each job submission.
+However, the job placement policies could be versatile, assigning different allocation (contiguous or random) to specific application.
+
+Thus, we propose the hybrid placement as a reconcile solution.
+In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation.
+We evaluate the effect of hybrid placement on improving network performance as well as preserving the performance of individual application.
+In the experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations.
+
+\subsection{Network Performance Analysis}
+
+Hybrid placement is also coupled with three routing policies, Minimal, Adaptive and Progressive Adaptive.
+They are denoted respectively as HM, HA and HPA.
+As presented in the previous section, random placement outperforms contiguous placement in terms of network performance, we only compare the results of hybrid placement with random placement due to the page limit.
 
@@
 \begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload I, II are running on dragonfly network under hybrid placement and random placement policies.} 
+\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under hybrid placement and random placement policies.} 
 \label{tab: hyb-placement-wkld-commtime}
@@
 \midrule % In-table horizontal line
-Workload I  &273 &255 &255 &255 &265 &264  \\ % Content row 1
-\midrule
-Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
+Time(ms)  &273 &255 &255 &255 &265 &264  \\ % Content row 1
+%\midrule
+%Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
 \midrule % In-table horizontal line
@@
 
-The solution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs.
-Using contiguous placement and minimal routing could be a way to avoid network sharing, but both the workload and network performance could suffer degradation due to local congestion.
-It is also unrealistic to use different routing scheme for each application with regard to its communication intensity, since routing scheme is pre-configured in the system and can not be changed on the fly.
-However, the job placement can be versatile to assign different allocation (contiguous or random) to specific application.
+As shown in Table \ref{tab: hyb-placement-wkld-commtime}, hybrid placement and random placement perform comparably.
+When coupled with minimal routing, RM outperforms HM.
+However, when coupled with (progressive) adaptive routing, HA and HPA outperform RA and RPA.
+HA and HPA perform equally well as compared with RM.
+
+\subsection{Individual Application Analysis}
 
@@
     \end{subfigure}%
-   \caption{Application communication time.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
-\textbf{HM, HA, HPA} denote hybrid placement coupled with minimal, adaptive and progressive adaptive routing respectively.
-}
+   \caption{Application communication time. Workload \Rmnum{1} is running under all the possible placement and routing configurations.}
    \label{fig:hyb-plcmt-apps-commtime}
@@
 
-Thus, we propose the hybrid placement as a reconcile solution.
-In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation.
-We evaluate the performance of hybrid placement and routing configurations with parallel Workload \Rmnum{1}.
-AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation.
-Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing schemes, together with other configurations.
-
-MultiGrid and CrystalRouter have basically the same performance with hybrid placement compared against random placement.
-Since they get random allocation in the hybrid placement scheme.
-AMG being improved a lot when hybrid placement in use.
-Compared with ``RA" and ``RPA", ``HA" and ``HPA" can significantly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}.
-This is due the contiguous allocation AMG gets in the hybrid placement scheme.
-AMG doesn't share router with other applications.
-However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter is still being redirected to the groups where AMG resides.
-Since AMG is less communication-intensive and can not fully utilize network bandwidth, it is likely that the intermediate routers pick for the traffic from MultiGrid and CrystalRouter are from AMG's group.
+Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing policies, together with other configurations.
+MultiGrid and CrystalRouter have basically the same performance with hybrid placement as compared with random placement.
+Since they still get random allocation in the hybrid placement.
+
+The performance of AMG is significantly improved when hybrid placement is in use.
+Compared with ``RA" and ``RPA", ``HA" and ``HPA" can greatly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}.
+This is due the contiguous allocation assigned to AMG in the hybrid placement policy.
+Thus, AMG can avoid sharing routers or groups with other applications in hybrid placement policy.
+When being coupled with minimal routing,
+hybrid placement and contiguous placement have similar performance for AMG.
+This is because the contiguous allocation assigned to AMG and minimal routing can prevent other applications  form sharing network resource with AMG.
+However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG.
+Since AMG is less communication-intensive and can not fully utilize network, it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups.
+So for AMG, ``HA" and ``HPA" are worse than ``CA" and ``CPA", but they are much better than ``RA" and ``RPA".
+
+\subsection{Key Observations}
+
+\emph{Compared with random placement policy, hybrid placement can guarantee similar network performance.}
+
+\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.
+} Unlike random placement which indulge ``bully", hybrid placement can restrain it to some extent.
 
@@
 Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network status when application is running.
-The traffic and busy time of router's each link are valuable information for detailed analysis.
+The traffic and saturated time of router's each link are valuable information for detailed analysis.
 

### 2016-03-29 draft.tex
add observations for section 6

@@
 The low latency and high bandwidth interconnect network plays a critical role in HPC system performance.
-As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scare resources.
+As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scarce resource.
 The high-radix, low-diameter dragonfly topology can lower the \NOTE{?} cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
@@
 
-\emph{Compared with random placement policy, hybrid placement can guarantee similar network performance.}
-
-\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.
-} Unlike random placement which indulge ``bully", hybrid placement can restrain it to some extent.
+Based on the results from experimenting with hybrid placement policy, we can make the following observations.
+
+\emph{Compared with random placement policy, hybrid placement can guarantee similar network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.
+
+\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.} Hybrid placement policy preserves contiguous allocation for less communication-intensive application, prevents network resource from being shared by others.
+Unlike random placement which indulges ``bully", hybrid placement can restrain it to some extent.
+
+Hybrid placement can guarantee the performance of individual application without causing performance degradation to network performance.
+Compared with contiguous and random placement policy, hybrid placement are more preferable to HPC systems with dragonfly networks.
 

### 2016-03-29 draft.tex
make changes in Introdcution based on my wife's comments

@@
 The high-radix, low-diameter dragonfly topology can lower the \NOTE{?} cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
-This make the dragonfly network an very promising choice for building petaflop and beyond supercomputers.
+This make the dragonfly network a very promising choice for building petaflop and beyond supercomputers.
 %The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
@@
 Unlike much existing work that rely on synthetic workloads, we use traces of three representative applications from the DOE Design Forward Project \cite{designforwardwebpage}.
-The advantage of using real application traces is straight forward: \TODO{ these traces can capture application communication behavior in detail that usually omitted in synthetic workload for the purpose of simplicity}.
-Applications usually are distinctive from each other in terms of data transfer amount, communication pattern, operation dependency etc.
-which can be impractical to reproduce in a synthetic workload.
+The advantage of using real application traces is straight forward: \TODO{these traces can capture detailed application communication behaviors that are  omitted in synthetic workload for simplification}.
+Applications are usually distinctive from each other in data transfer amount, communication pattern, operation dependency etc., which can be impractical to reproduce in a synthetic workload.
 
 We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies.
-We analyze the applications' performance in terms of communication time when running with different placement and routing configurations.
+We analyze the performance of network as well as individual application when running with different placement and routing configurations.
 Our evaluation is based on more than 1000 runs of simulation.
-Through extensive simulation with application traces, we make several interesting observations.
-
-%We made observation from our extensive study that, when dragonfly network is configured with random placement and adaptive routing scheme in order to reach hot-spots free and load balance, the performance of particular job(s) in the workload would suffer degradation.
-The communication intensive jobs in the workload can benefit from random placement and adaptive routing, with great performance improvement.
-Unfortunately, those less intensive jobs are the sacrifices for this improvement, their performance will be greatly reduced.
-We identify this phenomenon as ``bully" between concurrently running jobs.
+We make the following interesting observations through extensive simulation.
 
@@
 
-    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion.
-The network could reach the optimal performance by using random placement and adaptive routing.
-
-    \item ``Bully" behavior is happening between concurrently running jobs on dragonfly network when random placement and adaptive routing in use.
-The performance improvement obtained by communication-intensive jobs come with the cost of less intensive jobs suffering performance degradation.
-
-    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of each job by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
-Contiguous placement and minimal routing are preferred by less communication-intensive jobs, since it will prevent them from being ``bullied" by other communication-intensive jobs.
+    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion, optimizing the overall performance of the dragonfly network.
+
+    \item The ``bully" behavior occurs between concurrently running jobs on a dragonfly network when random placement and adaptive routing are in use.
+Communication-intensive jobs obtain performance improvement at the expense of less intensive jobs suffering performance degradation.
+
+    \item Random placement coupled with adaptive routing can improve the performance of communication-intensive jobs by enabling network resource sharing, though it introduces interference between concurrently running jobs.
+
+    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of less communication-intensive jobs by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
 
@@
 
-%These observations also reconfirm that interference between concurrently running jobs would make the performance of some jobs very unpredictable.
-The detailed analysis about the traffic and congestion in network level unveil the undercurrent beneath that interference.
-
-Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to job communication intensity.
-\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, while the less intensive jobs should run with contiguous placement and minimal routing.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly network has not been reported so far.
+Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to the job communication intensity.
+\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
 We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
-The computing centers could choose the configuration for implementing a dragonfly network with consideration about resource sharing between concurrently running jobs.
-System software such as workload manager could come up with better scheduling algorithm for jobs with distinctive communication behavior.
-And system administrators could be able to make accurate predication about system availability with the knowledge of jobs running status under different placement and routing configurations.
+For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks.
+System software developers could design better scheduling algorithms for jobs with distinct communication behavior.
+System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.
 
 The rest of this paper is organized as follows.
-Section \ref{sec:background} describes the dragonfly network and the placement and routing policies.
-Section \ref{sec: methodology} talks about the use of CODES as research vehicle and three representative applications from the DOE Design Forward Project.
-Section \ref{sec:workload-1} presents the analysis of three applications running on a dragonfly network with different placement and routing configurations.
-Section \ref{sec:workload-2} validates the observations we get in section \ref{sec:workload-1}.
+Section \ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies.
+Section \ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
+Section \ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations.
+Section \ref{sec:workload-2} validates the observations we obtain from previous section.
+Section \ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network.
 Section \ref{sec:related work} discusses the related work.
@@
 
-%Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by each job for execution.
-As studied by several researchers, the job placement could be an important factor that impact application performance \cite{hoefler-hpdc14} \cite{bhatele-sc11} \cite{jain-sc14}.
-In this work, we study the following two placement schemes that are most likely to be deployed in the future dragonfly system.
-
 \textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to job in a consecutive manner.
@@
 \label{tab: placement routing configs}
-%\centering % Centers the table on the page, comment out to left-justify
 \begin{tabular}{l c c c }
@@
 \toprule
-&\multicolumn{3}{c}{Routing Policies} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{3}{c}{Routing Policies} \\ 
 \cmidrule(l){2-4}
@@
 
-%Our analysis focuses on both overall network workload and individual application performance.
-For overall workload analysis, we focus on the time spent on communication by the workload, the network traffic throughput and busy time of links and channels.
-For individual application analysis, we study the time spent on communication by each MPI rank, traffic and busy time of each router that belongs to specific application.
-In our experiments, we collect and analyze the following data:
 Our analysis focus on the following metrics:
@@
 
-%\subsection{Workload Combinations}
-%\label{sec:workload-combination}
-%
-%We come up with two parallel workloads.
-The first workload consists of the original application traces described in Section \ref{sec: application traces}, while the second workload is a modified version of the first workload for the purpose of validation.
 \subsection{Workload Summary}
 \label{sec:workload summary}
-
-%In this work, we use two sets of parallel workloads to quantified study the network behavior as well as job interference when the dragonfly network equipped with different placement and routing configurations.
 
@@
 \label{tab:apps-detail}
-%\centering % Centers the table on the page, comment out to left-justify
 \begin{tabular}{l c c c }
@@
 \toprule
-&\multicolumn{3}{c}{Application Details} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{3}{c}{Application Details} \\ 
 \cmidrule(l){2-4}
@@
 
-% \begin{figure}[h!]
-%   \centering
-%   \includegraphics[width = 0.48\textwidth ]{data_amount}
-%   \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with MultiGrid and CrystalRouter.\NOTE{y axis in log?} }
-%   \label{fig:3app-data-amount}
-% \end{figure}
-% 
-% Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application.
-Based on this figure, we can tell that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive.
-
 \subsection{Network Performance Analysis}
 \label{sec: workload-1 network analysis}
-%  
-% \begin{figure}[h!]
-%   \centering
-%   \includegraphics[width = 0.48\textwidth ]{wkld/wkld-commtime}
-%   \caption{Time spent on communication by Workload I when 6 different placement and routing configurations are used.
-Random is better than contiguous in terms of improving communication efficiency.
-Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes.
-}
-%   \label{fig:wkld-commtime}
-% \end{figure}
 
@@
 \label{tab:wkld-commtime}
-%\centering % Centers the table on the page, comment out to left-justify
 \begin{tabular}{l c c c c c c }
@@
 \toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
 \cmidrule(l){2-7}
@@
 
-% \NOTE{The take-home message} from Figure \ref{fig:wkld-network-stime} and \ref{fig:wkld-network-traffic}.
-
-%MPI ranks are assigned to physical nodes that are adjacent to each other in contiguous placement, which confines the workload traffic to certain local area when coupled with minimal routing.
-This may result in local congestion and unbalanced network utilization.
-Contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest saturated time.
-
-%Random placement allocates MPI ranks to a set of randomly selected nodes all over the system, uniformly distributes workload traffic and avoids local congestion.
-When random placement is coupled with minimal routing, the packets will take the shortest path from source router to the destination router without routing to any intermediate routers, this will prevent the routing from generating extra traffic.
-When random placement is coupled with adaptive or progressive adaptive routing, the possibility of any congestion will be further reduced at the cost of extra intermediate traffic.
-
-%The random job placement coupled with either minimal or adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network.
-The workload performance get greatly improved with this configuration.
-However, when we isolated individual application from the workload, we unveil the fact that not every application can benefit from random job placement.
-
 \subsection{Individual Application Analysis}
@@
 On the other hand, the random placement can uniformly distribute their traffic all over the network, alleviate the possible congestion, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-
-%So far we know that the reason for AMG being the only victim from random placement and adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.
 
@@
 
-%Our study with synthetic workload confirms that the ``bully" behavior among concurrently running applications would happen when two conditions are satisfied.
-
-%\emph{First, the placement \& routing configuration allows network resource sharing between concurrently running applications.
-Random placement enables the router sharing and adaptive routing enables local and global channel sharing.}
-
 \emph{The application becomes ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
@@
 \section{Hybrid Job Placement}
+\label{sec: hybrid placement}
 
@@
 \label{tab: hyb-placement-wkld-commtime}
-%\centering % Centers the table on the page, comment out to left-justify
 \begin{tabular}{l c c c c c c }
@@
 \toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+&\multicolumn{6}{c}{Placement and Routing Configurations} \\
 \cmidrule(l){2-7}
@@
 
-%\section{Summary}
-%Based on the results we got from both real application traces and synthetic workload, we can make the following observations:
-%
-%\begin{itemize}
-%    \item Random placement and adaptive routing can uniformly distribute workload traffic over the network, make the whole network load-balanced and hot-spots free. 
-%    \item Random placement and adaptive routing can not guarantee QoS for each application in the workload.
-In order to reach load-balanced and hot-spots free, the traffic from congested routers will be redirected to other less busy routers.
-This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.
-%    \item Contiguous placement and minimal routing guarantee a consistent performance of each application.
-Although, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization, it can reduce the interference between concurrently running applications, thus prevent less communication-intensive application from being ``bullied" by its communication-intensive peers.
-%\end{itemize}
-
-%We believe choosing the ideal placement and routing strategies for workload running on dragonfly network should be based on application's communication intensity.
-The less intensive applications should avoid sharing network resource with other applications, reduce the possible interference.
-Contiguous placement and adaptive routing can guarantee the QoS for the less intensive applications, thus prevent the ``bully" from happening.
-
-%The communication-intensive applications tend to cause local congestion.
-It is preferable to enable communication-intensive applications to have extra network resource by sharing with other applications.
-Random placement and adaptive routing can alleviate the local congestion by redirecting traffic to other less busy routers in the network.
-
-%So the ideal placement and routing strategies for workload running on dragonfly network should be like this.
-The communication-intensive applications should be randomly allocated over the system and adaptive routing should be used by these applications to alleviate the local congestion.
-On the other hand, less intensive application should get contiguous allocation, minimal routing should be used by these applications to avoid network sharing and reduce interference.
-
 \section{Related Work}
@@
 
-% that's all folks
 \end{document}

### 2016-03-29 draft.tex
tweak some sentences, change some words

@@
 As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scarce resource.
-The high-radix, low-diameter dragonfly topology can lower the \NOTE{?} cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
+The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
 This make the dragonfly network a very promising choice for building petaflop and beyond supercomputers.
@@
 Unlike much existing work that rely on synthetic workloads, we use traces of three representative applications from the DOE Design Forward Project \cite{designforwardwebpage}.
-The advantage of using real application traces is straight forward: \TODO{these traces can capture detailed application communication behaviors that are  omitted in synthetic workload for simplification}.
+The advantage of using real application traces is straight forward: these traces can capture detailed application communication behaviors that are  omitted in synthetic workload for simplification.
 Applications are usually distinctive from each other in data transfer amount, communication pattern, operation dependency etc., which can be impractical to reproduce in a synthetic workload.
@@
 Thus, the radix of each router is $k = a+h+p-1$.
-The implementation of such dragonfly network could choose different value for ``a", ``p" and ``h" in different computing centers.
-The adoption of proper $a$, $h$, $p$ could be involving many factors, such as system scale, building cost and workload requirements.
-
-For the purpose of load balance, it is recommended that the proper dragonfly configuration should follow $a=2p=2h$\cite{kim-micro}.
+Different computing centers could choose different values for ``a", ``p" and ``h" when deploying their dragonfly network.
+The adoption of proper $a$, $h$, $p$ involves many factors, such as system scale, building cost and workload.
+
+It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$ \cite{kim-micro}.
 Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g $.
@@
   \caption{Dragonfly Network Overview.
-Illustration of part of dragonfly network.
 There are 19 groups, 6 routers in each group, 3 compute nodes connected to each router, 342 nodes in total.
@@
 The assignment fills up a group first, only crosses group boundaries and start to fill the next group as necessary.
-Job $J2$, illustrated as blue in Figure \ref{fig:dragonfly-overview}, gets the required amount of nodes by contiguous placement.
+Shown in Figure \ref{fig:dragonfly-overview}, $J2$ gets the required amount of nodes by contiguous placement.
 Contiguous placement confines the tasks of a job into the same group, which may result in local network congestion and increase the possibility of hot-spots.
@@
 \textbf{Random Placement:} In this policy, job will get a set of nodes that randomly selected from all the available nodes in the system.
-The nodes assigned to each job would be attached to different routers in different groups, as illustrated in Figure \ref{fig:dragonfly-overview} the red nodes assigned to job $J1$.
-Some routers may be shared by different jobs when random placement in use.
+The nodes assigned to $J1$ in Figure \ref{fig:dragonfly-overview} would be attached to different routers in different groups.
+Routers may be shared by different jobs when random placement is in use.
 Random placement can distribute the tasks of a job uniformly across the whole system, thus avoid the possible local congestion and reach load balance.
@@
 \label{sec:routing-schemes}
-The routing policy refers to the strategy adopted to route messages \NOTE{(message refers to a stream of packets)} from the source router to the destination router.
-Previously studied routing policies for dragonfly network include minimal routing, adaptive routing \cite{dally-dragonfly}, and progressive adaptive routing\cite{jiang}, and some of their variations \cite{won-prog-adaptive}.
+The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router.
+Previously studied routing policies for dragonfly network include minimal routing, adaptive routing \cite{dally-dragonfly}, progressive adaptive routing\cite{jiang} and some of their variations \cite{won-prog-adaptive}.
 In this work we study three widely adopted routing policies on dragonfly networks.
 
-\textbf{Minimal:} In this policy, a message from source router will take the the shortest path to the destination router.
+\textbf{Minimal:} In this policy, a message from source router takes the the shortest path to the destination router.
 When there are multiple shortest paths between the source and destination router, the message will be evenly divided among the paths.
@@
 
-\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest path, depends on the congestion situation along that path.
+\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest path, depending on the congestion situation along that path.
 For the non-shortest path, an intermediate router will be randomly chosen.
-The message will first take the shortest path from source to that intermediate router, then it will take the shortest path from that intermediate router to the destination.
-Since routing path are chosen adaptively based on the congestion situation, it can avoid local congestion and possible hot-spots.
+The message first takes the shortest path from source to that intermediate router, then it takes the shortest path from that intermediate router to the destination.
+Since routing path is chosen adaptively based on the congestion situation, adaptive routing can avoid local congestion and possible hot-spots.
 Adaptive routing collapses to minimal routing in the absence of traffic congestion.
@@
 \textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated.
-And any decision to route non-minimally at source router or at a subsequent hop is permanent and won't be re-evaluated \cite{jiang}.
+Any decision to route non-minimally at source router or at a subsequent hop is permanent and won't be re-evaluated \cite{jiang}.
 The progressive adaptive is capable of handling the case where a global link is congested but this information has not yet propagated back to the source router \cite{jiang}.
@@
 
-It is difficult to do experiment with concurrently running jobs on HPC system\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
+It is difficult to experiment with concurrently running jobs on HPC system \cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
 One reason is that job placement and routing policies are part of system configuration, it is impossible for user to make changes at will.
@@
 It can drive these models through an MPI simulation later that utilizing DUMPI traces\cite{sst}.
-In this work, we perform an in-depth analysis of job interference with different job placement and routing policies on dragonfly network.
+In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on dragonfly network.
 
@@
 
-\NOTE{justify network size}The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it.
+The parameters for building the dragonfly network been studied in our work are inspired the model proposed by Kim et.
+al \cite{kim-micro}.
+Our dragonfly network consists of 33 groups, each group contains 8 routers, and each router has 4 compute nodes attached to it.
 Overall, there are 264 routers and 1056 compute nodes in the network.
-The ratio between aggregated local and global channel bandwidth are set propotional to the Cray Cascade system\cite{faanes} based on the dragonfly topology\cite{dally-dragonfly}.
-
-In this work, we study both the network behavior and the job interference when dragonfly network is configured with 6 different job placement and routing policy combinations, which are summarized in Table \ref{tab: placement routing configs}.
+The aggregated bandwidth of terminal link,  local and global channels are proportional to those of Cray Cascade system\cite{faanes}.
+In this work, we study network performance as well as job interference when 6 different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table \ref{tab: placement routing configs}.\footnote{With respect to random placement, we experiment with 50 sets of distinctive allocation generated by random placement.
+The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.}
 
@@
 
-    \item \textbf{Network Traffic:} The traffic refers to the amount of data go through each router in the network.
+    \item \textbf{Network Traffic:} The traffic refers to the amount of data go through each port of the router.
 For each router, the traffic go through its terminal link, local channel and global channel are analyzed respectively.
 
-    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when  the buffer of certain port in the router is full.
-Saturated time can denote the congestion on certain port.
+    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of certain port is full. Saturated time can denote the congestion on certain port.
 
@@
 
-\NOTE{limitations:}Since our study is about network behavior and job interference during communication, the time spent by each MPI rank on computation will not be counted in our experiments.
-
-With respect to random placement, we conduct our experiments with 50 sets of distinctive allocation generated by random placement.
-The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.
+Since our study focus on network performance and job interference during communication, the time spent in computation by each MPI rank will not be counted in our experiments.
 
@@
 
-In this study, we use two sets of parallel workloads.
+Two sets of parallel workloads are used in this work.
 Workload \Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
-As we see in Table \ref{tab:apps-detail}, AMG has the least amount of data transfer, thus contributes the least amount of traffic in Workload \Rmnum{1}.
+As we see in Table \ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload \Rmnum{1}.
 Workload \Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
 sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x.
-sAMG contributes the dominant amount of traffic in Workload \Rmnum{2}.
+sAMG is the most communication-intensive job in Workload \Rmnum{2}.
 
@@
 
-Table \ref{tab:apps-detail} summarizes the details of each application.
+%Table \ref{tab:apps-detail} summarizes the details of each application.
 It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.
@@
 
-\section{Study of Parallel Workload \Rmnum{1 }}
+\section{Study of Parallel Workload \Rmnum{1}}
 %\section{Identify the ``Bully"}
@@
 
-We study the network behavior as well as application interference from two perspectives.
-First, we analyze the network performance when Workload \Rmnum{1 } is running under different placement and routing configurations.
-Then, we isolate each application from the workload, and analyze the interference by scrutinizing the traffic go through the routers that serving each application.
+We study the network performance as well as job interference from two perspectives.
+First, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
+Then, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic go through the routers that serving each job.
 These analysis allow us to identify the ``bully" in the workload.
@@
 The average communication time spent by all MPI ranks when Workload \Rmnum{1} is running under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}.
+The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.
 The contiguous placement coupled with minimal routing (CM) results in highest communication time.
-When contiguous placement coupled with progressive adaptive and adaptive routing (CA, CPA), Workload \Rmnum{1} spends comparable amount of time to complete communication.
-The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.
+When coupled with (progressive) adaptive routing (CA, CPA), the communication time can be reduced but still higher than random placement polices.
 
@@
     \end{subfigure}%
-   \caption{The aggregate traffic and saturated time of links in different level in the dragonfly network when Workload \Rmnum{1} running under 6 different placement and routing configurations.
-``CA" and ``CPA" have comparably same performance and the corresponding lines are overlapped.
+   \caption{The aggregate traffic and saturated time of the dragonfly network when Workload \Rmnum{1} running under 6 different placement and routing configurations.
+``CA" and ``CPA" performs comparably, the corresponding lines are overlapped.
 }
@@
 
-Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{1} is running on dragonfly network with 6 different placement and routing configurations.
-
-%global link traffic and busy time explanation
-When Workload \Rmnum{1} running with contiguous placement and minimal routing(CM), all its traffic is happening in the contiguously allocated groups, causing congestion along certain shortest paths from source routers to destination routers.
-Both the traffic through the global channels in those congested paths and the corresponding saturated time are the highest compared with other configurations, shown as the blue dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
-When contiguous placement is coupled with (progressive) adaptive routing (CA and CPA), the traffic through congested global channels will be greatly reduced, so does corresponding saturated time, shown as the red and green dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
+Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels as well as the corresponding saturated time when Workload \Rmnum{1} is running on dragonfly network with 6 different placement and routing configurations.
+When contiguous placement and minimal routing(CM) is in use, all the traffic goes within the contiguously allocated groups, causing congestion along certain shortest paths from source to destination routers.
+Both the traffic and the corresponding saturated time of global channels are the highest compared with other configurations, shown as the blue dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
+When contiguous placement is coupled with (progressive) adaptive routing (CA and CPA), the traffic through congested global channels will be greatly reduced, so does the corresponding saturated time, shown as the red and green dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
 Since (progressive) adaptive routing are congestion aware, the traffic would be redirected to the intermediate routers in other idle groups when congestion occurs, thus the traffic burden on the contiguously allocated groups will be alleviated.
@@
 Random placement policy performs comparably with three different routing policies.
-Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic go through global channels are quite balanced across all the routers in the network, thus no particular global channel will suffer high traffic burden.
-When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by adaptive and progressive routing, which results in generating less traffic.
+Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic through global channels are quite balanced across all the routers, thus no particular global channel will suffer high traffic burden.
+When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic.
 That's why the blue solid line is lower than the red and green solid line.
@@
 
-We observe similar phenomena from the local channel traffic (Figure \ref{fig:local-channel-traffic}) and saturated time (Figure \ref{fig:local-channel-stime}).
-Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus high aggregate traffic on the local channels of certain routers.
+We observe similar phenomena from the local channel traffic and saturated time, shown in Figure \ref{fig:local-channel-traffic}, \ref{fig:local-channel-stime}).
+Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus the aggregate traffic through local channels of certain routers is quite high.
 Even with adaptive or progressive adaptive routing, the local congestion caused by grouping all MPI ranks in the same group(s) in contiguous placement can not be eliminated.
@@
 %terminal link traffic and busy time explanation
-Figure \ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which won't change when different placement and routing configurations in use.
+Figure \ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which stay the same when different placement and routing configurations are in use.
 All 6 lines are overlapped in Figure \ref{fig:terminal-link-traffic}.
-However, due to the traffic changes on global and local channels, the saturated time of terminal links will experience variability when different routing schemes in use, as shown in Figure \ref{fig:terminal-link-stime}.
+However, due to the traffic changes on global and local channels, the saturated time of terminal links will experience variability when different routing schemes are in use, as shown in Figure \ref{fig:terminal-link-stime}.
 When contiguous placement coupled with minimal routing(CM), the accumulated congestion on local and global channels cause extremely long saturated time on the terminal link, shown as the blue dashed line in Figure \ref{fig:terminal-link-stime}.
@@
 As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MultiGrid and CrystalRouter suffer the longest communication time when running with contiguous placement and minimal routing (CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter is significantly reduced.
+When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter are significantly reduced.
 Random placement further reduces their communication time, and reaches the best performance when coupled with (progressive) adaptive routing (RPA, RA).
-Both MultiGrid and CrystalRouter show the same trend as the workload when running under different placement and routing configurations.
-
+Both MultiGrid and CrystalRouter show the same trend when they are running under different placement and routing configurations.
 AMG is quite an exception.
-As shown in Figure \ref{fig:amg-commtime}, the communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA).
+The communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA), shown in Figure \ref{fig:amg-commtime}.
 The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
-The performance of AMG running under contiguous placement coupled with minimal routing (CM) is no better than random coupled with minimal routing (RM), but still much better than random with (progressive) adaptive routing (RPA, RA).
+CM is no better than RM, but still much better RPA, RA.
 
@@
    \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" have comparably same performance and the corresponding lines are overlapped.
+``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
 More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
@@
 AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use.
-The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slow down AMG's communication.
+The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slowing down AMG's communication.
 \footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
@@
 Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
-However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.
+%However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.
 
@@
 
-In this section, we will verify the observations made in the previous section when Workload \Rmnum{1 } is running on dragonfly network under different placement and routing configurations.
-By generating a synthetic application, we turn the ``bully" into ``bullee".
-
-The synthetic application, sAMG, is generated by increasing AMG data transfer amount by 100x.
-We run the Workload \Rmnum{2 } that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with different placement and routing configurations.
-As shown in Table \ref{tab:apps-detail}, sAMG become the most communication-intensive application in Workload \Rmnum{2 }.
+In this section, we will verify the observations made in the previous section when Workload \Rmnum{1} is running on the dragonfly network under different placement and routing configurations.
+We conduct the same sets of experiments with Workload \Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter.
+By replacing AMG with sAMG, we turn the ``bully" into ``bullee".
 
@@
 The average communication time spent by all MPI ranks when Workload \Rmnum{2} is running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
-Since the total data transfer amount of Workload \Rmnum{2} increases a lot due to the presence of sAMG, the time spent on communication under all configurations increase as well.
 The contiguous placement coupled with minimal routing results in highest communication time.
@@
 And they have comparable results when coupled contiguous placement.
-The performance of Workload \Rmnum{2} under different configurations keep the same trend as it of Workload \Rmnum{1}.
-
-Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running on dragonfly network with 6 different placement and routing configurations.
+The performance of Workload \Rmnum{2} under different configurations keep the similar pattern as it of Workload \Rmnum{1}.
+
+Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running with 6 different configurations.
 Contiguous placement coupled with minimal routing(CM) results in most traffic go through certain local and global channel, thus the longest saturated time for terminal link, local and global channel.
-When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion can get alleviated.
-The random placement coupled with any routing policy(RM, RA, RPA) performs comparably in terms of both traffic and saturated time.
-They are better than contiguous placement and minimal routing(CM), but not too much improvement against contiguous and (progressive) adaptive (CA, CPA).
+When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion could be mitigated.
+The random placement coupled with any routing policy(RM, RA, RPA) performs comparably.
+They are better than contiguous placement and minimal routing(CM), but only little improvement against contiguous and (progressive) adaptive (CA, CPA).
 
@@
 When random placement coupled with (progressive) adaptive routing is in use, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
-sAMG on the other hand benefits from random placement, shown in Figure \ref{fig:syn-samg-commtime}.
-Contiguous placement coupled with minimal routing prevents applications from sharing network resource, thus guarantee the performance of less communication intensive applications like MultiGrid and CrystalRouter while causing severe performance degradation to sAMG.
+Whereas, sAMG benefits from random placement and (progressive) adaptive routing, shown in Figure \ref{fig:syn-samg-commtime}.
+Contiguous placement coupled with minimal routing prevents applications from sharing network resource, guaranteeing the performance of less communication intensive applications like MultiGrid and CrystalRouter and causing severe performance degradation to sAMG.
 
@@
 % explain the network status of sAMG, MG and CR
-We look into the network level to scrutinize the traffic go through the routers serving each application.
+We look into the network level to scrutinize the traffic through the routers serving each application.
 Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers serving sAMG.
 The traffic skyrockets in both local and global channels when contiguous placement coupled with minimal routing (CM) is in use.
-The congestion will be alleviated in both local and global channels, when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use.
+The congestion will be alleviated in both local and global channels when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use.
 Random placement can further reduce the traffic burden on local and global channels by uniformly distributing sAMG traffic over the network.
@@
    \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" have comparably the same performance and the corresponding lines are overlapped.
+``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
 More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
@@
 
-The precaution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs.
+The precaution to stop ``bully" behavior is to avoid network sharing between concurrently running jobs.
 Using contiguous placement and minimal routing could be a way to avoid network sharing, but network performance could suffer degradation due to local congestion.
-Running each job with dedicated routing policy with regard to communication intensity is unrealistic, since routing policy is pre-configured in the system and can not be changed on the fly upon each job submission.
-However, the job placement policies could be versatile, assigning different allocation (contiguous or random) to specific application.
+Running each job with dedicated routing policy is unrealistic, since routing policy is pre-configured and can not be changed on the fly upon job submission.
+However, the job placement policies can be versatile for assigning different allocation (contiguous or random) to specific application.
 
 Thus, we propose the hybrid placement as a reconcile solution.
-In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation.
+In the hybrid placement, the less communication-intensive applications get contiguous allocation while the communication-intensive ones get random allocation.
 We evaluate the effect of hybrid placement on improving network performance as well as preserving the performance of individual application.
-In the experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations.
+In following experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations.
+\footnote{Due to page limit, we won't present the analysis about network traffic and saturated time in this section.}
 
@@
 
-Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing policies, together with other configurations.
+Figure \ref{fig:hyb-plcmt-apps-commtime} shows the communication time of each application when hybrid placement configurations are in use.
 MultiGrid and CrystalRouter have basically the same performance with hybrid placement as compared with random placement.
 Since they still get random allocation in the hybrid placement.
-
 The performance of AMG is significantly improved when hybrid placement is in use.
@@
 This is due the contiguous allocation assigned to AMG in the hybrid placement policy.
-Thus, AMG can avoid sharing routers or groups with other applications in hybrid placement policy.
-When being coupled with minimal routing,
-hybrid placement and contiguous placement have similar performance for AMG.
-This is because the contiguous allocation assigned to AMG and minimal routing can prevent other applications  form sharing network resource with AMG.
+When being coupled with minimal routing, hybrid placement and contiguous placement have similar performance for AMG.
 However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG.
@@
 
-\emph{Compared with random placement policy, hybrid placement can guarantee similar network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.
+\emph{Compared with random placement policy, hybrid placement can guarantee comparable network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.
 
 \emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.} Hybrid placement policy preserves contiguous allocation for less communication-intensive application, prevents network resource from being shared by others.
-Unlike random placement which indulges ``bully", hybrid placement can restrain it to some extent.
+Unlike random placement indulging the ``bully", hybrid placement can restrain it to some extent.
 
@@
 
-The impact of job placement to both system and application always catch researchers appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
+The impact of job placement to both system and application always catches researchers' appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
 Skinner et al.
@@
 Bhatele et al.
-studied the performance variability of a specific application, p3FD, running on different production system \cite{abhinav-sc13}.
+studied the performance variability of a specific application, p3FD, running on different production systems with torus networks \cite{abhinav-sc13}.
 They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource.
@@
 Jain et al.
-conducted a comprehensive analysis of various job placement and routing scheme with regard to network link throughput on dragonfly network \cite{jain-sc14}.
+conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network \cite{jain-sc14}.
 Their work is based on an analytical model and synthetic workload.
 Bhatele et al.
-used simulation to study the performance of synthetic workload under the different task mapping and routing schemes on two-level direct networks \cite{bhatele-sc11}.
+used simulation to study the performance of synthetic workload under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.
 
@@
 Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
-We found that although random placement coupled with adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation.
-Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network status when application is running.
+We found that although random placement coupled with adaptive routing can improve the network performance, the less communication-intensive applications in the workload may suffer performance degradation.
+Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network performance when application is running.
 The traffic and saturated time of router's each link are valuable information for detailed analysis.
@@
 In this paper, we have conducted extensive study about application's behavior when running on dragonfly network with different job placement and routing configurations.
-We resorted to CODES, a high-fidelity HPC network simulation tool, and used three parallel scientific applications traces collected from production system to analysis the applications' behavior on network level.
-We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network to reach load balance and hot-spots free for the network, the performance of certain application would be impaired.
-We identify this phenomenon as ``bully" between concurrently running applications, and the victim always being the less communication-intensive one.
-On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, the configuration can guarantee the performance of ``bullee" application by limiting the network sharing between concurrently running peers.
-
-Due the presence of this ``bully", we suggest that when the batch scheduler make job placement for workload on dragonfly system, random placement shouldn't be the rule of thumb.
-Instead, the placement should made with consideration of jobs communication intensity.
-The less intensive application should get contiguous allocation coupled with adaptive routing, the intensive ones should get random allocation coupled with minimal routing.
+We resorted to CODES, a high-fidelity HPC network simulation tool, and used three parallel scientific applications traces collected from production system to analyze the applications' behavior on network level.
+We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network to reach load balance and hot-spots free for the network, the performance of certain job would be impaired.
+We identify this phenomenon as ``bully" between concurrently running jobs, and the victim always being the less communication-intensive one.
+On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, it can guarantee the performance of ``bullee" application by limiting the network sharing from concurrently running peers.
+
+Due the presence of this ``bully", we propose to use hybrid placement policy for workload running on systems with dragonfly networks.
+In hybrid placement policy, the less intensive applications get contiguous allocations, and the intensive ones get random allocations.
 We believe the findings presented in this paper can illuminate a path to more efficient workload manager for future systems with dragonfly network.

### 2016-03-30 draft.tex
made changes for section 1, 2, 3

@@
 \label{sec:network}
-The dragonfly is a two-level hierarchical topology.
-It consists of several groups connected by all-to-all links.
-In each group, there could be ``a" number of routers connected via all-to-all local channels.
-For each router, there could be ``p" number of compute nodes attached to it via terminal links.
-The router has ``h" number of global channels that used as intergroup connections through which the router connected to other routers in different groups.
+The dragonfly is a two-level hierarchical topology, consisting of several groups connected by all-to-all links.
+In each group, there could be $a$ routers connected via all-to-all local channels.
+For each router, there could be $p$ compute nodes attached to it via terminal links.
+The router has $h$ global channels used as intergroup connections through which the router connected to other routers in different groups.
 Thus, the radix of each router is $k = a+h+p-1$.
-Different computing centers could choose different values for ``a", ``p" and ``h" when deploying their dragonfly network.
+Different computing centers could choose different values for  $a$, $h$, $p$ when deploying their dragonfly network.
 The adoption of proper $a$, $h$, $p$ involves many factors, such as system scale, building cost and workload.
 
-It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$ \cite{kim-micro}.
-Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g $.
-An implementation of dragonfly network follows such configuration is illustrated in Figure \ref{fig:dragonfly-overview}.
-There are 6 routers in each group, each router has 3 compute nodes attached to it.
-This dragonfly implementation consists of 19 groups and 342 nodes in total.
+It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}.
+Under this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $.
+An implementation of dragonfly network follows such configuration is illustrated in Figure~\ref{fig:dragonfly-overview}.
+There are six routers in each group, each router has three compute nodes attached to it.
+This dragonfly network consists of 19 groups and 342 nodes in total.
 
@@
   \caption{Dragonfly Network Overview.
-There are 19 groups, 6 routers in each group, 3 compute nodes connected to each router, 342 nodes in total.
-Job $J1$ requires for 7 nodes, gets its allocation by random placement.
-Job $J2$ requires for 8 nodes, gets its allocation by contiguous placement.
-}
+There are 19 groups, six routers in each group, three compute nodes connected to each router, 342 nodes in total.
+Job $J1$ requires seven nodes, getting its allocation by random placement.
+Job $J2$ requires eight nodes, getting its allocation by contiguous placement.}
   \label{fig:dragonfly-overview}
@@
 
-For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning the tasks of the application onto the system by a system software such as batch scheduler \cite{xu-cluster14}.
+For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning tasks of the application onto the system by a system software such as batch scheduler~\cite{xu-cluster14}.
 In this work, we study two alternative placement policies considered by the community for dragonfly systems:
 
-\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to job in a consecutive manner.
-The assignment fills up a group first, only crosses group boundaries and start to fill the next group as necessary.
-Shown in Figure \ref{fig:dragonfly-overview}, $J2$ gets the required amount of nodes by contiguous placement.
+\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to a job in a consecutive manner.
+The assignment first fills up a group, then crosses group boundaries and starts to fill the next group if necessary.
+As shown in Figure~\ref{fig:dragonfly-overview}, $J2$ gets eight nodes by contiguous placement.
 Contiguous placement confines the tasks of a job into the same group, which may result in local network congestion and increase the possibility of hot-spots.
 
-\textbf{Random Placement:} In this policy, job will get a set of nodes that randomly selected from all the available nodes in the system.
-The nodes assigned to $J1$ in Figure \ref{fig:dragonfly-overview} would be attached to different routers in different groups.
+\textbf{Random Placement:} In this policy, a job gets a set of nodes randomly selected from all the available nodes in the system.
+The nodes assigned to $J1$ in Figure~\ref{fig:dragonfly-overview} are attached to different routers in different groups.
 Routers may be shared by different jobs when random placement is in use.
-Random placement can distribute the tasks of a job uniformly across the whole system, thus avoid the possible local congestion and reach load balance.
+Random placement can distribute the tasks of a job uniformly across the whole system to avoid the possible local congestion.
 However, random placement may cause possible congestion on global links.
@@
 \label{sec:routing-schemes}
+
 The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router.
-Previously studied routing policies for dragonfly network include minimal routing, adaptive routing \cite{dally-dragonfly}, progressive adaptive routing\cite{jiang} and some of their variations \cite{won-prog-adaptive}.
+Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
 In this work we study three widely adopted routing policies on dragonfly networks.
 
-\textbf{Minimal:} In this policy, a message from source router takes the the shortest path to the destination router.
+\textbf{Minimal:} In this policy, a message takes the shortest path from the source router to the destination router.
 When there are multiple shortest paths between the source and destination router, the message will be evenly divided among the paths.
@@
 
-\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest path, depending on the congestion situation along that path.
+\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest paths, depending on the congestion situation along those paths.
 For the non-shortest path, an intermediate router will be randomly chosen.
-The message first takes the shortest path from source to that intermediate router, then it takes the shortest path from that intermediate router to the destination.
-Since routing path is chosen adaptively based on the congestion situation, adaptive routing can avoid local congestion and possible hot-spots.
-Adaptive routing collapses to minimal routing in the absence of traffic congestion.
+The message takes the intermediate router as a via point, connecting the source and destination router through two separate shortest paths.
+Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.
 
 \textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated.
-Any decision to route non-minimally at source router or at a subsequent hop is permanent and won't be re-evaluated \cite{jiang}.
-The progressive adaptive is capable of handling the case where a global link is congested but this information has not yet propagated back to the source router \cite{jiang}.
+Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}.
+The progressive adaptive is capable of handling the case where a global channel is congested but the source router has not been informed yet~\cite{jiang}.
 The packet will take the non-minimal route only when the congestion is encountered.
@@
 
-It is difficult to experiment with concurrently running jobs on HPC system \cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
-One reason is that job placement and routing policies are part of system configuration, it is impossible for user to make changes at will.
+It is difficult to experiment with concurrently running jobs on HPC system~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
+One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will.
 Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
-Last but not least, configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
+The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
 Therefore, we resort to simulation in our work.
@@
 \label{sec:simulation-tool}
-A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability \cite{codes}.
-CODES supports dragonfly network\cite{codes-dragonfly} \cite{misbah-tpds}, as well as other topologies such as torus\cite{misbah-pads-2014}\cite{ning-pads-2011} and fat-tree\cite{ning-pads-2015}, with packet-level high-fidelity simulation.
-It can drive these models through an MPI simulation later that utilizing DUMPI traces\cite{sst}.
-In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on dragonfly network.
+
+A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability~\cite{codes}.
+CODES supports dragonfly~\cite{codes-dragonfly}~\cite{misbah-tpds}, torus~\cite{misbah-pads-2014}~\cite{ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
+It can drive these models through an MPI simulation layer utilizing DUMPI traces~\cite{sst}.
+In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on the dragonfly network.
 
@@
 
-We choose three representative parallel applications from the DOE Design Forward Project\cite{designforwardwebpage}.
-We believe these applications can be representative of a wide array of applications running on leadership-class supercomputers.
-Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from production elliptic solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
+We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent of a wide array of applications running on leadership-class supercomputers.
+Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
 
 \textbf{AMG:} The Algebraic MultiGrid Solver is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
-It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL \cite{amg}.
-
-\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes \cite{boxlib}.
-It is widely used for structured grid physics packages.
-
-\textbf{CrystalRouter:} The CrystalRouter MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory.
+It has been derived directly from the BoomerAMG solver developed in the Center for Applied Scientific Computing (CASC) at LLNL~\cite{amg}.
+
+\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes~\cite{boxlib}, which are used for structured grid physics packages.
+
+\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
 It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.
@@
 
-The parameters for building the dragonfly network been studied in our work are inspired the model proposed by Kim et.
-al \cite{kim-micro}.
-Our dragonfly network consists of 33 groups, each group contains 8 routers, and each router has 4 compute nodes attached to it.
+The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et.
+al~\cite{kim-micro}.
+Our dragonfly network consists of 33 groups, each of which contains 8 routers.
+Each router has four compute nodes attached to it.
 Overall, there are 264 routers and 1056 compute nodes in the network.
-The aggregated bandwidth of terminal link,  local and global channels are proportional to those of Cray Cascade system\cite{faanes}.
-In this work, we study network performance as well as job interference when 6 different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table \ref{tab: placement routing configs}.\footnote{With respect to random placement, we experiment with 50 sets of distinctive allocation generated by random placement.
+The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}.
+In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.
+
+%\footnote{With respect to random placement, we experiment with 50 sets of distinctive allocation generated by random placement.
 The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.}
@@
 
-Our analysis focus on the following metrics:
+Our analysis focuses on the following metrics:
 \begin{itemize}
 
-    \item \textbf{Network Traffic:} The traffic refers to the amount of data go through each port of the router.
-For each router, the traffic go through its terminal link, local channel and global channel are analyzed respectively.
-
-    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of certain port is full. Saturated time can denote the congestion on certain port.
-
-    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time spent by the rank to complete its message exchange with all other ranks.
-For each job, this metric refers to the time spent to complete the message exchange by all its ranks.
+    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router.
+
+    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full.
+We analyze the saturated time of ports corresponding to terminal link, local and global channel.
+
+    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks.
+\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in our experiments.
+}
 
 \end{itemize}
-
-Since our study focus on network performance and job interference during communication, the time spent in computation by each MPI rank will not be counted in our experiments.
 
@@
 Two sets of parallel workloads are used in this work.
-Workload \Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
-As we see in Table \ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload \Rmnum{1}.
-Workload \Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
+Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
+In Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}.
+Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
 sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x.
-sAMG is the most communication-intensive job in Workload \Rmnum{2}.
-
-Workload \Rmnum{1} is used to identify the ``bully" behavior between concurrently running jobs on dragonfly network.
-Workload \Rmnum{2} is used to verify the results and conclusion obtained from the study about Workload \Rmnum{1}.
+sAMG is the most communication-intensive job in Workload~\Rmnum{2}.
+
+Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running jobs on the dragonfly network.
+Workload~\Rmnum{2} is used to verify the results and conclusion obtained from the study of Workload~\Rmnum{1}.
 
@@
 
-\section{Study of Parallel Workload \Rmnum{1}}
+\section{Study of Parallel Workload~\Rmnum{1}}
 %\section{Identify the ``Bully"}
@@
 
-We study the network performance as well as job interference from two perspectives.
-First, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
-Then, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic go through the routers that serving each job.
-These analysis allow us to identify the ``bully" in the workload.
+We study the network performance and job interference from two perspectives.
+Firstly, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
+Secondly, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic going through the routers that serve each job.
+The analysis allows us to identify the ``bully" in the workload.
 
@@
 \begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under 6 different placement and routing configurations.} 
+\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
 \label{tab:wkld-commtime}

### 2016-03-30 draft.tex
change the first paragraph in section 3

@@
 
-It is difficult to experiment with concurrently running jobs on HPC system~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
+Configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
+Even with access to systems with such networks, job placement and routing policies are part of system configuration, which is impossible for user to make changes at will~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
+Therefore, we resort to simulation in our work.
+
+%It is difficult to experiment with concurrently running jobs on HPC systems~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
 One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will.
@@
 
-We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent of a wide array of applications running on leadership-class supercomputers.
+We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent a wide array of applications running on leadership-class supercomputers.
 Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
@@
 
-\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
+\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000~\cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
 It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.
@@
 al~\cite{kim-micro}.
-Our dragonfly network consists of 33 groups, each of which contains 8 routers.
+Our dragonfly network consists of 33 groups, each of which contains eight routers.
 Each router has four compute nodes attached to it.
@@
 
-    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router.
+    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router.
+We analyze the traffic on the terminal link, local and global channel of each router.
+The network reaches optimal performance when the traffic is uniformly distributed and no particular router is over-loaded.
 
@@
 We analyze the saturated time of ports corresponding to terminal link, local and global channel.
+The saturated time indicates the congestion level of routers.
 
     \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks.
-\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in our experiments.
+The performance of each application is measured by the communication time.
+\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in the experiments.
 }
@@
 \label{sec:workload-1}
-
-We study the network performance and job interference from two perspectives.
-Firstly, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
-Secondly, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic going through the routers that serve each job.
+The study of parallel workload~\Rmnum{1} consists of two parts.
+Firstly, we analyze the over-all network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
+Secondly, we isolate each application from the workload, analyzing its performance and the interference form its peers by scrutinizing the traffic going through the routers that serve each job.
 The analysis allows us to identify the ``bully" in the workload.

### 2016-03-30 background.tex
put each section into separate .tex file

--- 2016-03-30 draft.tex
@@
-%% bare_conf_compsoc.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE Computer
-%% Society conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-\documentclass[conference,compsoc]{IEEEtran}
-% Some/most Computer Society conferences require the compsoc mode option,
-% but others may want the standard conference format.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference,compsoc]{../sty/IEEEtran}
-
-% *** MISC UTILITY PACKAGES ***
-%
-\usepackage{ifpdf}
-\usepackage{framed}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage{cite}
-\fi
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage{amsmath}
-\usepackage{cuted}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a sans serif font rather
-% than the serif font used in traditional IEEE formatting and thus the need
-% to invoke different subfig.sty package options depending on whether
-% compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-\usepackage{verbatim}
-\usepackage{soul}
-\usepackage{xcolor}
-\newcommand{\TODO}[1]{\hl{TODO: #1}}
-\newcommand{\NOTE}[1]{\hl {NOTE: #1}}
-\newcommand{\changed}[1]{\textcolor{red}{#1}}
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-\usepackage{graphicx} % Required for including pictures
-\graphicspath{{pics/}} % Specifies the directory where pictures are stored
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{booktabs}
-\usepackage{multirow} % make table
-
-\makeatletter % Put Roman Number in Text
-\newcommand{\rmnum}[1]{\romannumeral #1}
-\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
-\makeatother
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Watch Out for the Bully! Job Interference Study on Dragonfly Network}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-% \author{\IEEEauthorblockN{Michael Shell}
-% \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-% Georgia Institute of Technology\\
-% Atlanta, Georgia 30332--0250\\
-% Email: http://www.michaelshell.org/contact.html}
-% \and
-% \IEEEauthorblockN{Homer Simpson}
-% \IEEEauthorblockA{Twentieth Century Fox\\
-% Springfield, USA\\
-% Email: homer@thesimpsons.com}
-% \and
-% \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-% \IEEEauthorblockA{Starfleet Academy\\
-% San Francisco, California 96678-2391\\
-% Telephone: (800) 555--1212\\
-% Fax: (888) 555--1212}}
-
-\author{
-
-\IEEEauthorblockN{Xu Yang\IEEEauthorrefmark{1}, John Jenkins\IEEEauthorrefmark{2}, Misbah Mubarak\IEEEauthorrefmark{2}, Robert B. Ross\IEEEauthorrefmark{2}, Zhiling Lan\IEEEauthorrefmark{1}}
-
-\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science,
-Illinois Institute of Technology,
-Chicago, Illinois, USA 60616\\
-\{xyang56\}@hawk.iit.edu, lan@iit.edu}
-
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Mathematics and Computer Science Division, Argonne National Laboratory,
-Argonne, IL, USA 60439\\
-\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}
-}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page (and note that there is less available width in this regard for
-% compsoc conferences compared to traditional conferences), use this
-% alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
-\begin{abstract}
-
-The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers.
-Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks, since random placement with adaptive routing can uniformly distribute traffic over the network and alleviate congestion.
-However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network when multiple jobs are running concurrently, they can not guarantee the best performance for each single job.
-The performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs.
-We refer this phenomenon as ``bully" between concurrently running jobs.
-We presented a detailed analysis about this ``bully" behavior between jobs at the network level based on a sophisticated, high-fidelity discrete even-driven simulation tool.
-The observations and analysis presented in this work illuminate a path to the adoption of more efficient job placement policy and routing algorithm for HPC systems with dragonfly network.
-
-\end{abstract}
-
-% no keywords
-
-% \keywords{Dragonfly, Job placement, Routing, Interference}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-\label{sec:intro}
-
-The low latency and high bandwidth interconnect network plays a critical role in HPC system performance.
-As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scarce resource.
-The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
-This make the dragonfly network a very promising choice for building petaflop and beyond supercomputers.
-%The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
-
-While dragonfly topologies provide low-latency and high-bandwidth networking, efficiently utilizing it is a significant concern.
-In particular, intelligent job placement to avoid interference is of paramount importance to guarantee the performance of each job when it shares network resources with other concurrently running peers \cite{bhatele2015, dskinner}.
-Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
-
-In this work, we study the interference between concurrently running jobs on dragonfly networks with different job placement and routing policies.
-We use CODES, an HPC network simulation toolkit with high fidelity and excellent scalability for packet level simulation \cite{codes}.
-Unlike much existing work that rely on synthetic workloads, we use traces of three representative applications from the DOE Design Forward Project \cite{designforwardwebpage}.
-The advantage of using real application traces is straight forward: these traces can capture detailed application communication behaviors that are  omitted in synthetic workload for simplification.
-Applications are usually distinctive from each other in data transfer amount, communication pattern, operation dependency etc., which can be impractical to reproduce in a synthetic workload.
-
-We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies.
-We analyze the performance of network as well as individual application when running with different placement and routing configurations.
-Our evaluation is based on more than 1000 runs of simulation.
-We make the following interesting observations through extensive simulation.
-
-\begin{itemize}
-
-    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion, optimizing the overall performance of the dragonfly network.
-
-    \item The ``bully" behavior occurs between concurrently running jobs on a dragonfly network when random placement and adaptive routing are in use.
-Communication-intensive jobs obtain performance improvement at the expense of less intensive jobs suffering performance degradation.
-
-    \item Random placement coupled with adaptive routing can improve the performance of communication-intensive jobs by enabling network resource sharing, though it introduces interference between concurrently running jobs.
-
-    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of less communication-intensive jobs by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
-
-\end{itemize}
-
-Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to the job communication intensity.
-\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
-We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
-For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks.
-System software developers could design better scheduling algorithms for jobs with distinct communication behavior.
-System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.
-
-The rest of this paper is organized as follows.
-Section \ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies.
-Section \ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
-Section \ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations.
-Section \ref{sec:workload-2} validates the observations we obtain from previous section.
-Section \ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network.
-Section \ref{sec:related work} discusses the related work.
-Finally, the conclusion is presented in Section \ref{sec:conclusion}.
-
 \section{Background}
@@
 The packet will take the non-minimal route only when the congestion is encountered.
-
-\section{Methodology}
-\label{sec: methodology}
-
-It is difficult to experiment with concurrently running jobs on HPC system~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
-One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will.
-Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
-The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
-Therefore, we resort to simulation in our work.
-
-\subsection{Simulation Tool}
-\label{sec:simulation-tool}
-
-A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability~\cite{codes}.
-CODES supports dragonfly~\cite{codes-dragonfly}~\cite{misbah-tpds}, torus~\cite{misbah-pads-2014}~\cite{ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
-It can drive these models through an MPI simulation layer utilizing DUMPI traces~\cite{sst}.
-In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on the dragonfly network.
-
-\subsection{Parallel Applications}
-\label{sec: application traces}
-
-We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent of a wide array of applications running on leadership-class supercomputers.
-Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
-
-\textbf{AMG:} The Algebraic MultiGrid Solver is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
-It has been derived directly from the BoomerAMG solver developed in the Center for Applied Scientific Computing (CASC) at LLNL~\cite{amg}.
-
-\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes~\cite{boxlib}, which are used for structured grid physics packages.
-
-\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
-It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.
-
-\subsection{System Configuration}
-\label{sec: simulation configuration}
-
-The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et.
-al~\cite{kim-micro}.
-Our dragonfly network consists of 33 groups, each of which contains 8 routers.
-Each router has four compute nodes attached to it.
-Overall, there are 264 routers and 1056 compute nodes in the network.
-The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}.
-In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.
-
-%\footnote{With respect to random placement, we experiment with 50 sets of distinctive allocation generated by random placement.
-The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.}
-
-\begin{table}[ht]
-\begin{center}
-\caption{The notation for different placement and routing configurations} 
-\label{tab: placement routing configs}
-\begin{tabular}{l c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{3}{c}{Routing Policies} \\ 
-\cmidrule(l){2-4}
-Placement Policies & Minimal & Adaptive & Progressive Adaptive\\ % Column names row
-\midrule % In-table horizontal line
-Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
-\midrule
-Random  &   RM  &   RA   &  RPA   \\ 
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-Our analysis focuses on the following metrics:
-\begin{itemize}
-
-    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router.
-
-    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full.
-We analyze the saturated time of ports corresponding to terminal link, local and global channel.
-
-    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks.
-\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in our experiments.
-}
-
-\end{itemize}
-
-\subsection{Workload Summary}
-\label{sec:workload summary}
-
-Two sets of parallel workloads are used in this work.
-Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
-In Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}.
-Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
-sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x.
-sAMG is the most communication-intensive job in Workload~\Rmnum{2}.
-
-Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running jobs on the dragonfly network.
-Workload~\Rmnum{2} is used to verify the results and conclusion obtained from the study of Workload~\Rmnum{1}.
-
-%Table \ref{tab:apps-detail} summarizes the details of each application.
-It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.
-
-\begin{table}[ht]
-\begin{center}
-\caption{The details of each application.} 
-\label{tab:apps-detail}
-\begin{tabular}{l c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{3}{c}{Application Details} \\ 
-\cmidrule(l){2-4}
-App Name & Num. Rank & Avg. Data/Rank & Total Data\\ % Column names row
-\midrule % In-table horizontal line
-AMG  &    216 &   0.6MB   &     130MB\\ % Content row 1
-\midrule
-MultiGrid  &    125 &   5MB   &     625MB\\ 
-\midrule
-CrystalRouter  &   100  &  35MB    &     3500MB\\ 
-\midrule
-sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Study of Parallel Workload~\Rmnum{1}}
-%\section{Identify the ``Bully"}
-\label{sec:workload-1}
-
-We study the network performance and job interference from two perspectives.
-Firstly, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
-Secondly, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic going through the routers that serve each job.
-The analysis allows us to identify the ``bully" in the workload.
-
-\subsection{Network Performance Analysis}
-\label{sec: workload-1 network analysis}
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
-\label{tab:wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
-\cmidrule(l){2-7}
-	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The average communication time spent by all MPI ranks when Workload \Rmnum{1} is running under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}.
-The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.
-The contiguous placement coupled with minimal routing (CM) results in highest communication time.
-When coupled with (progressive) adaptive routing (CA, CPA), the communication time can be reduced but still higher than random placement polices.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:global-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:local-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:terminal-link-traffic}
-    \end{subfigure}\\
-
-    \centering   
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-stime}
-        \caption{Global Channel Saturated Time}
-        \label{fig:global-channel-stime}
-    \end{subfigure}\hfill
-     \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-stime}
-        \caption{Local Channel Saturated Time}
-        \label{fig:local-channel-stime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-stime}
-        \caption{Terminal Link Saturated Time}
-        \label{fig:terminal-link-stime}
-    \end{subfigure}%
-   \caption{The aggregate traffic and saturated time of the dragonfly network when Workload \Rmnum{1} running under 6 different placement and routing configurations.
-``CA" and ``CPA" performs comparably, the corresponding lines are overlapped.
-}
-   \label{fig:wkld-network-traffic-stime}
-\end{figure*}
-
-Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels as well as the corresponding saturated time when Workload \Rmnum{1} is running on dragonfly network with 6 different placement and routing configurations.
-When contiguous placement and minimal routing(CM) is in use, all the traffic goes within the contiguously allocated groups, causing congestion along certain shortest paths from source to destination routers.
-Both the traffic and the corresponding saturated time of global channels are the highest compared with other configurations, shown as the blue dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
-When contiguous placement is coupled with (progressive) adaptive routing (CA and CPA), the traffic through congested global channels will be greatly reduced, so does the corresponding saturated time, shown as the red and green dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
-Since (progressive) adaptive routing are congestion aware, the traffic would be redirected to the intermediate routers in other idle groups when congestion occurs, thus the traffic burden on the contiguously allocated groups will be alleviated.
-
-Random placement policy performs comparably with three different routing policies.
-Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic through global channels are quite balanced across all the routers, thus no particular global channel will suffer high traffic burden.
-When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic.
-That's why the blue solid line is lower than the red and green solid line.
-Since the random placement can uniformly distribute traffic, there are no sudden surge of saturated time of global channel over the network, shown as solid lines in Figure \ref{fig:global-channel-stime}.
-
-%local channel traffic and busy time explanation
-
-We observe similar phenomena from the local channel traffic and saturated time, shown in Figure \ref{fig:local-channel-traffic}, \ref{fig:local-channel-stime}).
-Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus the aggregate traffic through local channels of certain routers is quite high.
-Even with adaptive or progressive adaptive routing, the local congestion caused by grouping all MPI ranks in the same group(s) in contiguous placement can not be eliminated.
-Random placement is effective at addressing this type of congestion.
-
-%terminal link traffic and busy time explanation
-Figure \ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which stay the same when different placement and routing configurations are in use.
-All 6 lines are overlapped in Figure \ref{fig:terminal-link-traffic}.
-However, due to the traffic changes on global and local channels, the saturated time of terminal links will experience variability when different routing schemes are in use, as shown in Figure \ref{fig:terminal-link-stime}.
-When contiguous placement coupled with minimal routing(CM), the accumulated congestion on local and global channels cause extremely long saturated time on the terminal link, shown as the blue dashed line in Figure \ref{fig:terminal-link-stime}.
-This again manifests the severe congestion caused by using contiguous placement and minimal routing.
-
-\subsection{Individual Application Analysis}
-\label{sec: workload-1 app analysis}
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/amg/commtime}
-        \caption{AMG}
-        \label{fig:amg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/mg/commtime}
-        \caption{MultiGrid}
-        \label{fig:mg-commtime}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/cr/commtime}
-        \caption{CrystalRouter}
-        \label{fig:cr-commtime}
-    \end{subfigure}%
-   \caption{The communication time of all ranks in each application.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
-Random placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
-   \label{fig:apps-commtime}
-\end{figure*}
-
-Figure \ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
-
-As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MultiGrid and CrystalRouter suffer the longest communication time when running with contiguous placement and minimal routing (CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter are significantly reduced.
-Random placement further reduces their communication time, and reaches the best performance when coupled with (progressive) adaptive routing (RPA, RA).
-Both MultiGrid and CrystalRouter show the same trend when they are running under different placement and routing configurations.
-AMG is quite an exception.
-The communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA), shown in Figure \ref{fig:amg-commtime}.
-The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
-CM is no better than RM, but still much better RPA, RA.
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
-        \caption{AMG Local Channel Traffic}
-        \label{fig:amg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
-        \label{fig:mg-lc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
-        \label{fig:cr-lc-traffic}
-    \end{subfigure}\\
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
-        \caption{AMG Global Channel Traffic}
-        \label{fig:amg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:mg-gc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:cr-gc-traffic}
-    \end{subfigure}%
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
-   \label{fig:3app-lc-gc-traffic}
-\end{figure*}
-
-% Show the evidence from network level, explain why AMG is different. 
-We look into network level to identify the culprit behind AMG's abnormal behavior with random placement and adaptive routing.
-By identifying the compute nodes each MPI rank resides on and routers that serving each application, we can see that the traffic go through the routers serving AMG skyrockets when random placement and adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and \ref{fig:amg-gc-traffic}.
-Adaptive routing will redirect the traffic of other applications to go through the routers belonging to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
-
-No router will be shared between applications under contiguous placement.
-A number of successive groups will be allocated to the same application under contiguous placement policy.
-When contiguous placement coupled with minimal routing, application will be free of interference from its concurrently running peers.
-However, application communication traffic will be confined within their allocated groups, thus congestion is very likely to happen depending on application communication intensity.
-As the lest communication-intensive application in Workload \Rmnum{1}, AMG can benefit from contiguous placement.
-Under contiguous placement, the traffic go through the local and global channels of the routers belonging to AMG is significantly lower than with random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
-
-MultiGrid and CrystalRouter are more communication-intensive compared with AMG.
-They will suffer congestion on both local and global channels when contiguous placement is in use, shown as the dashed line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-On the other hand, the random placement can uniformly distribute their traffic all over the network, alleviate the possible congestion, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-
-\subsection{Key Observations}
-In summary, based on the results presented in section \ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we have made the following observations.
-
-\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers.
-Therefore, the network could reach the status of load-balanced and hot-spots free.
-
-\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network random placement and adaptive routing are in use.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
-AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use.
-The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slowing down AMG's communication.
-\footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
-
-\emph{Consistent performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} The router and group sharing between jobs are prohibited in contiguous placement policy.
-The traffic won't be redirected from congested routers to less busy ones when minimal routing is in use.
-Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
-%However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.
-
-\section{Study of Parallel Workload \Rmnum{2 }}
-%\section{``Bully" become ``Bullee"}
-\label{sec:workload-2}
-
-In this section, we will verify the observations made in the previous section when Workload \Rmnum{1} is running on the dragonfly network under different placement and routing configurations.
-We conduct the same sets of experiments with Workload \Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter.
-By replacing AMG with sAMG, we turn the ``bully" into ``bullee".
-
-\subsection{Network Performance Analysis}
-\label{sec: workload-2 network analysis}
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under 6 different placement and routing configurations.} 
-\label{tab:syn-wkld-commtime}
-%\centering % Centers the table on the page, comment out to left-justify
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
-\cmidrule(l){2-7}
-	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The average communication time spent by all MPI ranks when Workload \Rmnum{2} is running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
-The contiguous placement coupled with minimal routing results in highest communication time.
-The random placement coupled with minimal routing is the most efficient.
-Progressive adaptive routing is better than adaptive routing when random placement is in use.
-And they have comparable results when coupled contiguous placement.
-The performance of Workload \Rmnum{2} under different configurations keep the similar pattern as it of Workload \Rmnum{1}.
-
-Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running with 6 different configurations.
-Contiguous placement coupled with minimal routing(CM) results in most traffic go through certain local and global channel, thus the longest saturated time for terminal link, local and global channel.
-When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion could be mitigated.
-The random placement coupled with any routing policy(RM, RA, RPA) performs comparably.
-They are better than contiguous placement and minimal routing(CM), but only little improvement against contiguous and (progressive) adaptive (CA, CPA).
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:synwkld-global-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:synwkld-local-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:synwkld-terminal-link-traffic}
-    \end{subfigure}\\
-
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
-        \caption{Global Channel Saturated Time}
-        \label{fig:synwkld-global-channel-stime}
-    \end{subfigure}\hfill
-     \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
-        \caption{Local Channel Saturated Time}
-        \label{fig:synwkld-local-channel-stime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
-        \caption{Terminal Link Saturated Time}
-        \label{fig:synwkld-terminal-link-stime}
-    \end{subfigure}%
-   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under 6 different placement and routing configurations.}
-   \label{fig:synwkld-network-traffic-stime}
-\end{figure*}
-
-\subsection{Individual Application Analysis}
-\label{sec: workload-2 app analysis}
-
-The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}.
-The ``bully" in Workload \Rmnum{1} becomes the ``bullyee" in Workload \Rmnum{2}.
-MultiGrid and CrystalRouter are the less communication-intensive applications in Workload \Rmnum{2}.
-When random placement coupled with (progressive) adaptive routing is in use, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
-Whereas, sAMG benefits from random placement and (progressive) adaptive routing, shown in Figure \ref{fig:syn-samg-commtime}.
-Contiguous placement coupled with minimal routing prevents applications from sharing network resource, guaranteeing the performance of less communication intensive applications like MultiGrid and CrystalRouter and causing severe performance degradation to sAMG.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
-        \caption{sAMG}
-        \label{fig:syn-samg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
-        \caption{MultiGrid}
-        \label{fig:syn-mg-commtime}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
-        \caption{CrystalRouter}
-        \label{fig:syn-cr-commtime}
-    \end{subfigure}%
-   \caption{The communication time of all ranks in each application.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
-The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullee", MultiGrid and CrystalRouter, suffer performance degradation.}
-   \label{fig:syn-apps-commtime}
-\end{figure*}
-
-% explain the network status of sAMG, MG and CR
-We look into the network level to scrutinize the traffic through the routers serving each application.
-Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers serving sAMG.
-The traffic skyrockets in both local and global channels when contiguous placement coupled with minimal routing (CM) is in use.
-The congestion will be alleviated in both local and global channels when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use.
-Random placement can further reduce the traffic burden on local and global channels by uniformly distributing sAMG traffic over the network.
-
-The traffic go through the local and global channels of the routers serving MultiGrid and CrystalRouter are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}.
-There are more traffic going through when random placement is in use, compared with contiguous placement.
-The extra traffic coming from the ``bully" sAMG cause performance degradation to MultiGrid and CrystalRouter.
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
-        \caption{sAMG Local Channel Traffic}
-        \label{fig:syn-samg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
-        \label{fig:syn-mg-lc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
-        \label{fig:syn-cr-lc-traffic}
-    \end{subfigure}\\
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
-        \caption{sAMG Global Channel Traffic}
-        \label{fig:syn-samg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:syn-mg-gc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:syn-cr-gc-traffic}
-    \end{subfigure}%
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
-   \label{fig:syn-3app-gc-traffic}
-\end{figure*}
-
-\subsection{Key Observations}
-
-In summary, based on the Workload \Rmnum{2}, we have made the following observations.
-
-\emph{The application becomes ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
-
-\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullee" when running concurrently with sAMG in Workload \Rmnum{2}.
-
-\section{Hybrid Job Placement}
-\label{sec: hybrid placement}
-
-The precaution to stop ``bully" behavior is to avoid network sharing between concurrently running jobs.
-Using contiguous placement and minimal routing could be a way to avoid network sharing, but network performance could suffer degradation due to local congestion.
-Running each job with dedicated routing policy is unrealistic, since routing policy is pre-configured and can not be changed on the fly upon job submission.
-However, the job placement policies can be versatile for assigning different allocation (contiguous or random) to specific application.
-
-Thus, we propose the hybrid placement as a reconcile solution.
-In the hybrid placement, the less communication-intensive applications get contiguous allocation while the communication-intensive ones get random allocation.
-We evaluate the effect of hybrid placement on improving network performance as well as preserving the performance of individual application.
-In following experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations.
-\footnote{Due to page limit, we won't present the analysis about network traffic and saturated time in this section.}
-
-\subsection{Network Performance Analysis}
-
-Hybrid placement is also coupled with three routing policies, Minimal, Adaptive and Progressive Adaptive.
-They are denoted respectively as HM, HA and HPA.
-As presented in the previous section, random placement outperforms contiguous placement in terms of network performance, we only compare the results of hybrid placement with random placement due to the page limit.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under hybrid placement and random placement policies.} 
-\label{tab: hyb-placement-wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\
-\cmidrule(l){2-7}
-	      & HM & HA & HPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  &273 &255 &255 &255 &265 &264  \\ % Content row 1
-%\midrule
-%Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-As shown in Table \ref{tab: hyb-placement-wkld-commtime}, hybrid placement and random placement perform comparably.
-When coupled with minimal routing, RM outperforms HM.
-However, when coupled with (progressive) adaptive routing, HA and HPA outperform RA and RPA.
-HA and HPA perform equally well as compared with RM.
-
-\subsection{Individual Application Analysis}
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
-        \caption{AMG Communication Time}
-        \label{fig:hyb-plcmt-amg-commtime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
-        \caption{MG Communication Time}
-        \label{fig:hyb-plcmt-mg-commtime}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
-        \caption{CR Communication Time}
-        \label{fig:hyb-plcmt-cr-commtime}
-    \end{subfigure}%
-   \caption{Application communication time. Workload \Rmnum{1} is running under all the possible placement and routing configurations.}
-   \label{fig:hyb-plcmt-apps-commtime}
-\end{figure*}
-
-Figure \ref{fig:hyb-plcmt-apps-commtime} shows the communication time of each application when hybrid placement configurations are in use.
-MultiGrid and CrystalRouter have basically the same performance with hybrid placement as compared with random placement.
-Since they still get random allocation in the hybrid placement.
-The performance of AMG is significantly improved when hybrid placement is in use.
-Compared with ``RA" and ``RPA", ``HA" and ``HPA" can greatly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}.
-This is due the contiguous allocation assigned to AMG in the hybrid placement policy.
-When being coupled with minimal routing, hybrid placement and contiguous placement have similar performance for AMG.
-However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG.
-Since AMG is less communication-intensive and can not fully utilize network, it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups.
-So for AMG, ``HA" and ``HPA" are worse than ``CA" and ``CPA", but they are much better than ``RA" and ``RPA".
-
-\subsection{Key Observations}
-
-Based on the results from experimenting with hybrid placement policy, we can make the following observations.
-
-\emph{Compared with random placement policy, hybrid placement can guarantee comparable network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.
-
-\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.} Hybrid placement policy preserves contiguous allocation for less communication-intensive application, prevents network resource from being shared by others.
-Unlike random placement indulging the ``bully", hybrid placement can restrain it to some extent.
-
-Hybrid placement can guarantee the performance of individual application without causing performance degradation to network performance.
-Compared with contiguous and random placement policy, hybrid placement are more preferable to HPC systems with dragonfly networks.
-
-\section{Related Work}
-\label{sec:related work}
-
-The impact of job placement to both system and application always catches researchers' appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
-Skinner et al.
-identified that network congestion could cause significant performance variability \cite{dskinner}.
-Bhatele et al.
-studied the performance variability of a specific application, p3FD, running on different production systems with torus networks \cite{abhinav-sc13}.
-They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource.
-Jokanovic et al.
-studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing \cite{jose-ipdps15}.
-
-Recently, several researchers have investigated the job placement and routing schemes on dragonfly network.
-Bogdan et al.
-proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network \cite{hoefler-hpdc14}.
-Jain et al.
-conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network \cite{jain-sc14}.
-Their work is based on an analytical model and synthetic workload.
-Bhatele et al.
-used simulation to study the performance of synthetic workload under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.
-
-Our work different from the previous works in the following ways.
-First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system.
-Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
-We found that although random placement coupled with adaptive routing can improve the network performance, the less communication-intensive applications in the workload may suffer performance degradation.
-Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network performance when application is running.
-The traffic and saturated time of router's each link are valuable information for detailed analysis.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-In this paper, we have conducted extensive study about application's behavior when running on dragonfly network with different job placement and routing configurations.
-We resorted to CODES, a high-fidelity HPC network simulation tool, and used three parallel scientific applications traces collected from production system to analyze the applications' behavior on network level.
-We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network to reach load balance and hot-spots free for the network, the performance of certain job would be impaired.
-We identify this phenomenon as ``bully" between concurrently running jobs, and the victim always being the less communication-intensive one.
-On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, it can guarantee the performance of ``bullee" application by limiting the network sharing from concurrently running peers.
-
-Due the presence of this ``bully", we propose to use hybrid placement policy for workload running on systems with dragonfly networks.
-In hybrid placement policy, the less intensive applications get contiguous allocations, and the intensive ones get random allocations.
-We believe the findings presented in this paper can illuminate a path to more efficient workload manager for future systems with dragonfly network.
-
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-%   \section*{Acknowledgment}
-\fi
-
-The work at Illinois Institute of Technology is supported in part by U.S.
-National Science Foundation grants CNS-1320125 and CCF-1422009.
-This work is also supported by the U.S.
-Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract DE-AC02-06CH11357.
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{4}
-
-\bibliographystyle{IEEEtran}
-\bibliography{./reference}
-
- \vspace{1\baselineskip}
-
- \begin{framed}
- The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
-Argonne, a U.S.
-Department of Energy Office of Science laboratory, is operated under Contract No.
-DE-AC02-06CH11357.
-The U.S.
-Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
- \end{framed}
-
-\end{document}

### 2016-03-30 conclusion.tex
put each section into separate .tex file

--- 2016-03-30 draft.tex
@@
-%% bare_conf_compsoc.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE Computer
-%% Society conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-\documentclass[conference,compsoc]{IEEEtran}
-% Some/most Computer Society conferences require the compsoc mode option,
-% but others may want the standard conference format.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference,compsoc]{../sty/IEEEtran}
-
-% *** MISC UTILITY PACKAGES ***
-%
-\usepackage{ifpdf}
-\usepackage{framed}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage{cite}
-\fi
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage{amsmath}
-\usepackage{cuted}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a sans serif font rather
-% than the serif font used in traditional IEEE formatting and thus the need
-% to invoke different subfig.sty package options depending on whether
-% compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-\usepackage{verbatim}
-\usepackage{soul}
-\usepackage{xcolor}
-\newcommand{\TODO}[1]{\hl{TODO: #1}}
-\newcommand{\NOTE}[1]{\hl {NOTE: #1}}
-\newcommand{\changed}[1]{\textcolor{red}{#1}}
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-\usepackage{graphicx} % Required for including pictures
-\graphicspath{{pics/}} % Specifies the directory where pictures are stored
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{booktabs}
-\usepackage{multirow} % make table
-
-\makeatletter % Put Roman Number in Text
-\newcommand{\rmnum}[1]{\romannumeral #1}
-\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
-\makeatother
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Watch Out for the Bully! Job Interference Study on Dragonfly Network}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-% \author{\IEEEauthorblockN{Michael Shell}
-% \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-% Georgia Institute of Technology\\
-% Atlanta, Georgia 30332--0250\\
-% Email: http://www.michaelshell.org/contact.html}
-% \and
-% \IEEEauthorblockN{Homer Simpson}
-% \IEEEauthorblockA{Twentieth Century Fox\\
-% Springfield, USA\\
-% Email: homer@thesimpsons.com}
-% \and
-% \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-% \IEEEauthorblockA{Starfleet Academy\\
-% San Francisco, California 96678-2391\\
-% Telephone: (800) 555--1212\\
-% Fax: (888) 555--1212}}
-
-\author{
-
-\IEEEauthorblockN{Xu Yang\IEEEauthorrefmark{1}, John Jenkins\IEEEauthorrefmark{2}, Misbah Mubarak\IEEEauthorrefmark{2}, Robert B. Ross\IEEEauthorrefmark{2}, Zhiling Lan\IEEEauthorrefmark{1}}
-
-\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science,
-Illinois Institute of Technology,
-Chicago, Illinois, USA 60616\\
-\{xyang56\}@hawk.iit.edu, lan@iit.edu}
-
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Mathematics and Computer Science Division, Argonne National Laboratory,
-Argonne, IL, USA 60439\\
-\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}
-}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page (and note that there is less available width in this regard for
-% compsoc conferences compared to traditional conferences), use this
-% alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
-\begin{abstract}
-
-The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers.
-Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks, since random placement with adaptive routing can uniformly distribute traffic over the network and alleviate congestion.
-However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network when multiple jobs are running concurrently, they can not guarantee the best performance for each single job.
-The performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs.
-We refer this phenomenon as ``bully" between concurrently running jobs.
-We presented a detailed analysis about this ``bully" behavior between jobs at the network level based on a sophisticated, high-fidelity discrete even-driven simulation tool.
-The observations and analysis presented in this work illuminate a path to the adoption of more efficient job placement policy and routing algorithm for HPC systems with dragonfly network.
-
-\end{abstract}
-
-% no keywords
-
-% \keywords{Dragonfly, Job placement, Routing, Interference}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-\label{sec:intro}
-
-The low latency and high bandwidth interconnect network plays a critical role in HPC system performance.
-As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scarce resource.
-The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
-This make the dragonfly network a very promising choice for building petaflop and beyond supercomputers.
-%The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
-
-While dragonfly topologies provide low-latency and high-bandwidth networking, efficiently utilizing it is a significant concern.
-In particular, intelligent job placement to avoid interference is of paramount importance to guarantee the performance of each job when it shares network resources with other concurrently running peers \cite{bhatele2015, dskinner}.
-Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
-
-In this work, we study the interference between concurrently running jobs on dragonfly networks with different job placement and routing policies.
-We use CODES, an HPC network simulation toolkit with high fidelity and excellent scalability for packet level simulation \cite{codes}.
-Unlike much existing work that rely on synthetic workloads, we use traces of three representative applications from the DOE Design Forward Project \cite{designforwardwebpage}.
-The advantage of using real application traces is straight forward: these traces can capture detailed application communication behaviors that are  omitted in synthetic workload for simplification.
-Applications are usually distinctive from each other in data transfer amount, communication pattern, operation dependency etc., which can be impractical to reproduce in a synthetic workload.
-
-We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies.
-We analyze the performance of network as well as individual application when running with different placement and routing configurations.
-Our evaluation is based on more than 1000 runs of simulation.
-We make the following interesting observations through extensive simulation.
-
-\begin{itemize}
-
-    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion, optimizing the overall performance of the dragonfly network.
-
-    \item The ``bully" behavior occurs between concurrently running jobs on a dragonfly network when random placement and adaptive routing are in use.
-Communication-intensive jobs obtain performance improvement at the expense of less intensive jobs suffering performance degradation.
-
-    \item Random placement coupled with adaptive routing can improve the performance of communication-intensive jobs by enabling network resource sharing, though it introduces interference between concurrently running jobs.
-
-    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of less communication-intensive jobs by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
-
-\end{itemize}
-
-Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to the job communication intensity.
-\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
-We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
-For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks.
-System software developers could design better scheduling algorithms for jobs with distinct communication behavior.
-System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.
-
-The rest of this paper is organized as follows.
-Section \ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies.
-Section \ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
-Section \ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations.
-Section \ref{sec:workload-2} validates the observations we obtain from previous section.
-Section \ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network.
-Section \ref{sec:related work} discusses the related work.
-Finally, the conclusion is presented in Section \ref{sec:conclusion}.
-
-\section{Background}
-\label{sec:background}
-
-In this section, we review the dragonfly topology, including the placement and routing policies examined in previous work.
-
-\subsection{Dragonfly Network}
-\label{sec:network}
-The dragonfly is a two-level hierarchical topology, consisting of several groups connected by all-to-all links.
-In each group, there could be $a$ routers connected via all-to-all local channels.
-For each router, there could be $p$ compute nodes attached to it via terminal links.
-The router has $h$ global channels used as intergroup connections through which the router connected to other routers in different groups.
-Thus, the radix of each router is $k = a+h+p-1$.
-Different computing centers could choose different values for  $a$, $h$, $p$ when deploying their dragonfly network.
-The adoption of proper $a$, $h$, $p$ involves many factors, such as system scale, building cost and workload.
-
-It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}.
-Under this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $.
-An implementation of dragonfly network follows such configuration is illustrated in Figure~\ref{fig:dragonfly-overview}.
-There are six routers in each group, each router has three compute nodes attached to it.
-This dragonfly network consists of 19 groups and 342 nodes in total.
-
-\begin{figure}[h!] 
-  \centering
-  \includegraphics[width=0.48\textwidth]{dragonfly-overview}
-  \caption{Dragonfly Network Overview.
-There are 19 groups, six routers in each group, three compute nodes connected to each router, 342 nodes in total.
-Job $J1$ requires seven nodes, getting its allocation by random placement.
-Job $J2$ requires eight nodes, getting its allocation by contiguous placement.}
-  \label{fig:dragonfly-overview}
-\end{figure}
-
-\subsection{Job Placement on Dragonfly}
-\label{sec:placement-schemes}
-
-For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning tasks of the application onto the system by a system software such as batch scheduler~\cite{xu-cluster14}.
-In this work, we study two alternative placement policies considered by the community for dragonfly systems:
-
-\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to a job in a consecutive manner.
-The assignment first fills up a group, then crosses group boundaries and starts to fill the next group if necessary.
-As shown in Figure~\ref{fig:dragonfly-overview}, $J2$ gets eight nodes by contiguous placement.
-Contiguous placement confines the tasks of a job into the same group, which may result in local network congestion and increase the possibility of hot-spots.
-
-\textbf{Random Placement:} In this policy, a job gets a set of nodes randomly selected from all the available nodes in the system.
-The nodes assigned to $J1$ in Figure~\ref{fig:dragonfly-overview} are attached to different routers in different groups.
-Routers may be shared by different jobs when random placement is in use.
-Random placement can distribute the tasks of a job uniformly across the whole system to avoid the possible local congestion.
-However, random placement may cause possible congestion on global links.
-
-\subsection{Routing on Dragonfly}
-\label{sec:routing-schemes}
-
-The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router.
-Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
-In this work we study three widely adopted routing policies on dragonfly networks.
-
-\textbf{Minimal:} In this policy, a message takes the shortest path from the source router to the destination router.
-When there are multiple shortest paths between the source and destination router, the message will be evenly divided among the paths.
-Minimal routing can guarantee the minimum hops the message takes from source to destination.
-However, it may result in congestion along the shortest path.
-
-\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest paths, depending on the congestion situation along those paths.
-For the non-shortest path, an intermediate router will be randomly chosen.
-The message takes the intermediate router as a via point, connecting the source and destination router through two separate shortest paths.
-Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.
-
-\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated.
-Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}.
-The progressive adaptive is capable of handling the case where a global channel is congested but the source router has not been informed yet~\cite{jiang}.
-The packet will take the non-minimal route only when the congestion is encountered.
-
-\section{Methodology}
-\label{sec: methodology}
-
-It is difficult to experiment with concurrently running jobs on HPC system~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
-One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will.
-Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
-The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
-Therefore, we resort to simulation in our work.
-
-\subsection{Simulation Tool}
-\label{sec:simulation-tool}
-
-A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability~\cite{codes}.
-CODES supports dragonfly~\cite{codes-dragonfly}~\cite{misbah-tpds}, torus~\cite{misbah-pads-2014}~\cite{ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
-It can drive these models through an MPI simulation layer utilizing DUMPI traces~\cite{sst}.
-In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on the dragonfly network.
-
-\subsection{Parallel Applications}
-\label{sec: application traces}
-
-We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent of a wide array of applications running on leadership-class supercomputers.
-Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
-
-\textbf{AMG:} The Algebraic MultiGrid Solver is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
-It has been derived directly from the BoomerAMG solver developed in the Center for Applied Scientific Computing (CASC) at LLNL~\cite{amg}.
-
-\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes~\cite{boxlib}, which are used for structured grid physics packages.
-
-\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
-It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.
-
-\subsection{System Configuration}
-\label{sec: simulation configuration}
-
-The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et.
-al~\cite{kim-micro}.
-Our dragonfly network consists of 33 groups, each of which contains 8 routers.
-Each router has four compute nodes attached to it.
-Overall, there are 264 routers and 1056 compute nodes in the network.
-The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}.
-In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.
-
-%\footnote{With respect to random placement, we experiment with 50 sets of distinctive allocation generated by random placement.
-The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.}
-
-\begin{table}[ht]
-\begin{center}
-\caption{The notation for different placement and routing configurations} 
-\label{tab: placement routing configs}
-\begin{tabular}{l c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{3}{c}{Routing Policies} \\ 
-\cmidrule(l){2-4}
-Placement Policies & Minimal & Adaptive & Progressive Adaptive\\ % Column names row
-\midrule % In-table horizontal line
-Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
-\midrule
-Random  &   RM  &   RA   &  RPA   \\ 
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-Our analysis focuses on the following metrics:
-\begin{itemize}
-
-    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router.
-
-    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full.
-We analyze the saturated time of ports corresponding to terminal link, local and global channel.
-
-    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks.
-\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in our experiments.
-}
-
-\end{itemize}
-
-\subsection{Workload Summary}
-\label{sec:workload summary}
-
-Two sets of parallel workloads are used in this work.
-Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
-In Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}.
-Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
-sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x.
-sAMG is the most communication-intensive job in Workload~\Rmnum{2}.
-
-Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running jobs on the dragonfly network.
-Workload~\Rmnum{2} is used to verify the results and conclusion obtained from the study of Workload~\Rmnum{1}.
-
-%Table \ref{tab:apps-detail} summarizes the details of each application.
-It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.
-
-\begin{table}[ht]
-\begin{center}
-\caption{The details of each application.} 
-\label{tab:apps-detail}
-\begin{tabular}{l c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{3}{c}{Application Details} \\ 
-\cmidrule(l){2-4}
-App Name & Num. Rank & Avg. Data/Rank & Total Data\\ % Column names row
-\midrule % In-table horizontal line
-AMG  &    216 &   0.6MB   &     130MB\\ % Content row 1
-\midrule
-MultiGrid  &    125 &   5MB   &     625MB\\ 
-\midrule
-CrystalRouter  &   100  &  35MB    &     3500MB\\ 
-\midrule
-sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Study of Parallel Workload~\Rmnum{1}}
-%\section{Identify the ``Bully"}
-\label{sec:workload-1}
-
-We study the network performance and job interference from two perspectives.
-Firstly, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
-Secondly, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic going through the routers that serve each job.
-The analysis allows us to identify the ``bully" in the workload.
-
-\subsection{Network Performance Analysis}
-\label{sec: workload-1 network analysis}
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
-\label{tab:wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
-\cmidrule(l){2-7}
-	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The average communication time spent by all MPI ranks when Workload \Rmnum{1} is running under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}.
-The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.
-The contiguous placement coupled with minimal routing (CM) results in highest communication time.
-When coupled with (progressive) adaptive routing (CA, CPA), the communication time can be reduced but still higher than random placement polices.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:global-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:local-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:terminal-link-traffic}
-    \end{subfigure}\\
-
-    \centering   
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-stime}
-        \caption{Global Channel Saturated Time}
-        \label{fig:global-channel-stime}
-    \end{subfigure}\hfill
-     \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-stime}
-        \caption{Local Channel Saturated Time}
-        \label{fig:local-channel-stime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-stime}
-        \caption{Terminal Link Saturated Time}
-        \label{fig:terminal-link-stime}
-    \end{subfigure}%
-   \caption{The aggregate traffic and saturated time of the dragonfly network when Workload \Rmnum{1} running under 6 different placement and routing configurations.
-``CA" and ``CPA" performs comparably, the corresponding lines are overlapped.
-}
-   \label{fig:wkld-network-traffic-stime}
-\end{figure*}
-
-Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels as well as the corresponding saturated time when Workload \Rmnum{1} is running on dragonfly network with 6 different placement and routing configurations.
-When contiguous placement and minimal routing(CM) is in use, all the traffic goes within the contiguously allocated groups, causing congestion along certain shortest paths from source to destination routers.
-Both the traffic and the corresponding saturated time of global channels are the highest compared with other configurations, shown as the blue dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
-When contiguous placement is coupled with (progressive) adaptive routing (CA and CPA), the traffic through congested global channels will be greatly reduced, so does the corresponding saturated time, shown as the red and green dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
-Since (progressive) adaptive routing are congestion aware, the traffic would be redirected to the intermediate routers in other idle groups when congestion occurs, thus the traffic burden on the contiguously allocated groups will be alleviated.
-
-Random placement policy performs comparably with three different routing policies.
-Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic through global channels are quite balanced across all the routers, thus no particular global channel will suffer high traffic burden.
-When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic.
-That's why the blue solid line is lower than the red and green solid line.
-Since the random placement can uniformly distribute traffic, there are no sudden surge of saturated time of global channel over the network, shown as solid lines in Figure \ref{fig:global-channel-stime}.
-
-%local channel traffic and busy time explanation
-
-We observe similar phenomena from the local channel traffic and saturated time, shown in Figure \ref{fig:local-channel-traffic}, \ref{fig:local-channel-stime}).
-Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus the aggregate traffic through local channels of certain routers is quite high.
-Even with adaptive or progressive adaptive routing, the local congestion caused by grouping all MPI ranks in the same group(s) in contiguous placement can not be eliminated.
-Random placement is effective at addressing this type of congestion.
-
-%terminal link traffic and busy time explanation
-Figure \ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which stay the same when different placement and routing configurations are in use.
-All 6 lines are overlapped in Figure \ref{fig:terminal-link-traffic}.
-However, due to the traffic changes on global and local channels, the saturated time of terminal links will experience variability when different routing schemes are in use, as shown in Figure \ref{fig:terminal-link-stime}.
-When contiguous placement coupled with minimal routing(CM), the accumulated congestion on local and global channels cause extremely long saturated time on the terminal link, shown as the blue dashed line in Figure \ref{fig:terminal-link-stime}.
-This again manifests the severe congestion caused by using contiguous placement and minimal routing.
-
-\subsection{Individual Application Analysis}
-\label{sec: workload-1 app analysis}
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/amg/commtime}
-        \caption{AMG}
-        \label{fig:amg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/mg/commtime}
-        \caption{MultiGrid}
-        \label{fig:mg-commtime}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/cr/commtime}
-        \caption{CrystalRouter}
-        \label{fig:cr-commtime}
-    \end{subfigure}%
-   \caption{The communication time of all ranks in each application.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
-Random placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
-   \label{fig:apps-commtime}
-\end{figure*}
-
-Figure \ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
-
-As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MultiGrid and CrystalRouter suffer the longest communication time when running with contiguous placement and minimal routing (CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter are significantly reduced.
-Random placement further reduces their communication time, and reaches the best performance when coupled with (progressive) adaptive routing (RPA, RA).
-Both MultiGrid and CrystalRouter show the same trend when they are running under different placement and routing configurations.
-AMG is quite an exception.
-The communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA), shown in Figure \ref{fig:amg-commtime}.
-The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
-CM is no better than RM, but still much better RPA, RA.
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
-        \caption{AMG Local Channel Traffic}
-        \label{fig:amg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
-        \label{fig:mg-lc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
-        \label{fig:cr-lc-traffic}
-    \end{subfigure}\\
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
-        \caption{AMG Global Channel Traffic}
-        \label{fig:amg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:mg-gc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:cr-gc-traffic}
-    \end{subfigure}%
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
-   \label{fig:3app-lc-gc-traffic}
-\end{figure*}
-
-% Show the evidence from network level, explain why AMG is different. 
-We look into network level to identify the culprit behind AMG's abnormal behavior with random placement and adaptive routing.
-By identifying the compute nodes each MPI rank resides on and routers that serving each application, we can see that the traffic go through the routers serving AMG skyrockets when random placement and adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and \ref{fig:amg-gc-traffic}.
-Adaptive routing will redirect the traffic of other applications to go through the routers belonging to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
-
-No router will be shared between applications under contiguous placement.
-A number of successive groups will be allocated to the same application under contiguous placement policy.
-When contiguous placement coupled with minimal routing, application will be free of interference from its concurrently running peers.
-However, application communication traffic will be confined within their allocated groups, thus congestion is very likely to happen depending on application communication intensity.
-As the lest communication-intensive application in Workload \Rmnum{1}, AMG can benefit from contiguous placement.
-Under contiguous placement, the traffic go through the local and global channels of the routers belonging to AMG is significantly lower than with random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
-
-MultiGrid and CrystalRouter are more communication-intensive compared with AMG.
-They will suffer congestion on both local and global channels when contiguous placement is in use, shown as the dashed line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-On the other hand, the random placement can uniformly distribute their traffic all over the network, alleviate the possible congestion, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-
-\subsection{Key Observations}
-In summary, based on the results presented in section \ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we have made the following observations.
-
-\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers.
-Therefore, the network could reach the status of load-balanced and hot-spots free.
-
-\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network random placement and adaptive routing are in use.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
-AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use.
-The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slowing down AMG's communication.
-\footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
-
-\emph{Consistent performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} The router and group sharing between jobs are prohibited in contiguous placement policy.
-The traffic won't be redirected from congested routers to less busy ones when minimal routing is in use.
-Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
-%However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.
-
-\section{Study of Parallel Workload \Rmnum{2 }}
-%\section{``Bully" become ``Bullee"}
-\label{sec:workload-2}
-
-In this section, we will verify the observations made in the previous section when Workload \Rmnum{1} is running on the dragonfly network under different placement and routing configurations.
-We conduct the same sets of experiments with Workload \Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter.
-By replacing AMG with sAMG, we turn the ``bully" into ``bullee".
-
-\subsection{Network Performance Analysis}
-\label{sec: workload-2 network analysis}
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under 6 different placement and routing configurations.} 
-\label{tab:syn-wkld-commtime}
-%\centering % Centers the table on the page, comment out to left-justify
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
-\cmidrule(l){2-7}
-	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The average communication time spent by all MPI ranks when Workload \Rmnum{2} is running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
-The contiguous placement coupled with minimal routing results in highest communication time.
-The random placement coupled with minimal routing is the most efficient.
-Progressive adaptive routing is better than adaptive routing when random placement is in use.
-And they have comparable results when coupled contiguous placement.
-The performance of Workload \Rmnum{2} under different configurations keep the similar pattern as it of Workload \Rmnum{1}.
-
-Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running with 6 different configurations.
-Contiguous placement coupled with minimal routing(CM) results in most traffic go through certain local and global channel, thus the longest saturated time for terminal link, local and global channel.
-When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion could be mitigated.
-The random placement coupled with any routing policy(RM, RA, RPA) performs comparably.
-They are better than contiguous placement and minimal routing(CM), but only little improvement against contiguous and (progressive) adaptive (CA, CPA).
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:synwkld-global-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:synwkld-local-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:synwkld-terminal-link-traffic}
-    \end{subfigure}\\
-
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
-        \caption{Global Channel Saturated Time}
-        \label{fig:synwkld-global-channel-stime}
-    \end{subfigure}\hfill
-     \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
-        \caption{Local Channel Saturated Time}
-        \label{fig:synwkld-local-channel-stime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
-        \caption{Terminal Link Saturated Time}
-        \label{fig:synwkld-terminal-link-stime}
-    \end{subfigure}%
-   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under 6 different placement and routing configurations.}
-   \label{fig:synwkld-network-traffic-stime}
-\end{figure*}
-
-\subsection{Individual Application Analysis}
-\label{sec: workload-2 app analysis}
-
-The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}.
-The ``bully" in Workload \Rmnum{1} becomes the ``bullyee" in Workload \Rmnum{2}.
-MultiGrid and CrystalRouter are the less communication-intensive applications in Workload \Rmnum{2}.
-When random placement coupled with (progressive) adaptive routing is in use, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
-Whereas, sAMG benefits from random placement and (progressive) adaptive routing, shown in Figure \ref{fig:syn-samg-commtime}.
-Contiguous placement coupled with minimal routing prevents applications from sharing network resource, guaranteeing the performance of less communication intensive applications like MultiGrid and CrystalRouter and causing severe performance degradation to sAMG.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
-        \caption{sAMG}
-        \label{fig:syn-samg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
-        \caption{MultiGrid}
-        \label{fig:syn-mg-commtime}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
-        \caption{CrystalRouter}
-        \label{fig:syn-cr-commtime}
-    \end{subfigure}%
-   \caption{The communication time of all ranks in each application.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
-The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullee", MultiGrid and CrystalRouter, suffer performance degradation.}
-   \label{fig:syn-apps-commtime}
-\end{figure*}
-
-% explain the network status of sAMG, MG and CR
-We look into the network level to scrutinize the traffic through the routers serving each application.
-Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers serving sAMG.
-The traffic skyrockets in both local and global channels when contiguous placement coupled with minimal routing (CM) is in use.
-The congestion will be alleviated in both local and global channels when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use.
-Random placement can further reduce the traffic burden on local and global channels by uniformly distributing sAMG traffic over the network.
-
-The traffic go through the local and global channels of the routers serving MultiGrid and CrystalRouter are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}.
-There are more traffic going through when random placement is in use, compared with contiguous placement.
-The extra traffic coming from the ``bully" sAMG cause performance degradation to MultiGrid and CrystalRouter.
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
-        \caption{sAMG Local Channel Traffic}
-        \label{fig:syn-samg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
-        \label{fig:syn-mg-lc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
-        \label{fig:syn-cr-lc-traffic}
-    \end{subfigure}\\
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
-        \caption{sAMG Global Channel Traffic}
-        \label{fig:syn-samg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:syn-mg-gc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:syn-cr-gc-traffic}
-    \end{subfigure}%
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
-   \label{fig:syn-3app-gc-traffic}
-\end{figure*}
-
-\subsection{Key Observations}
-
-In summary, based on the Workload \Rmnum{2}, we have made the following observations.
-
-\emph{The application becomes ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
-
-\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullee" when running concurrently with sAMG in Workload \Rmnum{2}.
-
-\section{Hybrid Job Placement}
-\label{sec: hybrid placement}
-
-The precaution to stop ``bully" behavior is to avoid network sharing between concurrently running jobs.
-Using contiguous placement and minimal routing could be a way to avoid network sharing, but network performance could suffer degradation due to local congestion.
-Running each job with dedicated routing policy is unrealistic, since routing policy is pre-configured and can not be changed on the fly upon job submission.
-However, the job placement policies can be versatile for assigning different allocation (contiguous or random) to specific application.
-
-Thus, we propose the hybrid placement as a reconcile solution.
-In the hybrid placement, the less communication-intensive applications get contiguous allocation while the communication-intensive ones get random allocation.
-We evaluate the effect of hybrid placement on improving network performance as well as preserving the performance of individual application.
-In following experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations.
-\footnote{Due to page limit, we won't present the analysis about network traffic and saturated time in this section.}
-
-\subsection{Network Performance Analysis}
-
-Hybrid placement is also coupled with three routing policies, Minimal, Adaptive and Progressive Adaptive.
-They are denoted respectively as HM, HA and HPA.
-As presented in the previous section, random placement outperforms contiguous placement in terms of network performance, we only compare the results of hybrid placement with random placement due to the page limit.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under hybrid placement and random placement policies.} 
-\label{tab: hyb-placement-wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\
-\cmidrule(l){2-7}
-	      & HM & HA & HPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  &273 &255 &255 &255 &265 &264  \\ % Content row 1
-%\midrule
-%Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-As shown in Table \ref{tab: hyb-placement-wkld-commtime}, hybrid placement and random placement perform comparably.
-When coupled with minimal routing, RM outperforms HM.
-However, when coupled with (progressive) adaptive routing, HA and HPA outperform RA and RPA.
-HA and HPA perform equally well as compared with RM.
-
-\subsection{Individual Application Analysis}
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
-        \caption{AMG Communication Time}
-        \label{fig:hyb-plcmt-amg-commtime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
-        \caption{MG Communication Time}
-        \label{fig:hyb-plcmt-mg-commtime}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
-        \caption{CR Communication Time}
-        \label{fig:hyb-plcmt-cr-commtime}
-    \end{subfigure}%
-   \caption{Application communication time. Workload \Rmnum{1} is running under all the possible placement and routing configurations.}
-   \label{fig:hyb-plcmt-apps-commtime}
-\end{figure*}
-
-Figure \ref{fig:hyb-plcmt-apps-commtime} shows the communication time of each application when hybrid placement configurations are in use.
-MultiGrid and CrystalRouter have basically the same performance with hybrid placement as compared with random placement.
-Since they still get random allocation in the hybrid placement.
-The performance of AMG is significantly improved when hybrid placement is in use.
-Compared with ``RA" and ``RPA", ``HA" and ``HPA" can greatly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}.
-This is due the contiguous allocation assigned to AMG in the hybrid placement policy.
-When being coupled with minimal routing, hybrid placement and contiguous placement have similar performance for AMG.
-However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG.
-Since AMG is less communication-intensive and can not fully utilize network, it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups.
-So for AMG, ``HA" and ``HPA" are worse than ``CA" and ``CPA", but they are much better than ``RA" and ``RPA".
-
-\subsection{Key Observations}
-
-Based on the results from experimenting with hybrid placement policy, we can make the following observations.
-
-\emph{Compared with random placement policy, hybrid placement can guarantee comparable network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.
-
-\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.} Hybrid placement policy preserves contiguous allocation for less communication-intensive application, prevents network resource from being shared by others.
-Unlike random placement indulging the ``bully", hybrid placement can restrain it to some extent.
-
-Hybrid placement can guarantee the performance of individual application without causing performance degradation to network performance.
-Compared with contiguous and random placement policy, hybrid placement are more preferable to HPC systems with dragonfly networks.
-
-\section{Related Work}
-\label{sec:related work}
-
-The impact of job placement to both system and application always catches researchers' appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
-Skinner et al.
-identified that network congestion could cause significant performance variability \cite{dskinner}.
-Bhatele et al.
-studied the performance variability of a specific application, p3FD, running on different production systems with torus networks \cite{abhinav-sc13}.
-They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource.
-Jokanovic et al.
-studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing \cite{jose-ipdps15}.
-
-Recently, several researchers have investigated the job placement and routing schemes on dragonfly network.
-Bogdan et al.
-proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network \cite{hoefler-hpdc14}.
-Jain et al.
-conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network \cite{jain-sc14}.
-Their work is based on an analytical model and synthetic workload.
-Bhatele et al.
-used simulation to study the performance of synthetic workload under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.
-
-Our work different from the previous works in the following ways.
-First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system.
-Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
-We found that although random placement coupled with adaptive routing can improve the network performance, the less communication-intensive applications in the workload may suffer performance degradation.
-Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network performance when application is running.
-The traffic and saturated time of router's each link are valuable information for detailed analysis.
-
 \section{Conclusion}
@@
 We believe the findings presented in this paper can illuminate a path to more efficient workload manager for future systems with dragonfly network.
-
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-%   \section*{Acknowledgment}
-\fi
-
-The work at Illinois Institute of Technology is supported in part by U.S.
-National Science Foundation grants CNS-1320125 and CCF-1422009.
-This work is also supported by the U.S.
-Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract DE-AC02-06CH11357.
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{4}
-
-\bibliographystyle{IEEEtran}
-\bibliography{./reference}
-
- \vspace{1\baselineskip}
-
- \begin{framed}
- The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
-Argonne, a U.S.
-Department of Energy Office of Science laboratory, is operated under Contract No.
-DE-AC02-06CH11357.
-The U.S.
-Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
- \end{framed}
-
-\end{document}

### 2016-03-30 draft.tex
put each section into separate .tex file

--- 2016-03-30 draft.tex
@@
 
-\section{Introduction}
-\label{sec:intro}
+\input{intro}
 
-The low latency and high bandwidth interconnect network plays a critical role in HPC system performance.
-As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scarce resource.
-The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
-This make the dragonfly network a very promising choice for building petaflop and beyond supercomputers.
-%The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
+\input{background}
 
-While dragonfly topologies provide low-latency and high-bandwidth networking, efficiently utilizing it is a significant concern.
-In particular, intelligent job placement to avoid interference is of paramount importance to guarantee the performance of each job when it shares network resources with other concurrently running peers \cite{bhatele2015, dskinner}.
-Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
+\input{methodology}
 
-In this work, we study the interference between concurrently running jobs on dragonfly networks with different job placement and routing policies.
-We use CODES, an HPC network simulation toolkit with high fidelity and excellent scalability for packet level simulation \cite{codes}.
-Unlike much existing work that rely on synthetic workloads, we use traces of three representative applications from the DOE Design Forward Project \cite{designforwardwebpage}.
-The advantage of using real application traces is straight forward: these traces can capture detailed application communication behaviors that are  omitted in synthetic workload for simplification.
-Applications are usually distinctive from each other in data transfer amount, communication pattern, operation dependency etc., which can be impractical to reproduce in a synthetic workload.
+\input{study_workload_1}
 
-We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies.
-We analyze the performance of network as well as individual application when running with different placement and routing configurations.
-Our evaluation is based on more than 1000 runs of simulation.
-We make the following interesting observations through extensive simulation.
+\input{study_workload_2}
 
-\begin{itemize}
+\input{hybrid_placement}
 
-    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion, optimizing the overall performance of the dragonfly network.
+\input{related_work}
 
-    \item The ``bully" behavior occurs between concurrently running jobs on a dragonfly network when random placement and adaptive routing are in use.
-Communication-intensive jobs obtain performance improvement at the expense of less intensive jobs suffering performance degradation.
-
-    \item Random placement coupled with adaptive routing can improve the performance of communication-intensive jobs by enabling network resource sharing, though it introduces interference between concurrently running jobs.
-
-    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of less communication-intensive jobs by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
-
-\end{itemize}
-
-Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to the job communication intensity.
-\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
-We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
-For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks.
-System software developers could design better scheduling algorithms for jobs with distinct communication behavior.
-System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.
-
-The rest of this paper is organized as follows.
-Section \ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies.
-Section \ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
-Section \ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations.
-Section \ref{sec:workload-2} validates the observations we obtain from previous section.
-Section \ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network.
-Section \ref{sec:related work} discusses the related work.
-Finally, the conclusion is presented in Section \ref{sec:conclusion}.
-
-\section{Background}
-\label{sec:background}
-
-In this section, we review the dragonfly topology, including the placement and routing policies examined in previous work.
-
-\subsection{Dragonfly Network}
-\label{sec:network}
-The dragonfly is a two-level hierarchical topology, consisting of several groups connected by all-to-all links.
-In each group, there could be $a$ routers connected via all-to-all local channels.
-For each router, there could be $p$ compute nodes attached to it via terminal links.
-The router has $h$ global channels used as intergroup connections through which the router connected to other routers in different groups.
-Thus, the radix of each router is $k = a+h+p-1$.
-Different computing centers could choose different values for  $a$, $h$, $p$ when deploying their dragonfly network.
-The adoption of proper $a$, $h$, $p$ involves many factors, such as system scale, building cost and workload.
-
-It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}.
-Under this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $.
-An implementation of dragonfly network follows such configuration is illustrated in Figure~\ref{fig:dragonfly-overview}.
-There are six routers in each group, each router has three compute nodes attached to it.
-This dragonfly network consists of 19 groups and 342 nodes in total.
-
-\begin{figure}[h!] 
-  \centering
-  \includegraphics[width=0.48\textwidth]{dragonfly-overview}
-  \caption{Dragonfly Network Overview.
-There are 19 groups, six routers in each group, three compute nodes connected to each router, 342 nodes in total.
-Job $J1$ requires seven nodes, getting its allocation by random placement.
-Job $J2$ requires eight nodes, getting its allocation by contiguous placement.}
-  \label{fig:dragonfly-overview}
-\end{figure}
-
-\subsection{Job Placement on Dragonfly}
-\label{sec:placement-schemes}
-
-For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning tasks of the application onto the system by a system software such as batch scheduler~\cite{xu-cluster14}.
-In this work, we study two alternative placement policies considered by the community for dragonfly systems:
-
-\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to a job in a consecutive manner.
-The assignment first fills up a group, then crosses group boundaries and starts to fill the next group if necessary.
-As shown in Figure~\ref{fig:dragonfly-overview}, $J2$ gets eight nodes by contiguous placement.
-Contiguous placement confines the tasks of a job into the same group, which may result in local network congestion and increase the possibility of hot-spots.
-
-\textbf{Random Placement:} In this policy, a job gets a set of nodes randomly selected from all the available nodes in the system.
-The nodes assigned to $J1$ in Figure~\ref{fig:dragonfly-overview} are attached to different routers in different groups.
-Routers may be shared by different jobs when random placement is in use.
-Random placement can distribute the tasks of a job uniformly across the whole system to avoid the possible local congestion.
-However, random placement may cause possible congestion on global links.
-
-\subsection{Routing on Dragonfly}
-\label{sec:routing-schemes}
-
-The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router.
-Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
-In this work we study three widely adopted routing policies on dragonfly networks.
-
-\textbf{Minimal:} In this policy, a message takes the shortest path from the source router to the destination router.
-When there are multiple shortest paths between the source and destination router, the message will be evenly divided among the paths.
-Minimal routing can guarantee the minimum hops the message takes from source to destination.
-However, it may result in congestion along the shortest path.
-
-\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest paths, depending on the congestion situation along those paths.
-For the non-shortest path, an intermediate router will be randomly chosen.
-The message takes the intermediate router as a via point, connecting the source and destination router through two separate shortest paths.
-Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.
-
-\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated.
-Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}.
-The progressive adaptive is capable of handling the case where a global channel is congested but the source router has not been informed yet~\cite{jiang}.
-The packet will take the non-minimal route only when the congestion is encountered.
-
-\section{Methodology}
-\label{sec: methodology}
-
-It is difficult to experiment with concurrently running jobs on HPC system~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
-One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will.
-Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
-The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
-Therefore, we resort to simulation in our work.
-
-\subsection{Simulation Tool}
-\label{sec:simulation-tool}
-
-A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability~\cite{codes}.
-CODES supports dragonfly~\cite{codes-dragonfly}~\cite{misbah-tpds}, torus~\cite{misbah-pads-2014}~\cite{ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
-It can drive these models through an MPI simulation layer utilizing DUMPI traces~\cite{sst}.
-In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on the dragonfly network.
-
-\subsection{Parallel Applications}
-\label{sec: application traces}
-
-We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent of a wide array of applications running on leadership-class supercomputers.
-Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
-
-\textbf{AMG:} The Algebraic MultiGrid Solver is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages.
-It has been derived directly from the BoomerAMG solver developed in the Center for Applied Scientific Computing (CASC) at LLNL~\cite{amg}.
-
-\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes~\cite{boxlib}, which are used for structured grid physics packages.
-
-\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000 \cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
-It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.
-
-\subsection{System Configuration}
-\label{sec: simulation configuration}
-
-The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et.
-al~\cite{kim-micro}.
-Our dragonfly network consists of 33 groups, each of which contains 8 routers.
-Each router has four compute nodes attached to it.
-Overall, there are 264 routers and 1056 compute nodes in the network.
-The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}.
-In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.
-
-%\footnote{With respect to random placement, we experiment with 50 sets of distinctive allocation generated by random placement.
-The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.}
-
-\begin{table}[ht]
-\begin{center}
-\caption{The notation for different placement and routing configurations} 
-\label{tab: placement routing configs}
-\begin{tabular}{l c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{3}{c}{Routing Policies} \\ 
-\cmidrule(l){2-4}
-Placement Policies & Minimal & Adaptive & Progressive Adaptive\\ % Column names row
-\midrule % In-table horizontal line
-Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
-\midrule
-Random  &   RM  &   RA   &  RPA   \\ 
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-Our analysis focuses on the following metrics:
-\begin{itemize}
-
-    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router.
-
-    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full.
-We analyze the saturated time of ports corresponding to terminal link, local and global channel.
-
-    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks.
-\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in our experiments.
-}
-
-\end{itemize}
-
-\subsection{Workload Summary}
-\label{sec:workload summary}
-
-Two sets of parallel workloads are used in this work.
-Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
-In Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}.
-Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
-sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x.
-sAMG is the most communication-intensive job in Workload~\Rmnum{2}.
-
-Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running jobs on the dragonfly network.
-Workload~\Rmnum{2} is used to verify the results and conclusion obtained from the study of Workload~\Rmnum{1}.
-
-%Table \ref{tab:apps-detail} summarizes the details of each application.
-It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.
-
-\begin{table}[ht]
-\begin{center}
-\caption{The details of each application.} 
-\label{tab:apps-detail}
-\begin{tabular}{l c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{3}{c}{Application Details} \\ 
-\cmidrule(l){2-4}
-App Name & Num. Rank & Avg. Data/Rank & Total Data\\ % Column names row
-\midrule % In-table horizontal line
-AMG  &    216 &   0.6MB   &     130MB\\ % Content row 1
-\midrule
-MultiGrid  &    125 &   5MB   &     625MB\\ 
-\midrule
-CrystalRouter  &   100  &  35MB    &     3500MB\\ 
-\midrule
-sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Study of Parallel Workload~\Rmnum{1}}
-%\section{Identify the ``Bully"}
-\label{sec:workload-1}
-
-We study the network performance and job interference from two perspectives.
-Firstly, we analyze the network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
-Secondly, we isolate each job from the workload, and analyze the interference by scrutinizing the traffic going through the routers that serve each job.
-The analysis allows us to identify the ``bully" in the workload.
-
-\subsection{Network Performance Analysis}
-\label{sec: workload-1 network analysis}
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
-\label{tab:wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
-\cmidrule(l){2-7}
-	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The average communication time spent by all MPI ranks when Workload \Rmnum{1} is running under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}.
-The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.
-The contiguous placement coupled with minimal routing (CM) results in highest communication time.
-When coupled with (progressive) adaptive routing (CA, CPA), the communication time can be reduced but still higher than random placement polices.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:global-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:local-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:terminal-link-traffic}
-    \end{subfigure}\\
-
-    \centering   
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/gc-stime}
-        \caption{Global Channel Saturated Time}
-        \label{fig:global-channel-stime}
-    \end{subfigure}\hfill
-     \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/lc-stime}
-        \caption{Local Channel Saturated Time}
-        \label{fig:local-channel-stime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/tl-stime}
-        \caption{Terminal Link Saturated Time}
-        \label{fig:terminal-link-stime}
-    \end{subfigure}%
-   \caption{The aggregate traffic and saturated time of the dragonfly network when Workload \Rmnum{1} running under 6 different placement and routing configurations.
-``CA" and ``CPA" performs comparably, the corresponding lines are overlapped.
-}
-   \label{fig:wkld-network-traffic-stime}
-\end{figure*}
-
-Figure \ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels as well as the corresponding saturated time when Workload \Rmnum{1} is running on dragonfly network with 6 different placement and routing configurations.
-When contiguous placement and minimal routing(CM) is in use, all the traffic goes within the contiguously allocated groups, causing congestion along certain shortest paths from source to destination routers.
-Both the traffic and the corresponding saturated time of global channels are the highest compared with other configurations, shown as the blue dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
-When contiguous placement is coupled with (progressive) adaptive routing (CA and CPA), the traffic through congested global channels will be greatly reduced, so does the corresponding saturated time, shown as the red and green dashed line in Figure \ref{fig:global-channel-traffic} and \ref{fig:global-channel-stime}.
-Since (progressive) adaptive routing are congestion aware, the traffic would be redirected to the intermediate routers in other idle groups when congestion occurs, thus the traffic burden on the contiguously allocated groups will be alleviated.
-
-Random placement policy performs comparably with three different routing policies.
-Shown as the solid lines in Figure \ref{fig:global-channel-traffic}, the traffic through global channels are quite balanced across all the routers, thus no particular global channel will suffer high traffic burden.
-When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic.
-That's why the blue solid line is lower than the red and green solid line.
-Since the random placement can uniformly distribute traffic, there are no sudden surge of saturated time of global channel over the network, shown as solid lines in Figure \ref{fig:global-channel-stime}.
-
-%local channel traffic and busy time explanation
-
-We observe similar phenomena from the local channel traffic and saturated time, shown in Figure \ref{fig:local-channel-traffic}, \ref{fig:local-channel-stime}).
-Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus the aggregate traffic through local channels of certain routers is quite high.
-Even with adaptive or progressive adaptive routing, the local congestion caused by grouping all MPI ranks in the same group(s) in contiguous placement can not be eliminated.
-Random placement is effective at addressing this type of congestion.
-
-%terminal link traffic and busy time explanation
-Figure \ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which stay the same when different placement and routing configurations are in use.
-All 6 lines are overlapped in Figure \ref{fig:terminal-link-traffic}.
-However, due to the traffic changes on global and local channels, the saturated time of terminal links will experience variability when different routing schemes are in use, as shown in Figure \ref{fig:terminal-link-stime}.
-When contiguous placement coupled with minimal routing(CM), the accumulated congestion on local and global channels cause extremely long saturated time on the terminal link, shown as the blue dashed line in Figure \ref{fig:terminal-link-stime}.
-This again manifests the severe congestion caused by using contiguous placement and minimal routing.
-
-\subsection{Individual Application Analysis}
-\label{sec: workload-1 app analysis}
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/amg/commtime}
-        \caption{AMG}
-        \label{fig:amg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/mg/commtime}
-        \caption{MultiGrid}
-        \label{fig:mg-commtime}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{wkld/cr/commtime}
-        \caption{CrystalRouter}
-        \label{fig:cr-commtime}
-    \end{subfigure}%
-   \caption{The communication time of all ranks in each application.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
-Random placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
-   \label{fig:apps-commtime}
-\end{figure*}
-
-Figure \ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
-
-As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MultiGrid and CrystalRouter suffer the longest communication time when running with contiguous placement and minimal routing (CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter are significantly reduced.
-Random placement further reduces their communication time, and reaches the best performance when coupled with (progressive) adaptive routing (RPA, RA).
-Both MultiGrid and CrystalRouter show the same trend when they are running under different placement and routing configurations.
-AMG is quite an exception.
-The communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA), shown in Figure \ref{fig:amg-commtime}.
-The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
-CM is no better than RM, but still much better RPA, RA.
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
-        \caption{AMG Local Channel Traffic}
-        \label{fig:amg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
-        \label{fig:mg-lc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
-        \label{fig:cr-lc-traffic}
-    \end{subfigure}\\
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
-        \caption{AMG Global Channel Traffic}
-        \label{fig:amg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:mg-gc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:cr-gc-traffic}
-    \end{subfigure}%
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
-   \label{fig:3app-lc-gc-traffic}
-\end{figure*}
-
-% Show the evidence from network level, explain why AMG is different. 
-We look into network level to identify the culprit behind AMG's abnormal behavior with random placement and adaptive routing.
-By identifying the compute nodes each MPI rank resides on and routers that serving each application, we can see that the traffic go through the routers serving AMG skyrockets when random placement and adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and \ref{fig:amg-gc-traffic}.
-Adaptive routing will redirect the traffic of other applications to go through the routers belonging to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
-
-No router will be shared between applications under contiguous placement.
-A number of successive groups will be allocated to the same application under contiguous placement policy.
-When contiguous placement coupled with minimal routing, application will be free of interference from its concurrently running peers.
-However, application communication traffic will be confined within their allocated groups, thus congestion is very likely to happen depending on application communication intensity.
-As the lest communication-intensive application in Workload \Rmnum{1}, AMG can benefit from contiguous placement.
-Under contiguous placement, the traffic go through the local and global channels of the routers belonging to AMG is significantly lower than with random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
-
-MultiGrid and CrystalRouter are more communication-intensive compared with AMG.
-They will suffer congestion on both local and global channels when contiguous placement is in use, shown as the dashed line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-On the other hand, the random placement can uniformly distribute their traffic all over the network, alleviate the possible congestion, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-
-\subsection{Key Observations}
-In summary, based on the results presented in section \ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we have made the following observations.
-
-\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers.
-Therefore, the network could reach the status of load-balanced and hot-spots free.
-
-\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network random placement and adaptive routing are in use.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
-AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use.
-The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slowing down AMG's communication.
-\footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
-
-\emph{Consistent performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} The router and group sharing between jobs are prohibited in contiguous placement policy.
-The traffic won't be redirected from congested routers to less busy ones when minimal routing is in use.
-Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
-%However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.
-
-\section{Study of Parallel Workload \Rmnum{2 }}
-%\section{``Bully" become ``Bullee"}
-\label{sec:workload-2}
-
-In this section, we will verify the observations made in the previous section when Workload \Rmnum{1} is running on the dragonfly network under different placement and routing configurations.
-We conduct the same sets of experiments with Workload \Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter.
-By replacing AMG with sAMG, we turn the ``bully" into ``bullee".
-
-\subsection{Network Performance Analysis}
-\label{sec: workload-2 network analysis}
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under 6 different placement and routing configurations.} 
-\label{tab:syn-wkld-commtime}
-%\centering % Centers the table on the page, comment out to left-justify
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
-\cmidrule(l){2-7}
-	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The average communication time spent by all MPI ranks when Workload \Rmnum{2} is running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
-The contiguous placement coupled with minimal routing results in highest communication time.
-The random placement coupled with minimal routing is the most efficient.
-Progressive adaptive routing is better than adaptive routing when random placement is in use.
-And they have comparable results when coupled contiguous placement.
-The performance of Workload \Rmnum{2} under different configurations keep the similar pattern as it of Workload \Rmnum{1}.
-
-Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running with 6 different configurations.
-Contiguous placement coupled with minimal routing(CM) results in most traffic go through certain local and global channel, thus the longest saturated time for terminal link, local and global channel.
-When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion could be mitigated.
-The random placement coupled with any routing policy(RM, RA, RPA) performs comparably.
-They are better than contiguous placement and minimal routing(CM), but only little improvement against contiguous and (progressive) adaptive (CA, CPA).
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
-        \caption{Global Channel Traffic}
-        \label{fig:synwkld-global-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
-        \caption{Local Channel Traffic}
-        \label{fig:synwkld-local-channel-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
-        \caption{Terminal Link Traffic}
-        \label{fig:synwkld-terminal-link-traffic}
-    \end{subfigure}\\
-
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
-        \caption{Global Channel Saturated Time}
-        \label{fig:synwkld-global-channel-stime}
-    \end{subfigure}\hfill
-     \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
-        \caption{Local Channel Saturated Time}
-        \label{fig:synwkld-local-channel-stime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
-        \caption{Terminal Link Saturated Time}
-        \label{fig:synwkld-terminal-link-stime}
-    \end{subfigure}%
-   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under 6 different placement and routing configurations.}
-   \label{fig:synwkld-network-traffic-stime}
-\end{figure*}
-
-\subsection{Individual Application Analysis}
-\label{sec: workload-2 app analysis}
-
-The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}.
-The ``bully" in Workload \Rmnum{1} becomes the ``bullyee" in Workload \Rmnum{2}.
-MultiGrid and CrystalRouter are the less communication-intensive applications in Workload \Rmnum{2}.
-When random placement coupled with (progressive) adaptive routing is in use, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
-Whereas, sAMG benefits from random placement and (progressive) adaptive routing, shown in Figure \ref{fig:syn-samg-commtime}.
-Contiguous placement coupled with minimal routing prevents applications from sharing network resource, guaranteeing the performance of less communication intensive applications like MultiGrid and CrystalRouter and causing severe performance degradation to sAMG.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
-        \caption{sAMG}
-        \label{fig:syn-samg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
-        \caption{MultiGrid}
-        \label{fig:syn-mg-commtime}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
-        \caption{CrystalRouter}
-        \label{fig:syn-cr-commtime}
-    \end{subfigure}%
-   \caption{The communication time of all ranks in each application.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
-The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullee", MultiGrid and CrystalRouter, suffer performance degradation.}
-   \label{fig:syn-apps-commtime}
-\end{figure*}
-
-% explain the network status of sAMG, MG and CR
-We look into the network level to scrutinize the traffic through the routers serving each application.
-Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers serving sAMG.
-The traffic skyrockets in both local and global channels when contiguous placement coupled with minimal routing (CM) is in use.
-The congestion will be alleviated in both local and global channels when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use.
-Random placement can further reduce the traffic burden on local and global channels by uniformly distributing sAMG traffic over the network.
-
-The traffic go through the local and global channels of the routers serving MultiGrid and CrystalRouter are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}.
-There are more traffic going through when random placement is in use, compared with contiguous placement.
-The extra traffic coming from the ``bully" sAMG cause performance degradation to MultiGrid and CrystalRouter.
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
-        \caption{sAMG Local Channel Traffic}
-        \label{fig:syn-samg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
-        \label{fig:syn-mg-lc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
-        \label{fig:syn-cr-lc-traffic}
-    \end{subfigure}\\
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
-        \caption{sAMG Global Channel Traffic}
-        \label{fig:syn-samg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:syn-mg-gc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:syn-cr-gc-traffic}
-    \end{subfigure}%
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
-   \label{fig:syn-3app-gc-traffic}
-\end{figure*}
-
-\subsection{Key Observations}
-
-In summary, based on the Workload \Rmnum{2}, we have made the following observations.
-
-\emph{The application becomes ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
-
-\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullee" when running concurrently with sAMG in Workload \Rmnum{2}.
-
-\section{Hybrid Job Placement}
-\label{sec: hybrid placement}
-
-The precaution to stop ``bully" behavior is to avoid network sharing between concurrently running jobs.
-Using contiguous placement and minimal routing could be a way to avoid network sharing, but network performance could suffer degradation due to local congestion.
-Running each job with dedicated routing policy is unrealistic, since routing policy is pre-configured and can not be changed on the fly upon job submission.
-However, the job placement policies can be versatile for assigning different allocation (contiguous or random) to specific application.
-
-Thus, we propose the hybrid placement as a reconcile solution.
-In the hybrid placement, the less communication-intensive applications get contiguous allocation while the communication-intensive ones get random allocation.
-We evaluate the effect of hybrid placement on improving network performance as well as preserving the performance of individual application.
-In following experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations.
-\footnote{Due to page limit, we won't present the analysis about network traffic and saturated time in this section.}
-
-\subsection{Network Performance Analysis}
-
-Hybrid placement is also coupled with three routing policies, Minimal, Adaptive and Progressive Adaptive.
-They are denoted respectively as HM, HA and HPA.
-As presented in the previous section, random placement outperforms contiguous placement in terms of network performance, we only compare the results of hybrid placement with random placement due to the page limit.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under hybrid placement and random placement policies.} 
-\label{tab: hyb-placement-wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\
-\cmidrule(l){2-7}
-	      & HM & HA & HPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  &273 &255 &255 &255 &265 &264  \\ % Content row 1
-%\midrule
-%Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-As shown in Table \ref{tab: hyb-placement-wkld-commtime}, hybrid placement and random placement perform comparably.
-When coupled with minimal routing, RM outperforms HM.
-However, when coupled with (progressive) adaptive routing, HA and HPA outperform RA and RPA.
-HA and HPA perform equally well as compared with RM.
-
-\subsection{Individual Application Analysis}
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
-        \caption{AMG Communication Time}
-        \label{fig:hyb-plcmt-amg-commtime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
-        \caption{MG Communication Time}
-        \label{fig:hyb-plcmt-mg-commtime}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
-        \caption{CR Communication Time}
-        \label{fig:hyb-plcmt-cr-commtime}
-    \end{subfigure}%
-   \caption{Application communication time. Workload \Rmnum{1} is running under all the possible placement and routing configurations.}
-   \label{fig:hyb-plcmt-apps-commtime}
-\end{figure*}
-
-Figure \ref{fig:hyb-plcmt-apps-commtime} shows the communication time of each application when hybrid placement configurations are in use.
-MultiGrid and CrystalRouter have basically the same performance with hybrid placement as compared with random placement.
-Since they still get random allocation in the hybrid placement.
-The performance of AMG is significantly improved when hybrid placement is in use.
-Compared with ``RA" and ``RPA", ``HA" and ``HPA" can greatly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}.
-This is due the contiguous allocation assigned to AMG in the hybrid placement policy.
-When being coupled with minimal routing, hybrid placement and contiguous placement have similar performance for AMG.
-However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG.
-Since AMG is less communication-intensive and can not fully utilize network, it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups.
-So for AMG, ``HA" and ``HPA" are worse than ``CA" and ``CPA", but they are much better than ``RA" and ``RPA".
-
-\subsection{Key Observations}
-
-Based on the results from experimenting with hybrid placement policy, we can make the following observations.
-
-\emph{Compared with random placement policy, hybrid placement can guarantee comparable network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.
-
-\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.} Hybrid placement policy preserves contiguous allocation for less communication-intensive application, prevents network resource from being shared by others.
-Unlike random placement indulging the ``bully", hybrid placement can restrain it to some extent.
-
-Hybrid placement can guarantee the performance of individual application without causing performance degradation to network performance.
-Compared with contiguous and random placement policy, hybrid placement are more preferable to HPC systems with dragonfly networks.
-
-\section{Related Work}
-\label{sec:related work}
-
-The impact of job placement to both system and application always catches researchers' appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
-Skinner et al.
-identified that network congestion could cause significant performance variability \cite{dskinner}.
-Bhatele et al.
-studied the performance variability of a specific application, p3FD, running on different production systems with torus networks \cite{abhinav-sc13}.
-They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource.
-Jokanovic et al.
-studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing \cite{jose-ipdps15}.
-
-Recently, several researchers have investigated the job placement and routing schemes on dragonfly network.
-Bogdan et al.
-proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network \cite{hoefler-hpdc14}.
-Jain et al.
-conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network \cite{jain-sc14}.
-Their work is based on an analytical model and synthetic workload.
-Bhatele et al.
-used simulation to study the performance of synthetic workload under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.
-
-Our work different from the previous works in the following ways.
-First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system.
-Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
-We found that although random placement coupled with adaptive routing can improve the network performance, the less communication-intensive applications in the workload may suffer performance degradation.
-Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network performance when application is running.
-The traffic and saturated time of router's each link are valuable information for detailed analysis.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-In this paper, we have conducted extensive study about application's behavior when running on dragonfly network with different job placement and routing configurations.
-We resorted to CODES, a high-fidelity HPC network simulation tool, and used three parallel scientific applications traces collected from production system to analyze the applications' behavior on network level.
-We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network to reach load balance and hot-spots free for the network, the performance of certain job would be impaired.
-We identify this phenomenon as ``bully" between concurrently running jobs, and the victim always being the less communication-intensive one.
-On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, it can guarantee the performance of ``bullee" application by limiting the network sharing from concurrently running peers.
-
-Due the presence of this ``bully", we propose to use hybrid placement policy for workload running on systems with dragonfly networks.
-In hybrid placement policy, the less intensive applications get contiguous allocations, and the intensive ones get random allocations.
-We believe the findings presented in this paper can illuminate a path to more efficient workload manager for future systems with dragonfly network.
+\input{conclusion}
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{./reference}
+\bibliography{IEEEabrv,reference}
 

### 2016-03-30 hybrid_placement.tex
put each section into separate .tex file

\section{Hybrid Job Placement}
\label{sec: hybrid placement}

The precaution to stop ``bully" behavior is to avoid network sharing between concurrently running jobs. Using contiguous placement and minimal routing could be a way to avoid network sharing, but network performance could suffer degradation due to local congestion. Running each job with dedicated routing policy is unrealistic, since routing policy is pre-configured and can not be changed on the fly upon job submission. However, the job placement policies can be versatile for assigning different allocation (contiguous or random) to specific application.

Thus, we propose the hybrid placement as a reconcile solution. In the hybrid placement, the less communication-intensive applications get contiguous allocation while the communication-intensive ones get random allocation. We evaluate the effect of hybrid placement on improving network performance as well as preserving the performance of individual application. In following experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations. \footnote{Due to page limit, we won't present the analysis about network traffic and saturated time in this section.}

\subsection{Network Performance Analysis}

Hybrid placement is also coupled with three routing policies, Minimal, Adaptive and Progressive Adaptive. They are denoted respectively as HM, HA and HPA. As presented in the previous section, random placement outperforms contiguous placement in terms of network performance, we only compare the results of hybrid placement with random placement due to the page limit.

\begin{table}[ht]
\begin{center}
\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under hybrid placement and random placement policies.} 
\label{tab: hyb-placement-wkld-commtime}
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement and Routing Configurations} \\
\cmidrule(l){2-7}
          & HM & HA & HPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Time(ms)  &273 &255 &255 &255 &265 &264  \\ % Content row 1
%\midrule
%Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

As shown in Table \ref{tab: hyb-placement-wkld-commtime}, hybrid placement and random placement perform comparably. When coupled with minimal routing, RM outperforms HM. However, when coupled with (progressive) adaptive routing, HA and HPA outperform RA and RPA. HA and HPA perform equally well as compared with RM.

\subsection{Individual Application Analysis}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:hyb-plcmt-amg-commtime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:hyb-plcmt-mg-commtime}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:hyb-plcmt-cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Workload \Rmnum{1} is running under all the possible placement and routing configurations.}
   \label{fig:hyb-plcmt-apps-commtime}
\end{figure*}

Figure \ref{fig:hyb-plcmt-apps-commtime} shows the communication time of each application when hybrid placement configurations are in use. MultiGrid and CrystalRouter have basically the same performance with hybrid placement as compared with random placement. Since they still get random allocation in the hybrid placement. The performance of AMG is significantly improved when hybrid placement is in use. Compared with ``RA" and ``RPA", ``HA" and ``HPA" can greatly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}. This is due the contiguous allocation assigned to AMG in the hybrid placement policy. When being coupled with minimal routing, hybrid placement and contiguous placement have similar performance for AMG. However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG. Since AMG is less communication-intensive and can not fully utilize network, it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups. So for AMG, ``HA" and ``HPA" are worse than ``CA" and ``CPA", but they are much better than ``RA" and ``RPA".

\subsection{Key Observations}

Based on the results from experimenting with hybrid placement policy, we can make the following observations.

\emph{Compared with random placement policy, hybrid placement can guarantee comparable network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.

\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.} Hybrid placement policy preserves contiguous allocation for less communication-intensive application, prevents network resource from being shared by others. Unlike random placement indulging the ``bully", hybrid placement can restrain it to some extent.

Hybrid placement can guarantee the performance of individual application without causing performance degradation to network performance. Compared with contiguous and random placement policy, hybrid placement are more preferable to HPC systems with dragonfly networks.

### 2016-03-30 intro.tex
put each section into separate .tex file

\section{Introduction}
\label{sec:intro}

The low latency and high bandwidth interconnect network plays a critical role in HPC system performance. As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scarce resource. The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}. This make the dragonfly network a very promising choice for building petaflop and beyond supercomputers. 
%The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.

While dragonfly topologies provide low-latency and high-bandwidth networking, efficiently utilizing it is a significant concern. In particular, intelligent job placement to avoid interference is of paramount importance to guarantee the performance of each job when it shares network resources with other concurrently running peers \cite{bhatele2015, dskinner}. Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.

In this work, we study the interference between concurrently running jobs on dragonfly networks with different job placement and routing policies. We use CODES, an HPC network simulation toolkit with high fidelity and excellent scalability for packet level simulation \cite{codes}. Unlike much existing work that rely on synthetic workloads, we use traces of three representative applications from the DOE Design Forward Project \cite{designforwardwebpage}. The advantage of using real application traces is straight forward: these traces can capture detailed application communication behaviors that are  omitted in synthetic workload for simplification. Applications are usually distinctive from each other in data transfer amount, communication pattern, operation dependency etc., which can be impractical to reproduce in a synthetic workload.

We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies. We analyze the performance of network as well as individual application when running with different placement and routing configurations. Our evaluation is based on more than 1000 runs of simulation. We make the following interesting observations through extensive simulation.

\begin{itemize}

    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion, optimizing the overall performance of the dragonfly network.

    \item The ``bully" behavior occurs between concurrently running jobs on a dragonfly network when random placement and adaptive routing are in use. Communication-intensive jobs obtain performance improvement at the expense of less intensive jobs suffering performance degradation.

    \item Random placement coupled with adaptive routing can improve the performance of communication-intensive jobs by enabling network resource sharing, though it introduces interference between concurrently running jobs.

    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of less communication-intensive jobs by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.

\end{itemize}

Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to the job communication intensity. \emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far. We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators. For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks. System software developers could design better scheduling algorithms for jobs with distinct communication behavior. System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.

The rest of this paper is organized as follows. Section \ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies. Section \ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project. Section \ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations. Section \ref{sec:workload-2} validates the observations we obtain from previous section. Section \ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network. Section \ref{sec:related work} discusses the related work. Finally, the conclusion is presented in Section \ref{sec:conclusion}.

### 2016-03-30 methodology.tex
put each section into separate .tex file

\section{Methodology}
\label{sec: methodology}

Configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being. Even with access to systems with such networks, job placement and routing policies are part of system configuration, which is impossible for user to make changes at will~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}. Therefore, we resort to simulation in our work.

%It is difficult to experiment with concurrently running jobs on HPC systems~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}. One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will. Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results. The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being. Therefore, we resort to simulation in our work.

\subsection{Simulation Tool}
\label{sec:simulation-tool}

A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability~\cite{codes}. CODES supports dragonfly~\cite{codes-dragonfly}~\cite{misbah-tpds}, torus~\cite{misbah-pads-2014}~\cite{ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation. It can drive these models through an MPI simulation layer utilizing DUMPI traces~\cite{sst}. In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on the dragonfly network.

\subsection{Parallel Applications}
\label{sec: application traces}

We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent a wide array of applications running on leadership-class supercomputers. Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).

\textbf{AMG:} The Algebraic MultiGrid Solver is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages. It has been derived directly from the BoomerAMG solver developed in the Center for Applied Scientific Computing (CASC) at LLNL~\cite{amg}.

\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes~\cite{boxlib}, which are used for structured grid physics packages.

\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000~\cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory. It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.

\subsection{System Configuration}
\label{sec: simulation configuration}

The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et. al~\cite{kim-micro}. Our dragonfly network consists of 33 groups, each of which contains eight routers. Each router has four compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}. In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.

%\footnote{With respect to random placement, we experiment with 50 sets of distinctive allocation generated by random placement. The corresponding experimental results are median chosen, which intended to eliminate the possibility of variation.}

\begin{table}[ht]
\begin{center}
\caption{The notation for different placement and routing configurations} 
\label{tab: placement routing configs}
\begin{tabular}{l c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{3}{c}{Routing Policies} \\ 
\cmidrule(l){2-4}
Placement Policies & Minimal & Adaptive & Progressive Adaptive\\ % Column names row
\midrule % In-table horizontal line
Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
\midrule
Random  &   RM  &   RA   &  RPA   \\ 
\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

Our analysis focuses on the following metrics:
\begin{itemize}

    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router. We analyze the traffic on the terminal link, local and global channel of each router. The network reaches optimal performance when the traffic is uniformly distributed and no particular router is over-loaded.

    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full. We analyze the saturated time of ports corresponding to terminal link, local and global channel. The saturated time indicates the congestion level of routers.

    \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks. The performance of each application is measured by the communication time.  
\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in the experiments.
}

\end{itemize}

\subsection{Workload Summary}
\label{sec:workload summary}

Two sets of parallel workloads are used in this work. Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter. In Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}. Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter. sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x. sAMG is the most communication-intensive job in Workload~\Rmnum{2}.

Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running jobs on the dragonfly network. Workload~\Rmnum{2} is used to verify the results and conclusion obtained from the study of Workload~\Rmnum{1}.

%Table \ref{tab:apps-detail} summarizes the details of each application. It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.

\begin{table}[ht]
\begin{center}
\caption{The details of each application.} 
\label{tab:apps-detail}
\begin{tabular}{l c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{3}{c}{Application Details} \\ 
\cmidrule(l){2-4}
App Name & Num. Rank & Avg. Data/Rank & Total Data\\ % Column names row
\midrule % In-table horizontal line
AMG  &    216 &   0.6MB   &     130MB\\ % Content row 1
\midrule
MultiGrid  &    125 &   5MB   &     625MB\\ 
\midrule
CrystalRouter  &   100  &  35MB    &     3500MB\\ 
\midrule
sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

### 2016-03-30 related_work.tex
put each section into separate .tex file

\section{Related Work}
\label{sec:related work}

The impact of job placement to both system and application always catches researchers' appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}. Skinner et al. identified that network congestion could cause significant performance variability \cite{dskinner}. Bhatele et al. studied the performance variability of a specific application, p3FD, running on different production systems with torus networks \cite{abhinav-sc13}. They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource. Jokanovic et al. studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing \cite{jose-ipdps15}.

Recently, several researchers have investigated the job placement and routing schemes on dragonfly network. Bogdan et al. proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network \cite{hoefler-hpdc14}. Jain et al. conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network \cite{jain-sc14}. Their work is based on an analytical model and synthetic workload. Bhatele et al. used simulation to study the performance of synthetic workload under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.

Our work different from the previous works in the following ways. First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system. Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload. We found that although random placement coupled with adaptive routing can improve the network performance, the less communication-intensive applications in the workload may suffer performance degradation. Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network performance when application is running. The traffic and saturated time of router's each link are valuable information for detailed analysis.

### 2016-03-30 study_workload_1.tex
put each section into separate .tex file

\section{Study of Parallel Workload~\Rmnum{1}}
%\section{Identify the ``Bully"}
\label{sec:workload-1}

The study of parallel workload~\Rmnum{1} consists of two parts. Firstly, we analyze the over-all network performance when Workload \Rmnum{1} is running under different placement and routing configurations. Secondly, we isolate each application from the workload, analyze its performance  by scrutinizing the traffic going through the routers that serve each job. The analysis allows us to identify the ``bully" in the workload.

\subsection{Network Performance Analysis}
\label{sec: workload-1 network analysis}

\iffalse

\begin{table}[ht]
\begin{center}
\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
\label{tab:wkld-commtime}
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
\cmidrule(l){2-7}
          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1

\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

The average communication time spent by all MPI ranks when Workload~\Rmnum{1} is running under different placement and routing configurations shown in Table~\ref{tab:wkld-commtime}. The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations. The contiguous placement coupled with minimal routing (CM) results in highest communication time. When coupled with (progressive) adaptive routing (CA, CPA), the communication time can be reduced but still higher than random placement polices.

\fi

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:global-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:local-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:terminal-link-traffic}
    \end{subfigure}\\

    \centering   
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-stime}
        \caption{Global Channel Saturated Time}
        \label{fig:global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-stime}
        \caption{Local Channel Saturated Time}
        \label{fig:local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-stime}
        \caption{Terminal Link Saturated Time}
        \label{fig:terminal-link-stime}
    \end{subfigure}%
   \caption{The aggregate traffic and saturated time of the dragonfly network when Workload~\Rmnum{1} running under six different placement and routing configurations. ``CA" and ``CPA" performs comparably, the corresponding lines are overlapped. }
   \label{fig:wkld-network-traffic-stime}
\end{figure*}

Figure~\ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local and global channels as well as the corresponding saturated time when Workload~\Rmnum{1} is running on the dragonfly network with six different placement and routing configurations. When contiguous placement coupled with minimal routing(CM) is in use, all the traffic are confined within the contiguously allocated groups, causing congestion on some routers along certain shortest paths from the source to the destination. The congested routers are over-loaded with high volume of traffic going through their local and global channels, shown as the blue dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. In the meanwhile, the corresponding saturated time of their local and global channels are also the highest compared with other configurations, shown as the blue dashed line in Figure~\ref{fig:global-channel-stime} and Figure~\ref{fig:local-channel-stime} .

When contiguous placement coupled with progressive adaptive routing (CPA) is in use, the traffic would take non-shortest paths via intermediate routers to void congestion. The congested routers along the shortest paths will not suffer the high volume of traffic as they used to. The traffic through local and global channels are greatly reduced, shown as the green dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. The corresponding saturated time on local and global channels also drop a lot, indicating the congestion are alleviated by using progressive adaptive routing. The adaptive routing performs comparably compared with progressive adaptive routing, thus CA is overlapped with CPA in the all the figures above.

Random placement policy performs comparably with three different routing policies.
Random placement can uniformly distribute MPI ranks over the network, balance the traffic load over the network. Shown as the solid lines in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, no router suffers exceptional high volume of traffic on its local and global channels. When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic. The blue solid line(RM) is lower than the red and green solid line (RA, RPA) in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}.

Due to the same reason, no router suffers exceptionally long saturated time on their global channels when random placement coupled (progressive) adaptive are in use, shown as red and green solid lines in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. However, when random placement is couple with minimal routing, the saturated time on certain routers along the shortest paths would increase, shown as the prolonged blue solid line in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. Since the minimal routing always chooses the shortest paths, increasing the possibility of congestion along those paths.

%local channel traffic and busy time explanation

%We observe similar phenomena from the local channel traffic and saturated time, shown in Figure \ref{fig:local-channel-traffic}, \ref{fig:local-channel-stime}). Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus the aggregate traffic through local channels of certain routers is quite high. Even with adaptive or progressive adaptive routing, the local congestion caused by grouping all MPI ranks in the same group(s) in contiguous placement can not be eliminated. Random placement is effective at addressing this type of congestion.

%terminal link traffic and busy time explanation
Figure~\ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which stay the same when different placement and routing configurations are in use. All six lines are overlapped in Figure~\ref{fig:terminal-link-traffic}. However, due to the traffic changes on local and channels, the saturated time of terminal links will experience variability when different routing policies are in use, as shown in Figure~\ref{fig:terminal-link-stime}. When contiguous placement coupled with minimal routing(CM), the accumulated congestion on local and global channels cause extremely long saturated time on the terminal links, shown as the blue dashed line in Figure~\ref{fig:terminal-link-stime}. This again manifests the severe congestion caused by using contiguous placement and minimal routing.

\subsection{Individual Application Analysis}
\label{sec: workload-1 app analysis}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{wkld/amg/commtime}
        \caption{AMG}
        \label{fig:amg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{wkld/mg/commtime}
        \caption{MultiGrid}
        \label{fig:mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{wkld/cr/commtime}
        \caption{CrystalRouter}
        \label{fig:cr-commtime}
    \end{subfigure}%
   \caption{The communication time of all ranks in each application. Random placement and adaptive routing can improve the communication time of MultiGrid and CrystalRouter, while AMG's communication time is greatly prolonged.}
   \label{fig:apps-commtime}
\end{figure*}
\TODO{resume from here}
We isolate each application from Workload~\Rmnum{1} to study the performance application
Figure \ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.

As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MultiGrid and CrystalRouter suffer the longest communication time when running with contiguous placement and minimal routing (CM). When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter are significantly reduced. Random placement further reduces their communication time, and reaches the best performance when coupled with (progressive) adaptive routing (RPA, RA). Both MultiGrid and CrystalRouter show the same trend when they are running under different placement and routing configurations. AMG is quite an exception. The communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA), shown in Figure \ref{fig:amg-commtime}. The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG. CM is no better than RM, but still much better RPA, RA.

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:cr-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:cr-gc-traffic}
    \end{subfigure}%
   \caption{The aggregate traffic go through the local and global channels of routers serving specific application. ``CA" and ``CPA" perform comparably, the corresponding lines are overlapped. More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
   \label{fig:3app-lc-gc-traffic}
\end{figure*}

% Show the evidence from network level, explain why AMG is different. 
We look into network level to identify the culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the compute nodes each MPI rank resides on and routers that serving each application, we can see that the traffic go through the routers serving AMG skyrockets when random placement and adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and \ref{fig:amg-gc-traffic}. Adaptive routing will redirect the traffic of other applications to go through the routers belonging to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.

No router will be shared between applications under contiguous placement. A number of successive groups will be allocated to the same application under contiguous placement policy. When contiguous placement coupled with minimal routing, application will be free of interference from its concurrently running peers. However, application communication traffic will be confined within their allocated groups, thus congestion is very likely to happen depending on application communication intensity. As the lest communication-intensive application in Workload \Rmnum{1}, AMG can benefit from contiguous placement. Under contiguous placement, the traffic go through the local and global channels of the routers belonging to AMG is significantly lower than with random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.

MultiGrid and CrystalRouter are more communication-intensive compared with AMG. They will suffer congestion on both local and global channels when contiguous placement is in use, shown as the dashed line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}. On the other hand, the random placement can uniformly distribute their traffic all over the network, alleviate the possible congestion, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.

\subsection{Key Observations}
In summary, based on the results presented in section \ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we have made the following observations.

\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers. Therefore, the network could reach the status of load-balanced and hot-spots free.

\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network random placement and adaptive routing are in use.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter. AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use. The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slowing down AMG's communication. \footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}

\emph{Consistent performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} The router and group sharing between jobs are prohibited in contiguous placement policy. The traffic won't be redirected from congested routers to less busy ones when minimal routing is in use. Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated. 
%However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.

### 2016-03-30 study_workload_2.tex
put each section into separate .tex file

\section{Study of Parallel Workload \Rmnum{2 }}
%\section{``Bully" become ``Bullee"}
\label{sec:workload-2}

In this section, we will verify the observations made in the previous section when Workload \Rmnum{1} is running on the dragonfly network under different placement and routing configurations. We conduct the same sets of experiments with Workload \Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter. By replacing AMG with sAMG, we turn the ``bully" into ``bullee".

\subsection{Network Performance Analysis}
\label{sec: workload-2 network analysis}

\begin{table}[ht]
\begin{center}
\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under 6 different placement and routing configurations.} 
\label{tab:syn-wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1

\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

The average communication time spent by all MPI ranks when Workload \Rmnum{2} is running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}. The contiguous placement coupled with minimal routing results in highest communication time. The random placement coupled with minimal routing is the most efficient. Progressive adaptive routing is better than adaptive routing when random placement is in use. And they have comparable results when coupled contiguous placement. The performance of Workload \Rmnum{2} under different configurations keep the similar pattern as it of Workload \Rmnum{1}.

Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running with 6 different configurations. Contiguous placement coupled with minimal routing(CM) results in most traffic go through certain local and global channel, thus the longest saturated time for terminal link, local and global channel. When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion could be mitigated. The random placement coupled with any routing policy(RM, RA, RPA) performs comparably. They are better than contiguous placement and minimal routing(CM), but only little improvement against contiguous and (progressive) adaptive (CA, CPA).

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:synwkld-global-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:synwkld-local-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:synwkld-terminal-link-traffic}
    \end{subfigure}\\

    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
        \caption{Global Channel Saturated Time}
        \label{fig:synwkld-global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
        \caption{Local Channel Saturated Time}
        \label{fig:synwkld-local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
        \caption{Terminal Link Saturated Time}
        \label{fig:synwkld-terminal-link-stime}
    \end{subfigure}%
   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under 6 different placement and routing configurations.}
   \label{fig:synwkld-network-traffic-stime}
\end{figure*}

\subsection{Individual Application Analysis}
\label{sec: workload-2 app analysis}

The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}. The ``bully" in Workload \Rmnum{1} becomes the ``bullyee" in Workload \Rmnum{2}. MultiGrid and CrystalRouter are the less communication-intensive applications in Workload \Rmnum{2}.  When random placement coupled with (progressive) adaptive routing is in use, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}. Whereas, sAMG benefits from random placement and (progressive) adaptive routing, shown in Figure \ref{fig:syn-samg-commtime}. Contiguous placement coupled with minimal routing prevents applications from sharing network resource, guaranteeing the performance of less communication intensive applications like MultiGrid and CrystalRouter and causing severe performance degradation to sAMG.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
        \caption{sAMG}
        \label{fig:syn-samg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
        \caption{MultiGrid}
        \label{fig:syn-mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
        \caption{CrystalRouter}
        \label{fig:syn-cr-commtime}
    \end{subfigure}%
   \caption{The communication time of all ranks in each application. Three applications running concurrently on dragonfly network with different placement and routing configurations. The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullee", MultiGrid and CrystalRouter, suffer performance degradation.}
   \label{fig:syn-apps-commtime}
\end{figure*}

% explain the network status of sAMG, MG and CR
We look into the network level to scrutinize the traffic through the routers serving each application. Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers serving sAMG. The traffic skyrockets in both local and global channels when contiguous placement coupled with minimal routing (CM) is in use. The congestion will be alleviated in both local and global channels when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use. Random placement can further reduce the traffic burden on local and global channels by uniformly distributing sAMG traffic over the network.

The traffic go through the local and global channels of the routers serving MultiGrid and CrystalRouter are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}. There are more traffic going through when random placement is in use, compared with contiguous placement. The extra traffic coming from the ``bully" sAMG cause performance degradation to MultiGrid and CrystalRouter.

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}%
   \caption{The aggregate traffic go through the local and global channels of routers serving specific application. ``CA" and ``CPA" perform comparably, the corresponding lines are overlapped. More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

\subsection{Key Observations}

In summary, based on the Workload \Rmnum{2}, we have made the following observations.

\emph{The application becomes ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.

\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullee" when running concurrently with sAMG in Workload \Rmnum{2}.

### 2016-03-31 study_workload_1.tex
half way through section 4

@@
         \centering
-        \includegraphics[height=1.5 in]{wkld/amg/commtime}
-        \caption{AMG}
-        \label{fig:amg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
         \includegraphics[height=1.5 in]{wkld/mg/commtime}
@@
     \end{subfigure}%
+    \hspace{1em}%
     \begin{subfigure}[t]{0.32\textwidth}
@@
     \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{wkld/amg/commtime}
+        \caption{AMG}
+        \label{fig:amg-commtime}
+    \end{subfigure}%
     \caption{The communication time of all ranks in each application.
@@
 \end{figure*}
-\TODO{resume from here}
-We isolate each application from Workload~\Rmnum{1} to study the performance application
-Figure \ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under 6 different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
 
-As shown in Figure \ref{fig:mg-commtime}, \ref{fig:cr-commtime}, MultiGrid and CrystalRouter suffer the longest communication time when running with contiguous placement and minimal routing (CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA), the communication time of both MultiGrid and CrystalRouter are significantly reduced.
-Random placement further reduces their communication time, and reaches the best performance when coupled with (progressive) adaptive routing (RPA, RA).
-Both MultiGrid and CrystalRouter show the same trend when they are running under different placement and routing configurations.
+We study the performance of each application individually by isolating it from Workload~\Rmnum{1}.   
+Figure~\ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under six different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
+
+As shown in Figure~\ref{fig:mg-commtime}, MultiGrid takes the most communication time when it is running with contiguous placement and minimal routing (CM).
+When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA) are in use, the communication time is significantly reduced.
+Random placement coupled with minimal routing (RM) can make further improvement, and reaches the best performance(lowest communication time) when coupled with adaptive and progressive adaptive routing(RA, RPA).
+Due to the variance of data transfer amount among MPI ranks, MultiGrid communication time also presents great variation, indicated by the long boxes in Figure~\ref{fig:mg-commtime}.
+
+CrystalRouter takes more communication time compared with the other applications because of its high volume of data transfer. When it is running with six placement and routing configurations, 
+CrystalRouter communication time presents similarly trend as MultiGrid but with little variance, shown in Figure~\ref{fig:cr-commtime}.
+
 AMG is quite an exception. 
-The communication time of AMG skyrockets when running under random placement coupled with (progressive) adaptive routing (RPA, RA), shown in Figure \ref{fig:amg-commtime}.
-The contiguous placement coupled with (progressive) adaptive routing can reach the best performance for AMG.
-CM is no better than RM, but still much better RPA, RA.
+The communication time of AMG running with different placement and routing configuration are shown in Figure~\ref{fig:amg-commtime}.
+When contiguous placement is in use, AMG behaves similarly as MultiGrid and CrystalRouter over three routing policies. 
+It takes comparable amount of communication time when contiguous placement coupled with adaptive and progressive routing. 
+When coupled with minimal routing, the communication time increase twofold. 
+AMG behaves abnormally when random placement is in use. 
+The communication time skyrockets when random placement coupled with (progressive) adaptive routing (RPA, RA) are in use.
+Minimal routing (RM) can mitigate this performance degradation, but still worse than CA and CPA.
+
+We observe that when Workload~\Rmnum{1} is running with random placement and (progressive) adaptive routing, the performance of MultiGrid and CrystalRouter are significant improved, whereas AMG suffers performance degradation.
 
@@
     \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
-        \caption{AMG Local Channel Traffic}
-        \label{fig:amg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
     \begin{subfigure}[t]{0.32\textwidth}
@@
         \label{fig:cr-lc-traffic}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
+        \caption{AMG Local Channel Traffic}
+        \label{fig:amg-lc-traffic}
     \end{subfigure}\\  
     \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
-        \caption{AMG Global Channel Traffic}
-        \label{fig:amg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
@@
         \label{fig:cr-gc-traffic}
-    \end{subfigure}%
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
+        \caption{AMG Global Channel Traffic}
+        \label{fig:amg-gc-traffic}
+    \end{subfigure}
    \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
@@
 \end{figure*}
+
+\TODO{resume from here}
 

### 2016-03-31 background.tex
finished the rewrite for section 4; made corresponding changes as necessary in section 3

@@
 
-\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to a job in a consecutive manner.
+\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to an application in a consecutive manner.
 The assignment first fills up a group, then crosses group boundaries and starts to fill the next group if necessary.
 As shown in Figure~\ref{fig:dragonfly-overview}, $J2$ gets eight nodes by contiguous placement.
-Contiguous placement confines the tasks of a job into the same group, which may result in local network congestion and increase the possibility of hot-spots.
+Contiguous placement confines the tasks of an application into the same group and uses minimum number of routers serving each application, which may result in local network congestion and increase the possibility of hot-spots.
 
@@
 The nodes assigned to $J1$ in Figure~\ref{fig:dragonfly-overview} are attached to different routers in different groups.
-Routers may be shared by different jobs when random placement is in use.
-Random placement can distribute the tasks of a job uniformly across the whole system to avoid the possible local congestion.
+Routers may be shared by different jobs and more routers are involved in serving each application when random placement is in use.
+Random placement can distribute the tasks of an application uniformly across the network to avoid the possible local congestion.
 However, random placement may cause possible congestion on global links.

### 2016-03-31 study_workload_1.tex
finished the rewrite for section 4; made corresponding changes as necessary in section 3

@@
 The study of parallel workload~\Rmnum{1} consists of two parts.
-Firstly, we analyze the over-all network performance when Workload \Rmnum{1} is running under different placement and routing configurations.
+Firstly, we analyze the over-all network performance when Workload~\Rmnum{1} is running under different placement and routing configurations.
 Secondly, we isolate each application from the workload, analyze its performance by scrutinizing the traffic going through the routers that serve each job.
@@
 
-\iffalse
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
-\label{tab:wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
-\cmidrule(l){2-7}
-          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The average communication time spent by all MPI ranks when Workload~\Rmnum{1} is running under different placement and routing configurations shown in Table~\ref{tab:wkld-commtime}.
-The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.
-The contiguous placement coupled with minimal routing (CM) results in highest communication time.
-When coupled with (progressive) adaptive routing (CA, CPA), the communication time can be reduced but still higher than random placement polices.
-
-\fi
+We study the network performance under different placement and routing configurations by analyzing the traffic going through the routers and their saturated time. 
+The distribution of traffic over the network can reveal the loading situation, 
+indicating whether the network is load-balanced or not. 
+The saturated time can indicate the congestion situation on certain part of the network.
 
@@
 
-Figure~\ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local and global channels as well as the corresponding saturated time when Workload~\Rmnum{1} is running on the dragonfly network with six different placement and routing configurations.
-When contiguous placement coupled with minimal routing(CM) is in use, all the traffic are confined within the contiguously allocated groups, causing congestion on some routers along certain shortest paths from the source to the destination.
-The congested routers are over-loaded with high volume of traffic going through their local and global channels, shown as the blue dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}.
-In the meanwhile, the corresponding saturated time of their local and global channels are also the highest compared with other configurations, shown as the blue dashed line in Figure~\ref{fig:global-channel-stime} and Figure~\ref{fig:local-channel-stime} .
+Figure~\ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local and global channels 
+as well as the corresponding saturated time when 
+Workload~\Rmnum{1} is running on the dragonfly network with six different placement and routing configurations. 
+When contiguous placement coupled with minimal routing(CM) is in use, 
+all the traffic are confined within the contiguously allocated groups, 
+causing congestion on some routers along certain shortest paths from the source to the destination. 
+The congested routers are over-loaded with high volume of traffic going through their local and global channels, 
+shown as the blue dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. 
+In the meanwhile, the corresponding saturated time of their local and global channels are also the highest compared with other configurations, 
+shown as the blue dashed line in Figure~\ref{fig:global-channel-stime} and Figure~\ref{fig:local-channel-stime} .
 
-When contiguous placement coupled with progressive adaptive routing (CPA) is in use, the traffic would take non-shortest paths via intermediate routers to void congestion.
+When contiguous placement coupled with progressive adaptive routing (CPA) is in use, 
+the traffic would take non-shortest paths via intermediate routers to void congestion. 
 The congested routers along the shortest paths will not suffer the high volume of traffic as they used to. 
-The traffic through local and global channels are greatly reduced, shown as the green dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}.
-The corresponding saturated time on local and global channels also drop a lot, indicating the congestion are alleviated by using progressive adaptive routing.
-The adaptive routing performs comparably compared with progressive adaptive routing, thus CA is overlapped with CPA in the all the figures above.
+The traffic through local and global channels are greatly reduced, 
+shown as the green dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. 
+The corresponding saturated time on local and global channels also drop a lot, 
+indicating the congestion are alleviated by using progressive adaptive routing. 
+The adaptive routing performs comparably compared with progressive adaptive routing, 
+thus CA is overlapped with CPA in the all the figures above.
 
 Random placement policy performs comparably with three different routing policies.
-Random placement can uniformly distribute MPI ranks over the network, balance the traffic load over the network.
-Shown as the solid lines in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, no router suffers exceptional high volume of traffic on its local and global channels.
-When the random placements coupled with minimal routing (RM), the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic.
+Random placement can uniformly distribute MPI ranks over the network, 
+balance the traffic load over the network. 
+Shown as the solid lines in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, 
+no router suffers exceptional high volume of traffic on its local and global channels. 
+When the random placements coupled with minimal routing (RM), 
+the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic. 
 The blue solid line(RM) is lower than the red and green solid line (RA, RPA) in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}.
 
-Due to the same reason, no router suffers exceptionally long saturated time on their global channels when random placement coupled (progressive) adaptive are in use, shown as red and green solid lines in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}.
-However, when random placement is couple with minimal routing, the saturated time on certain routers along the shortest paths would increase, shown as the prolonged blue solid line in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}.
-Since the minimal routing always chooses the shortest paths, increasing the possibility of congestion along those paths.
-
-%local channel traffic and busy time explanation
-
-%We observe similar phenomena from the local channel traffic and saturated time, shown in Figure \ref{fig:local-channel-traffic}, \ref{fig:local-channel-stime}).
-Contiguous placement coupled with minimal routing (CM) results in local congestion, and thus the aggregate traffic through local channels of certain routers is quite high.
-Even with adaptive or progressive adaptive routing, the local congestion caused by grouping all MPI ranks in the same group(s) in contiguous placement can not be eliminated.
-Random placement is effective at addressing this type of congestion.
+Due to the same reason, 
+no router suffers exceptionally long saturated time on their global channels when random placement coupled (progressive) adaptive are in use, 
+shown as red and green solid lines in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. 
+However, when random placement is couple with minimal routing, 
+the saturated time on certain routers along the shortest paths would increase, 
+shown as the prolonged blue solid line in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. 
+Since the minimal routing always chooses the shortest paths, 
+increasing the possibility of congestion along those paths.
 
 %terminal link traffic and busy time explanation
-Figure~\ref{fig:terminal-link-traffic} is for the purpose of symmetry, it shows the traffic per rank (aka traffic through terminal links), which stay the same when different placement and routing configurations are in use.
+Figure~\ref{fig:terminal-link-traffic} is for the purpose of symmetry, 
+it shows the traffic per rank (aka traffic through terminal links), 
+which stay the same when different placement and routing configurations are in use. 
 All six lines are overlapped in Figure~\ref{fig:terminal-link-traffic}. 
-However, due to the traffic changes on local and channels, the saturated time of terminal links will experience variability when different routing policies are in use, as shown in Figure~\ref{fig:terminal-link-stime}.
-When contiguous placement coupled with minimal routing(CM), the accumulated congestion on local and global channels cause extremely long saturated time on the terminal links, shown as the blue dashed line in Figure~\ref{fig:terminal-link-stime}.
+However, due to the traffic changes on local and channels, 
+the saturated time of terminal links will experience variability when different routing policies are in use, as shown in Figure~\ref{fig:terminal-link-stime}. 
+When contiguous placement coupled with minimal routing(CM), 
+the accumulated congestion on local and global channels cause extremely long saturated time on the terminal links, 
+shown as the blue dashed line in Figure~\ref{fig:terminal-link-stime}. 
 This again manifests the severe congestion caused by using contiguous placement and minimal routing.
+
+%===========================================================
+%from the workload perspective to study the network performance. 
+The efficiency of the workload communication is another perspective to evaluate the network performance. 
+The average communication time spent by all MPI ranks when Workload~\Rmnum{1} is running under different placement and routing configurations shown in Table~\ref{tab:wkld-commtime}. 
+The random placement policy performs comparably with all routing policies (RM, RA and RPA).
+They outperform all contiguous placement configurations (CM, CA and CPA).
+The contiguous placement coupled with minimal routing (CM) results in highest communication time.
+When coupled with (progressive) adaptive routing (CA, CPA), the average communication time can be greatly reduced.
+When random placement is in use, the workload communication efficiency can be further improved.
+
+\begin{table}[ht]
+\begin{center}
+\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
+\label{tab:wkld-commtime}
+\begin{tabular}{l c c c c c c }
+\toprule % Top horizontal line
+\toprule
+&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
+\cmidrule(l){2-7}
+          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
+\midrule % In-table horizontal line
+Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
+
+\midrule % In-table horizontal line
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\end{center}
+\end{table}
+
+The random placement can balance the network traffic load by uniformly distribute the traffic.
+The (progressive) adaptive routing can avoid the hot-spots by redirecting the traffic away from congested area.
+The network can reach its optimal performance, when random placement coupled with (progressive) adaptive routing are in use.
 
@@
 We study the performance of each application individually by isolating it from Workload~\Rmnum{1}.   
-Figure~\ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, when they running concurrently under six different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
+Figure~\ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, 
+when they running concurrently under six different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
 
-As shown in Figure~\ref{fig:mg-commtime}, MultiGrid takes the most communication time when it is running with contiguous placement and minimal routing (CM).
-When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA) are in use, the communication time is significantly reduced.
-Random placement coupled with minimal routing (RM) can make further improvement, and reaches the best performance(lowest communication time) when coupled with adaptive and progressive adaptive routing(RA, RPA).
-Due to the variance of data transfer amount among MPI ranks, MultiGrid communication time also presents great variation, indicated by the long boxes in Figure~\ref{fig:mg-commtime}.
+As shown in Figure~\ref{fig:mg-commtime}, 
+MultiGrid takes the most communication time when it is running with contiguous placement and minimal routing (CM). 
+When contiguous placement coupled with adaptive or progressive adaptive routing (CA, CPA) are in use, 
+the communication time is significantly reduced. 
+Random placement coupled with minimal routing (RM) can make further improvement, 
+and reaches the best performance(lowest communication time) when coupled with adaptive and progressive adaptive routing(RA, RPA). 
+Due to the variance of data transfer amount among MPI ranks, 
+MultiGrid communication time also presents great variation, 
+indicating by the long boxes in Figure~\ref{fig:mg-commtime}.
 
-CrystalRouter takes more communication time compared with the other applications because of its high volume of data transfer. When it is running with six placement and routing configurations, 
+CrystalRouter takes more communication time compared with the other applications because of its high volume of data transfer. 
+When it is running with six placement and routing configurations, 
 CrystalRouter communication time presents similarly trend as MultiGrid but with little variance, shown in Figure~\ref{fig:cr-commtime}.
@@
 
-We observe that when Workload~\Rmnum{1} is running with random placement and (progressive) adaptive routing, the performance of MultiGrid and CrystalRouter are significant improved, whereas AMG suffers performance degradation.
+We observe that when Workload~\Rmnum{1} is running with random placement and (progressive) adaptive routing, 
+the performance of MultiGrid and CrystalRouter are significant improved, whereas AMG suffers performance degradation.
 
@@
         \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
+        \caption{MultiGrid Local Channel Traffic}
         \label{fig:mg-lc-traffic}
@@
         \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
+        \caption{CrystalRouter Local Channel Traffic}
         \label{fig:cr-lc-traffic}
@@
         \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
+        \caption{MultiGrid Global Channel Traffic}
         \label{fig:mg-gc-traffic}
@@
         \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
+        \caption{CrystalRouter Global Channel Traffic}
         \label{fig:cr-gc-traffic}
@@
 
-\TODO{resume from here}
+% Show the evidence from network level, explain why AMG is different. 
+We look into network level to identify the culprit behind AMG's abnormal behavior with random placement. 
+By identifying the compute nodes that each MPI rank resides on and the routers that serving each application, 
+we analyze the traffic going through the routers belonging to each application and 
+present the results in Figure~\ref{fig:3app-lc-gc-traffic}. 
+Compared with contiguous placement, 
+the number of routers serving each application when random placement is in use are greatly increased, 
+thus the solid lines are longer than dashed lines as shown in Figure~\ref{fig:3app-lc-gc-traffic}.
 
-% Show the evidence from network level, explain why AMG is different. 
-We look into network level to identify the culprit behind AMG's abnormal behavior with random placement and adaptive routing.
-By identifying the compute nodes each MPI rank resides on and routers that serving each application, we can see that the traffic go through the routers serving AMG skyrockets when random placement and adaptive routing is in use, shown in Figure \ref{fig:amg-lc-traffic} and \ref{fig:amg-gc-traffic}.
-Adaptive routing will redirect the traffic of other applications to go through the routers belonging to AMG, and increase the traffic burden on those routers, thus slow down the communication of AMG.
+The routers serving MultiGrid and CrystalRouter have high volume of traffic on both local and global channels when contiguous placement is in use, 
+shown as the dashed line in Figure~\ref{fig:mg-lc-traffic},~\ref{fig:mg-gc-traffic} and Figure~\ref{fig:cr-lc-traffic},~\ref{fig:cr-gc-traffic}. 
+On the other hand, the random placement can uniformly distribute the traffic of MultiGrid and CrystalRouter over the network, 
+alleviate local congestion and balance the traffic load among all routers, 
+shown as the solid lines in Figure~\ref{fig:mg-lc-traffic},~\ref{fig:mg-gc-traffic} and Figure~\ref{fig:cr-lc-traffic},~\ref{fig:cr-gc-traffic}. 
+MultiGrid and CrystalRouter benefit from random placement by getting their high volume of traffic being redirected 
+from their over-loaded routers to the less busy routers in the network. 
+In this case, a majority of those less busy routers are belonging to AMG.
 
-No router will be shared between applications under contiguous placement.
-A number of successive groups will be allocated to the same application under contiguous placement policy.
-When contiguous placement coupled with minimal routing, application will be free of interference from its concurrently running peers.
-However, application communication traffic will be confined within their allocated groups, thus congestion is very likely to happen depending on application communication intensity.
-As the lest communication-intensive application in Workload \Rmnum{1}, AMG can benefit from contiguous placement.
-Under contiguous placement, the traffic go through the local and global channels of the routers belonging to AMG is significantly lower than with random placement, shown in Figure \ref{fig:amg-lc-traffic}, \ref{fig:amg-gc-traffic}.
+Since AMG is less communication-intensive, 
+the routers serving AMG have small volume of traffic on local and global channels when the contiguous placement is use, 
+shown as the dashed line in Figure~\ref{fig:amg-lc-traffic},~\ref{fig:amg-gc-traffic}. 
+When random placement is in use, 
+more routers are involved in serving AMG, 
+and the traffic skyrockets on the local and global channels, 
+shown as the solid lines in Figure~\ref{fig:amg-lc-traffic},~\ref{fig:amg-gc-traffic}. 
+The increased traffic comes from the communication-intensive MultiGrid and CrystalRouter.
 
-MultiGrid and CrystalRouter are more communication-intensive compared with AMG.
-They will suffer congestion on both local and global channels when contiguous placement is in use, shown as the dashed line in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
-On the other hand, the random placement can uniformly distribute their traffic all over the network, alleviate the possible congestion, shown as the solid lines in Figure \ref{fig:mg-lc-traffic}, \ref{fig:mg-gc-traffic} and Figure \ref{fig:cr-lc-traffic}, \ref{fig:cr-gc-traffic}.
+AMG behaves abnormally when random placement is in use 
+because the routers serving AMG have to take the traffic from MultiGrid and CrystalRouter. 
+The extra traffic from the other communication-intensive applications 
+takes advantage the network resources belonging to AMG and slows down AMG's communication. 
+We refers this phenomenon as AMG being ``bullied" by MultiGrid and CrystalRouter.
 
 \subsection{Key Observations}
-In summary, based on the results presented in section \ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we have made the following observations.
+In summary, based on the results presented in section~\ref{sec: workload-1 network analysis} and~\ref{sec: workload-1 app analysis}, we have made the following observations.
 
-\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers.
+\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} 
+Random placement can uniformly distribute MPI ranks of application over the network, 
+and adaptive routing can redirect the traffic from congested routers to other less busy routers. 
 Therefore, the network could reach the status of load-balanced and hot-spots free.
 
-\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network random placement and adaptive routing are in use.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
+\emph{The performance of less communication-intensive jobs in workload suffers degradation when random placement and adaptive routing are in use.} 
+AMG in Workload~\Rmnum{1} are ``bullied" by its concurrently running communication-intensive peers, MultiGrid and CrystalRouter. 
 AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use. 
-The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slowing down AMG's communication.
-\footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
+The traffic from MultiGrid and CrystalRouter is redirected to the routers that serving AMG, 
+slowing down AMG's communication. 
+\footnote{We have tried three different congestion sensing schemes that used in adaptive routing~\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
 
-\emph{Consistent performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} The router and group sharing between jobs are prohibited in contiguous placement policy.
-The traffic won't be redirected from congested routers to less busy ones when minimal routing is in use.
+\emph{The consistency performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} 
+The router and group sharing among applications are prohibited in contiguous placement policy. Minimal routing will not redirect traffic from congested routers to less busy ones.
 Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
-%However, contiguous placement and minimal routing usually results in local congestion and unbalanced network utilization.

### 2016-04-01 study_workload_2.tex
rewrite section 5 done

@@
 \section{Study of Parallel Workload \Rmnum{2 }}
-%\section{``Bully" become ``Bullee"}
+%\section{``Bully" become ``bullied"}
 \label{sec:workload-2}
 
-In this section, we will verify the observations made in the previous section when Workload \Rmnum{1} is running on the dragonfly network under different placement and routing configurations.
-We conduct the same sets of experiments with Workload \Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter.
-By replacing AMG with sAMG, we turn the ``bully" into ``bullee".
+In this section, we will verify the observations made in the previous section 
+when Workload~\Rmnum{1} is running on the dragonfly network under different placement and routing configurations. 
+We conduct the same sets of experiments with Workload~\Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter. 
+By replacing AMG with sAMG, we turn the ``bully" into the ``bullied".
 
@@
 
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under 6 different placement and routing configurations.} 
-\label{tab:syn-wkld-commtime}
-%\centering % Centers the table on the page, comment out to left-justify
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
-\cmidrule(l){2-7}
-          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
+Due to the replacement of AMG by sAMg, 
+the volume of data transfer in Workload~\Rmnum{2} is much higher than Workload~\Rmnum{1}, 
+thus the aggregate traffic on terminal links, local and global channels is greatly increased, 
+as shown in Figure~\ref{fig:synwkld-network-traffic-stime}. 
+The similar pattern in Figure~\ref{fig:wkld-network-traffic-stime} can be observed from Figure~\ref{fig:synwkld-network-traffic-stime}.
+Contiguous placement coupled with minimal routing(CM) results in congestion on some routers along certain shortest paths from the source to the destination. 
+Those congested routers are over-loaded with high volume of traffic going through their local and global channels, 
+shown as the blue dashed line in Figure~\ref{fig:synwkld-global-channel-traffic} and~\ref{fig:synwkld-local-channel-traffic}. 
+In the meanwhile, the corresponding saturated time of their local and global channels are also the highest compared with other configurations, 
+shown as the blue dashed line in Figure~\ref{fig:synwkld-global-channel-stime} and Figure~\ref{fig:synwkld-local-channel-stime}.
 
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
+When contiguous placement coupled with (progressive) adaptive routing is in use, the high volume of traffic are redirected by taking the intermediate routers in other groups to void congestion.
+Therefore, the traffic on the global channels can be uniformly distributed over the network and the corresponding saturated time are greatly reduced, illustrated by the red and green dashed lines.
+However, (progressive) adaptive routing can not effectively balance the traffic load for local channels.
+As shown by the red and green dashed lines in Figure~\ref{fig:synwkld-local-channel-traffic}, some routers still have high volume of traffic on their local channels.
 
-The average communication time spent by all MPI ranks when Workload \Rmnum{2} is running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}.
-The contiguous placement coupled with minimal routing results in highest communication time.
-The random placement coupled with minimal routing is the most efficient.
-Progressive adaptive routing is better than adaptive routing when random placement is in use.
-And they have comparable results when coupled contiguous placement.
-The performance of Workload \Rmnum{2} under different configurations keep the similar pattern as it of Workload \Rmnum{1}.
-
-Figure \ref{fig:synwkld-network-traffic-stime} shows the aggregate traffic for terminal links, local channels and global channels, and the corresponding saturated time when Workload \Rmnum{2} is running with 6 different configurations.
-Contiguous placement coupled with minimal routing(CM) results in most traffic go through certain local and global channel, thus the longest saturated time for terminal link, local and global channel.
-When contiguous placement is coupled with (progressive) adaptive routing (CA, CPA), the local congestion could be mitigated.
-The random placement coupled with any routing policy(RM, RA, RPA) performs comparably.
-They are better than contiguous placement and minimal routing(CM), but only little improvement against contiguous and (progressive) adaptive (CA, CPA).
+Random placement policy performs comparably with three different routing policies.
+By uniformly distributing MPI ranks over the network, 
+random placement can balance the traffic load over the network,
+illustrated by the solid lines in Figure~\ref{fig:synwkld-global-channel-traffic} and~\ref{fig:synwkld-local-channel-traffic}. 
+Progressive adaptive and adaptive routing generate more traffic than minimal routing
+as the packets take non-shortest paths via intermediate routers to avoid congestions, 
+thus the blue solid line(RM) is lower than the red and green solid line (RA, RPA).
 
@@
     \end{subfigure}%
-   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under 6 different placement and routing configurations.}
+   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under six different placement and routing configurations.}
    \label{fig:synwkld-network-traffic-stime}
 \end{figure*}
+
+The average communication time spent by all MPI ranks when Workload~\Rmnum{2} is running under different placement and routing configurations shown in Table~\ref{tab:syn-wkld-commtime}. 
+We can observe the similar pattern as in Table~\ref{tab:wkld-commtime}
+The contiguous placement coupled with minimal routing results in highest communication time. 
+The random placement coupled with minimal routing is the most efficient. 
+Progressive adaptive routing is better than adaptive routing when random placement is in use, 
+and they have comparable results when coupled contiguous placement. 
+Same as Workload~\Rmnum{1}, the network reaches the optimal performance when Workload~\Rmnum{2} is running with random placement and adaptive routing.
+
+\begin{table}[ht]
+\begin{center}
+\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under six different placement and routing configurations.} 
+\label{tab:syn-wkld-commtime}
+%\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c c c c }
+\toprule % Top horizontal line
+\toprule
+&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-7}
+          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
+\midrule % In-table horizontal line
+Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
+
+\midrule % In-table horizontal line
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 
-The communication time of each application shown in Figure \ref{fig:syn-apps-commtime}.
-The ``bully" in Workload \Rmnum{1} becomes the ``bullyee" in Workload \Rmnum{2}.
-MultiGrid and CrystalRouter are the less communication-intensive applications in Workload \Rmnum{2}.
-When random placement coupled with (progressive) adaptive routing is in use, MultiGrid and CrystalRouter suffer prolonged communication time, shown in Figure \ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}.
-Whereas, sAMG benefits from random placement and (progressive) adaptive routing, shown in Figure \ref{fig:syn-samg-commtime}.
-Contiguous placement coupled with minimal routing prevents applications from sharing network resource, guaranteeing the performance of less communication intensive applications like MultiGrid and CrystalRouter and causing severe performance degradation to sAMG.
+We study the performance of each application individually by isolating it from Workload~\Rmnum{2}.   
+Figure~\ref{fig:syn-apps-commtime} shows the distribution of communication time of three applications in per rank manner, 
+when they running concurrently under six different placement and routing configurations.
+The ``bully" in Workload~\Rmnum{1} becomes the ``bullied" in Workload~\Rmnum{2}. 
+MultiGrid and CrystalRouter are the less communication-intensive applications in Workload~\Rmnum{2}. 
+When random placement coupled with (progressive) adaptive routing is in use, 
+MultiGrid and CrystalRouter suffer prolonged communication time, 
+as shown in Figure~\ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}. 
+Whereas, sAMG benefits from random placement and (progressive) adaptive routing, 
+its communication time drops a lot compared with using contiguous placement, shown in Figure~\ref{fig:syn-samg-commtime}. 
+Contiguous placement coupled with minimal routing prevents applications from sharing network resource, 
+guaranteeing the performance of less communication-intensive applications like MultiGrid and CrystalRouter 
+and causing severe performance degradation to sAMG.
 
@@
     \centering
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
-        \caption{sAMG}
-        \label{fig:syn-samg-commtime}
-    \end{subfigure}%
-    \hspace{1em}%
     \begin{subfigure}[t]{0.32\textwidth}
@@
     \end{subfigure}%
+    \hspace{1em}%
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
+        \caption{sAMG}
+        \label{fig:syn-samg-commtime}
+    \end{subfigure}%
+
    \caption{The communication time of all ranks in each application.
 Three applications running concurrently on dragonfly network with different placement and routing configurations.
-The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullee", MultiGrid and CrystalRouter, suffer performance degradation.}
+The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullied", MultiGrid and CrystalRouter, suffer performance degradation.}
    \label{fig:syn-apps-commtime}
@@
 We look into the network level to scrutinize the traffic through the routers serving each application. 
-Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers serving sAMG.
-The traffic skyrockets in both local and global channels when contiguous placement coupled with minimal routing (CM) is in use.
-The congestion will be alleviated in both local and global channels when contiguous placement coupled with (progressive) adaptive routing (CA, CPA) are in use.
-Random placement can further reduce the traffic burden on local and global channels by uniformly distributing sAMG traffic over the network.
+The routers serving sAMG have high volume of traffic on both local and global channels when contiguous placement is in use, 
+shown as the dashed line in Figure~\ref{fig:syn-samg-lc-traffic},~\ref{fig:syn-samg-gc-traffic}.
+The random placement can alleviate the local congestion by uniformly distributing the traffic of sAMG over the network, getting more routers involved in serving sAMG, as illustrated by solid lines. 
+sAMG benefits from random placement by getting their high volume of traffic being redirected 
+from its over-loaded routers to the less busy routers in the network. 
+In this case, a majority of those less busy routers are belonging to MultiGrid and CrystalRouter.
 
-The traffic go through the local and global channels of the routers serving MultiGrid and CrystalRouter are shown in Figure \ref{fig:syn-mg-lc-traffic}, \ref{fig:syn-mg-gc-traffic} and Figure \ref{fig:syn-cr-lc-traffic}, \ref{fig:syn-cr-gc-traffic}.
-There are more traffic going through when random placement is in use, compared with contiguous placement.
-The extra traffic coming from the ``bully" sAMG cause performance degradation to MultiGrid and CrystalRouter.
+%MultiGrid and CrystalRouter are the less communication-intensive applications in Workload~\Rmnum{2}.
+When MultiGrid is running with contiguous placement, the serving routers have relatively small volume of traffic on their local and global channels, as shown by the dashed lines in Figure~\ref{fig:syn-mg-lc-traffic},~\ref{fig:syn-mg-gc-traffic}.
+When coupled with (progressive) adaptive routing, more routers are involved in serving MultiGrid, thus the red and green dashed lines are shorter than the blue one.
+When random placement is in use, the MPI ranks of MultiGrid are randomly distributed across the network and sharing routers with other applications.
+The routers serving MultiGrid have much more traffic on their local and global channels, as shown by the solid lines in Figure~\ref{fig:syn-mg-lc-traffic},~\ref{fig:syn-mg-gc-traffic}.
+The increased traffic comes from the ``bully" sAMG.
+
+CrystalRouter has more data transfer than MultiGrid.
+However, it still becomes the victim of the ``bully" sAMG.
+We can observe the similar pattern about CrystalRouter from Figure~\ref{fig:syn-cr-lc-traffic},~\ref{fig:syn-cr-gc-traffic} as MultiGrid.
+When random placement is in use, the routers serving CrystalRouter have more traffic going through.
+The extra traffic comes from from the ``bully" sAMG causing performance degradation to MultiGrid and CrystalRouter.
 
@@
         \centering
-        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
-        \caption{sAMG Local Channel Traffic}
-        \label{fig:syn-samg-lc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
         \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
-        \caption{MG Local Channel Traffic}
+        \caption{MultiGrid Local Channel Traffic}
         \label{fig:syn-mg-lc-traffic}
@@
         \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
-        \caption{CR Local Channel Traffic}
+        \caption{CrystalRouter Local Channel Traffic}
         \label{fig:syn-cr-lc-traffic}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
+        \caption{sAMG Local Channel Traffic}
+        \label{fig:syn-samg-lc-traffic}
     \end{subfigure}\\
     \centering
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
+        \caption{MultiGrid Global Channel Traffic}
+        \label{fig:syn-mg-gc-traffic}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
+        \caption{CrystalRouter Global Channel Traffic}
+        \label{fig:syn-cr-gc-traffic}
+    \end{subfigure}\hfill
     \begin{subfigure}[t]{0.32\textwidth}
@@
         \label{fig:syn-samg-gc-traffic}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
-        \caption{MG Global Channel Traffic}
-        \label{fig:syn-mg-gc-traffic}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
-        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
-        \caption{CR Global Channel Traffic}
-        \label{fig:syn-cr-gc-traffic}
-    \end{subfigure}%
+    \end{subfigure}
    \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
+Compared with contiguous placement, More routers are involved in serving each application when random placement is in use.}
    \label{fig:syn-3app-gc-traffic}
@@
 
-In summary, based on the Workload \Rmnum{2}, we have made the following observations.
+We have made the following observations from the study with Workload~\Rmnum{2}.
 
-\emph{The application becomes ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
+\emph{The application becomes the ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} The ``bully" takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
 
-\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullee" when running concurrently with sAMG in Workload \Rmnum{2}.
+\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullied" when running concurrently with sAMG, since sAMG contributes the dominant portion of traffic in  in Workload \Rmnum{2}.

### 2016-04-01 hybrid_placement.tex
rewrite paragraph 1,2 in Section 6

@@
 
-The precaution to stop ``bully" behavior is to avoid network sharing between concurrently running jobs.
-Using contiguous placement and minimal routing could be a way to avoid network sharing, but network performance could suffer degradation due to local congestion.
-Running each job with dedicated routing policy is unrealistic, since routing policy is pre-configured and can not be changed on the fly upon job submission.
-However, the job placement policies can be versatile for assigning different allocation (contiguous or random) to specific application.
+Based on our experiments with two workloads, the ``bullying" is inevitable when the dragonfly network is configured with random placement and (progressive) adaptive routing. 
+The precaution to stop the ``bullying" is to avoid network sharing between concurrently running jobs, 
+and contiguous placement and minimal routing could be an effective way. 
+However, the network would suffer severe local congestion and unbalanced utilization when contiguous placement and minimal routing is in use. 
+Running each job with dedicated routing policy is unrealistic, 
+since routing policy is part of system configuration which can not be changed on the fly upon job submission. 
+Assigning preferable allocation to each job based on its communication intensity is applicable for the batch scheduler with intelligent job placement policy.
 
-Thus, we propose the hybrid placement as a reconcile solution.
-In the hybrid placement, the less communication-intensive applications get contiguous allocation while the communication-intensive ones get random allocation.
-We evaluate the effect of hybrid placement on improving network performance as well as preserving the performance of individual application.
-In following experiments with Workload \Rmnum{1}, the hybrid placement policy assigns AMG with contiguous allocation, MultiGrid and CrystalRouter with random allocations.
+We propose a hybrid job placement policy to assign each job with preferable allocation. 
+According to the hybrid placement policy, 
+the less communication-intensive jobs get contiguous allocation to partially avoid network sharing with the ``bully", 
+while the communication-intensive jobs get random allocation in order to share network resource with each other. 
+When Workload~\Rmnum{1} is running on the dragonfly network with hybrid placement policy, 
+AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocations. 
+The experiment results show that hybrid placement performs comparably as random placement for improving network performance and mitigates the degradation of AMG caused by the ``bullying".
 \footnote{Due to page limit, we won't present the analysis about network traffic and saturated time in this section.}

### 2016-04-02 hybrid_placement.tex
rewrite section 6 done

@@
 The experiment results show that hybrid placement performs comparably as random placement for improving network performance and mitigates the degradation of AMG caused by the ``bullying".
-\footnote{Due to page limit, we won't present the analysis about network traffic and saturated time in this section.}
 
@@
 
-Hybrid placement is also coupled with three routing policies, Minimal, Adaptive and Progressive Adaptive.
-They are denoted respectively as HM, HA and HPA.
-As presented in the previous section, random placement outperforms contiguous placement in terms of network performance, we only compare the results of hybrid placement with random placement due to the page limit.
+Hybrid placement is also coupled with three routing policies, minimal, adaptive and progressive adaptive, denoted respectively as HM, HA and HPA.
+As presented in section~\ref{sec: workload-1 network analysis} and~\ref{sec: workload-2 network analysis}, random placement outperforms contiguous placement in terms of network performance, the analysis in this section only focuses on the comparison between hybrid and random placement policies.
 
@@
 
-As shown in Table \ref{tab: hyb-placement-wkld-commtime}, hybrid placement and random placement perform comparably.
-When coupled with minimal routing, RM outperforms HM.
-However, when coupled with (progressive) adaptive routing, HA and HPA outperform RA and RPA.
-HA and HPA perform equally well as compared with RM.
+Due to page limit, we only present the average communication time spent by Workload~\Rmnum{1} for the evaluation of the network performance.
+\footnote{The analysis about network traffic and saturated time are omitted in this section due to page limit.}
+As shown in Table~\ref{tab: hyb-placement-wkld-commtime}, 
+hybrid placement coupled with (progressive) adaptive routing (HA, HPA) can guarantee the same performance as random placement coupled with minimal routing (RM), thus the average workload communication time stays unchanged.
+When hybrid placement coupled with minimal routing (HM) is in use, 
+the network performance declines  as indicated by the increasing average communication time. 
+The consecutive groups assigned to AMG results in the diminishing of network resource shared by MultiGrid and CrystalRouter, 
+causing unbalanced utilization over the network.
 
@@
         \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
-        \caption{AMG Communication Time}
-        \label{fig:hyb-plcmt-amg-commtime}
-    \end{subfigure}\hfill
-    \hspace{1em}%
-    \begin{subfigure}[t]{0.32\textwidth}
-        \centering
         \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
-        \caption{MG Communication Time}
+        \caption{MultiGrid Communication Time}
         \label{fig:hyb-plcmt-mg-commtime}
@@
         \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
-        \caption{CR Communication Time}
+        \caption{CrystalRouter Communication Time}
         \label{fig:hyb-plcmt-cr-commtime}
-    \end{subfigure}%
-   \caption{Application communication time. Workload \Rmnum{1} is running under all the possible placement and routing configurations.}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.32\textwidth}
+        \centering
+        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
+        \caption{AMG Communication Time}
+        \label{fig:hyb-plcmt-amg-commtime}
+    \end{subfigure}
+   \caption{Application communication time. Workload~\Rmnum{1} is running with all placement and routing configurations.}
    \label{fig:hyb-plcmt-apps-commtime}
@@
 
-Figure \ref{fig:hyb-plcmt-apps-commtime} shows the communication time of each application when hybrid placement configurations are in use.
-MultiGrid and CrystalRouter have basically the same performance with hybrid placement as compared with random placement.
-Since they still get random allocation in the hybrid placement.
-The performance of AMG is significantly improved when hybrid placement is in use.
-Compared with ``RA" and ``RPA", ``HA" and ``HPA" can greatly reduce AMG communication time, shown in Figure \ref{fig:hyb-plcmt-amg-commtime}.
+The communication time of each application under all placement and routing configurations are presented in Figure~\ref{fig:hyb-plcmt-apps-commtime}. 
+As shown in Figure~\ref{fig:hyb-plcmt-mg-commtime} and~{fig:hyb-plcmt-cr-commtime},
+MultiGrid and CrystalRouter have similar performance with hybrid placement (HM, HA, HPA) as compared with random placement (RM, RA, RPA),
+since they are still assigned with random allocations in the hybrid placement policy. 
+The performance of AMG is significantly improved when hybrid placement configurations are in use. 
+The communication time of AMG are reduced by half when the placement policy switched from random to hybrid, 
+as shown in Figure \ref{fig:hyb-plcmt-amg-commtime}. 
 This is due the contiguous allocation assigned to AMG in the hybrid placement policy. 
@@
 However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG. 
-Since AMG is less communication-intensive and can not fully utilize network, it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups.
-So for AMG, ``HA" and ``HPA" are worse than ``CA" and ``CPA", but they are much better than ``RA" and ``RPA".
+Since AMG is less communication-intensive and can not fully utilize network, 
+it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups.
+Both the communication-intensive and the less intensive application can benefit from hybrid placement coupled with (progressive) adaptive routing.
 
-\subsection{Key Observations}
-
-Based on the results from experimenting with hybrid placement policy, we can make the following observations.
-
-\emph{Compared with random placement policy, hybrid placement can guarantee comparable network performance.} Hybrid placement policy allows network sharing between communication intensive applications, thus alleviates the potential congestion and improves network utilization.
-
-\emph{Hybrid placement can mitigate the performance degradation of less communication-intensive application.} Hybrid placement policy preserves contiguous allocation for less communication-intensive application, prevents network resource from being shared by others.
-Unlike random placement indulging the ``bully", hybrid placement can restrain it to some extent.
-
-Hybrid placement can guarantee the performance of individual application without causing performance degradation to network performance.
-Compared with contiguous and random placement policy, hybrid placement are more preferable to HPC systems with dragonfly networks.
+The experiments with hybrid placement demonstrate that assigning each application with its preferable allocation can mitigate the negative effect of the ``bullying", in the meanwhile, 
+the network can still reach the optimal performance.
+Compared with random placement policy, hybrid placement can guarantee comparable network performance, by enabling network sharing between communication intensive applications .
+It can also mitigate the performance degradation of less communication-intensive applications, 
+by assigning them with contiguous allocation to partially avoid network sharing.
+Unlike random placement indulging the ``bullying", hybrid placement can restrain it to some extent.
+Hybrid placement policy is worthy of consideration for the adoption on dragonfly systems in the future.

### 2016-04-03 intro.tex
rewrite the 1st paragraph in Introduction

@@
 
-The low latency and high bandwidth interconnect network plays a critical role in HPC system performance.
-As computational capabilities continue to grow due to many-core nodes with accelerators, the network is increasingly becoming a scarce resource.
-The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}.
-This make the dragonfly network a very promising choice for building petaflop and beyond supercomputers.
-%The procurement results from Trinity and CORAL project shows the great performance improvement can be got from using dragonfly network.
+Low-latency and high-bandwidth interconnect networks play a critical role in improving HPC system performance. 
+The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
+making it a very promising choice for building petaflop and beyond supercomputers. 
+Even with such powerful networks, 
+intelligent job placement is still of paramount importance to the efficient use of dragonfly connected systems. 
+An ideal job placement policy should not only guarantee load balance on the network 
+but also mitigate the performance degradation of each application due to interference.  
+(Interference itself is inevitable on the dragonfly~\cite{bhatele2015, dskinner}.)
 
-While dragonfly topologies provide low-latency and high-bandwidth networking, efficiently utilizing it is a significant concern.
-In particular, intelligent job placement to avoid interference is of paramount importance to guarantee the performance of each job when it shares network resources with other concurrently running peers \cite{bhatele2015, dskinner}.
-Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks \cite{jain-sc14, bhatele-sc11, brandt2014}.
+Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}.
+They focus on the performance of network without analyzing the performance of each individual application.
+In this work....
 
-In this work, we study the interference between concurrently running jobs on dragonfly networks with different job placement and routing policies.
+%In this work, we study the interference between concurrently running jobs on dragonfly networks with different job placement and routing policies.
 We use CODES, an HPC network simulation toolkit with high fidelity and excellent scalability for packet level simulation \cite{codes}.
@@
 
-We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies.
+%We conduct extensive experiments with three applications running on dragonfly network with two job placement policies and three routing policies.
 We analyze the performance of network as well as individual application when running with different placement and routing configurations.

### 2016-04-03 draft.tex
rewriting abstract and introduction done; tweak format in section 4

@@
 The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
-Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks, since random placement with adaptive routing can uniformly distribute traffic over the network and alleviate congestion.
-However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network when multiple jobs are running concurrently, they can not guarantee the best performance for each single job.
-The performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs.
-We refer this phenomenon as ``bully" between concurrently running jobs.
+Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
+However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
+We have observed that the performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs. 
+We identify this ``bully" behavior with the help of detailed network simulation and real application traces and validate the underneath causes.
+We propose a hybrid job placement policy that provide either contiguous or random allocation to each application based on its communication intensity. 
+With the help of the simulation, we demonstrate that this hybrid job placement policy can lead to performance improvement for less communication-intensive applications.
+
+%We refer this phenomenon as ``bully" between concurrently running jobs.
 We presented a detailed analysis about this ``bully" behavior between jobs at the network level based on a sophisticated, high-fidelity discrete even-driven simulation tool.

### 2016-04-03 intro.tex
rewriting abstract and introduction done; tweak format in section 4

@@
 Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}.
-They focus on the performance of network without analyzing the performance of each individual application.
-In this work....
+These works explore the possible job placement and routing configurations that could optimize the overall network performance.
+In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
+Our analysis focus on the performance of each application with interference in presence.
+
+%We have observed that when running concurrently on the dragonfly network, applications interfere with each other and the less communication-intensive applications are ``bullied" by the communication-intensive ones.
+The ``bully" applications get great performance improvement at the cost of performance degradation to the ``bullied" applications.
+We choose three representative applications from the DOE Design Forward Project~\cite{designforwardwebpage} to study the root cause of the ``bullying" with simulation on CODES, an high-fidelity, packet-level HPC network simulation toolkit~\cite{codes}.
+
+We choose three representative applications from the DOE Design Forward Project~\cite{designforwardwebpage} to analyze the interference among them.
+Our study is based on the simulation with CODES, an high-fidelity, packet-level HPC network simulation toolkit~\cite{codes}.
+For each application, we examine it with two job placement policies and three routing policies.
+We make the following interesting observations through extensive simulation.
 
@@
 
-    \item Random placement coupled with adaptive routing can uniformly distribute traffic over the network, avoid hot-spots and alleviate traffic congestion, optimizing the overall performance of the dragonfly network.
+    \item Concurrently running applications on a dragonfly network interfere with each other when they share network resources.
+Communication-intensive applications ``bully" their less intensive peers and obtain performance improvement at the expense of less intensive ones suffering performance degradation.
 
-    \item The ``bully" behavior occurs between concurrently running jobs on a dragonfly network when random placement and adaptive routing are in use.
-Communication-intensive jobs obtain performance improvement at the expense of less intensive jobs suffering performance degradation.
+    \item Random placement can improve the performance of communication-intensive applications by enabling network resource sharing, though it introduces interference causing performance degradation.
 
-    \item Random placement coupled with adaptive routing can improve the performance of communication-intensive jobs by enabling network resource sharing, though it introduces interference between concurrently running jobs.
-
-    \item Contiguous placement coupled with minimal routing can guarantee consistency performance of less communication-intensive jobs by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
+    \item Contiguous placement can guarantee consistency performance of less communication-intensive applications by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
 
@@
 
-Based on our observations, the optimal job placement and routing solution for the workload running dragonfly system should be specific to the job communication intensity.
-\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
-We believe the observations and analysis presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
+Based on the aforementioned key observations, the optimal job placement policy for the workload running dragonfly system should be specific to the application communication intensity.
+Thus, we propose a hybrid job placement, which can assign the communication-intensive applications with random allocation and less intensive applications with contiguous allocation.
+Our experiment results show that hybrid job placement can mitigate the performance degradation of less communication-intensive applications while still guarantee the best performance of communication-intensive applications.
+%\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.}
+
+To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
+We believe the observations and new placement policy presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
 For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks.

### 2016-04-03 hybrid_placement.tex
cut off tables in section 4,5,6. reduce num of pages to 12

@@
 The experiment results show that hybrid placement performs comparably as random placement for improving network performance and mitigates the degradation of AMG caused by the ``bullying".
+\footnote{The analysis about network traffic and saturated time are omitted in this section due to page limit.}
 
-\subsection{Network Performance Analysis}
+%\subsection{Network Performance Analysis}
+%
+%Hybrid placement is also coupled with three routing policies, minimal, adaptive and progressive adaptive, denoted respectively as HM, HA and HPA.
+As presented in section~\ref{sec: workload-1 network analysis} and~\ref{sec: workload-2 network analysis}, random placement outperforms contiguous placement in terms of network performance, the analysis in this section only focuses on the comparison between hybrid and random placement policies.
+%
+%\begin{table}[ht]
+%\begin{center}
+%\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under hybrid placement and random placement policies.} 
+%\label{tab: hyb-placement-wkld-commtime}
+%\begin{tabular}{l c c c c c c }
+%\toprule % Top horizontal line
+%\toprule
+%&\multicolumn{6}{c}{Placement and Routing Configurations} \\
+%\cmidrule(l){2-7}
+%          & HM & HA & HPA & RM & RA & RPA \\ % Column names row
+%\midrule % In-table horizontal line
+%Time(ms)  &273 &255 &255 &255 &265 &264  \\ % Content row 1
+%%\midrule
+%%Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
+%\midrule % In-table horizontal line
+%\bottomrule % Bottom horizontal line
+%\end{tabular}
+%\end{center}
+%\end{table}
+%
+%Due to page limit, we only present the average communication time spent by Workload~\Rmnum{1} for the evaluation of the network performance.
+%\footnote{The analysis about network traffic and saturated time are omitted in this section due to page limit.}
+%As shown in Table~\ref{tab: hyb-placement-wkld-commtime}, 
+%hybrid placement coupled with (progressive) adaptive routing (HA, HPA) can guarantee the same performance as random placement coupled with minimal routing (RM), thus the average workload communication time stays unchanged.
+%When hybrid placement coupled with minimal routing (HM) is in use, 
+%the network performance declines  as indicated by the increasing average communication time. 
+%The consecutive groups assigned to AMG results in the diminishing of network resource shared by MultiGrid and CrystalRouter, 
+%causing unbalanced utilization over the network.
 
-Hybrid placement is also coupled with three routing policies, minimal, adaptive and progressive adaptive, denoted respectively as HM, HA and HPA.
-As presented in section~\ref{sec: workload-1 network analysis} and~\ref{sec: workload-2 network analysis}, random placement outperforms contiguous placement in terms of network performance, the analysis in this section only focuses on the comparison between hybrid and random placement policies.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under hybrid placement and random placement policies.} 
-\label{tab: hyb-placement-wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\
-\cmidrule(l){2-7}
-          & HM & HA & HPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  &273 &255 &255 &255 &265 &264  \\ % Content row 1
-%\midrule
-%Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-Due to page limit, we only present the average communication time spent by Workload~\Rmnum{1} for the evaluation of the network performance.
-\footnote{The analysis about network traffic and saturated time are omitted in this section due to page limit.}
-As shown in Table~\ref{tab: hyb-placement-wkld-commtime}, 
-hybrid placement coupled with (progressive) adaptive routing (HA, HPA) can guarantee the same performance as random placement coupled with minimal routing (RM), thus the average workload communication time stays unchanged.
-When hybrid placement coupled with minimal routing (HM) is in use, 
-the network performance declines  as indicated by the increasing average communication time. 
-The consecutive groups assigned to AMG results in the diminishing of network resource shared by MultiGrid and CrystalRouter, 
-causing unbalanced utilization over the network.
-
-\subsection{Individual Application Analysis}
+%\subsection{Individual Application Analysis}
 

### 2016-04-03 intro.tex
cut off tables in section 4,5,6. reduce num of pages to 12

@@
 %\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
-
-To the best of our knowledge, using parallel application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
-We believe the observations and new placement policy presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
-For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks.
+To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
+We believe the observations and new placement policy presented in this paper are valuable to the HPC community.
+%We believe the observations and new placement policy presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators.
+%For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks.
 System software developers could design better scheduling algorithms for jobs with distinct communication behavior.

### 2016-04-03 study_workload_1.tex
rewriting abstract and introduction done; tweak format in section 4
cut off tables in section 4,5,6. reduce num of pages to 12

@@
 %from the workload perspective to study the network performance. 
-The efficiency of the workload communication is another perspective to evaluate the network performance. 
-The average communication time spent by all MPI ranks when Workload~\Rmnum{1} is running under different placement and routing configurations shown in Table~\ref{tab:wkld-commtime}. 
-The random placement policy performs comparably with all routing policies (RM, RA and RPA).
+%The efficiency of the workload communication is another perspective to evaluate the network performance. 
+%The average communication time spent by all MPI ranks when Workload~\Rmnum{1} is running under different placement and routing configurations shown in Table~\ref{tab:wkld-commtime}. 
+%The random placement policy performs comparably with all routing policies (RM, RA and RPA).
 They outperform all contiguous placement configurations (CM, CA and CPA).
@@
 When random placement is in use, the workload communication efficiency can be further improved.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
-\label{tab:wkld-commtime}
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
-\cmidrule(l){2-7}
-          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
-
-The random placement can balance the network traffic load by uniformly distribute the traffic.
+%
+%
+%\begin{table}[ht]
+%\begin{center}
+%\caption{Average communication time by all MPI ranks when Workload I is running on the dragonfly network under six different placement and routing configurations.} 
+%\label{tab:wkld-commtime}
+%\begin{tabular}{l c c c c c c }
+%\toprule % Top horizontal line
+%\toprule
+%&\multicolumn{6}{c}{Placement and Routing Configurations} \\ 
+%\cmidrule(l){2-7}
+%          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
+%\midrule % In-table horizontal line
+%Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1
+%
+%\midrule % In-table horizontal line
+%\bottomrule % Bottom horizontal line
+%\end{tabular}
+%\end{center}
+%\end{table}
+%
+%
+%The random placement can balance the network traffic load by uniformly distribute the traffic.
 The (progressive) adaptive routing can avoid the hot-spots by redirecting the traffic away from congested area.
 The network can reach its optimal performance, when random placement coupled with (progressive) adaptive routing are in use.
+%
 
@@
 It takes comparable amount of communication time when contiguous placement coupled with adaptive and progressive routing. 
-When coupled with minimal routing, the communication time increase twofold. 
-AMG behaves abnormally when random placement is in use. 
+When coupled with minimal routing, the communication time almost doubles. 
 The communication time skyrockets when random placement coupled with (progressive) adaptive routing (RPA, RA) are in use.
 Minimal routing (RM) can mitigate this performance degradation, but still worse than CA and CPA.
-
 We observe that when Workload~\Rmnum{1} is running with random placement and (progressive) adaptive routing,
@@
 The increased traffic comes from the communication-intensive MultiGrid and CrystalRouter. 
-
 AMG behaves abnormally when random placement is in use 

### 2016-04-03 study_workload_2.tex
cut off tables in section 4,5,6. reduce num of pages to 12

@@
 
-The average communication time spent by all MPI ranks when Workload~\Rmnum{2} is running under different placement and routing configurations shown in Table~\ref{tab:syn-wkld-commtime}. 
-We can observe the similar pattern as in Table~\ref{tab:wkld-commtime}
-The contiguous placement coupled with minimal routing results in highest communication time. 
-The random placement coupled with minimal routing is the most efficient. 
-Progressive adaptive routing is better than adaptive routing when random placement is in use, 
-and they have comparable results when coupled contiguous placement. 
-Same as Workload~\Rmnum{1}, the network reaches the optimal performance when Workload~\Rmnum{2} is running with random placement and adaptive routing.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under six different placement and routing configurations.} 
-\label{tab:syn-wkld-commtime}
-%\centering % Centers the table on the page, comment out to left-justify
-\begin{tabular}{l c c c c c c }
-\toprule % Top horizontal line
-\toprule
-&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
-\cmidrule(l){2-7}
-          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
-\midrule % In-table horizontal line
-Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
-
-\midrule % In-table horizontal line
-\bottomrule % Bottom horizontal line
-\end{tabular}
-\end{center}
-\end{table}
+%+================================================================
+%The average communication time spent by all MPI ranks when Workload~\Rmnum{2} is running under different placement and routing configurations shown in Table~\ref{tab:syn-wkld-commtime}. 
+%We can observe the similar pattern as in Table~\ref{tab:wkld-commtime}
+%The contiguous placement coupled with minimal routing results in highest communication time. 
+%The random placement coupled with minimal routing is the most efficient. 
+%Progressive adaptive routing is better than adaptive routing when random placement is in use, 
+%and they have comparable results when coupled contiguous placement. 
+%Same as Workload~\Rmnum{1}, the network reaches the optimal performance when Workload~\Rmnum{2} is running with random placement and adaptive routing. 
+%
+%\begin{table}[ht]
+%\begin{center}
+%\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under six different placement and routing configurations.} 
+%\label{tab:syn-wkld-commtime}
+%%\centering % Centers the table on the page, comment out to left-justify
+%\begin{tabular}{l c c c c c c }
+%\toprule % Top horizontal line
+%\toprule
+%&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+%\cmidrule(l){2-7}
+%          & CM & CA & CPA & RM & RA & RPA \\ % Column names row
+%\midrule % In-table horizontal line
+%Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1
+%
+%\midrule % In-table horizontal line
+%\bottomrule % Bottom horizontal line
+%\end{tabular}
+%\end{center}
+%\end{table}
 

### 2016-04-04 draft.tex
tweak some sentences

@@
 However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
-We have observed that the performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs. 
-We identify this ``bully" behavior with the help of detailed network simulation and real application traces and validate the underneath causes.
-We propose a hybrid job placement policy that provide either contiguous or random allocation to each application based on its communication intensity. 
-With the help of the simulation, we demonstrate that this hybrid job placement policy can lead to performance improvement for less communication-intensive applications.
+The performance improvement of communication-intensive jobs comes with at the cost of performance degradation of less intensive jobs. 
+We identify this ``bully" behavior and validate its underneath causes with the help of detailed network simulation and real application traces.
+We propose a hybrid job placement policy providing either contiguous or random allocation to each application based on its communication intensity. 
+Our experiment results demonstrate that this hybrid job placement policy can lead to performance improvement for less communication-intensive applications.
 

### 2016-04-04 intro.tex
tweak some sentences

@@
 Even with such powerful networks, 
-intelligent job placement is still of paramount importance to the efficient use of dragonfly connected systems. 
-An ideal job placement policy should not only guarantee load balance on the network 
-but also mitigate the performance degradation of each application due to interference.  
-(Interference itself is inevitable on the dragonfly~\cite{bhatele2015, dskinner}.)
+intelligent job placement is still of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}. 
+%An ideal job placement policy should not only load balance the network 
+%but also guarantee the performance of every single application by minimizing the inevitable interference on the dragonfly network.
 
 Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}.
-These works explore the possible job placement and routing configurations that could optimize the overall network performance.
+These works explore the possible job placement and routing configurations that could optimize the overall network performance without scrutinizing the possible interference.
 In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
@@
 
-Based on the aforementioned key observations, the optimal job placement policy for the workload running dragonfly system should be specific to the application communication intensity.
+Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity.
 Thus, we propose a hybrid job placement, which can assign the communication-intensive applications with random allocation and less intensive applications with contiguous allocation.

### 2016-04-04 study_workload_2.tex
tweak some sentences

@@
 
-\emph{The application becomes the ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} The ``bully" takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
+\emph{The application becomes the ``bully" only because it has more amount of data transfer compared with its concurrently running peers.} The ``bully" takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
 

### 2016-04-04 intro.tex
tweak some words in Introduction

@@
 In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
-Our analysis focus on the performance of each application with interference in presence.
+Our analysis focus on the performance of every single application in the presence of interference .
 
@@
 For each application, we examine it with two job placement policies and three routing policies.
-We make the following interesting observations through extensive simulation.
+We make the following interesting observations through extensive simulations.
 
@@
 
-    \item Random placement can improve the performance of communication-intensive applications by enabling network resource sharing, though it introduces interference causing performance degradation.
+    \item Random placement can improve the performance of communication-intensive applications by enabling network resource sharing, though it introduces interference causing performance degradation to the less intensive applications.
 
-    \item Contiguous placement can guarantee consistency performance of less communication-intensive applications by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
+    \item Contiguous placement can guarantee the consistency performance of less communication-intensive applications by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
 
@@
 Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity.
-Thus, we propose a hybrid job placement, which can assign the communication-intensive applications with random allocation and less intensive applications with contiguous allocation.
-Our experiment results show that hybrid job placement can mitigate the performance degradation of less communication-intensive applications while still guarantee the best performance of communication-intensive applications.
+Thus, we propose a hybrid job placement, which assigns random allocations to the communication-intensive applications and contiguous allocations to the less intensive ones.
+Our experiment results show that hybrid job placement can mitigate the performance degradation for the less communication-intensive applications without affecting the performance of communication-intensive applications.
 %\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
@@
 The rest of this paper is organized as follows.
-Section \ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies.
-Section \ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
-Section \ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations.
-Section \ref{sec:workload-2} validates the observations we obtain from previous section.
-Section \ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network.
-Section \ref{sec:related work} discusses the related work.
-Finally, the conclusion is presented in Section \ref{sec:conclusion}.
+Section~\ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies.
+Section~\ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
+Section~\ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations.
+Section~\ref{sec:workload-2} validates the observations we obtain from previous section.
+Section~\ref{sec: hybrid placement} presents a alternative placement policy for the dragonfly network.
+Section~\ref{sec:related work} discusses the related work.
+Finally, the conclusion is presented in Section~\ref{sec:conclusion}.

### 2016-04-04 background.tex
tweak some sentences in Section 2

@@
 For each router, there could be $p$ compute nodes attached to it via terminal links.
-The router has $h$ global channels used as intergroup connections through which the router connected to other routers in different groups.
+The router has $h$ global channels used as intergroup connections through which it connected to other routers in different groups.
 Thus, the radix of each router is $k = a+h+p-1$.
 Different computing centers could choose different values for  $a$, $h$, $p$ when deploying their dragonfly network.
-The adoption of proper $a$, $h$, $p$ involves many factors, such as system scale, building cost and workload.
+The adoption of proper $a$, $h$, $p$ involves many factors such as system scale, building cost and workload characteristics.
 
 It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}.
-Under this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $.
+According to this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $.
 An implementation of dragonfly network follows such configuration is illustrated in Figure~\ref{fig:dragonfly-overview}.
@@
 
-For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning tasks of the application onto the system by a system software such as batch scheduler~\cite{xu-cluster14}.
+For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning the required number of nodes to the application by a system software such as batch scheduler~\cite{xu-cluster14}.
 In this work, we study two alternative placement policies considered by the community for dragonfly systems:
+
+\textbf{Random Placement:} In this policy, an application gets the required number of nodes randomly selected from all the available nodes in the system.
+As illustrated in Figure~\ref{fig:dragonfly-overview}, $J1$ gets random allocation in which nodes are attached to different routers in different groups.
+Routers may be shared by different applications and more routers are involved in serving each application when random placement is in use.
+Random placement can distribute the tasks of an application uniformly across the network to avoid the possible local congestion.
+However, random placement may cause congestion on global links.
 
@@
 The assignment first fills up a group, then crosses group boundaries and starts to fill the next group if necessary.
-As shown in Figure~\ref{fig:dragonfly-overview}, $J2$ gets eight nodes by contiguous placement.
+As illustrated in Figure~\ref{fig:dragonfly-overview}, $J2$ gets eight nodes by contiguous placement.
 Contiguous placement confines the tasks of an application into the same group and uses minimum number of routers serving each application, which may result in local network congestion and increase the possibility of hot-spots.
-
-\textbf{Random Placement:} In this policy, a job gets a set of nodes randomly selected from all the available nodes in the system.
-The nodes assigned to $J1$ in Figure~\ref{fig:dragonfly-overview} are attached to different routers in different groups.
-Routers may be shared by different jobs and more routers are involved in serving each application when random placement is in use.
-Random placement can distribute the tasks of an application uniformly across the network to avoid the possible local congestion.
-However, random placement may cause possible congestion on global links.
 
@@
 Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
-In this work we study three widely adopted routing policies on dragonfly networks.
+In this work we study three alternative routing policies considered by the community for dragonfly networks.
 
 \textbf{Minimal:} In this policy, a message takes the shortest path from the source router to the destination router.
-When there are multiple shortest paths between the source and destination router, the message will be evenly divided among the paths.
-Minimal routing can guarantee the minimum hops the message takes from source to destination.
-However, it may result in congestion along the shortest path.
+When there are multiple shortest paths between the source and destination, the message will be evenly divided among the paths.
+Minimal routing can guarantee the minimum hops the message takes from the source to the destination.
+However, it may result in congestion along the shortest paths.
 
@@
 Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}.
-The progressive adaptive is capable of handling the case where a global channel is congested but the source router has not been informed yet~\cite{jiang}.
+The progressive adaptive is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}.
 The packet will take the non-minimal route only when the congestion is encountered.

### 2016-04-04 methodology.tex
change some words in Section 3

@@
 Configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
-Even with access to systems with such networks, job placement and routing policies are part of system configuration, which is impossible for user to make changes at will~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
+Even with access to systems with such networks, job placement and routing policies are part of system configuration, which is impossible for user to make changes at will~\cite{jain-sc14, bhatele-sc11, zhou-ipdps-2015, jokanovic-ipdps-2015}.
 Therefore, we resort to simulation in our work.
@@
 A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability~\cite{codes}.
-CODES supports dragonfly~\cite{codes-dragonfly}~\cite{misbah-tpds}, torus~\cite{misbah-pads-2014}~\cite{ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
+CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
 It can drive these models through an MPI simulation layer utilizing DUMPI traces~\cite{sst}.
@@
 The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}.
-In this work, we study both the network performance and job interference when six different job placement and routing policy combinations are in use on the dragonfly network, which are summarized in Table~\ref{tab: placement routing configs}.
+In this paper, we simulate the running of those three applications on a dragonfly network when different job placement and routing policy combinations are in use.
+Table~\ref{tab: placement routing configs} lists the notations for all the job placement and routing policy combinations.
 
@@
 
+We analyze both the overall network performance and the performance of every single application.
 Our analysis focuses on the following metrics:
@@
 Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
-In Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}.
+As shown in Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}.
 Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
@@
 
-Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running jobs on the dragonfly network.
+Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running applications on the dragonfly network.
 Workload~\Rmnum{2} is used to verify the results and conclusion obtained from the study of Workload~\Rmnum{1}.

### 2016-04-04 study_workload_1.tex
change some words in Section 4

@@
 
-The study of parallel workload~\Rmnum{1} consists of two parts.
-Firstly, we analyze the over-all network performance when Workload~\Rmnum{1} is running under different placement and routing configurations.
-Secondly, we isolate each application from the workload, analyze its performance by scrutinizing the traffic going through the routers that serve each job.
-The analysis allows us to identify the ``bully" in the workload.
+The study of Workload~\Rmnum{1} consists of two parts.
+Firstly, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations.
+Secondly, we isolate each application from the workload, analyze its performance by scrutinizing the traffic going through its serving routers.
+The analysis allows us to identify the ``bully" in Workload~\Rmnum{1}.
 
@@
 
-We study the network performance under different placement and routing configurations by analyzing the traffic going through the routers and their saturated time. 
-The distribution of traffic over the network can reveal the loading situation, 
+We study the network performance by analyzing the traffic going through all the routers in the network and their saturated time. 
+The traffic distribution can reveal the loading situation in the network, 
 indicating whether the network is load-balanced or not. 
@@
 Workload~\Rmnum{1} is running on the dragonfly network with six different placement and routing configurations. 
+%explain CM
 When contiguous placement coupled with minimal routing(CM) is in use, 
-all the traffic are confined within the contiguously allocated groups, 
+all the traffic are confined within the consecutively allocated groups, 
 causing congestion on some routers along certain shortest paths from the source to the destination. 
@@
 In the meanwhile, the corresponding saturated time of their local and global channels are also the highest compared with other configurations, 
-shown as the blue dashed line in Figure~\ref{fig:global-channel-stime} and Figure~\ref{fig:local-channel-stime} .
-
+as shown in Figure~\ref{fig:global-channel-stime} and Figure~\ref{fig:local-channel-stime} .
+%explain CA and CPA
 When contiguous placement coupled with progressive adaptive routing (CPA) is in use, 
 the traffic would take non-shortest paths via intermediate routers to void congestion. 
-The congested routers along the shortest paths will not suffer the high volume of traffic as they used to. 
+The congested routers along the shortest paths will not suffer the high volume of traffic as they used to be. 
 The traffic through local and global channels are greatly reduced, 
@@
 
+%Explain RM
 Random placement policy performs comparably with three different routing policies.
@@
 the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic. 
-The blue solid line(RM) is lower than the red and green solid line (RA, RPA) in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}.
-
-Due to the same reason, 
+That's why blue solid line(RM) is lower than the red and green solid line (RA, RPA) in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. 
+%Explain RA, RPA
+For the same reason, 
 no router suffers exceptionally long saturated time on their global channels when random placement coupled (progressive) adaptive are in use, 
@@
 
-%terminal link traffic and busy time explanation
+% Explain terminal link traffic and busy time
 Figure~\ref{fig:terminal-link-traffic} is for the purpose of symmetry, 
@@
 We study the performance of each application individually by isolating it from Workload~\Rmnum{1}.   
-Figure~\ref{fig:apps-commtime} shows the distribution of communication time of three applications in per rank manner, 
-when they running concurrently under six different placement and routing configurations listed in Table\ref{tab: placement routing configs}.
-
+Figure~\ref{fig:apps-commtime} shows the distribution of their communication time when running concurrently under different placement and routing configurations.
 As shown in Figure~\ref{fig:mg-commtime}, 

### 2016-04-04 methodology.tex
methodology tweaks + todo notes

@@
 
-A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability~\cite{codes}.
-CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
-It can drive these models through an MPI simulation layer utilizing DUMPI traces~\cite{sst}.
-In this work, we perform an in-depth analysis of network performance as well as job interference when different job placement and routing policies are in use on the dragonfly network.
+We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{codes}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community.
+CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with flit-level high-fidelity simulation.
+It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI tracer~\cite{sst}.
 
@@
 
-We choose three parallel applications from the DOE Design Forward Project~\cite{designforwardwebpage}, which can represent a wide array of applications running on leadership-class supercomputers.
-Specifically, we study the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
+We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforwardwebpage} \TODO{can we get a better cite?}.
+Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
 
@@
 
-\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes~\cite{boxlib}, which are used for structured grid physics packages.
+\textbf{MultiGrid:} The geometric multi-grid v-cycle from the production elliptic solver BoxLib is a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes~\cite{boxlib}, which are used in structured grid physics packages.
 
-\textbf{CrystalRouter:} The Crystal Router MiniApp is the communication kernel of the full application Nek5000~\cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
+\textbf{CrystalRouter:} The Crystal Router MiniApp is a communication kernel of Nek5000~\cite{nek5000}, a spectral element CFD application developed at Argonne National Laboratory.
 It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores, and spatiotemporal chaos.
@@
 
-The parameters for building the dragonfly network studied in our work are inspired by the model proposed by Kim et.
-al~\cite{kim-micro}.
-Our dragonfly network consists of 33 groups, each of which contains eight routers.
+The parameters for building the dragonfly network studied in our work are informed by the model proposed by Kim et al.~\cite{kim-micro}.
+Our dragonfly network consists of 33 groups, each containing eight routers.
 Each router has four compute nodes attached to it.
 Overall, there are 264 routers and 1056 compute nodes in the network.
-The aggregated bandwidth of terminal link,  local and global channels are proportional to those of the Cray Cascade system~\cite{faanes}.
-In this paper, we simulate the running of those three applications on a dragonfly network when different job placement and routing policy combinations are in use.
-Table~\ref{tab: placement routing configs} lists the notations for all the job placement and routing policy combinations.
+\TODO{What's the resulting router radix?} The aggregate bandwidth of the terminal links, as well as the local and global channels, are proportional to those of the Cray Cascade system~\cite{faanes} \TODO{What are these bandwidths?}.
+In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.
 
@@
 
-    \item \textbf{Network Saturated Time:} The saturated time refers to the time period when the buffer of a certain port in the router is full.
-We analyze the saturated time of ports corresponding to terminal link, local and global channel.
+    \item \textbf{Network Saturation Time:} The saturation time refers to the time period when the buffer of a certain port in the router is full.
+We analyze the saturation time of ports corresponding to terminal links, local and global channels.
 The saturated time indicates the congestion level of routers.
@@
     \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks.
-The performance of each application is measured by the communication time.
-\footnote{Since our study focuses on network performance and job interference during communication, the computation time of each MPI rank will not be counted in the experiments.
-}
+Due to our use of simulation, we are able to measure the absolute (simulated) time a message takes to reach its destination.
+\TODO{Verify this.
+Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the \TODO{max?
+avg across ranks?
+distribution?} communication time.
+\end{itemize}
 
-\end{itemize}
+Note that we do not model computation for each MPI rank due to both the complexities inherent in performance prediction on separate parallel architectures as well as the emphasis on the side of the Design Forward traces on communication behavior rather than compute representation; users are instructed to treat the traces as if they came from one MPI rank-per-node configuration, despite being gathered using a rank-per-core approach.
+We instead allow MPI communications to proceed as quickly as they are able.
+\TODO{is this a good enough explanation?
+Anything else we should add?}
 
@@
 
-Two sets of parallel workloads are used in this work.
+Two sets of parallel workloads are used in this study.
 Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter.
-As shown in Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in Workload~\Rmnum{1}.
+As shown in Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in the workload.
 Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter.
-sAMG, a synthetic version of AMG, is generated by increasing AMG data transfer amount by 100x.
-sAMG is the most communication-intensive job in Workload~\Rmnum{2}.
+sAMG, a synthetic version of AMG, is generated by increasing the data transferred in AMG's MPI calls by a factor of 100, making it the most communication-intensive job in the workload.
+We do this for reasons that will become clear in the following sections.
 
-Workload~\Rmnum{1} is used to identify the ``bully" behavior among concurrently running applications on the dragonfly network.
-Workload~\Rmnum{2} is used to verify the results and conclusion obtained from the study of Workload~\Rmnum{1}.
+Each rank of each application is run on a dedicated node, following the recommended interpretation of the traces by the Design Forward team.
 
@@
 \begin{center}
-\caption{The details of each application.} 
+\caption{Application Summaries}
 \label{tab:apps-detail}
@@
 \toprule
-&\multicolumn{3}{c}{Application Details} \\ 
-\cmidrule(l){2-4}
 App Name & Num. Rank & Avg. Data/Rank & Total Data\\ % Column names row

### 2016-04-04 methodology.tex
one other todo in methodology

@@
 Overall, there are 264 routers and 1056 compute nodes in the network.
-\TODO{What's the resulting router radix?} The aggregate bandwidth of the terminal links, as well as the local and global channels, are proportional to those of the Cray Cascade system~\cite{faanes} \TODO{What are these bandwidths?}.
+\TODO{What's the resulting router radix?
+What's the classic $a,h,p$ (or whatever they are :) parameters?} The aggregate bandwidth of the terminal links, as well as the local and global channels, are proportional to those of the Cray Cascade system~\cite{faanes} \TODO{What are these bandwidths?}.
 In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

### 2016-04-04 methodology.tex
trivial tweak
make changes based on John's TODO for Section 3

--- 2016-04-04 methodology.tex
@@
 
-We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforwardwebpage} \TODO{can we get a better cite?}.
+We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforwardwebpage} \NOTE{can we get a better cite?
+done}.
 Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
@@
 The parameters for building the dragonfly network studied in our work are informed by the model proposed by Kim et al.~\cite{kim-micro}. 
-Our dragonfly network consists of 33 groups, each containing eight routers.
-Each router has four compute nodes attached to it.
-Overall, there are 264 routers and 1056 compute nodes in the network.
-\TODO{What's the resulting router radix?} The aggregate bandwidth of the terminal links, as well as the local and global channels, are proportional to those of the Cray Cascade system~\cite{faanes} \TODO{What are these bandwidths?}.
+In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels.
+For each router, there could be $p = 4$ compute nodes attached to it via terminal links.
+The router has $h = 4$ global channels used as intergroup connections through which it connected to other routers in different groups.
+The radix of each router is $k = a+h+p-1 = 13$.
+The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$.
+\NOTE{What's the resulting router radix?
+What's the classic $a,h,p$ (or whatever they are :) parameters?
+done!
+} The dragonfly network aggregate bandwidth is 5.25 GiB/s for the local and terminal router-ports, 4.7 GiB/s for the global ports, proportional to the Cray Cascade system~\cite{faanes} \NOTE{What are these bandwidths?
+done!}.
 In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.
@@
 \TODO{Verify this.
-Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the \TODO{max?
+Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the distribution of MPI ranks \NOTE{max?
 avg across ranks?
-distribution?} communication time.
+distribution?
+done!} communication time.
 \end{itemize}
@@
 \TODO{is this a good enough explanation?
-Anything else we should add?}
+Anything else we should add?
+sounds excellent to me!}
 

### 2016-04-05 study_workload_1.tex

@@
 The study of Workload~\Rmnum{1} consists of two parts.
-Firstly, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations.
-Secondly, we isolate each application from the workload, analyze its performance by scrutinizing the traffic going through its serving routers.
-The analysis allows us to identify the ``bully" in Workload~\Rmnum{1}.
+First, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations.
+Second, we isolate each application from the workload and analyze its performance on both a per-rank basis as well as by considering router traffic resident to application ranks.
+The analysis allows us to identify the ``bully'' in Workload~\Rmnum{1}.
+
+\TODO{Add in a few words across the section (not here) on how previous work compares as you go through the results.}
 
@@
 
-We study the network performance by analyzing the traffic going through all the routers in the network and their saturated time. 
-The traffic distribution can reveal the loading situation in the network, 
-indicating whether the network is load-balanced or not. 
-The saturated time can indicate the congestion situation on certain part of the network.
+We first study the network performance at the system level by analyzing the degree of traffic and saturation seen at each router.
 
@@
         \includegraphics[height=1.8 in]{wkld/gc-stime}
-        \caption{Global Channel Saturated Time}
+        \caption{Global Channel Saturation Time}
         \label{fig:global-channel-stime}
@@
         \includegraphics[height=1.8 in]{wkld/lc-stime}
-        \caption{Local Channel Saturated Time}
+        \caption{Local Channel Saturation Time}
         \label{fig:local-channel-stime}
@@
         \includegraphics[height=1.8 in]{wkld/tl-stime}
-        \caption{Terminal Link Saturated Time}
+        \caption{Terminal Link Saturation Time}
         \label{fig:terminal-link-stime}
     \end{subfigure}%
-   \caption{The aggregate traffic and saturated time of the dragonfly network when Workload~\Rmnum{1} running under six different placement and routing configurations.
-``CA" and ``CPA" performs comparably, the corresponding lines are overlapped.
-}
+    \caption{Aggregate traffic and saturation time for Workload~\Rmnum{1} under the configurations listed in Table~\ref{tab: placement routing configs}. ``CA'' and ``CPA'' have equivalent behavior.}
    \label{fig:wkld-network-traffic-stime}
@@
 
-Figure~\ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local and global channels 
-as well as the corresponding saturated time when 
-Workload~\Rmnum{1} is running on the dragonfly network with six different placement and routing configurations. 
+Figure~\ref{fig:wkld-network-traffic-stime} shows the aggregate traffic for terminal links, local and global channels,
+as well as the corresponding saturation time for Workload~\Rmnum{1} under the placement and routing configurations summarized in Table~\ref{tab: placement routing configs}.
 %explain CM
-When contiguous placement coupled with minimal routing(CM) is in use, 
-all the traffic are confined within the consecutively allocated groups, 
-causing congestion on some routers along certain shortest paths from the source to the destination. 
-The congested routers are over-loaded with high volume of traffic going through their local and global channels, 
-shown as the blue dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. 
-In the meanwhile, the corresponding saturated time of their local and global channels are also the highest compared with other configurations, 
-as shown in Figure~\ref{fig:global-channel-stime} and Figure~\ref{fig:local-channel-stime} .
+When contiguous placement is coupled with minimal routing (CM), 
+application traffic is confined within the consecutively allocated groups, 
+causing congestion on some routers along minimal paths to and from application nodes. 
+Both local and global channels experience significant congestion, as applications span multiple groups.
+Similarly, the saturation time for both local and global channels are also the highest compared with other configurations.
 %explain CA and CPA
-When contiguous placement coupled with progressive adaptive routing (CPA) is in use, 
-the traffic would take non-shortest paths via intermediate routers to void congestion. 
-The congested routers along the shortest paths will not suffer the high volume of traffic as they used to be. 
-The traffic through local and global channels are greatly reduced, 
-shown as the green dashed line in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. 
-The corresponding saturated time on local and global channels also drop a lot, 
-indicating the congestion are alleviated by using progressive adaptive routing. 
-The adaptive routing performs comparably compared with progressive adaptive routing, 
-thus CA is overlapped with CPA in the all the figures above.
+When contiguous placement is coupled with adaptive (CA) and progressive adaptive (CPA) routing, 
+traffic is able to take non-minimal paths via intermediate routers, helping to alleviate congestion along the minimal paths. 
+The resulting traffic through the most utilized local and global channels are greatly reduced, 
+as shown in Figures~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. \TODO{Traffic is not substantially reduced for local channel traffic}.
+Similarly, the corresponding saturation time on local and global channels is also reduced significantly, 
+demonstrating the efficacy of adaptive routing in this case. \TODO{How do we explain the similar distribution of traffic on local channels compared to the dissimilar distribution of saturation time?}
+For contiguous placement, we see no perceptible difference in behavior between adaptive and progressive adaptive routing.
 
 %Explain RM
-Random placement policy performs comparably with three different routing policies.
-Random placement can uniformly distribute MPI ranks over the network, 
-balance the traffic load over the network. 
-Shown as the solid lines in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, 
-no router suffers exceptional high volume of traffic on its local and global channels. 
-When the random placements coupled with minimal routing (RM), 
-the packets can avoid unnecessary intermediate forwarding as introduced by (progressive) adaptive routing, thus generating less traffic. 
-That's why blue solid line(RM) is lower than the red and green solid line (RA, RPA) in Figure~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. 
+In most cases for this study, the random placement policy behaves similarly across routing policies.
+Random placement uniformly distributes MPI ranks over the network, 
+balancing the resulting traffic load. 
+As shown in Figures~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, 
+no router suffers exceptionally high volume of traffic on its local and global channels. 
+When random placement is coupled with minimal routing (RM), less traffic is generated on account of
+the packets avoiding intermediate forwarding.
+At the same time, there is still significant congestion on local channels due to the lack of ability of packets to traverse non-minimal routes, falling into the same trap as the contiguous-minimal configuration.
+\TODO{check this}
 %Explain RA, RPA
-For the same reason, 
-no router suffers exceptionally long saturated time on their global channels when random placement coupled (progressive) adaptive are in use, 
-shown as red and green solid lines in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. 
-However, when random placement is couple with minimal routing, 
-the saturated time on certain routers along the shortest paths would increase, 
-shown as the prolonged blue solid line in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}. 
-Since the minimal routing always chooses the shortest paths, 
-increasing the possibility of congestion along those paths.
+Coupled with (progressive) adaptive routing,
+no router suffers exceptionally long saturation times on their global channels when random placement is in use, 
+as shown in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}.
+Further, in comparison to contiguous allocations, random allocations result in a more evenly distributed load on the resulting channels, as expected.
 
 % Explain terminal link traffic and busy time
-Figure~\ref{fig:terminal-link-traffic} is for the purpose of symmetry, 
-it shows the traffic per rank (aka traffic through terminal links), 
-which stay the same when different placement and routing configurations are in use. 
-All six lines are overlapped in Figure~\ref{fig:terminal-link-traffic}. 
-However, due to the traffic changes on local and channels, 
-the saturated time of terminal links will experience variability when different routing policies are in use, as shown in Figure~\ref{fig:terminal-link-stime}. 
-When contiguous placement coupled with minimal routing(CM), 
-the accumulated congestion on local and global channels cause extremely long saturated time on the terminal links, 
-shown as the blue dashed line in Figure~\ref{fig:terminal-link-stime}. 
-This again manifests the severe congestion caused by using contiguous placement and minimal routing.
+Figures~\ref{fig:terminal-link-traffic} and \ref{fig:terminal-link-stime} are presented for the purpose of symmetry, 
+showing the traffic per terminal link as well as the saturation time experienced at each terminal.
+The terminal traffic distribution corresponds directly to application traffic, as we are using one MPI rank per node (terminal).
+However, saturation times are different, resulting from the aforementioned network behavior.
+Particularly, contiguous allocations coupled with minimal routing results in a ``long-tail`` distribution of saturation time.
 
@@
     \end{subfigure}%
-    \caption{The communication time of all ranks in each application.
-Random placement and adaptive routing can improve the communication time of MultiGrid and CrystalRouter, while AMG's communication time is greatly prolonged.}
+    \caption{Communication time distribution across application ranks in Workload~\Rmnum{1}.}
    \label{fig:apps-commtime}
@@
 
-We study the performance of each application individually by isolating it from Workload~\Rmnum{1}.   
-Figure~\ref{fig:apps-commtime} shows the distribution of their communication time when running concurrently under different placement and routing configurations.
+Now that the system-level view has been analyzed, we turn to evaluate the
+behavior of each application within Workload~\Rmnum{1}.
+Figure~\ref{fig:apps-commtime} shows the communication time distribution across
+application ranks for different placement and routing configurations.
+
+The relative behavior of contiguous allocations is roughly similar in all three
+applications. Contiguous placement with minimal routing results in poor relative
+performance across the board compared to the adaptive routing alternatives.
+Given the analyses in Section~\ref{sec: workload-1 network analysis}, this is to
+be expected -- the contiguous-minimal configuration results in significant
+congestion.
+
+For the MultiGrid and CrystalRouter applications (Figures~\ref{fig:mg-commtime} and
+\ref{fig:cr-commtime}, respectively), using random allocation with any routing
+method results in performance improvements over contiguous allocations, which is
+largely in agreement with previous work (see Section~\ref{sec:related work}).
+\TODO{did previous work make this strong a claim?}. The high-radix nature of the
+network topology ensures that the benefits from the resulting load balancing
+outweigh the costs of extra hops for point-to-point messages.
+
+The AMG application (Figure~\ref{fig:amg-commtime}), however, shows markedly
+different behavior when using random allocation. Random allocation with minimal
+routing results in worse performance than contiguous-adaptive configurations,
+while using adaptive routing results in significant performance regressions. As
+this is a counterintuitive result not reached by other works, we investigate
+further.
+
+\begin{comment} JJ - doing some reorg, so keeping the old text just in case
+Now that the system-level view has been analyzed, we turn to evaluate the behavior of each application within Workload~\Rmnum{1}.
+Figure~\ref{fig:apps-commtime} shows the communication time distribution across application ranks for different placement and routing configurations.
 As shown in Figure~\ref{fig:mg-commtime}, 
@@
 the performance of MultiGrid and CrystalRouter are significant improved, whereas AMG suffers performance degradation. 
+\end{comment}
 
@@
     \end{subfigure}
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-``CA" and ``CPA" perform comparably, the corresponding lines are overlapped.
-More routers are involved in serving each application when random placement is in use, compared with contiguous placement.}
+   \caption{Aggregate workload traffic for routers serving specific applications.
+``CA'' and ``CPA'' have equivalent behavior.
+More routers are involved in serving each application when random placement is in use, compared to contiguous placement.}
    \label{fig:3app-lc-gc-traffic}
@@
 % Show the evidence from network level, explain why AMG is different.
-We look into network level to identify the culprit behind AMG's abnormal behavior with random placement. 
-By identifying the compute nodes that each MPI rank resides on and the routers that serving each application, 
-we analyze the traffic going through the routers belonging to each application and 
-present the results in Figure~\ref{fig:3app-lc-gc-traffic}. 
-Compared with contiguous placement, 
-the number of routers serving each application when random placement is in use are greatly increased, 
-thus the solid lines are longer than dashed lines as shown in Figure~\ref{fig:3app-lc-gc-traffic}.
 
-The routers serving MultiGrid and CrystalRouter have high volume of traffic on both local and global channels when contiguous placement is in use, 
+We step back to a network-level system view to identify the culprit behind AMG's
+abnormal behavior with random placement. This time, however, we identify the
+compute nodes that each MPI rank resides on and the routers that are serving
+each application, and analyze the traffic on a per-application basis.  The
+results of this experimentation are presented in
+Figure~\ref{fig:3app-lc-gc-traffic}. Note that different numbers of routers are
+used in the contiguous and random allocation configurations, as each router
+serves multiple terminals.
+
+The system behavior with respect to the CrystalRouter application arguably best
+matches expectations. Use of contiguous allocations result in a subset of
+channels with a significant traffic load while a significant portion are
+unused. Use of random allocations result in a comparatively smoother traffic
+distribution, with some variation on the margins due to the randomness.
+
+MultiGrid shows roughly similar behavior for contiguous allocations, but
+different behavior along the local channels. There is a significant variation in
+the traffic distribution of local channels, even with adaptive routing, which
+should have the net effect of distributing said traffic.
+
+AMG shows a similar level of variation to MultiGrid in this case. However, it is
+the least communication-intensive application of the three by a significant
+factor. In effect, the routers serving the AMG application are being utilized by
+MultiGrid and CrystalRouter, resulting in AMG traffic queuing up in their
+respective routers. Since the relative traffic is so low, AMG ends up
+experiencing significant slowdowns due to this effect. We refer to this phenomenon
+as AMG being ``bullied" by MultiGrid and CrystalRouter.
+
+\begin{comment} JJ - some more reorg here, also a few of the observations don't match the data
+
+The routers serving MultiGrid and CrystalRouter have a high traffic volume on both local and global channels when contiguous placement is in use, 
 shown as the dashed line in Figure~\ref{fig:mg-lc-traffic},~\ref{fig:mg-gc-traffic} and Figure~\ref{fig:cr-lc-traffic},~\ref{fig:cr-gc-traffic}. 
@@
 We refers this phenomenon as AMG being ``bullied" by MultiGrid and CrystalRouter.
+\end{comment}
 
 \subsection{Key Observations}
-In summary, based on the results presented in section~\ref{sec: workload-1 network analysis} and~\ref{sec: workload-1 app analysis}, we have made the following observations.
 
-\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} 
+In summary, based on the simulations presented in Section~\ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we have made the following observations.
+
+\emph{System-level performance is significantly improved when random placement and adaptive routing are in use.} 
 Random placement can uniformly distribute MPI ranks of application over the network, 
 and adaptive routing can redirect the traffic from congested routers to other less busy routers. 
-Therefore, the network could reach the status of load-balanced and hot-spots free.
+The combination of the two minimizes hot-spots and promotes load-balanced distribution.
+The resulting increased number of hops per message was not a significant detriment in comparison.
+This matches what is seen in the literature.
 
-\emph{The performance of less communication-intensive jobs in workload suffers degradation when random placement and adaptive routing are in use.} 
+\emph{The performance of communication-intensive jobs in the system improves using a random allocation policies}
+Both CrystalRouter and MultiGrid, the two most communication-intensive jobs,
+both saw improved distributions of communication performance when moving to a
+random allocation. Again, this matches what is seen in the literature.
+
+\emph{The performance of less communication-intensive jobs in workload regresses when random placement and adaptive routing are in use.} 
 AMG in Workload~\Rmnum{1} are ``bullied" by its concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
-AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use. 
-The traffic from MultiGrid and CrystalRouter is redirected to the routers that serving AMG, 
+AMG shares routers and groups with MultiGrid and CrystalRouter under random placement. 
+The traffic from MultiGrid and CrystalRouter is (re)directed to the routers that serve AMG, 
 slowing down AMG's communication. 
-\footnote{We have tried three different congestion sensing schemes that used in adaptive routing~\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}
+\footnote{We have tried three different congestion ``sensing'' schemes in the literature for adaptive routing~\cite{won-prog-adaptive}.
+Although there are some variations between the results, none of the congestion sensing scheme prevent the ``bully'' behavior.}
 
-\emph{The consistency performance of each application can be guaranteed when contiguous placement and minimal routing are in use.} 
-The router and group sharing among applications are prohibited in contiguous placement policy. Minimal routing will not redirect traffic from congested routers to less busy ones.
-Thus the interference between concurrently running jobs will be eliminated and the ``bully" behavior will be terminated.
+\emph{In contrast, performance consistency of each application is achieved only when contiguous placement and minimal routing are in use.} 
+As a corollary to the previous observation, router and group sharing among applications are guaranteed to be prohibited when using contiguous placement with minimal routing.
+This renders the ``bully'' behavior moot, though with the downside of significant performance degradation, so such approaches must be carefully considered.
+\TODO{not sure whether to keep this -- we don't really talk about performance consistency in the preceding text. It's a valid observation, though, so it should be somewhere...}

### 2016-04-05 study_workload_1.tex
extra comment, add label

@@
 \subsection{Key Observations}
+\label{sec:workload-1-observations}
 
@@
 \emph{In contrast, performance consistency of each application is achieved only when contiguous placement and minimal routing are in use.} 
-As a corollary to the previous observation, router and group sharing among applications are guaranteed to be prohibited when using contiguous placement with minimal routing.
+As a corollary to the previous observation, router and group sharing among applications are guaranteed to be prohibited when using contiguous placement with minimal routing (sharing of spare nodes within a group notwithstanding).
 This renders the ``bully'' behavior moot, though with the downside of significant performance degradation, so such approaches must be carefully considered.

### 2016-04-05 study_workload_2.tex
extra comment, add label

@@
 
-In this section, we will verify the observations made in the previous section 
-when Workload~\Rmnum{1} is running on the dragonfly network under different placement and routing configurations. 
-We conduct the same sets of experiments with Workload~\Rmnum{2}, which consists of sAMG, MultiGrid and CrystalRouter. 
-By replacing AMG with sAMG, we turn the ``bully" into the ``bullied".
+In this section, we use a different experimental configuration to verify and
+explore the observations made in the previous section. Specifically, we conduct
+the same sets of experiments through Workload~\Rmnum{2}, which consists of sAMG,
+MultiGrid and CrystalRouter. By replacing AMG with sAMG, we turn the ``bully"
+into the ``bullied".
 
@@
 
-Due to the replacement of AMG by sAMg, 
-the volume of data transfer in Workload~\Rmnum{2} is much higher than Workload~\Rmnum{1}, 
-thus the aggregate traffic on terminal links, local and global channels is greatly increased, 
-as shown in Figure~\ref{fig:synwkld-network-traffic-stime}. 
-The similar pattern in Figure~\ref{fig:wkld-network-traffic-stime} can be observed from Figure~\ref{fig:synwkld-network-traffic-stime}.
-Contiguous placement coupled with minimal routing(CM) results in congestion on some routers along certain shortest paths from the source to the destination. 
-Those congested routers are over-loaded with high volume of traffic going through their local and global channels, 
-shown as the blue dashed line in Figure~\ref{fig:synwkld-global-channel-traffic} and~\ref{fig:synwkld-local-channel-traffic}. 
-In the meanwhile, the corresponding saturated time of their local and global channels are also the highest compared with other configurations, 
-shown as the blue dashed line in Figure~\ref{fig:synwkld-global-channel-stime} and Figure~\ref{fig:synwkld-local-channel-stime}.
-
-When contiguous placement coupled with (progressive) adaptive routing is in use, the high volume of traffic are redirected by taking the intermediate routers in other groups to void congestion.
-Therefore, the traffic on the global channels can be uniformly distributed over the network and the corresponding saturated time are greatly reduced, illustrated by the red and green dashed lines.
-However, (progressive) adaptive routing can not effectively balance the traffic load for local channels.
-As shown by the red and green dashed lines in Figure~\ref{fig:synwkld-local-channel-traffic}, some routers still have high volume of traffic on their local channels.
-
-Random placement policy performs comparably with three different routing policies.
-By uniformly distributing MPI ranks over the network, 
-random placement can balance the traffic load over the network,
-illustrated by the solid lines in Figure~\ref{fig:synwkld-global-channel-traffic} and~\ref{fig:synwkld-local-channel-traffic}. 
-Progressive adaptive and adaptive routing generate more traffic than minimal routing
-as the packets take non-shortest paths via intermediate routers to avoid congestions, 
-thus the blue solid line(RM) is lower than the red and green solid line (RA, RPA).
+Figure~\ref{fig:synwkld-network-traffic-stime} shows aggregate traffic and
+saturation times for Workload~\Rmnum{2}, corresponding to
+Figure~\ref{fig:wkld-network-traffic-stime} in Workload~\Rmnum{1}.  Replacing
+AMG with sAMg results in greater aggregate traffic as well as more saturation
+than in Workload~\Rmnum{1}, but regardless, similar patterns can be observed.
+Contiguous placement with minimal routing results in load imbalances with
+respect to both traffic and saturation. The addition of adaptive routing
+alleviates these effects to some degree, particularly with respect to global
+channel usage, while trading off saturation in global channels for saturation in
+the local channels. \TODO{Did we make this observation in the earlier section?
+Should check...} Using random placement again shows roughly similar performance
+characteristics across routing configurations, with adaptive routing helping to
+balance aggregate load while increasing the aggregate traffic due to the related
+indirection.
 
@@
 
-We study the performance of each application individually by isolating it from Workload~\Rmnum{2}.   
-Figure~\ref{fig:syn-apps-commtime} shows the distribution of communication time of three applications in per rank manner, 
-when they running concurrently under six different placement and routing configurations.
+We study the performance of each application individually in the same manner as
+in Section~\ref{sec: workload-1 app analysis}.
+Figure~\ref{fig:syn-apps-commtime} shows the communication time distributions of
+the ranks of the three applications, running concurrently in Workload~\Rmnum{2}.
 The ``bully" in Workload~\Rmnum{1} becomes the ``bullied" in Workload~\Rmnum{2}. 
@@
 as shown in Figure~\ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}. 
-Whereas, sAMG benefits from random placement and (progressive) adaptive routing, 
-its communication time drops a lot compared with using contiguous placement, shown in Figure~\ref{fig:syn-samg-commtime}. 
-Contiguous placement coupled with minimal routing prevents applications from sharing network resource, 
-guaranteeing the performance of less communication-intensive applications like MultiGrid and CrystalRouter 
-and causing severe performance degradation to sAMG.
+Whereas, sAMG (Figure~\ref{fig:syn-samg-commtime}) benefits from random placement and (progressive) adaptive routing
+in a similar manner to CrystalRouter in Figure~\ref{fig:cr-commtime}.
+Contiguous placement coupled with minimal routing, while preventing the bully
+behavior, results in poor performance for all of the apps, except CrystalRouter,
+which we also expect is due to a higher degree of performance isolation.
 
@@
 % explain the network status of sAMG, MG and CR
-We look into the network level to scrutinize the traffic through the routers serving each application. 
-The routers serving sAMG have high volume of traffic on both local and global channels when contiguous placement is in use, 
-shown as the dashed line in Figure~\ref{fig:syn-samg-lc-traffic},~\ref{fig:syn-samg-gc-traffic}.
-The random placement can alleviate the local congestion by uniformly distributing the traffic of sAMG over the network, getting more routers involved in serving sAMG, as illustrated by solid lines. 
-sAMG benefits from random placement by getting their high volume of traffic being redirected 
-from its over-loaded routers to the less busy routers in the network. 
-In this case, a majority of those less busy routers are belonging to MultiGrid and CrystalRouter.
+Once again, we look at the network-level system view to scrutinize the traffic through the routers serving each application. 
+The routers serving sAMG have a high volume of traffic on both local and global channels when contiguous placement is in use, 
+as shown in Figures~\ref{fig:syn-samg-lc-traffic} and \ref{fig:syn-samg-gc-traffic}.
+As in previous results, the use of random placement alleviates the local congestion by uniformly distributing the traffic of sAMG over the network, getting more routers involved in serving sAMG.
+In this case, a majority of those less busy routers are also serving MultiGrid and CrystalRouter.
 
 %MultiGrid and CrystalRouter are the less communication-intensive applications in Workload~\Rmnum{2}.
-When MultiGrid is running with contiguous placement, the serving routers have relatively small volume of traffic on their local and global channels, as shown by the dashed lines in Figure~\ref{fig:syn-mg-lc-traffic},~\ref{fig:syn-mg-gc-traffic}.
-When coupled with (progressive) adaptive routing, more routers are involved in serving MultiGrid, thus the red and green dashed lines are shorter than the blue one.
-When random placement is in use, the MPI ranks of MultiGrid are randomly distributed across the network and sharing routers with other applications.
-The routers serving MultiGrid have much more traffic on their local and global channels, as shown by the solid lines in Figure~\ref{fig:syn-mg-lc-traffic},~\ref{fig:syn-mg-gc-traffic}.
-The increased traffic comes from the ``bully" sAMG.
+When MultiGrid is running with contiguous placement, the serving routers have a comparatively small volume of traffic on their local and global channels, as shown in Figure~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
+When coupled with (progressive) adaptive routing, more MultiGrid traffic traverses global channels, while more aggregate traffic is seen on the local channels due to the additional intermediate hops.
+When random placement is in use, the MPI ranks of MultiGrid are randomly distributed across the network and share routers with other applications.
+The routers serving MultiGrid have much more traffic on their local and global channels, as shown in Figures~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
+The increased traffic comes largely from sAMG.
 
-CrystalRouter has more data transfer than MultiGrid.
-However, it still becomes the victim of the ``bully" sAMG.
+While CrystalRouter is more communication-intensive than MultiGrid, it still becomes the victim of the ``bully" sAMG.
 We can observe the similar pattern about CrystalRouter from Figure~\ref{fig:syn-cr-lc-traffic},~\ref{fig:syn-cr-gc-traffic} as MultiGrid.
-When random placement is in use, the routers serving CrystalRouter have more traffic going through.
-The extra traffic comes from from the ``bully" sAMG causing performance degradation to MultiGrid and CrystalRouter.
+When random placement is in use, the routers serving CrystalRouter experience just as much, if not more, traffic than the contiguous placement in the extreme case, much of which originating from other applications (sAMG).
 
@@
 
-\subsection{Key Observations}
+\subsection{Observations}
 
-We have made the following observations from the study with Workload~\Rmnum{2}.
+\NOTE{rewrote this somewhat. The observations made were essentially the same
+as the previous section}
 
-\emph{The application becomes the ``bully" only because it has more amount of data transfer compared with its concurrently running peers.} The ``bully" takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
+Revisiting the observations in Section~\ref{sec:workload-1-observations}, we
+find that those observations are held under this separate configuration.
+System-level performance is still much improved in terms of load-balancing.
+sAMG, being far and away the most communication-intensive application, benefits
+greatly from random placement, whereas in Workload~\Rmnum{1} it was effectively
+penalized for being less communication-intensive. CrystalRouter, being the
+comparatively less communication-intensive application in Workload~\Rmnum{2},
+experiences performance regressions in Workload~\Rmnum{2} under random-adaptive
+policies.
 
-\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullied" when running concurrently with sAMG, since sAMG contributes the dominant portion of traffic in  in Workload \Rmnum{2}.
+Interestingly, in both Workload~\Rmnum{1} and \Rmnum{2}, MultiGrid experiences
+a more subtle performance behavior than the significant swings in performance
+seen in the other applications. These behaviors persisted across multiple runs
+with different random seeds. We are continuing to work towards understanding
+the root causes and implications of this behavior. \TODO{Is this a reasonable
+observation?}

### 2016-04-05 hybrid_placement.tex
hybrid placement first pass

@@
 
-Based on our experiments with two workloads, the ``bullying" is inevitable when the dragonfly network is configured with random placement and (progressive) adaptive routing. 
-The precaution to stop the ``bullying" is to avoid network sharing between concurrently running jobs, 
-and contiguous placement and minimal routing could be an effective way. 
-However, the network would suffer severe local congestion and unbalanced utilization when contiguous placement and minimal routing is in use. 
-Running each job with dedicated routing policy is unrealistic, 
-since routing policy is part of system configuration which can not be changed on the fly upon job submission. 
-Assigning preferable allocation to each job based on its communication intensity is applicable for the batch scheduler with intelligent job placement policy.
+Based on our experiments with Workloads~\Rmnum{1} and \Rmnum{2}, the ``bullying" behavior is
+exhibited when the dragonfly network is configured with random placement and
+(progressive) adaptive routing, and there is a large relative gap between the
+communication intensity of applications running on the network.
+As shown through our experimentation, contiguous placement policies give up too
+much in terms of congestion and load balance, and hence are an impractical
+solution. Further, running each job with a dedicated routing policy is unrealistic, 
+since routing policy is part of system configuration which can not be changed
+on the fly upon job submission and the policies of some jobs (adaptive)
+will still interfere with others.
 
+%Assigning preferable allocation to each job based on its communication intensity is applicable for the batch scheduler with intelligent job placement policy.
+
+\TODO{I'll revisit this later on. As Rob mentioned, I thought we weren't
+proposing a solution. (Could just need a language tweak).}
 We propose a hybrid job placement policy to assign each job with preferable allocation. 
@@
 AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocations.
-The experiment results show that hybrid placement performs comparably as random placement for improving network performance and mitigates the degradation of AMG caused by the ``bullying".
-\footnote{The analysis about network traffic and saturated time are omitted in this section due to page limit.}
 
@@
 
-The communication time of each application under all placement and routing configurations are presented in Figure~\ref{fig:hyb-plcmt-apps-commtime}. 
-As shown in Figure~\ref{fig:hyb-plcmt-mg-commtime} and~{fig:hyb-plcmt-cr-commtime},
+For the purpose of brevity, we only present the
+communication time distribution of each application under all placement and routing configurations, including the hybrid placement method.
+These results are presented in Figure~\ref{fig:hyb-plcmt-apps-commtime}.
+As shown in Figure~\ref{fig:hyb-plcmt-mg-commtime} and~\ref{fig:hyb-plcmt-cr-commtime},
 MultiGrid and CrystalRouter have similar performance with hybrid placement (HM, HA, HPA) as compared with random placement (RM, RA, RPA),
 since they are still assigned with random allocations in the hybrid placement policy. 
-The performance of AMG is significantly improved when hybrid placement configurations are in use. 
-The communication time of AMG are reduced by half when the placement policy switched from random to hybrid, 
-as shown in Figure \ref{fig:hyb-plcmt-amg-commtime}. 
-This is due the contiguous allocation assigned to AMG in the hybrid placement policy. 
-When being coupled with minimal routing, hybrid placement and contiguous placement have similar performance for AMG. 
-However, when (progressive) adaptive routing are in use, the traffic from MultiGrid and CrystalRouter still might be redirected to the routers serving AMG. 
-Since AMG is less communication-intensive and can not fully utilize network, 
-it is likely that the intermediate routers picked for the traffic from MultiGrid and CrystalRouter could be from AMG's groups.
-Both the communication-intensive and the less intensive application can benefit from hybrid placement coupled with (progressive) adaptive routing.
+While the performance of AMG under hybrid placement, shown in Figure~\ref{fig:hyb-plcmt-amg-commtime}, still exhibits significan communication interference on account of the other applications as opposed to the best contiguous placement policies, the effects are significantly reduced compared to a random-adaptive policy.
+We believe this to be a result of more AMG-specific traffic occupying a smaller set of routers/groups, both reducing the resulting probability of traffic entering them through adaptive routing and increasing the relative proportion of link utilization by AMG.
+Of course, this comes with the costs associated with contiguous allocation, in which AMG's traffic is less likely to load balance across multiple dragonfly groups.
 
+\TODO{Also need to check language here. I don't think the goal is to ``solve'' the bully behavior in this work.}
 The experiments with hybrid placement demonstrate that assigning each application with its preferable allocation can mitigate the negative effect of the ``bullying", in the meanwhile, 

### 2016-04-06 methodology.tex
change the cite for Design Forward Project

@@
 
-We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforwardwebpage} \NOTE{can we get a better cite?
+We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-traces} \NOTE{can we get a better cite?
 done}.

### 2016-04-06 intro.tex
change the cite for Design Forward Project
changes made based on Rob's comments for Introduction

@@
 
-Low-latency and high-bandwidth interconnect networks play a critical role in improving HPC system performance. 
-The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
-making it a very promising choice for building petaflop and beyond supercomputers. 
+Low-latency and high-bandwidth interconnect networks play a critical role in ensuring HPC system performance. 
+The high-radix, low-diameter dragonfly topology can lower \NOTE{the extension cost?} of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
+making it a very promising choice for building supercomputers with millions of cores.
 Even with such powerful networks, 
-intelligent job placement is still of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}. 
+intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}. 
 %An ideal job placement policy should not only load balance the network 
@@
 Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}.
-These works explore the possible job placement and routing configurations that could optimize the overall network performance without scrutinizing the possible interference.
-In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
-Our analysis focus on the performance of every single application in the presence of interference .
+These works explore the possible job placement and routing configurations that could optimize the overall network performance without examining how different configurations impact the progress of individual applications.
+In this paper, we study the implications of contention for shared network links in the context of multiple HPC applications running on dragonfly systems when different job placement and routing configurations are in use.
+Our analysis focus on the overall network performance as well as the performance of every single application in the presence of network contention.
 
@@
 
-We choose three representative applications from the DOE Design Forward Project~\cite{designforwardwebpage} to analyze the interference among them.
-Our study is based on the simulation with CODES, an high-fidelity, packet-level HPC network simulation toolkit~\cite{codes}.
-For each application, we examine it with two job placement policies and three routing policies.
-We make the following interesting observations through extensive simulations.
+We choose three representative HPC applications from the DOE Design Forward Project~\cite{designforward-webpage} to analyze the interference among them.
+Our study is based on the simulation with CODES, a high-fidelity, flit-level HPC network simulation toolkit~\cite{codes}.
+For each application, we examine its performance with two job placement policies and three routing policies.
+We make the following observations through extensive simulations.
 
@@
     \item Concurrently running applications on a dragonfly network interfere with each other when they share network resources.
-Communication-intensive applications ``bully" their less intensive peers and obtain performance improvement at the expense of less intensive ones suffering performance degradation.
+Communication-intensive applications ``bully" their less intensive peers and obtain performance improvement at the expense of less intensive ones.
 
@@
 
-    \item Contiguous placement can guarantee the consistency performance of less communication-intensive applications by prohibiting network resource sharing, though it results in local network congestion and unbalanced network utilization.
+   \item Contiguous placement is beneficial to the consistency performance of less communication-intensive applications by prohibiting network resource sharing, because it reduces the opportunities for traffic from other applications to be loaded on links that serve as minimal routes for the less intensive application.
 
@@
 
-Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity.
-Thus, we propose a hybrid job placement, which assigns random allocations to the communication-intensive applications and contiguous allocations to the less intensive ones.
+Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity.\NOTE{we are not proposing new placement policy, we explore a possible better alternative.
+} Thus, we investigate a hybrid job placement, which assigns random allocations to the communication-intensive applications and contiguous allocations to the less intensive ones.
 Our experiment results show that hybrid job placement can mitigate the performance degradation for the less communication-intensive applications without affecting the performance of communication-intensive applications.

### 2016-04-06 methodology.tex
change cite in section 3

@@
 
-We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-traces} \NOTE{can we get a better cite?
+We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-webpage} \NOTE{can we get a better cite?
 done}.
@@
 \TODO{is this a good enough explanation?
-Anything else we should add?
-sounds excellent to me!}
+Anything else we should add?}
 
@@
 
-Each rank of each application is run on a dedicated node, following the recommended interpretation of the traces by the Design Forward team.
+Each rank of each application is run on a dedicated node, following the recommended interpretation of the traces by the Design Forward team~\cite{designforward-traces}.
 

### 2016-04-06 study_workload_2.tex
change the caption for Fig 5,6,7  in Section 5

@@
         \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
-        \caption{Global Channel Saturated Time}
+        \caption{Global Channel Saturation Time}
         \label{fig:synwkld-global-channel-stime}
@@
         \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
-        \caption{Local Channel Saturated Time}
+        \caption{Local Channel Saturation Time}
         \label{fig:synwkld-local-channel-stime}
@@
         \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
-        \caption{Terminal Link Saturated Time}
+        \caption{Terminal Link Saturation Time}
         \label{fig:synwkld-terminal-link-stime}
     \end{subfigure}%
-   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under six different placement and routing configurations.}
+   \caption{Aggregate traffic and saturation time for Workload~\Rmnum{2} under the configurations listed in Table~\ref{tab: placement routing configs}.}
    \label{fig:synwkld-network-traffic-stime}
@@
     \end{subfigure}%
-
-   \caption{The communication time of all ranks in each application.
-Three applications running concurrently on dragonfly network with different placement and routing configurations.
+    \caption{Communication time distribution across application ranks in Workload~\Rmnum{2}.
 The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullied", MultiGrid and CrystalRouter, suffer performance degradation.}
@@
     \end{subfigure}
-   \caption{The aggregate traffic go through the local and global channels of routers serving specific application.
-Compared with contiguous placement, More routers are involved in serving each application when random placement is in use.}
+    \caption{Aggregate workload traffic for routers serving specific applications.
+More routers are involved in serving each application when random placement is in use, compared to contiguous placement.}
    \label{fig:syn-3app-gc-traffic}

### 2016-04-06 intro.tex
intro tweaks

@@
 In this paper, we study the implications of contention for shared network links in the context of multiple HPC applications running on dragonfly systems when different job placement and routing configurations are in use.
-Our analysis focus on the overall network performance as well as the performance of every single application in the presence of network contention.
+Our analyses focus on the overall network performance as well as the performance of concurrently executing applications in the presence of network contention.
 
@@
 We choose three representative HPC applications from the DOE Design Forward Project~\cite{designforward-webpage} to analyze the interference among them.
-Our study is based on the simulation with CODES, a high-fidelity, flit-level HPC network simulation toolkit~\cite{codes}.
+Our study is based on simulation with CODES, a high-fidelity, flit-level HPC network simulation toolkit~\cite{codes}.
 For each application, we examine its performance with two job placement policies and three routing policies.
@@
 
-    \item Random placement can improve the performance of communication-intensive applications by enabling network resource sharing, though it introduces interference causing performance degradation to the less intensive applications.
+    \item Random placement of application processes in the dragonfly can improve the performance of communication-intensive applications by enabling network resource sharing, though it introduces interference causing performance degradation to the less intensive applications.
 
-   \item Contiguous placement is beneficial to the consistency performance of less communication-intensive applications by prohibiting network resource sharing, because it reduces the opportunities for traffic from other applications to be loaded on links that serve as minimal routes for the less intensive application.
+   \item Contiguous placement can be beneficial to the consistent performance of less communication-intensive applications by minimizing network resource sharing, because it reduces the opportunities for traffic from other applications to be loaded on links that serve as minimal routes for the less intensive application.
+However, this comes with the downside of at times greatly reduced system performance via load imbalance.
 
@@
 
-Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity.\NOTE{we are not proposing new placement policy, we explore a possible better alternative.
-} Thus, we investigate a hybrid job placement, which assigns random allocations to the communication-intensive applications and contiguous allocations to the less intensive ones.
-Our experiment results show that hybrid job placement can mitigate the performance degradation for the less communication-intensive applications without affecting the performance of communication-intensive applications.
+Based on the aforementioned key observations, one would expect that an ideal job placement policy on dragonfly systems would take relative communication intensity into account, and mix contiguous and non-contiguous placement based on application needs.
+To explore this expectation, we investigate a hybrid job placement policy, which assigns random allocations to communication-intensive applications and contiguous allocations to less intensive ones.
+Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive applications, though without eliminating the problem entirely.
 %\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
-To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported so far.
+To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported in the literature so far.
 We believe the observations and new placement policy presented in this paper are valuable to the HPC community.

### 2016-04-06 methodology.tex
moved cite, minor edits

--- 2016-04-06 methodology.tex
@@
 
-We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-traces} \NOTE{can we get a better cite?
+We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-webpage,designforward-traces} \NOTE{can we get a better cite?
 done}.
@@
 done!
-} The dragonfly network aggregate bandwidth is 5.25 GiB/s for the local and terminal router-ports, 4.7 GiB/s for the global ports, proportional to the Cray Cascade system~\cite{faanes} \NOTE{What are these bandwidths?
+} The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, proportional to the Cray Cascade system~\cite{faanes} \NOTE{What are these bandwidths?
 done!}.
@@
     \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router.
-We analyze the traffic on the terminal link, local and global channel of each router.
+We analyze the traffic on each terminal and on the local and global channels of each router.
 The network reaches optimal performance when the traffic is uniformly distributed and no particular router is over-loaded.
@@
 \TODO{Verify this.
-Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the distribution of MPI ranks \NOTE{max?
+Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the distribution of the corresponding MPI ranks' \NOTE{max?
 avg across ranks?
 distribution?
-done!} communication time.
+done!} communication times.
 \end{itemize}

### 2016-04-06 background.tex

@@
 According to this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $.
-An implementation of dragonfly network follows such configuration is illustrated in Figure~\ref{fig:dragonfly-overview}.
-There are six routers in each group, each router has three compute nodes attached to it.
+An example dragonfly network is illustrated in Figure~\ref{fig:dragonfly-overview}.
+There are six routers in each group $(a=6)$, three compute nodes per router $(p=3)$, and three global channels per router $(h=3)$.
 This dragonfly network consists of 19 groups and 342 nodes in total.
@@
   \includegraphics[width=0.48\textwidth]{dragonfly-overview}
-  \caption{Dragonfly Network Overview.
-There are 19 groups, six routers in each group, three compute nodes connected to each router, 342 nodes in total.
-Job $J1$ requires seven nodes, getting its allocation by random placement.
-Job $J2$ requires eight nodes, getting its allocation by contiguous placement.}
+  \caption{Five group slice of a 19-group dragonfly network. Job $J1$ is allocated using random placement, while Job $J2$ is allocated using contiguous placement.}
   \label{fig:dragonfly-overview}
 \end{figure}
+
+\subsection{Routing on Dragonfly}
+\label{sec:routing-schemes}
+
+The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router.
+Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
+In this work we study three alternative routing policies considered by the community for dragonfly networks.
+
+\textbf{Minimal:} In this policy, a message takes the minimal (shortest) path from the source router to the destination router.
+When there are multiple minimal paths between the source and destination, the message will be evenly divided among the paths.
+Minimal routing can guarantee the minimum hops the message takes from the source to the destination.
+However, it may result in congestion along the minimal paths.
+
+\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths.
+For the non-minimal path, an intermediate router in a separate group will be randomly chosen.
+The message takes the intermediate router as a via point, connecting the source and destination router through two separate minimal paths.
+Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.
+
+\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated \TODO{packet granularity?
+flit granularity?}.
+Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang} \TODO{I thought PA does do re-evaluation?}.
+Progressive adaptive routing is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}.
+The packet will take the non-minimal route only when the congestion is encountered.
 
@@
 Contiguous placement confines the tasks of an application into the same group and uses minimum number of routers serving each application, which may result in local network congestion and increase the possibility of hot-spots.
-
-\subsection{Routing on Dragonfly}
-\label{sec:routing-schemes}
-
-The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router.
-Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
-In this work we study three alternative routing policies considered by the community for dragonfly networks.
-
-\textbf{Minimal:} In this policy, a message takes the shortest path from the source router to the destination router.
-When there are multiple shortest paths between the source and destination, the message will be evenly divided among the paths.
-Minimal routing can guarantee the minimum hops the message takes from the source to the destination.
-However, it may result in congestion along the shortest paths.
-
-\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest paths, depending on the congestion situation along those paths.
-For the non-shortest path, an intermediate router will be randomly chosen.
-The message takes the intermediate router as a via point, connecting the source and destination router through two separate shortest paths.
-Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.
-
-\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated.
-Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}.
-The progressive adaptive is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}.
-The packet will take the non-minimal route only when the congestion is encountered.

### 2016-04-06 study_workload_1.tex
section 4 tweaks, took out comment blob

@@
 As shown in Figures~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}, 
-no router suffers exceptionally high volume of traffic on its local and global channels. 
+no router experiences an exceptionally high volume of traffic on its local and global channels. 
 When random placement is coupled with minimal routing (RM), less traffic is generated on account of
@@
 Coupled with (progressive) adaptive routing,
-no router suffers exceptionally long saturation times on their global channels when random placement is in use, 
+saturation times are effectively minimized on both global and local channels when random placement is in use, 
 as shown in Figure~\ref{fig:global-channel-stime} and~\ref{fig:local-channel-stime}.
@@
 method results in performance improvements over contiguous allocations, which is
-largely in agreement with previous work (see Section~\ref{sec:related work}).
+largely in agreement with the literature (see Section~\ref{sec:related work}).
 \TODO{did previous work make this strong a claim?}. The high-radix nature of the
@@
 different behavior along the local channels. There is a significant variation in
-the traffic distribution of local channels, even with adaptive routing, which
-should have the net effect of distributing said traffic.
+the traffic distribution on local channels, even with adaptive routing, which
+nevertheless has the net effect of reducing the maximal traffic load.
 
-AMG shows a similar level of variation to MultiGrid in this case. However, it is
-the least communication-intensive application of the three by a significant
-factor. In effect, the routers serving the AMG application are being utilized by
-MultiGrid and CrystalRouter, resulting in AMG traffic queuing up in their
-respective routers. Since the relative traffic is so low, AMG ends up
-experiencing significant slowdowns due to this effect. We refer to this phenomenon
-as AMG being ``bullied" by MultiGrid and CrystalRouter.
-
-\begin{comment} JJ - some more reorg here, also a few of the observations don't match the data
-
-The routers serving MultiGrid and CrystalRouter have a high traffic volume on both local and global channels when contiguous placement is in use, 
-shown as the dashed line in Figure~\ref{fig:mg-lc-traffic},~\ref{fig:mg-gc-traffic} and Figure~\ref{fig:cr-lc-traffic},~\ref{fig:cr-gc-traffic}. 
-On the other hand, the random placement can uniformly distribute the traffic of MultiGrid and CrystalRouter over the network, 
-alleviate local congestion and balance the traffic load among all routers, 
-shown as the solid lines in Figure~\ref{fig:mg-lc-traffic},~\ref{fig:mg-gc-traffic} and Figure~\ref{fig:cr-lc-traffic},~\ref{fig:cr-gc-traffic}. 
-MultiGrid and CrystalRouter benefit from random placement by getting their high volume of traffic being redirected 
-from their over-loaded routers to the less busy routers in the network. 
-In this case, a majority of those less busy routers are belonging to AMG.
-
-Since AMG is less communication-intensive, 
-the routers serving AMG have small volume of traffic on local and global channels when the contiguous placement is use, 
-shown as the dashed line in Figure~\ref{fig:amg-lc-traffic},~\ref{fig:amg-gc-traffic}. 
-When random placement is in use, 
-more routers are involved in serving AMG, 
-and the traffic skyrockets on the local and global channels, 
-shown as the solid lines in Figure~\ref{fig:amg-lc-traffic},~\ref{fig:amg-gc-traffic}. 
-The increased traffic comes from the communication-intensive MultiGrid and CrystalRouter. 
-AMG behaves abnormally when random placement is in use 
-because the routers serving AMG have to take the traffic from MultiGrid and CrystalRouter. 
-The extra traffic from the other communication-intensive applications 
-takes advantage the network resources belonging to AMG and slows down AMG's communication. 
-We refers this phenomenon as AMG being ``bullied" by MultiGrid and CrystalRouter.
-\end{comment}
+AMG shows a similar level of variation to MultiGrid in this case. However, it
+is the least communication-intensive application of the three by a significant
+factor. As evidenced by the wide gap between the router traffic in contiguous
+and random placement configurations, the routers serving the AMG application
+are being utilized by MultiGrid and CrystalRouter, resulting in AMG traffic
+contending with traffic of other applications. The net effect, as shown in
+Figure~\ref{fig:amg-commtime}, is significant slowdowns for AMG.
+We refer to this phenomenon as AMG being ``bullied" by MultiGrid and CrystalRouter.
 
@@
 
-In summary, based on the simulations presented in Section~\ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we have made the following observations.
+In summary, based on the simulations presented in Section~\ref{sec: workload-1 network analysis} and \ref{sec: workload-1 app analysis}, we make the following observations.
 
@@
 
-\emph{The performance of communication-intensive jobs in the system improves using a random allocation policies}
+\emph{The performance of communication-intensive jobs in the system improves through use of random allocation policies.}
 Both CrystalRouter and MultiGrid, the two most communication-intensive jobs,
@@
 \emph{The performance of less communication-intensive jobs in workload regresses when random placement and adaptive routing are in use.} 
-AMG in Workload~\Rmnum{1} are ``bullied" by its concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
+AMG in Workload~\Rmnum{1} is ``bullied" by its concurrently running communication-intensive peers, MultiGrid and CrystalRouter.
 AMG shares routers and groups with MultiGrid and CrystalRouter under random placement. 

### 2016-04-06 methodology.tex
remove TODO and NOTE in Section 3

@@
 
-We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-webpage,designforward-traces} \NOTE{can we get a better cite?
-done}.
-Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
+We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-webpage,designforward-traces} Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
 
@@
 The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
-\NOTE{What's the resulting router radix?
-What's the classic $a,h,p$ (or whatever they are :) parameters?
-done!
-} The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, proportional to the Cray Cascade system~\cite{faanes} \NOTE{What are these bandwidths?
-done!}.
+%\NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } 
+The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, proportional to the Cray Cascade system~\cite{faanes} 
+%\NOTE{What are these bandwidths? done!}. 
 In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.
@@
 Due to our use of simulation, we are able to measure the absolute (simulated) time a message takes to reach its destination.
-\TODO{Verify this.
-Or is comm time the time that the terminal link is busy?} The performance of each application is measured by the distribution of the corresponding MPI ranks' \NOTE{max?
-avg across ranks?
-distribution?
-done!} communication times.
+The performance of each application is measured by the communication time distribution across all its ranks.
+
     \end{itemize}
@@
 We instead allow MPI communications to proceed as quickly as they are able.
-\TODO{is this a good enough explanation?
-Anything else we should add?}
+%\TODO{is this a good enough explanation? Anything else we should add?}
 

### 2016-04-06 study_workload_2.tex
section 5 edits

@@
 channel usage, while trading off saturation in global channels for saturation in
-the local channels. \TODO{Did we make this observation in the earlier section?
-Should check...} Using random placement again shows roughly similar performance
+the local channels. Using random placement again shows roughly similar performance
 characteristics across routing configurations, with adaptive routing helping to
@@
 The ``bully" in Workload~\Rmnum{1} becomes the ``bullied" in Workload~\Rmnum{2}. 
-MultiGrid and CrystalRouter are the less communication-intensive applications in Workload~\Rmnum{2}. 
-When random placement coupled with (progressive) adaptive routing is in use, 
-MultiGrid and CrystalRouter suffer prolonged communication time, 
+MultiGrid and CrystalRouter are in this instance the less communication-intensive applications. 
+With random placement and (progressive) adaptive routing, 
+MultiGrid and CrystalRouter experience prolonged communication time, 
 as shown in Figure~\ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}. 
-Whereas, sAMG (Figure~\ref{fig:syn-samg-commtime}) benefits from random placement and (progressive) adaptive routing
-in a similar manner to CrystalRouter in Figure~\ref{fig:cr-commtime}.
+On the other hand, sAMG (Figure~\ref{fig:syn-samg-commtime}) benefits from those configurations
+in a similar manner to CrystalRouter in Workload~\Rmnum{1}.
 Contiguous placement coupled with minimal routing, while preventing the bully
-behavior, results in poor performance for all of the apps, except CrystalRouter,
-which we also expect is due to a higher degree of performance isolation.
+behavior, results in poor performance for all of the applications except CrystalRouter,
+which we also expect is due to a higher degree of network isolation.
 
@@
 %MultiGrid and CrystalRouter are the less communication-intensive applications in Workload~\Rmnum{2}.
-When MultiGrid is running with contiguous placement, the serving routers have a comparatively small volume of traffic on their local and global channels, as shown in Figure~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
+% JJ - I shortened this
+%When MultiGrid is running with contiguous placement, the serving routers have a comparatively small volume of traffic on their local and global channels, as shown in Figure~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
 When coupled with (progressive) adaptive routing, more MultiGrid traffic traverses global channels, while more aggregate traffic is seen on the local channels due to the additional intermediate hops.
-When random placement is in use, the MPI ranks of MultiGrid are randomly distributed across the network and share routers with other applications.
+%When random placement is in use, the MPI ranks of MultiGrid are randomly distributed across the network and share routers with other applications.
 The routers serving MultiGrid have much more traffic on their local and global channels, as shown in Figures~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
 The increased traffic comes largely from sAMG.
+\TODO{can shorten this}
 
-While CrystalRouter is more communication-intensive than MultiGrid, it still becomes the victim of the ``bully" sAMG.
-We can observe the similar pattern about CrystalRouter from Figure~\ref{fig:syn-cr-lc-traffic},~\ref{fig:syn-cr-gc-traffic} as MultiGrid.
-When random placement is in use, the routers serving CrystalRouter experience just as much, if not more, traffic than the contiguous placement in the extreme case, much of which originating from other applications (sAMG).
+MultiGrid in Workload~\Rmnum{2} appears most similar to AMG in Workload~\Rmnum{1} when considering resident channel behavior, as shown in Figures~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
+There is a large gap in traffic volume between the contiguous and random placement approaches, due to other applications (sAMG in particular) utilizing the same links.
+CrystalRouter in Workload~\Rmnum{2} additionally experiences more load on its channels using random allocation configurations, as shown in Figure~\ref{fig:syn-cr-lc-traffic} and \ref{fig:syn-cr-lc-traffic}.
+However, the maximal load under random allocation is closer to that seen in contiguous allocations as compared to MultiGrid.
 
@@
 sAMG, being far and away the most communication-intensive application, benefits
-greatly from random placement, whereas in Workload~\Rmnum{1} it was effectively
+greatly from random placement, whereas in Workload~\Rmnum{1} AMG was effectively
 penalized for being less communication-intensive. CrystalRouter, being the
 comparatively less communication-intensive application in Workload~\Rmnum{2},
-experiences performance regressions in Workload~\Rmnum{2} under random-adaptive
+experiences performance regressions in Workload~\Rmnum{2} under random and adaptive
 policies.
@@
 seen in the other applications. These behaviors persisted across multiple runs
-with different random seeds. We are continuing to work towards understanding
-the root causes and implications of this behavior. \TODO{Is this a reasonable
+with different random seeds. Additionally, CrystalRouter in Workload~\Rmnum{2}
+sees less drastic changes in maximal load, but still experiences performance
+regressions. We are continuing to work towards understanding the root causes
+and implications of this behavior, for which we expect application-specific
+communication patterns to be an important factor. \TODO{Is this a reasonable
 observation?}

### 2016-04-06 hybrid_placement.tex
hybrid placement text

@@
 
-\TODO{I'll revisit this later on. As Rob mentioned, I thought we weren't
-proposing a solution. (Could just need a language tweak).}
-We propose a hybrid job placement policy to assign each job with preferable allocation. 
-According to the hybrid placement policy, 
-the less communication-intensive jobs get contiguous allocation to partially avoid network sharing with the ``bully", 
-while the communication-intensive jobs get random allocation in order to share network resource with each other. 
-When Workload~\Rmnum{1} is running on the dragonfly network with hybrid placement policy, 
-AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocations.
+\TODO{Is this reasonable?}
+
+As a natural extension of our observations, one question that arises is whether
+we can combine aspects from both random and contiguous allocation policies in
+which each application receives the performance benefits from system load
+balancing while avoiding the ``bully'' behavior. As an initial exploration of
+that question, we set up a mock hybrid job placement policy, in which less
+communication-intensive jobs receive contiguous allocations to avoid the
+``bully" effect, while the communication-intensive jobs are allocated randomly
+in order to distribute the communication load. For Workload~\Rmnum{1}, this
+means AMG gets a contiguous allocation while MultiGrid and CrystalRouter get
+random allocations. Note that we do not consider challenges inherent in
+designing an allocation policy for production usage, such as backfilling,
+reserving large contiguous sets of nodes, determining a metric for
+communication intensity, etc., preferring a restricted-scope experiment
+looking at the design space of dragonfly allocation policies in light of our experimental
+observations.
 
@@
     \end{subfigure}
-   \caption{Application communication time. Workload~\Rmnum{1} is running with all placement and routing configurations.}
+   \caption{Application communication time. Workload~\Rmnum{1} is running with all placement and routing configurations. Methods prefixed with ``H'' represent the hybrid allocation approach.}
    \label{fig:hyb-plcmt-apps-commtime}
@@
 As shown in Figure~\ref{fig:hyb-plcmt-mg-commtime} and~\ref{fig:hyb-plcmt-cr-commtime},
-MultiGrid and CrystalRouter have similar performance with hybrid placement (HM, HA, HPA) as compared with random placement (RM, RA, RPA),
-since they are still assigned with random allocations in the hybrid placement policy. 
-While the performance of AMG under hybrid placement, shown in Figure~\ref{fig:hyb-plcmt-amg-commtime}, still exhibits significan communication interference on account of the other applications as opposed to the best contiguous placement policies, the effects are significantly reduced compared to a random-adaptive policy.
-We believe this to be a result of more AMG-specific traffic occupying a smaller set of routers/groups, both reducing the resulting probability of traffic entering them through adaptive routing and increasing the relative proportion of link utilization by AMG.
+MultiGrid and CrystalRouter exhibit similar performance in both hybrid and random placement, as nodes are being placed randomly in each case.
+While the performance of AMG under hybrid placement, shown in Figure~\ref{fig:hyb-plcmt-amg-commtime}, still appears to exhibit significant communication interference on account of the other applications as opposed to the best contiguous placement policies, the effects are significantly reduced compared to a random-adaptive policy.
+We believe this to be a result of more AMG-specific traffic occupying a smaller set of routers/groups, both reducing the probability of traffic entering them through adaptive routing and increasing the relative proportion of link utilization by AMG.
 Of course, this comes with the costs associated with contiguous allocation, in which AMG's traffic is less likely to load balance across multiple dragonfly groups.
 
-\TODO{Also need to check language here. I don't think the goal is to ``solve'' the bully behavior in this work.}
-The experiments with hybrid placement demonstrate that assigning each application with its preferable allocation can mitigate the negative effect of the ``bullying", in the meanwhile, 
-the network can still reach the optimal performance.
-Compared with random placement policy, hybrid placement can guarantee comparable network performance, by enabling network sharing between communication intensive applications .
-It can also mitigate the performance degradation of less communication-intensive applications, 
-by assigning them with contiguous allocation to partially avoid network sharing.
-Unlike random placement indulging the ``bullying", hybrid placement can restrain it to some extent.
-Hybrid placement policy is worthy of consideration for the adoption on dragonfly systems in the future.
+\TODO{How's this?}
+These initial experiments demonstrate some degree of benefit derived from using a hybrid approach, helping to alleviate the ``bully'' effect while retaining the performance of communication-intensive applications.
+However, the behavior is still not ideal in this case -- AMG's communications still experience performance degradation versus the contiguous configurations.
+Hence, more work in this area is needed to fully understand the intricate relationships between job scheduling and system/application communication behavior to approach optimal network utilization and application performance in high-radix networks.

### 2016-04-06 background.tex
remove TODOs in Section 2

@@
 
-\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated \TODO{packet granularity?
-flit granularity?}.
-Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang} \TODO{I thought PA does do re-evaluation?}.
+\textbf{Progressive Adaptive:} In this policy, the decision to route a packet minimally at each hop in the source group will be re-evaluated.
+% \TODO{packet granularity? flit granularity? It is papacket granularity}. 
+Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}. 
+%\TODO{I thought PA does do re-evaluation? PA do re-evaluate in source group only}. 
 Progressive adaptive routing is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}.

### 2016-04-06 intro.tex
small tweak in Introduction

@@
 Low-latency and high-bandwidth interconnect networks play a critical role in ensuring HPC system performance. 
-The high-radix, low-diameter dragonfly topology can lower \NOTE{the extension cost?} of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
+The high-radix, low-diameter dragonfly topology can lower the overall cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
 making it a very promising choice for building supercomputers with millions of cores.

### 2016-04-06 related_work.tex
pass on related work

@@
 
-The impact of job placement to both system and application always catches researchers' appetite \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
-Skinner et al.
-identified that network congestion could cause significant performance variability \cite{dskinner}.
-Bhatele et al.
-studied the performance variability of a specific application, p3FD, running on different production systems with torus networks \cite{abhinav-sc13}.
-They noticed that the application performance would keep consistent when it got compact allocation and exclusive network resource.
+The impact of job placement on both systems and applications has been the subject of many studies \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
+We focus on the HPC-centric studies here.
+Skinner et al.\ identified significant performance variability due to network congestion \cite{dskinner} \TODO{what kind of system?}.
+Bhatele et al.\ studied the performance variability of a specific application, p3FD, running on different HPC production systems with torus network topologies \cite{abhinav-sc13}.
+They obtained performance consistency in their application when network resources were allocated compactly and exclusively \TODO{and wide variability otherwise?}.
 Jokanovic et al.
@@
 
-Recently, several researchers have investigated the job placement and routing schemes on dragonfly network.
-Bogdan et al.
-proposed novel solution for mapping tasks of application that conforms to Nearest Neighbor communication pattern on dragonfly network \cite{hoefler-hpdc14}.
+Recently, several researchers have investigated job placement and routing algorithms on dragonfly networks.
+Bogdan et al.\ proposed a novel solution for mapping applications exhibiting nearest neighbor communication patterns \cite{hoefler-hpdc14} \TODO{very brief blurb of what they did or what they found}.
 Jain et al.
@@
 Bhatele et al.
-used simulation to study the performance of synthetic workload under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.
+used \TODO{coarse-grain?} simulation to study the performance of synthetic workloads under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.
+\TODO{mention Misbah's dragonfly work, for which our work is based on}.
 
-Our work different from the previous works in the following ways.
-First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system.
-Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload.
-We found that although random placement coupled with adaptive routing can improve the network performance, the less communication-intensive applications in the workload may suffer performance degradation.
-Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network performance when application is running.
-The traffic and saturated time of router's each link are valuable information for detailed analysis.
+Our work complements the literature in the following ways.
+First, our simulations are driven by real application traces intended to be representative of production-scale application patterns.
+Second, we holistically examine behavior at both the overall system level as well as the application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did.
+Third, with the CODES simulation toolkit and related network models \TODO{cite codes, Misbah's dragonfly work}, we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity.
+We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature.

### 2016-04-06 background.tex
tweak to prog adaptive routing background

--- 2016-04-06 background.tex
@@
 
-\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated \TODO{packet granularity?
-flit granularity?}.
-Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang} \TODO{I thought PA does do re-evaluation?}.
-Progressive adaptive routing is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}.
-The packet will take the non-minimal route only when the congestion is encountered.
+\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to route a packet (non-)minimally is re-evaluated for each packet generated in the source group, as opposed to once for the entire message; the re-evaulation does not occur in intermediate groups~\cite{jiang}.
+Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.
 

### 2016-04-06 study_workload_1.tex
remove TODO in Section 4

@@
 
-\TODO{Add in a few words across the section (not here) on how previous work compares as you go through the results.}
+%\TODO{Add in a few words across the section (not here) on how previous work compares as you go through the results.}
 
@@
 The resulting traffic through the most utilized local and global channels are greatly reduced, 
-as shown in Figures~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. \TODO{Traffic is not substantially reduced for local channel traffic}.
+as shown in Figures~\ref{fig:global-channel-traffic} and~\ref{fig:local-channel-traffic}. 
+%\TODO{Traffic is not substantially reduced for local channel traffic}.
 Similarly, the corresponding saturation time on local and global channels is also reduced significantly, 
-demonstrating the efficacy of adaptive routing in this case. \TODO{How do we explain the similar distribution of traffic on local channels compared to the dissimilar distribution of saturation time?}
+demonstrating the efficacy of adaptive routing in this case. 
+%\TODO{How do we explain the similar distribution of traffic on local channels compared to the dissimilar distribution of saturation time?}
 For contiguous placement, we see no perceptible difference in behavior between adaptive and progressive adaptive routing.
@@
 At the same time, there is still significant congestion on local channels due to the lack of ability of packets to traverse non-minimal routes, falling into the same trap as the contiguous-minimal configuration.
-\TODO{check this}
+%\TODO{check this}
 %Explain RA, RPA
@@
 largely in agreement with the literature (see Section~\ref{sec:related work}).
-\TODO{did previous work make this strong a claim?}. The high-radix nature of the
+%\TODO{did previous work make this strong a claim? yes, that's the finding in Nik and Abi's SC papers}. 
+The high-radix nature of the
 network topology ensures that the benefits from the resulting load balancing
@@
 This renders the ``bully'' behavior moot, though with the downside of significant performance degradation, so such approaches must be carefully considered.
-\TODO{not sure whether to keep this -- we don't really talk about performance consistency in the preceding text. It's a valid observation, though, so it should be somewhere...}
+%\TODO{not sure whether to keep this -- we don't really talk about performance consistency in the preceding text. It's a valid observation, though, so it should be somewhere...}

### 2016-04-06 conclusion.tex

@@
-\section{Conclusion}
+\section{Conclusions and Future Work}
 \label{sec:conclusion}
 
-In this paper, we have conducted extensive study about application's behavior when running on dragonfly network with different job placement and routing configurations.
-We resorted to CODES, a high-fidelity HPC network simulation tool, and used three parallel scientific applications traces collected from production system to analyze the applications' behavior on network level.
-We found that when applications are running concurrently, although random placement can uniformly distribute the workload traffic over the network to reach load balance and hot-spots free for the network, the performance of certain job would be impaired.
-We identify this phenomenon as ``bully" between concurrently running jobs, and the victim always being the less communication-intensive one.
-On the other hand, the contiguous placement tend to cause local congestion, however when coupled with adaptive routing, it can guarantee the performance of ``bullee" application by limiting the network sharing from concurrently running peers.
+In this paper, we have conducted extensive studies on system and application behavior using various job placement and routing configurations on dragonfly network topologies.
+We took a simulation-based approach, utilizing the CODES simulation toolkit and related models for high-fidelity dragonfly simulation, driving the network with three production-representative scientific application traces.
+We found that, under the prevailing recommendation of random process placement and adaptive routing, the network effectively distributes the workload traffic to achieve a balanced load and strong overall performance, at the cost of impairing jobs with less intensive communication patterns.
+We identify this phenomenon as the ``bully" effect.
+On the other hand, contiguous process placement prevents such effects while exacerbating local congestion, though this can be mitigated somewhat through the addition of adaptive routing.
+Finally, we performed initial experimentation using a mock ``hybrid'' contiguous/random job placement policy, showing the effect of specializing allocation strategies on the resulting communication performance.
 
-Due the presence of this ``bully", we propose to use hybrid placement policy for workload running on systems with dragonfly networks.
-In hybrid placement policy, the less intensive applications get contiguous allocations, and the intensive ones get random allocations.
-We believe the findings presented in this paper can illuminate a path to more efficient workload manager for future systems with dragonfly network.
+We believe the findings and methodology presented in this paper can illuminate a path to a more efficient workload manager for future systems with dragonfly networks. \TODO{more future work here?}

### 2016-04-06 hybrid_placement.tex
remove TODO in Section 6

@@
 
-\TODO{Is this reasonable?}
+%\TODO{Is this reasonable? So much better}
 
@@
 
-\TODO{How's this?}
+%\TODO{How's this? Awesome}
 These initial experiments demonstrate some degree of benefit derived from using a hybrid approach, helping to alleviate the ``bully'' effect while retaining the performance of communication-intensive applications.

### 2016-04-06 methodology.tex
edit in Section 3
pass on our random experiment selection process

@@
 
-%Table \ref{tab:apps-detail} summarizes the details of each application.
-It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.
+As a significant portion of our experiments rely on nondeterministic behavior (random application allocation), we ran each configuration a total of 50 times with differing random seeds.
+We then chose a representative execution for presentation based on the median performance of the AMG application trace.
+While there is variation in repeated runs of the following experiments, the resulting trends and observations are representative of the full suite of experimentation.
 

### 2016-04-06 related_work.tex
changes made based on TODO in Related Work, TODOs removed

@@
 
-The impact of job placement on both systems and applications has been the subject of many studies \cite{dskinner} \cite{abhinav-sc13} \cite{jose-ipdps15}.
+The impact of job placement on both systems and applications has been the subject of many studies~\cite{dskinner,abhinav-sc13,jose-ipdps15}.
 We focus on the HPC-centric studies here.
-Skinner et al.\ identified significant performance variability due to network congestion \cite{dskinner} \TODO{what kind of system?}.
+Skinner et al.\ identified significant performance variability due to network contention.~\cite{dskinner}.
+They found that performance variability is inevitable when network sharing among concurrently running applications is allowed on either torus or fat-tree networks.
+%\TODO{what kind of system?}. 
 Bhatele et al.\ studied the performance variability of a specific application, p3FD, running on different HPC production systems with torus network topologies \cite{abhinav-sc13}.
-They obtained performance consistency in their application when network resources were allocated compactly and exclusively \TODO{and wide variability otherwise?}.
+They obtained performance consistency in their application when network resources were allocated compactly and exclusively and wide variability otherwise.
 Jokanovic et al.
-studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing \cite{jose-ipdps15}.
+studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing~\cite{jose-ipdps15}.
 
 Recently, several researchers have investigated job placement and routing algorithms on dragonfly networks.
-Bogdan et al.\ proposed a novel solution for mapping applications exhibiting nearest neighbor communication patterns \cite{hoefler-hpdc14} \TODO{very brief blurb of what they did or what they found}.
+Bogdan et al.\ proposed a novel solution for mapping applications exhibiting nearest neighbor communication patterns~\cite{hoefler-hpdc14}.
+They found that optimizing for throughput and not workload completion time is often misleading and the notion of system balance cited as a dragonfly design parameter is not always directly applicable to all workloads.
+%\TODO{very brief blurb of what they did or what they found}. 
 Jain et al.
-conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network \cite{jain-sc14}.
+conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network~\cite{jain-sc14}.
 Their work is based on an analytical model and synthetic workload.
 Bhatele et al.
-used \TODO{coarse-grain?} simulation to study the performance of synthetic workloads under the different task mapping and routing policies on two-level direct networks \cite{bhatele-sc11}.
-\TODO{mention Misbah's dragonfly work, for which our work is based on}.
+used coarse-grain simulation to study the performance of synthetic workloads under the different task mapping and routing policies on two-level direct networks~\cite{bhatele-sc11}.
+Misbah et al.\ focused on  the modeling of large-scale dragonfly networks with parallel event driven simulation.
+The dragonfly network model for million-node configurations presented in their work strongly scales when going from 1,024 to 65,536 MPI tasks on IBM Blue Gene/P and IBM Blue Gene/Q systems~\cite{codes-dragonfly}.
+The dragonfly network used in this paper is from their work.
+%\TODO{mention Misbah's dragonfly work, for which our work is based on}.
 
@@
 Second, we holistically examine behavior at both the overall system level as well as the application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did.
-Third, with the CODES simulation toolkit and related network models \TODO{cite codes, Misbah's dragonfly work}, we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity.
+Third, with the CODES simulation toolkit and related network models~\cite{codes, codes-dragonfly},
+%\TODO{cite codes, Misbah's dragonfly work}, 
+we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity.
 We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature.

### 2016-04-06 related_work.tex
related work tweaks

@@
 Recently, several researchers have investigated job placement and routing algorithms on dragonfly networks.
-Bogdan et al.\ proposed a novel solution for mapping applications exhibiting nearest neighbor communication patterns~\cite{hoefler-hpdc14}.
-They found that optimizing for throughput and not workload completion time is often misleading and the notion of system balance cited as a dragonfly design parameter is not always directly applicable to all workloads.
+Bogdan et al.\ proposed a communication-matrix-based analytic modeling framework for mapping application workloads onto network topologies~\cite{hoefler-hpdc14}.
+They found that, in the context of dragonfly networks, optimizing for throughput and not workload completion time is often misleading and the notion of system balance cited as a dragonfly design parameter is not always directly applicable to all workloads.
 %\TODO{very brief blurb of what they did or what they found}. 
@@
 used coarse-grain simulation to study the performance of synthetic workloads under the different task mapping and routing policies on two-level direct networks~\cite{bhatele-sc11}.
-Misbah et al.\ focused on  the modeling of large-scale dragonfly networks with parallel event driven simulation.
+Mubarak et al.\ focused on  the modeling of large-scale dragonfly networks with parallel event driven simulation.
 The dragonfly network model for million-node configurations presented in their work strongly scales when going from 1,024 to 65,536 MPI tasks on IBM Blue Gene/P and IBM Blue Gene/Q systems~\cite{codes-dragonfly}.
-The dragonfly network used in this paper is from their work.
+The dragonfly model used in this paper is from their work.
 %\TODO{mention Misbah's dragonfly work, for which our work is based on}.
@@
 We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature.
+However, in a sense, Bogdan et al.'s work suggests these types of behaviors as possibilities deriving from the balance-first design rationale for the dragonfly.

### 2016-04-06 conclusion.tex
add future work in Conclusion

@@
 Finally, we performed initial experimentation using a mock ``hybrid'' contiguous/random job placement policy, showing the effect of specializing allocation strategies on the resulting communication performance.
+We believe the findings and methodology presented in this paper can illuminate a path to a more efficient workload manager for future systems with dragonfly networks.
 
-We believe the findings and methodology presented in this paper can illuminate a path to a more efficient workload manager for future systems with dragonfly networks. \TODO{more future work here?}
+%\TODO{more future work here?}
+In the future, we plan to explore the intelligent job placement and routing configurations for diversified workloads running on the dragonfly network.
+The dragonfly connected system could have dedicated job placement and routing configuration based on the characteristics of its workload.
+We plan to collect workload traces from production system, and experiment with the simulated network of the system to explore the dedicated optimal job placement and routing configuration.
+We envision that effectiveness of such new placement and routing polices can be examined on a configurable dragonfly system.

### 2016-04-06 related_work.tex
teweak a sentence in Related Work

@@
 Skinner et al.\ identified significant performance variability due to network contention.~\cite{dskinner}.
-They found that performance variability is inevitable when network sharing among concurrently running applications is allowed on either torus or fat-tree networks.
+They found that performance variability is inevitable on either torus or fat-tree networks when network sharing among concurrently running applications is allowed.
 %\TODO{what kind of system?}. 

### 2016-04-08 background.tex
tweak Section 2 based on MM and Gail

@@
 The dragonfly is a two-level hierarchical topology, consisting of several groups connected by all-to-all links.
-In each group, there could be $a$ routers connected via all-to-all local channels.
-For each router, there could be $p$ compute nodes attached to it via terminal links.
+In each group, there can be $a$ routers connected via all-to-all local channels.
+For each router, there can be $p$ compute nodes attached to it via terminal links.
 The router has $h$ global channels used as intergroup connections through which it connected to other routers in different groups.
@@
 
-The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router.
+The routing policy refers to the strategy adopted to route  packets from the source router to the destination router.
 Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
@@
 
-\textbf{Minimal:} In this policy, a message takes the minimal (shortest) path from the source router to the destination router.
-When there are multiple minimal paths between the source and destination, the message will be evenly divided among the paths.
-Minimal routing can guarantee the minimum hops the message takes from the source to the destination.
-However, it may result in congestion along the minimal paths.
+\textbf{Minimal:} In this policy, a packet takes the minimal (shortest) path from the source to the destination.
+The packet first route locally from the source node to the global channel leading to the destination group.
+It traverses the global channel to the destination group and routes locally to the destination node.
+Minimal routing can guarantee the minimum hops a packet takes from the source to the destination. However, it usually results in congestion along the minimal paths.
 
-\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths.
+\textbf{Adaptive:} In this policy, the path a packet takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths.
 For the non-minimal path, an intermediate router in a separate group will be randomly chosen.
-The message takes the intermediate router as a via point, connecting the source and destination router through two separate minimal paths.
+The packet takes the intermediate router as a via point, connecting the source and destination router through two separate minimal paths.
 Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.
 
-\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to route a packet (non-)minimally is re-evaluated for each packet generated in the source group, as opposed to once for the entire message; the re-evaulation does not occur in intermediate groups~\cite{jiang}.
+\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to route a packet minimally is re-evaluated until a non-minimal route is chosen for the packet or as long as the packet is in its source group; the re-evaulation does not occur in intermediate groups~\cite{jiang}.
 Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.
@@
 Random placement can distribute the tasks of an application uniformly across the network to avoid the possible local congestion.
-However, random placement may cause congestion on global links.
 

### 2016-04-08 methodology.tex
metion CODES validation against booksim in section 3.1, add cite for booksim
tweak methodology section based on Gail

@@
 It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI tracer~\cite{sst}.
+The behavior and performance of CODES dragonfly network model has been validated by Mishab et al.\ \cite{codes-dragonfly} against booksim, a serial cycle-accurate interconnection network simulator~\cite{booksim-simulator}.
 
@@
 sAMG, a synthetic version of AMG, is generated by increasing the data transferred in AMG's MPI calls by a factor of 100, making it the most communication-intensive job in the workload.
-We do this for reasons that will become clear in the following sections.
+We add sAMG for reasons that will become clear in the following sections.
 

### 2016-04-08 conclusion.tex
tweak in Conclustion and Related work

@@
 The dragonfly connected system could have dedicated job placement and routing configuration based on the characteristics of its workload.
-We plan to collect workload traces from production system, and experiment with the simulated network of the system to explore the dedicated optimal job placement and routing configuration.
-We envision that effectiveness of such new placement and routing polices can be examined on a configurable dragonfly system.
+We plan to collect workload traces from a production HPC system, and experiment with the simulated network of the system to explore the dedicated optimal job placement and routing configuration.
+We envision that effectiveness of such new placement and routing polices can be examined in future on a configurable dragonfly system.

### 2016-04-08 methodology.tex
tweak section Methodology based on MM

--- 2016-04-06 methodology.tex
@@
 
-We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{codes}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community.
-CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with flit-level high-fidelity simulation.
-It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI tracer~\cite{sst}.
+We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{misbah-tpds}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community.
+CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
+It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI trace library available as part of the SST macro toolkit~\cite{sst}.
+The behavior and performance of CODES dragonfly network model has been validated by Mubarak et al.\ \cite{codes-dragonfly} against booksim, a serial cycle-accurate interconnection network simulator~\cite{booksim-simulator}.
 
@@
 The router has $h = 4$ global channels used as intergroup connections through which it connected to other routers in different groups.
-The radix of each router is $k = a+h+p-1 = 13$.
+The radix of each router is $k = a+h+p-1 = 15$.
 The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
 %\NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } 
-The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, proportional to the Cray Cascade system~\cite{faanes} 
+The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes} 
 %\NOTE{What are these bandwidths? done!}. 
@@
 \begin{center}
-\caption{The notation for different placement and routing configurations} 
+\caption{Nomenclature for different placement and routing configurations} 
 \label{tab: placement routing configs}
@@
 
-    \item \textbf{Network Traffic:} The traffic refers to the amount of data going through each router.
+    \item \textbf{Network Traffic:} The traffic refers to the amount of data in bytes going through each router.
 We analyze the traffic on each terminal and on the local and global channels of each router.
-The network reaches optimal performance when the traffic is uniformly distributed and no particular router is over-loaded.
+The network reaches optimal performance when the traffic is uniformly distributed and no particular network link is over-loaded.
 
@@
 Note that we do not model computation for each MPI rank due to both the complexities inherent in performance prediction on separate parallel architectures as well as the emphasis on the side of the Design Forward traces on communication behavior rather than compute representation; users are instructed to treat the traces as if they came from one MPI rank-per-node configuration, despite being gathered using a rank-per-core approach.
-We instead allow MPI communications to proceed as quickly as they are able.
+%We instead allow MPI communications to proceed as quickly as they are able. 
 %\TODO{is this a good enough explanation? Anything else we should add?}
@@
 As a significant portion of our experiments rely on nondeterministic behavior (random application allocation), we ran each configuration a total of 50 times with differing random seeds.
-We then chose a representative execution for presentation based on the median performance of the AMG application trace.
+We then chose a representative execution for presentation based on the median performance of each application.
 While there is variation in repeated runs of the following experiments, the resulting trends and observations are representative of the full suite of experimentation.

### 2016-04-08 conclusion.tex
typo check in Conclusion

@@
 
-In this paper, we have conducted extensive studies on system and application behavior using various job placement and routing configurations on dragonfly network topologies.
+In this paper, we have conducted extensive studies on system and application behavior using various job placement and routing configurations on dragonfly network topology.
 We took a simulation-based approach, utilizing the CODES simulation toolkit and related models for high-fidelity dragonfly simulation, driving the network with three production-representative scientific application traces.

### 2016-04-09 draft.tex
change a couple of words in abstract
add SlimFly citation

--- 2016-03-30 draft.tex
@@
 The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
-Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks, since random placement with adaptive routing can uniformly distribute traffic over the network and alleviate congestion.
-However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network when multiple jobs are running concurrently, they can not guarantee the best performance for each single job.
-The performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs.
-We refer this phenomenon as ``bully" between concurrently running jobs.
-We presented a detailed analysis about this ``bully" behavior between jobs at the network level based on a sophisticated, high-fidelity discrete even-driven simulation tool.
-The observations and analysis presented in this work illuminate a path to the adoption of more efficient job placement policy and routing algorithm for HPC systems with dragonfly network.
+Preliminary studies show that random job placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
+However, in this paper, we made the observation that while random job placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
+The performance improvement of communication-intensive applications comes at the expense of performance degradation of less intensive ones. 
+We identify this ``bully" behavior and validate its underneath causes with the help of detailed network simulation and real application traces.
+We investigate a hybrid job placement policy as an alternative for dragonfly connected systems.
+Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive ones.
 

### 2016-04-09 methodology.tex
move the 2nd paragraph in Section3.4 to section3.3
add SlimFly citation

@@
 We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{misbah-tpds}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community.
-CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation.
+CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and Slim Fly~\cite{wolfe-pads-2016} networks with flit-level high-fidelity simulation.
 It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI trace library available as part of the SST macro toolkit~\cite{sst}.
@@
 Note that we do not model computation for each MPI rank due to both the complexities inherent in performance prediction on separate parallel architectures as well as the emphasis on the side of the Design Forward traces on communication behavior rather than compute representation; users are instructed to treat the traces as if they came from one MPI rank-per-node configuration, despite being gathered using a rank-per-core approach.
+We follow the recommended interpretation in our simulations.
 %We instead allow MPI communications to proceed as quickly as they are able. 
@@
 We add sAMG for reasons that will become clear in the following sections.
-
-Each rank of each application is run on a dedicated node, following the recommended interpretation of the traces by the Design Forward team.
 

### 2016-04-09 draft.tex
abstract tweaks

@@
 The performance improvement of communication-intensive applications comes at the expense of performance degradation of less intensive ones. 
-We identify this ``bully" behavior and validate its underneath causes with the help of detailed network simulation and real application traces.
-We investigate a hybrid job placement policy as an alternative for dragonfly connected systems.
+We identify this ``bully" behavior and validate its underlying causes with the help of detailed network simulation and real application traces.
+We investigate a hybrid contiguous-noncontiguous job placement policy as an alternative for dragonfly connected systems.
 Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive ones.

### 2016-04-09 intro.tex
add SlimFly citation
intro trivia

@@
 
-Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}.
+Recent studies suggest that random node allocation for parallel jobs, coupled
+with adaptive routing, can alleviate local congestion, eliminate hot-spots and achieve load-balancing for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. 
 These works explore the possible job placement and routing configurations that could optimize the overall network performance without examining how different configurations impact the progress of individual applications.
@@
 
-We choose three representative HPC applications from the DOE Design Forward Project~\cite{designforward-webpage} to analyze the interference among them.
-Our study is based on simulation with CODES, a high-fidelity, flit-level HPC network simulation toolkit~\cite{codes}.
+We choose three representative HPC applications from the DOE Design Forward Project~\cite{designforward-webpage} and analyze the interference among them.
+Our study is based on simulation with CODES, a high-fidelity, flit-level HPC network simulation toolkit~\cite{misbah-tpds}.
 For each application, we examine its performance with two job placement policies and three routing policies.

### 2016-04-09 draft.tex
remove author list, ack, gov. liscence for double-blind review

--- 2016-04-09 draft.tex
@@
 
-\author{
-
-\IEEEauthorblockN{Xu Yang\IEEEauthorrefmark{1}, John Jenkins\IEEEauthorrefmark{2}, Misbah Mubarak\IEEEauthorrefmark{2}, Robert B. Ross\IEEEauthorrefmark{2}, Zhiling Lan\IEEEauthorrefmark{1}}
-
-\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science,
-Illinois Institute of Technology,
-Chicago, Illinois, USA 60616\\
-\{xyang56\}@hawk.iit.edu, lan@iit.edu}
-
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Mathematics and Computer Science Division, Argonne National Laboratory,
-Argonne, IL, USA 60439\\
-\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}
-}
+%\author{
+%
+%\IEEEauthorblockN{Xu Yang\IEEEauthorrefmark{1}, John Jenkins\IEEEauthorrefmark{2}, Misbah Mubarak\IEEEauthorrefmark{2}, Robert B. Ross\IEEEauthorrefmark{2}, Zhiling Lan\IEEEauthorrefmark{1}}
+%
+%\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science,
+%Illinois Institute of Technology,
+%Chicago, Illinois, USA 60616\\
+%\{xyang56\}@hawk.iit.edu, lan@iit.edu}
+%
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Mathematics and Computer Science Division, Argonne National Laboratory,
+%Argonne, IL, USA 60439\\
+%\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}
+%}
 
@@
 
-The work at Illinois Institute of Technology is supported in part by U.S.
+%The work at Illinois Institute of Technology is supported in part by U.S.
 National Science Foundation grants CNS-1320125 and CCF-1422009.
@@
 Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract DE-AC02-06CH11357.
+
+This work is supported in part by U.S. National Science Foundation and U.S. Department of Energy, Office of Science.
 
@@
 
-\begin{framed}
- The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
+%\begin{framed}
+% The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
 Argonne, a U.S.
@@
 Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
-\end{framed}
+%\end{framed}
 

### 2016-04-09 background.tex

@@
 The dragonfly is a two-level hierarchical topology, consisting of several groups connected by all-to-all links.
-In each group, there can be $a$ routers connected via all-to-all local channels.
-For each router, there can be $p$ compute nodes attached to it via terminal links.
-The router has $h$ global channels used as intergroup connections through which it connected to other routers in different groups.
-Thus, the radix of each router is $k = a+h+p-1$.
+Each group consists of $a$ routers connected via all-to-all local channels.
+For each router, $p$ compute nodes are attached to it via terminal links, while $h$ links are used as global channels for intergroup connections.
+The resulting radix of each router is $k = a+h+p-1$.
 Different computing centers could choose different values for  $a$, $h$, $p$ when deploying their dragonfly network.
@@
 
-It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}.
+It is recommended that for load balancing purposes, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}.
 According to this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $.
@@
 The routing policy refers to the strategy adopted to route  packets from the source router to the destination router.
-Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}.
+Previously studied routing policies for dragonfly networks include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and variations thereof~\cite{won-prog-adaptive}.
 In this work we study three alternative routing policies considered by the community for dragonfly networks.
@@
 \textbf{Minimal:} In this policy, a packet takes the minimal (shortest) path from the source to the destination.
-The packet first route locally from the source node to the global channel leading to the destination group.
+The packet first routes locally from the source node to the global channel leading to the destination group.
 It traverses the global channel to the destination group and routes locally to the destination node.
@@
 
-\textbf{Adaptive:} In this policy, the path a packet takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths.
+\textbf{Adaptive:} In this policy, the path a packet \TODO{packet granularity or message granularity?} takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths.
 For the non-minimal path, an intermediate router in a separate group will be randomly chosen.
-The packet takes the intermediate router as a via point, connecting the source and destination router through two separate minimal paths.
-Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.
+The packet is forwarded to the intermediate router, connecting the source and destination groups through two separate minimal paths.
+Adaptive routing can avoid hot-spots in the presence of congestion and collapses to minimal routing otherwise.
 
-\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to route a packet minimally is re-evaluated until a non-minimal route is chosen for the packet or as long as the packet is in its source group; the re-evaulation does not occur in intermediate groups~\cite{jiang}.
+\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to adaptively route message packets is continually re-evaluated within the source group until a non-minimal route is chosen; the re-evaluation does not occur in intermediate groups~\cite{jiang}.
 Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.
@@
 
-For a parallel application requiring multiple compute nodes, job placement policy refers to the way of assigning the required number of nodes to the application by a system software such as batch scheduler~\cite{xu-cluster14}.
+For a parallel application requiring multiple compute nodes, the job placement policy refers to the way of assigning the required number of nodes to the application by system software such as the batch scheduler~\cite{xu-cluster14}.
 In this work, we study two alternative placement policies considered by the community for dragonfly systems:
 
-\textbf{Random Placement:} In this policy, an application gets the required number of nodes randomly selected from all the available nodes in the system.
-As illustrated in Figure~\ref{fig:dragonfly-overview}, $J1$ gets random allocation in which nodes are attached to different routers in different groups.
+\textbf{Random Placement:} In this policy, an application gets the required number of nodes randomly from the available nodes in the system.
+As illustrated in Figure~\ref{fig:dragonfly-overview}, $J1$ is randomly allocated nodes attached to different routers in different groups.
 Routers may be shared by different applications and more routers are involved in serving each application when random placement is in use.
@@
 
-\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to an application in a consecutive manner.
-The assignment first fills up a group, then crosses group boundaries and starts to fill the next group if necessary.
-As illustrated in Figure~\ref{fig:dragonfly-overview}, $J2$ gets eight nodes by contiguous placement.
-Contiguous placement confines the tasks of an application into the same group and uses minimum number of routers serving each application, which may result in local network congestion and increase the possibility of hot-spots.
+\textbf{Contiguous Placement:} In this policy, the compute nodes are assigned to an application consecutively.
+The assignment first fills up a group, then crosses group boundaries as necessary.
+As illustrated in Figure~\ref{fig:dragonfly-overview}, $J2$ is allocated eight nodes by contiguous placement.
+Contiguous placement confines the tasks of an application into the same group and uses the minimum number of routers to serve each application, which may result in local network congestion and increase the possibility of hot-spots.

### 2016-04-09 methodology.tex

@@
 It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI trace library available as part of the SST macro toolkit~\cite{sst}.
-The behavior and performance of CODES dragonfly network model has been validated by Mubarak et al.\ \cite{codes-dragonfly} against booksim, a serial cycle-accurate interconnection network simulator~\cite{booksim-simulator}.
+The behavior and performance of the CODES dragonfly network model has been validated by Mubarak et al.\ \cite{codes-dragonfly} against BookSim, a serial cycle-accurate interconnection network simulator~\cite{booksim-simulator}.
 
@@
 
-We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-webpage,designforward-traces} Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
+We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-webpage,designforward-traces}.
+Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
 
@@
 In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels.
-For each router, there could be $p = 4$ compute nodes attached to it via terminal links.
-The router has $h = 4$ global channels used as intergroup connections through which it connected to other routers in different groups.
-The radix of each router is $k = a+h+p-1 = 15$.
+For each router, there are $p = 4$ compute nodes attached to it via terminal links.
+Each router also has $h = 4$ global channels used for intergroup connections.
+The radix of each router is hence $k = a+h+p-1 = 15$.
 The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
@@
 
-We analyze both the overall network performance and the performance of every single application.
+We analyze both the overall network performance and the performance of each application.
 Our analysis focuses on the following metrics:

### 2016-04-09 study_workload_1.tex
workload 1 trivia

@@
 Both local and global channels experience significant congestion, as applications span multiple groups.
-Similarly, the saturation time for both local and global channels are also the highest compared with other configurations.
+Similarly, the saturation time for both local and global channels are the highest compared with other configurations.
 %explain CA and CPA
@@
 Both CrystalRouter and MultiGrid, the two most communication-intensive jobs,
-both saw improved distributions of communication performance when moving to a
+saw improved distributions of communication performance when moving to a
 random allocation. Again, this matches what is seen in the literature.

### 2016-04-09 draft.tex
tweak words in Abstract--Lan

@@
 The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
-Preliminary studies show that random job placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
-However, in this paper, we made the observation that while random job placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
+Preliminary studies show that random job placement with adaptive routing should be the rule of thumb to utilize such networks since it can uniformly distribute traffic and alleviate congestion. 
+Nevertheless, in this work we find that while random job placement coupled with adaptive routing is good at load balancing network traffic, it can not guarantee the best performance for every single job.
 The performance improvement of communication-intensive applications comes at the expense of performance degradation of less intensive ones. 
 We identify this ``bully" behavior and validate its underlying causes with the help of detailed network simulation and real application traces.
-We investigate a hybrid contiguous-noncontiguous job placement policy as an alternative for dragonfly connected systems.
-Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive ones.
+We further investigate a hybrid contiguous-noncontiguous job placement policy as an alternative for dragonfly connected systems.
+Initial experimentation shows that this hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive ones.
 

### 2016-04-09 intro.tex
tweak Intro --Lan

@@
 intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}.
-%An ideal job placement policy should not only load balance the network 
-%but also guarantee the performance of every single application by minimizing the inevitable interference on the dragonfly network.
+%In order to explore the full potential of such powerful networks,  
+%intelligent job placement is of paramount importance~\cite{bhatele2015, jain-sc14}.
 
@@
 with adaptive routing, can alleviate local congestion, eliminate hot-spots and achieve load-balancing for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. 
-These works explore the possible job placement and routing configurations that could optimize the overall network performance without examining how different configurations impact the progress of individual applications.
-In this paper, we study the implications of contention for shared network links in the context of multiple HPC applications running on dragonfly systems when different job placement and routing configurations are in use.
+These studies explore the possible job placement and routing configurations that could optimize the overall network performance without examining how different configurations impact the progress of individual applications.
+\emph{In this paper, we study the implications of contention for shared network links in the context of multiple HPC applications running on dragonfly systems when different job placement and routing configurations are in use.}
 Our analyses focus on the overall network performance as well as the performance of concurrently executing applications in the presence of network contention.
@@
 Based on the aforementioned key observations, one would expect that an ideal job placement policy on dragonfly systems would take relative communication intensity into account, and mix contiguous and non-contiguous placement based on application needs.
-To explore this expectation, we investigate a hybrid job placement policy, which assigns random allocations to communication-intensive applications and contiguous allocations to less intensive ones.
+To explore this expectation, we investigate \emph{a hybrid job placement policy}, which assigns random allocations to communication-intensive applications and contiguous allocations to less intensive ones.
 Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive applications, though without eliminating the problem entirely.
-%\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
+
 To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported in the literature so far.
@@
 Section~\ref{sec:background} describes an implementation of the dragonfly network, introduces the placement policies and routing policies.
-Section~\ref{sec: methodology} talks about the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
+Section~\ref{sec: methodology} discusses the use of CODES as a research vehicle and three representative applications from the DOE Design Forward Project.
 Section~\ref{sec:workload-1} presents the observations and analysis of three applications running on a dragonfly network with different placement and routing configurations.

### 2016-04-09 background.tex
replace a reference in Section2.3

@@
 
-For a parallel application requiring multiple compute nodes, the job placement policy refers to the way of assigning the required number of nodes to the application by system software such as the batch scheduler~\cite{xu-cluster14}.
+For a parallel application requiring multiple compute nodes, the job placement policy refers to the way of assigning the required number of nodes to the application by system software such as the batch scheduler~\cite{tsafrir-tpds-2007}.
 In this work, we study two alternative placement policies considered by the community for dragonfly systems:

### 2016-04-09 methodology.tex
tweak in Methodology

@@
 Configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
-Even with access to systems with such networks, job placement and routing policies are part of system configuration, which is impossible for user to make changes at will~\cite{jain-sc14, bhatele-sc11, zhou-ipdps-2015, jokanovic-ipdps-2015}.
-Therefore, we resort to simulation in our work.
-
-%It is difficult to experiment with concurrently running jobs on HPC systems~\cite{zhou-ipdps-2015}\cite{jain-sc14}\cite{bhatele-sc11}\cite{jokanovic-ipdps-2015}.
-One reason is that job placement and routing policies are part of system configuration, which is impossible for user to make changes at will.
-Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results.
-The third reason is that configurable dragonfly networks that allow us to perform the exploration presented in this paper are hard to come by for the time being.
+Even with access to systems with such networks, job placement and routing policies are part of system configuration, which is impossible for users to make changes at will~\cite{jain-sc14, bhatele-sc11, zhou-ipdps-2015, jokanovic-ipdps-2015}.
 Therefore, we resort to simulation in our work.
@@
 
-The parameters for building the dragonfly network studied in our work are informed by the model proposed by Kim et al.~\cite{kim-micro}. 
+The parameters for building the dragonfly network studied in our work are chosen based on the model proposed by Kim et al.~\cite{kim-micro}. 
 In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels.
@@
     \item \textbf{Communication Time:} The communication time of each MPI rank refers to the time it spends in completing all its message exchanges with other ranks.
-Due to our use of simulation, we are able to measure the absolute (simulated) time a message takes to reach its destination.
+Due to the use of simulation, we are able to measure the absolute (simulated) time a message takes to reach its destination.
 The performance of each application is measured by the communication time distribution across all its ranks.
@@
 \begin{center}
-\caption{Application Summaries}
+\caption{Summary of Applications}
 \label{tab:apps-detail}

### 2016-04-09 background.tex
remove TODO in Section2.2

@@
 
-\textbf{Adaptive:} In this policy, the path a packet \TODO{packet granularity or message granularity?} takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths.
+\textbf{Adaptive:} In this policy, the path a packet takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths.
 For the non-minimal path, an intermediate router in a separate group will be randomly chosen.
@@
 Adaptive routing can avoid hot-spots in the presence of congestion and collapses to minimal routing otherwise.
+%\NOTE{The Universal Globally-Adaptive Load-balanced routing (Adaptive in our paper) chooses between minimal and non-minimal on a packet by packet basis depending on the state of the network to minimize the delay of the packet~\cite{jiang}.}
 

### 2016-04-09 study_workload_1.tex
tweak in Section 4

@@
 First, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations.
-Second, we isolate each application from the workload and analyze its performance on both a per-rank basis as well as by considering router traffic resident to application ranks.
+Second, we isolate each application from the workload and analyze its performance both on a per-rank basis as well as by considering router traffic resident to application ranks.
 The analysis allows us to identify the ``bully'' in Workload~\Rmnum{1}.
@@
 %Explain RM
-In most cases for this study, the random placement policy behaves similarly across routing policies.
+In most cases, the random placement policy behaves similarly across routing policies.
 Random placement uniformly distributes MPI ranks over the network, 
@@
 However, saturation times are different, resulting from the aforementioned network behavior.
-Particularly, contiguous allocations coupled with minimal routing results in a ``long-tail`` distribution of saturation time.
+Particularly, contiguous allocations coupled with minimal routing results in a ``long-tail" distribution of saturation time.
 
@@
 while using adaptive routing results in significant performance regressions. As
-this is a counterintuitive result not reached by other works, we investigate
+this is a counterintuitive result not discussed in other works, we investigate
 further.
@@
 The system behavior with respect to the CrystalRouter application arguably best
-matches expectations. Use of contiguous allocations result in a subset of
+matches expectations. Use of contiguous allocations results in a subset of
 channels with a significant traffic load while a significant portion are
-unused. Use of random allocations result in a comparatively smoother traffic
+unused. Use of random allocations results in a comparatively smoother traffic
 distribution, with some variation on the margins due to the randomness.

### 2016-04-09 study_workload_2.tex
remove TODO in Section 5
tweak in Section 5

@@
 Figure~\ref{fig:wkld-network-traffic-stime} in Workload~\Rmnum{1}. Replacing
-AMG with sAMg results in greater aggregate traffic as well as more saturation
+AMG with sAMG results in greater aggregate traffic as well as more saturation
 than in Workload~\Rmnum{1}, but regardless, similar patterns can be observed.
-Contiguous placement with minimal routing results in load imbalances with
+Contiguous placement with minimal routing results in load imbalance with
 respect to both traffic and saturation. The addition of adaptive routing
@@
 With random placement and (progressive) adaptive routing, 
-MultiGrid and CrystalRouter experience prolonged communication time, 
+both MultiGrid and CrystalRouter experience prolonged communication time, 
 as shown in Figure~\ref{fig:syn-mg-commtime}, \ref{fig:syn-cr-commtime}. 
@@
 in a similar manner to CrystalRouter in Workload~\Rmnum{1}.
-Contiguous placement coupled with minimal routing, while preventing the bully
+Contiguous placement coupled with minimal routing, while preventing the ``bully"
 behavior, results in poor performance for all of the applications except CrystalRouter,
-which we also expect is due to a higher degree of network isolation.
+which we expect is due to a higher degree of network isolation.
 
@@
 
-MultiGrid in Workload~\Rmnum{2} appears most similar to AMG in Workload~\Rmnum{1} when considering resident channel behavior, as shown in Figures~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
+MultiGrid in Workload~\Rmnum{2} is similar to AMG in Workload~\Rmnum{1} when considering resident channel behavior, as shown in Figures~\ref{fig:syn-mg-lc-traffic} and \ref{fig:syn-mg-gc-traffic}.
 There is a large gap in traffic volume between the contiguous and random placement approaches, due to other applications (sAMG in particular) utilizing the same links.
 CrystalRouter in Workload~\Rmnum{2} additionally experiences more load on its channels using random allocation configurations, as shown in Figure~\ref{fig:syn-cr-lc-traffic} and \ref{fig:syn-cr-lc-traffic}.
-However, the maximal load under random allocation is closer to that seen in contiguous allocations as compared to MultiGrid.
+However, the maximal load under random allocation is closer to that observed in contiguous allocations as compared to MultiGrid.
 
@@
 
-\subsection{Observations}
+\subsection{Key Observations}
 
-\NOTE{rewrote this somewhat. The observations made were essentially the same
-as the previous section}
+%\NOTE{rewrote this somewhat. The observations made were essentially the same as the previous section}
 
@@
 find that those observations are held under this separate configuration.
-System-level performance is still much improved in terms of load-balancing.
-sAMG, being far and away the most communication-intensive application, benefits
+%System-level performance is still much improved in terms of load-balancing.
+System-level performance is still much improved in terms of load-balancing with random placement.
+sAMG, being far and away the most communication-intensive application in Workload~\Rmnum{2}, benefits
 greatly from random placement, whereas in Workload~\Rmnum{1} AMG was effectively
@@
 Interestingly, in both Workload~\Rmnum{1} and \Rmnum{2}, MultiGrid experiences
-a more subtle performance behavior than the significant swings in performance
-seen in the other applications. These behaviors persisted across multiple runs
+a more subtle performance variatioin than the significant swings in performance
+observed in the other applications. These behaviors persisted across multiple runs
 with different random seeds. Additionally, CrystalRouter in Workload~\Rmnum{2}
-sees less drastic changes in maximal load, but still experiences performance
+exhibits less drastic changes in maximal load, but still experiences performance
 regressions. We are continuing to work towards understanding the root causes
 and implications of this behavior, for which we expect application-specific
-communication patterns to be an important factor. \TODO{Is this a reasonable
-observation?}
+communication patterns to be an important factor. 
+%\TODO{Is this a reasonable observation? Yes, it is.}

### 2016-04-09 hybrid_placement.tex
tweak in Section 6

@@
 
-Based on our experiments with Workloads~\Rmnum{1} and \Rmnum{2}, the ``bullying" behavior is
+Based on our experiments with Workloads~\Rmnum{1} and \Rmnum{2}, the ``bully" behavior is
 exhibited when the dragonfly network is configured with random placement and
-(progressive) adaptive routing, and there is a large relative gap between the
+(progressive) adaptive routing, and there is a large gap between the
 communication intensity of applications running on the network.
 As shown through our experimentation, contiguous placement policies give up too
-much in terms of congestion and load balance, and hence are an impractical
-solution. Further, running each job with a dedicated routing policy is unrealistic, 
+much in terms of congestion and load balance, hence being an impractical solution. 
+Further, running each job with a dedicated routing policy is unrealistic, 
 since routing policy is part of system configuration which can not be changed
-on the fly upon job submission and the policies of some jobs (adaptive)
-will still interfere with others.
+on the fly upon job submission. 
+%and the policies of some jobs (adaptive) will still interfere with others.
 
-%Assigning preferable allocation to each job based on its communication intensity is applicable for the batch scheduler with intelligent job placement policy.
-
-%\TODO{Is this reasonable? So much better}
-
-As a natural extension of our observations, one question that arises is whether
-we can combine aspects from both random and contiguous allocation policies in
+As a natural extension of our observations, one question that arises is \emph{whether
+we can combine the merits of random and contiguous placement policies in
 which each application receives the performance benefits from system load
-balancing while avoiding the ``bully'' behavior. As an initial exploration of
-that question, we set up a mock hybrid job placement policy, in which less
+balancing while avoiding the ``bully'' behavior.} As an initial exploration of
+the question, we set up a mock hybrid job placement policy, in which less
 communication-intensive jobs receive contiguous allocations to avoid the
@@
 However, the behavior is still not ideal in this case -- AMG's communications still experience performance degradation versus the contiguous configurations.
-Hence, more work in this area is needed to fully understand the intricate relationships between job scheduling and system/application communication behavior to approach optimal network utilization and application performance in high-radix networks.
+Hence, more work in this area is needed to fully understand the intricate relationships between job scheduling and system/application communication behavior to achieve optimal network utilization and application performance in high-radix networks.

### 2016-04-09 related_work.tex
tweak in Conclustion and Related work
tweak in Related Work

@@
 
-The impact of job placement on both systems and applications has been the subject of many studies~\cite{dskinner,abhinav-sc13,jose-ipdps15}.
+The impact of job placement on system behavior and application performance has been the subject of many studies.
+%~\cite{dskinner,abhinav-sc13,jose-ipdps15}. 
 We focus on the HPC-centric studies here.
@@
 
-Our work complements the literature in the following ways.
+Our work complements the literature in the following aspects.
 First, our simulations are driven by real application traces intended to be representative of production-scale application patterns.
-Second, we holistically examine behavior at both the overall system level as well as the application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did.
+Second, we holistically examine network behavior at both the overall system level as well as the individual application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did.
 Third, with the CODES simulation toolkit and related network models~\cite{codes, codes-dragonfly},
@@
 we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity.
-We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature.
+We believe these differences allowed us to uncover the ``bully'' behavior, which to our knowledge is unreported in the literature.
 However, in a sense, Bogdan et al.'s work suggests these types of behaviors as possibilities deriving from the balance-first design rationale for the dragonfly.

### 2016-04-09 conclusion.tex
wording
tweak in Conclusion

@@
 
-In this paper, we have conducted extensive studies on system and application behavior using various job placement and routing configurations on dragonfly network topology.
+In this paper, we have conducted extensive studies of system and application behavior using various job placement and routing configurations on a dragonfly network.
 We took a simulation-based approach, utilizing the CODES simulation toolkit and related models for high-fidelity dragonfly simulation, driving the network with three production-representative scientific application traces.
-We found that, under the prevailing recommendation of random process placement and adaptive routing, the network effectively distributes the workload traffic to achieve a balanced load and strong overall performance, at the cost of impairing jobs with less intensive communication patterns.
-We identify this phenomenon as the ``bully" effect.
-On the other hand, contiguous process placement prevents such effects while exacerbating local congestion, though this can be mitigated somewhat through the addition of adaptive routing.
-Finally, we performed initial experimentation using a mock ``hybrid'' contiguous/random job placement policy, showing the effect of specializing allocation strategies on the resulting communication performance.
-We believe the findings and methodology presented in this paper can illuminate a path to a more efficient workload manager for future systems with dragonfly networks.
+We found that, under the prevailing recommendation of random process placement and adaptive routing,
+%the network effectively distributes the workload traffic to achieve a balanced load and strong overall performance, 
+network traffic can be well distributed to achieve a balanced load and strong overall performance, 
+at the cost of impairing jobs with less intensive communication patterns.
+We denoted this as the ``bully" effect.
+On the other hand, contiguous process placement prevents such effects while exacerbating local congestion, though this can be mitigated through the addition of adaptive routing.
+Finally, we performed initial experimentation exploring a mock ``hybrid'' contiguous/random job placement policy. 
+Our preliminary study demonstrates the need of specialized job placement strategy based on application communication characteristics. 
+We believe the findings and methodology presented in this paper provide valuable insights for efficient workload management on dragonfly networks, hence being valuable to the broad HPC community.
 
 %\TODO{more future work here?}
-In the future, we plan to explore the intelligent job placement and routing configurations for diversified workloads running on the dragonfly network.
+In the future, we plan to explore intelligent job placement and routing configurations for diversified workloads running on the dragonfly network.
 The dragonfly connected system could have dedicated job placement and routing configuration based on the characteristics of its workload.

### 2016-04-09 draft.tex
blank author list and funding infor in Ack

@@
 % http://www.ctan.org/pkg/subfig
+
+%*******to add TODO and NOTE***********
 \usepackage{verbatim}
@@
 \newcommand{\changed}[1]{\textcolor{red}{#1}}
+%*******to blank author for blind review*********
+\sethlcolor{black}
+\makeatletter
+\newif\if@blind
+\@blindtrue %use \@blindfalse on final version
+\if@blind \sethlcolor{black}\else
+   \let\hl\relax
+\fi
 
@@
 
-%\author{
-%
-%\IEEEauthorblockN{Xu Yang\IEEEauthorrefmark{1}, John Jenkins\IEEEauthorrefmark{2}, Misbah Mubarak\IEEEauthorrefmark{2}, Robert B. Ross\IEEEauthorrefmark{2}, Zhiling Lan\IEEEauthorrefmark{1}}
-%
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science,
-%Illinois Institute of Technology,
-%Chicago, Illinois, USA 60616\\
-%\{xyang56\}@hawk.iit.edu, lan@iit.edu}
-%
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Mathematics and Computer Science Division, Argonne National Laboratory,
-%Argonne, IL, USA 60439\\
-%\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}
-%}
+\author{
+
+\IEEEauthorblockN{\hl{Xu Yang}\IEEEauthorrefmark{1}, \hl{John Jenkins}\IEEEauthorrefmark{2}, \hl{Misbah Mubarak}\IEEEauthorrefmark{2}, \hl{Robert B.
+Ross}\IEEEauthorrefmark{2}, \hl{Zhiling Lan}\IEEEauthorrefmark{1}}
+
+\IEEEauthorblockA{\IEEEauthorrefmark{1}\hl{Department of Computer Science,
+Illinois Institute of Technology,
+Chicago, Illinois, USA 60616}\\
+\hl{\{xyang56\}@hawk.iit.edu, lan@iit.edu}}
+
+\IEEEauthorblockA{\IEEEauthorrefmark{2}\hl{Mathematics and Computer Science Division, Argonne National Laboratory,
+Argonne, IL, USA 60439}\\
+\hl{\{jenkins,rross\}@mcs.anl.gov, mmubarak@anl.gov}}
+
+}
 
@@
 
-%The work at Illinois Institute of Technology is supported in part by U.S.
-National Science Foundation grants CNS-1320125 and CCF-1422009.
+The work at \hl{Illinois Institute of Technology} is supported in part by U.S.
+National Science Foundation grants \hl{CNS-1320125 and CCF-1422009}.
 This work is also supported by the U.S.
-Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract DE-AC02-06CH11357.
+Department of Energy, Office of Science, Advanced Scientific Computing Research, under Contract \hl{DE-AC02-06CH11357.}
 
-This work is supported in part by U.S. National Science Foundation and U.S. Department of Energy, Office of Science.
+%This work is supported in part by U.S. National Science Foundation and U.S. Department of Energy, Office of Science.
 
@@
 
-%\begin{framed}
-% The submitted manuscript has been created by UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
+\begin{framed}
+The submitted manuscript has been created by \hl{ UChicago Argonne, LLC, Operator of Argonne National Laboratory ("Argonne").
 Argonne, a U.S.
@@
 DE-AC02-06CH11357.
-The U.S.
+} The U.S.
 Government retains for itself, and others acting on its behalf, a paid-up nonexclusive, irrevocable worldwide license in said article to reproduce, prepare derivative works, distribute copies to the public, and perform publicly and display publicly, by or on behalf of the Government.
-%\end{framed}
+\end{framed}
 

### 2016-04-11 background.tex
trivial tweak

@@
 
-\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to adaptively route message packets is continually re-evaluated within the source group until a non-minimal route is chosen; the re-evaluation does not occur in intermediate groups~\cite{jiang}.
+\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to adaptively route a packet is continually re-evaluated within the source group until a non-minimal route is chosen; the re-evaluation does not occur in intermediate groups~\cite{jiang}.
 Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.

### 2016-04-11 study_workload_1.tex
trivial tweak

@@
 First, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations.
-Second, we isolate each application from the workload and analyze its performance both on a per-rank basis as well as by considering router traffic resident to application ranks.
+Second, we isolate each application from the workload and analyze its performance on both a per-rank basis as well as by considering router traffic resident to application ranks.
 The analysis allows us to identify the ``bully'' in Workload~\Rmnum{1}.

### 2016-04-11 methodology.tex
trivial tweak

@@
 %\NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } 
-The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes} 
+The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes}.  
 %\NOTE{What are these bandwidths? done!}. 
@@
 We analyze the saturation time of ports corresponding to terminal links, local and global channels.
-The saturated time indicates the congestion level of routers.
+The saturation time indicates the congestion level of routers.
 

### 2016-06-21 hybrid_placement.tex
remove blank out for doule-blind review, tweak Fig8 size

@@
         \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
+        \includegraphics[height=1.0 in]{hyb-plcmt/mg/commtime}
         \caption{MultiGrid Communication Time}
@@
         \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
+        \includegraphics[height=1.0 in]{hyb-plcmt/cr/commtime}
         \caption{CrystalRouter Communication Time}
@@
         \centering
-        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
+        \includegraphics[height=1.0 in]{hyb-plcmt/amg/commtime}
         \caption{AMG Communication Time}

### 2016-07-01 intro.tex
trivial tweak
update one reference

@@
 Even with such powerful networks, 
-intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}.
+intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele:ipdps2016, jain-sc14}.
 %In order to explore the full potential of such powerful networks,  
@@
    \item Contiguous placement can be beneficial to the consistent performance of less communication-intensive applications by minimizing network resource sharing, because it reduces the opportunities for traffic from other applications to be loaded on links that serve as minimal routes for the less intensive application.
-However, this comes with the downside of at times greatly reduced system performance via load imbalance.
+However, this comes with the downside of reduced system performance due to load imbalance.
 

### 2016-07-20 related_work.tex
trivial tweak
use last name for cite Bogdan Prisacari HPDC'14 paper

@@
 We focus on the HPC-centric studies here.
-Skinner et al.\ identified significant performance variability due to network contention.~\cite{dskinner}.
+Skinner et al.\ identified significant performance variability due to network contention~\cite{dskinner}.
 They found that performance variability is inevitable on either torus or fat-tree networks when network sharing among concurrently running applications is allowed.
@@
 Recently, several researchers have investigated job placement and routing algorithms on dragonfly networks.
-Bogdan et al.\ proposed a communication-matrix-based analytic modeling framework for mapping application workloads onto network topologies~\cite{hoefler-hpdc14}.
+Prisacari et al.\ proposed a communication-matrix-based analytic modeling framework for mapping application workloads onto network topologies~\cite{hoefler-hpdc14}.
 They found that, in the context of dragonfly networks, optimizing for throughput and not workload completion time is often misleading and the notion of system balance cited as a dragonfly design parameter is not always directly applicable to all workloads.
@@
 First, our simulations are driven by real application traces intended to be representative of production-scale application patterns.
-Second, we holistically examine network behavior at both the overall system level as well as the individual application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did.
+Second, we holistically examine network behavior at both the overall system level as well as the individual application level, though we do not consider communication-pattern specific application mappings as Prisacari et al.\ did.
 Third, with the CODES simulation toolkit and related network models~\cite{codes, codes-dragonfly},
@@
 We believe these differences allowed us to uncover the ``bully'' behavior, which to our knowledge is unreported in the literature.
-However, in a sense, Bogdan et al.'s work suggests these types of behaviors as possibilities deriving from the balance-first design rationale for the dragonfly.
+However, in a sense, Prisacari et al.'s work suggests these types of behaviors as possibilities deriving from the balance-first design rationale for the dragonfly.

### 2016-07-22 hybrid_placement.tex
tweak figures size

--- 2016-04-09 hybrid_placement.tex
@@
 MultiGrid and CrystalRouter exhibit similar performance in both hybrid and random placement, as nodes are being placed randomly in each case.
-While the performance of AMG under hybrid placement, shown in Figure~\ref{fig:hyb-plcmt-amg-commtime}, still appears to exhibit significant communication interference on account of the other applications as opposed to the best contiguous placement policies, the effects are significantly reduced compared to a random-adaptive policy.
+While the performance of AMG under hybrid placement, shown in Figure~\ref{fig:hyb-plcmt-amg-commtime}, still appears to exhibit significant communication interference on account of the other applications as opposed to the best contiguous placement policies, the effects are reduced compared to a random-adaptive policy.
 We believe this to be a result of more AMG-specific traffic occupying a smaller set of routers/groups, both reducing the probability of traffic entering them through adaptive routing and increasing the relative proportion of link utilization by AMG.

### 2016-07-22 study_workload_1.tex
tweak figures size

@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/gc-traffic}
+        \includegraphics[height=1.5 in]{wkld/gc-traffic}
         \caption{Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/lc-traffic}
+        \includegraphics[height=1.5 in]{wkld/lc-traffic}
         \caption{Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/tl-traffic}
+        \includegraphics[height=1.5 in]{wkld/tl-traffic}
         \caption{Terminal Link Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/gc-stime}
+        \includegraphics[height=1.5 in]{wkld/gc-stime}
         \caption{Global Channel Saturation Time}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/lc-stime}
+        \includegraphics[height=1.5 in]{wkld/lc-stime}
         \caption{Local Channel Saturation Time}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/tl-stime}
+        \includegraphics[height=1.5 in]{wkld/tl-stime}
         \caption{Terminal Link Saturation Time}
@@
 different behavior when using random allocation. Random allocation with minimal
-routing results in worse performance than contiguous-adaptive configurations,
+routing results in comparable performance to contiguous-adaptive configurations,
 while using adaptive routing results in significant performance regressions. As
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
+        \includegraphics[height=1.5 in]{wkld/mg/lc-traffic}
         \caption{MultiGrid Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
+        \includegraphics[height=1.5 in]{wkld/cr/lc-traffic}
         \caption{CrystalRouter Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
+        \includegraphics[height=1.5 in]{wkld/amg/lc-traffic}
         \caption{AMG Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
+        \includegraphics[height=1.5 in]{wkld/mg/gc-traffic}
         \caption{MultiGrid Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
+        \includegraphics[height=1.5 in]{wkld/cr/gc-traffic}
         \caption{CrystalRouter Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
+        \includegraphics[height=1.5 in]{wkld/amg/gc-traffic}
         \caption{AMG Global Channel Traffic}

### 2016-07-22 study_workload_2.tex
tweak in Section 6
tweak figures size

@@
 the same sets of experiments through Workload~\Rmnum{2}, which consists of sAMG,
-MultiGrid and CrystalRouter. By replacing AMG with sAMG, we turn the ``bully"
-into the ``bullied".
+MultiGrid and CrystalRouter.
+%\NOTE{By replacing AMG with sAMG, we turn the ``bully" into the ``bullied".} 
+The ``bully" becomes the ``bullied" with the presence of sAMG in Workload~\Rmnum{2}.
 
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/gc-traffic}
         \caption{Global Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/lc-traffic}
         \caption{Local Channel Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
+        \includegraphics[height=1.5 in]{syn-wkld/tl-traffic}
         \caption{Terminal Link Traffic}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
+        \includegraphics[height=1.5 in]{syn-wkld/gc-btime}
         \caption{Global Channel Saturation Time}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
+        \includegraphics[height=1.5 in]{syn-wkld/lc-btime}
         \caption{Local Channel Saturation Time}
@@
         \centering
-        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
+        \includegraphics[height=1.5 in]{syn-wkld/tl-btime}
         \caption{Terminal Link Saturation Time}
@@
 with different random seeds. Additionally, CrystalRouter in Workload~\Rmnum{2}
-exhibits less drastic changes in maximal load, but still experiences performance
+has less drastic changes in maximal load, but still experiences performance
 regressions. We are continuing to work towards understanding the root causes

### 2016-07-22 study_workload_1.tex
add copyright footnote; change shorthand for configurations e.g.CM -->cont-min

@@
     \end{subfigure}%
-    \caption{Aggregate traffic and saturation time for Workload~\Rmnum{1} under the configurations listed in Table~\ref{tab: placement routing configs}. ``CA'' and ``CPA'' have equivalent behavior.}
+    \caption{Aggregate traffic and saturation time for Workload~\Rmnum{1} under the configurations listed in Table~\ref{tab: placement routing configs}. ``adp'' and ``padp'' have equivalent behavior.}
    \label{fig:wkld-network-traffic-stime}
@@
 %explain CM
-When contiguous placement is coupled with minimal routing (CM), 
+When contiguous placement is coupled with minimal routing (cont-min), 
 application traffic is confined within the consecutively allocated groups, 
@@
 %explain CA and CPA
-When contiguous placement is coupled with adaptive (CA) and progressive adaptive (CPA) routing, 
+When contiguous placement is coupled with adaptive (cont-adp) and progressive adaptive (cont-padp) routing, 
 traffic is able to take non-minimal paths via intermediate routers, helping to alleviate congestion along the minimal paths. 
@@
 no router experiences an exceptionally high volume of traffic on its local and global channels. 
-When random placement is coupled with minimal routing (RM), less traffic is generated on account of
+When random placement is coupled with minimal routing (rand-min), less traffic is generated on account of
 the packets avoiding intermediate forwarding.
@@
    \caption{Aggregate workload traffic for routers serving specific applications.
-``CA'' and ``CPA'' have equivalent behavior.
+``adp'' and ``padp'' have equivalent behavior.
 More routers are involved in serving each application when random placement is in use, compared to contiguous placement.}

### 2016-08-05 methodology.tex
tweak figures size
add copyright footnote; change shorthand for configurations e.g.CM -->cont-min
minor tweak for final version

@@
 The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
-%\NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } 
-The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes}.  
+%The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes}.  
 %\NOTE{What are these bandwidths? done!}. 
+The dragonfly link bandwidths are asymmetric, 2Gib/s for the local and terminal router-ports and 4GiB/s for the global ports, indicated by the Cray Cascade system~\cite{faanes}.
 In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.
@@
 \midrule % In-table horizontal line
-Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
+%Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
+Contiguous  &  cont-min   &  cont-adp    &  cont-padp   \\ % Content row 1
 \midrule
-Random  &   RM  &   RA   &  RPA   \\ 
+%Random  &   RM  &   RA   &  RPA   \\ 
+Random  &   rand-min  &   rand-adp   &  rand-padp   \\ 
 \midrule % In-table horizontal line

### 2016-08-05 study_workload_2.tex
minor tweak for final version

@@
     \end{subfigure}%
-   \caption{Aggregate traffic and saturation time for Workload~\Rmnum{2} under the configurations listed in Table~\ref{tab: placement routing configs}.}
+   \caption{Aggregate traffic and saturation time for Workload~\Rmnum{2} under the configurations listed in Table~\ref{tab: placement routing configs}.
+For either contiguous or random placement, ``adp'' and ``padp'' have equivalent behavior.}
    \label{fig:synwkld-network-traffic-stime}
@@
     \caption{Aggregate workload traffic for routers serving specific applications.
-More routers are involved in serving each application when random placement is in use, compared to contiguous placement.}
+More routers are involved in serving each application when random placement is in use, compared to contiguous placement.
+For either contiguous or random placement, ``adp'' and ``padp'' have equivalent behavior.}
    \label{fig:syn-3app-gc-traffic}

### 2016-08-09 study_workload_1.tex
minor tweak for final version
change figs captions by Lan's comments

@@
     \end{subfigure}%
-    \caption{Aggregate traffic and saturation time for Workload~\Rmnum{1} under the configurations listed in Table~\ref{tab: placement routing configs}. ``adp'' and ``padp'' have equivalent behavior.}
+    \caption{Aggregate traffic and saturation time for Workload~\Rmnum{1} under the configurations listed in Table~\ref{tab: placement routing configs}.
+In these plots, "adp" and "padp" exhibit similar behaviors, and their curves are overlapped.}
    \label{fig:wkld-network-traffic-stime}
@@
    \caption{Aggregate workload traffic for routers serving specific applications.
-``adp'' and ``padp'' have equivalent behavior.
-More routers are involved in serving each application when random placement is in use, compared to contiguous placement.}
+More routers are involved in serving each application when random placement is in use, compared to contiguous placement.
+In these plots, "adp" and "padp" exhibit similar behaviors, and their curves are overlapped.}
    \label{fig:3app-lc-gc-traffic}
